### 2021-09-15 latex/robdml.tex
u

% CVPR 2022 Paper Template
% based on the CVPR template provided by Ming-Ming Cheng (https://github.com/MCG-NKU/CVPR_Template)
% modified and extended by Stefan Roth (stefan.roth@NOSPAMtu-darmstadt.de)

\documentclass[10pt,twocolumn,letterpaper]{article}

%%%%%%%%% PAPER TYPE  - PLEASE UPDATE FOR FINAL VERSION
\usepackage[review]{cvpr}      % To produce the REVIEW version
%\usepackage{cvpr}              % To produce the CAMERA-READY version
%\usepackage[pagenumbers]{cvpr} % To force page numbers, e.g. for an arXiv version

% Include other packages here, before hyperref.
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}

% It is strongly recommended to use hyperref, especially for the review version.
% hyperref with option pagebackref eases the reviewers' job.
% Please disable hyperref *only* if you encounter grave issues, e.g. with the
% file validation for the camera-ready version.
%
% If you comment hyperref and then uncomment it, you should delete
% ReviewTempalte.aux before re-running LaTeX.
% (Or just hit 'q' on the first LaTeX run, let it finish, and you
%  should be clear).
\usepackage[pagebackref,breaklinks,colorlinks]{hyperref}

% Support for easy cross-referencing
\usepackage[capitalize]{cleveref}
\crefname{section}{Sec.}{Secs.}
\Crefname{section}{Section}{Sections}
\Crefname{table}{Table}{Tables}
\crefname{table}{Tab.}{Tabs.}

%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\cvprPaperID{201} % *** Enter the CVPR Paper ID here
\def\confName{CVPR}
\def\confYear{2022}

\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{Enhancing Adversarial Robustness for Deep Metric Learning}

\author{Mo Zhou ~~~~~~~ Vishal M. Patel\\
Johns Hopkins University\\
{\tt\small mzhou32@jhu.edu ~~ vpatel36@jhu.edu}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
}
\maketitle

%%%%%%%%% ABSTRACT
\begin{abstract}
   The ABSTRACT is to be in fully justified italicized text, at the top of the left-hand column, below the author and affiliation information.
   Use the word ``Abstract'' as the title, in 12-point Times, boldface type, centered relative to the column, initially capitalized.
   The abstract is to be in 10-point, single-spaced type.
   Leave two blank lines after the Abstract, then begin the main text.
   Look at previous CVPR abstracts to get a feel for style and length.
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}
\label{sec:intro}

Please follow the steps outlined below when submitting your manuscript to the IEEE Computer Society Press.
This style guide now has several important modifications (for example, you are no longer warned against the use of sticky tape to attach your artwork to the paper), so all authors should read this new version.

%-------------------------------------------------------------------------
\subsection{Language}

All manuscripts must be in English.

\subsection{Dual submission}

Please refer to the author guidelines on the \confName\ \confYear\ web page for a
discussion of the policy on dual submissions.

\subsection{Paper length}
Papers, excluding the references section, must be no longer than eight pages in length.
The references section will not be included in the page count, and there is no limit on the length of the references section.
For example, a paper of eight pages with two pages of references would have a total length of 10 pages.
{\bf There will be no extra page charges for \confName\ \confYear.}

Overlength papers will simply not be reviewed.
This includes papers where the margins and formatting are deemed to have been significantly altered from those laid down by this style guide.
Note that this \LaTeX\ guide already sets figure captions and references in a smaller font.
The reason such papers will not be reviewed is that there is no provision for supervised revisions of manuscripts.
The reviewing process cannot determine the suitability of the paper for presentation in eight pages if it is reviewed in eleven.

%-------------------------------------------------------------------------
\subsection{The ruler}
The \LaTeX\ style defines a printed ruler which should be present in the version submitted for review.
The ruler is provided in order that reviewers may comment on particular lines in the paper without circumlocution.
If you are preparing a document using a non-\LaTeX\ document preparation system, please arrange for an equivalent ruler to appear on the final output pages.
The presence or absence of the ruler should not change the appearance of any other content on the page.
The camera-ready copy should not contain a ruler.
(\LaTeX\ users may use options of cvpr.sty to switch between different versions.)

Reviewers:
note that the ruler measurements do not align well with lines in the paper --- this turns out to be very difficult to do well when the paper contains many figures and equations, and, when done, looks ugly.
Just use fractional references (\eg, this line is $087.5$), although in most cases one would expect that the approximate location will be adequate.

\subsection{Paper ID}
Make sure that the Paper ID from the submission system is visible in the version submitted for review (replacing the ``*****'' you see in this document).
If you are using the \LaTeX\ template, \textbf{make sure to update paper ID in the appropriate place in the tex file}.

\subsection{Mathematics}

Please number all of your sections and displayed equations as in these examples:
\begin{equation}
  E = m\cdot c^2
  \label{eq:important}
\end{equation}
and
\begin{equation}
  v = a\cdot t.
  \label{eq:also-important}
\end{equation}
It is important for readers to be able to refer to any particular equation.
Just because you did not refer to it in the text does not mean some future reader might not need to refer to it.
It is cumbersome to have to use circumlocutions like ``the equation second from the top of page 3 column 1''.
(Note that the ruler will not be present in the final copy, so is not an alternative to equation numbers).
All authors will benefit from reading Mermin's description of how to write mathematics:
\url{http://www.pamitc.org/documents/mermin.pdf}.

\subsection{Blind review}

Many authors misunderstand the concept of anonymizing for blind review.
Blind review does not mean that one must remove citations to one's own work---in fact it is often impossible to review a paper unless the previous citations are known and available.

Blind review means that you do not use the words ``my'' or ``our'' when citing previous work.
That is all.
(But see below for tech reports.)

Saying ``this builds on the work of Lucy Smith [1]'' does not say that you are Lucy Smith;
it says that you are building on her work.
If you are Smith and Jones, do not say ``as we show in [7]'', say ``as Smith and Jones show in [7]'' and at the end of the paper, include reference 7 as you would any other cited work.

An example of a bad paper just asking to be rejected:
\begin{quote}
\begin{center}
    An analysis of the frobnicatable foo filter.
\end{center}

   In this paper we present a performance analysis of our previous paper [1], and show it to be inferior to all previously known methods.
   Why the previous paper was accepted without this analysis is beyond me.

   [1] Removed for blind review
\end{quote}

An example of an acceptable paper:
\begin{quote}
\begin{center}
     An analysis of the frobnicatable foo filter.
\end{center}

   In this paper we present a performance analysis of the  paper of Smith \etal [1], and show it to be inferior to all previously known methods.
   Why the previous paper was accepted without this analysis is beyond me.

   [1] Smith, L and Jones, C. ``The frobnicatable foo filter, a fundamental contribution to human knowledge''. Nature 381(12), 1-213.
\end{quote}

If you are making a submission to another conference at the same time, which covers similar or overlapping material, you may need to refer to that submission in order to explain the differences, just as you would if you had previously published related work.
In such cases, include the anonymized parallel submission~\cite{Authors14} as supplemental material and cite it as
\begin{quote}
[1] Authors. ``The frobnicatable foo filter'', F\&G 2014 Submission ID 324, Supplied as supplemental material {\tt fg324.pdf}.
\end{quote}

Finally, you may feel you need to tell the reader that more details can be found elsewhere, and refer them to a technical report.
For conference submissions, the paper must stand on its own, and not {\em require} the reviewer to go to a tech report for further details.
Thus, you may say in the body of the paper ``further details may be found in~\cite{Authors14b}''.
Then submit the tech report as supplemental material.
Again, you may not assume the reviewers will read this material.

Sometimes your paper is about a problem which you tested using a tool that is widely known to be restricted to a single institution.
For example, let's say it's 1969, you have solved a key problem on the Apollo lander, and you believe that the CVPR70 audience would like to hear about your
solution.
The work is a development of your celebrated 1968 paper entitled ``Zero-g frobnication: How being the only people in the world with access to the Apollo lander source code makes us a wow at parties'', by Zeus \etal.

You can handle this paper like any other.
Do not write ``We show how to improve our previous work [Anonymous, 1968].
This time we tested the algorithm on a lunar lander [name of lander removed for blind review]''.
That would be silly, and would immediately identify the authors.
Instead write the following:
\begin{quotation}
\noindent
   We describe a system for zero-g frobnication.
   This system is new because it handles the following cases:
   A, B.  Previous systems [Zeus et al. 1968] did not  handle case B properly.
   Ours handles it by including a foo term in the bar integral.

   ...

   The proposed system was integrated with the Apollo lunar lander, and went all the way to the moon, don't you know.
   It displayed the following behaviours, which show how well we solved cases A and B: ...
\end{quotation}
As you can see, the above text follows standard scientific convention, reads better than the first version, and does not explicitly name you as the authors.
A reviewer might think it likely that the new paper was written by Zeus \etal, but cannot make any decision based on that guess.
He or she would have to be sure that no other authors could have been contracted to solve problem B.
\medskip

\noindent
FAQ\medskip\\
{\bf Q:} Are acknowledgements OK?\\
{\bf A:} No.  Leave them for the final copy.\medskip\\
{\bf Q:} How do I cite my results reported in open challenges?
{\bf A:} To conform with the double-blind review policy, you can report results of other challenge participants together with your results in your paper.
For your results, however, you should not identify yourself and should not mention your participation in the challenge.
Instead present your results referring to the method proposed in your paper and draw conclusions based on the experimental comparison to other results.\medskip\\

\begin{figure}[t]
  \centering
  \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
   %\includegraphics[width=0.8\linewidth]{egfigure.eps}

   \caption{Example of caption.
   It is set in Roman so that mathematics (always set in Roman: $B \sin A = A \sin B$) may be included without an ugly clash.}
   \label{fig:onecol}
\end{figure}

\subsection{Miscellaneous}

\noindent
Compare the following:\\
\begin{tabular}{ll}
 \verb'$conf_a$' &  $conf_a$ \\
 \verb'$\mathit{conf}_a$' & $\mathit{conf}_a$
\end{tabular}\\
See The \TeX book, p165.

The space after \eg, meaning ``for example'', should not be a sentence-ending space.
So \eg is correct, {\em e.g.} is not.
The provided \verb'\eg' macro takes care of this.

When citing a multi-author paper, you may save space by using ``et alia'', shortened to ``\etal'' (not ``{\em et.\ al.}'' as ``{\em et}'' is a complete word).
If you use the \verb'\etal' macro provided, then you need not worry about double periods when used at the end of a sentence as in Alpher \etal.
However, use it only when there are three or more authors.
Thus, the following is correct:
   ``Frobnication has been trendy lately.
   It was introduced by Alpher~\cite{Alpher02}, and subsequently developed by
   Alpher and Fotheringham-Smythe~\cite{Alpher03}, and Alpher \etal~\cite{Alpher04}.''

This is incorrect: ``... subsequently developed by Alpher \etal~\cite{Alpher03} ...'' because reference~\cite{Alpher03} has just two authors.

% Update the cvpr.cls to do the following automatically.
% For this citation style, keep multiple citations in numerical (not
% chronological) order, so prefer \cite{Alpher03,Alpher02,Authors14} to
% \cite{Alpher02,Alpher03,Authors14}.

\begin{figure*}
  \centering
  \begin{subfigure}{0.68\linewidth}
    \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
    \caption{An example of a subfigure.}
    \label{fig:short-a}
  \end{subfigure}
  \hfill
  \begin{subfigure}{0.28\linewidth}
    \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
    \caption{Another example of a subfigure.}
    \label{fig:short-b}
  \end{subfigure}
  \caption{Example of a short caption, which should be centered.}
  \label{fig:short}
\end{figure*}

%------------------------------------------------------------------------
\section{Formatting your paper}
\label{sec:formatting}

All text must be in a two-column format.
The total allowable size of the text area is $6\frac78$ inches (17.46 cm) wide by $8\frac78$ inches (22.54 cm) high.
Columns are to be $3\frac14$ inches (8.25 cm) wide, with a $\frac{5}{16}$ inch (0.8 cm) space between them.
The main title (on the first page) should begin 1 inch (2.54 cm) from the top edge of the page.
The second and following pages should begin 1 inch (2.54 cm) from the top edge.
On all pages, the bottom margin should be $1\frac{1}{8}$ inches (2.86 cm) from the bottom edge of the page for $8.5 \times 11$-inch paper;
for A4 paper, approximately $1\frac{5}{8}$ inches (4.13 cm) from the bottom edge of the
page.

%-------------------------------------------------------------------------
\subsection{Margins and page numbering}

All printed material, including text, illustrations, and charts, must be kept
within a print area $6\frac{7}{8}$ inches (17.46 cm) wide by $8\frac{7}{8}$ inches (22.54 cm)
high.
%
Page numbers should be in the footer, centered and $\frac{3}{4}$ inches from the bottom of the page.
The review version should have page numbers, yet the final version submitted as camera ready should not show any page numbers.
The \LaTeX\ template takes care of this when used properly.

%-------------------------------------------------------------------------
\subsection{Type style and fonts}

Wherever Times is specified, Times Roman may also be used.
If neither is available on your word processor, please use the font closest in
appearance to Times to which you have access.

MAIN TITLE.
Center the title $1\frac{3}{8}$ inches (3.49 cm) from the top edge of the first page.
The title should be in Times 14-point, boldface type.
Capitalize the first letter of nouns, pronouns, verbs, adjectives, and adverbs;
do not capitalize articles, coordinate conjunctions, or prepositions (unless the title begins with such a word).
Leave two blank lines after the title.

AUTHOR NAME(s) and AFFILIATION(s) are to be centered beneath the title
and printed in Times 12-point, non-boldface type.
This information is to be followed by two blank lines.

The ABSTRACT and MAIN TEXT are to be in a two-column format.

MAIN TEXT.
Type main text in 10-point Times, single-spaced.
Do NOT use double-spacing.
All paragraphs should be indented 1 pica (approx.~$\frac{1}{6}$ inch or 0.422 cm).
Make sure your text is fully justified---that is, flush left and flush right.
Please do not place any additional blank lines between paragraphs.

Figure and table captions should be 9-point Roman type as in \cref{fig:onecol,fig:short}.
Short captions should be centred.

\noindent Callouts should be 9-point Helvetica, non-boldface type.
Initially capitalize only the first word of section titles and first-, second-, and third-order headings.

FIRST-ORDER HEADINGS.
(For example, {\large \bf 1. Introduction}) should be Times 12-point boldface, initially capitalized, flush left, with one blank line before, and one blank line after.

SECOND-ORDER HEADINGS.
(For example, { \bf 1.1. Database elements}) should be Times 11-point boldface, initially capitalized, flush left, with one blank line before, and one after.
If you require a third-order heading (we discourage it), use 10-point Times, boldface, initially capitalized, flush left, preceded by one blank line, followed by a period and your text on the same line.

%-------------------------------------------------------------------------
\subsection{Footnotes}

Please use footnotes\footnote{This is what a footnote looks like.
It often distracts the reader from the main flow of the argument.} sparingly.
Indeed, try to avoid footnotes altogether and include necessary peripheral observations in the text (within parentheses, if you prefer, as in this sentence).
If you wish to use a footnote, place it at the bottom of the column on the page on which it is referenced.
Use Times 8-point type, single-spaced.

%-------------------------------------------------------------------------
\subsection{Cross-references}

For the benefit of author(s) and readers, please use the
{\small\begin{verbatim}
  \cref{...}
\end{verbatim}}  command for cross-referencing to figures, tables, equations, or sections.
This will automatically insert the appropriate label alongside the cross-reference as in this example:
\begin{quotation}
  To see how our method outperforms previous work, please see \cref{fig:onecol} and \cref{tab:example}.
  It is also possible to refer to multiple targets as once, \eg~to \cref{fig:onecol,fig:short-a}.
  You may also return to \cref{sec:formatting} or look at \cref{eq:also-important}.
\end{quotation}
If you do not wish to abbreviate the label, for example at the beginning of the sentence, you can use the
{\small\begin{verbatim}
  \Cref{...}
\end{verbatim}}
command. Here is an example:
\begin{quotation}
  \Cref{fig:onecol} is also quite important.
\end{quotation}

%-------------------------------------------------------------------------
\subsection{References}

List and number all bibliographical references in 9-point Times, single-spaced, at the end of your paper.
When referenced in the text, enclose the citation number in square brackets, for
example~\cite{Authors14}.
Where appropriate, include page numbers and the name(s) of editors of referenced books.
When you cite multiple papers at once, please make sure that you cite them in numerical order like this \cite{Alpher02,Alpher03,Alpher05,Authors14b,Authors14}.
If you use the template as advised, this will be taken care of automatically.

\begin{table}
  \centering
  \begin{tabular}{@{}lc@{}}
    \toprule
    Method & Frobnability \\
    \midrule
    Theirs & Frumpy \\
    Yours & Frobbly \\
    Ours & Makes one's heart Frob\\
    \bottomrule
  \end{tabular}
  \caption{Results.   Ours is better.}
  \label{tab:example}
\end{table}

%-------------------------------------------------------------------------
\subsection{Illustrations, graphs, and photographs}

All graphics should be centered.
In \LaTeX, avoid using the \texttt{center} environment for this purpose, as this adds potentially unwanted whitespace.
Instead use
{\small\begin{verbatim}
  \centering
\end{verbatim}}
at the beginning of your figure.
Please ensure that any point you wish to make is resolvable in a printed copy of the paper.
Resize fonts in figures to match the font in the body text, and choose line widths that render effectively in print.
Readers (and reviewers), even of an electronic copy, may choose to print your paper in order to read it.
You cannot insist that they do otherwise, and therefore must not assume that they can zoom in to see tiny details on a graphic.

When placing figures in \LaTeX, it's almost always best to use \verb+\includegraphics+, and to specify the figure width as a multiple of the line width as in the example below
{\small\begin{verbatim}
   \usepackage{graphicx} ...
   \includegraphics[width=0.8\linewidth]
                   {myfile.pdf}
\end{verbatim}
}

%-------------------------------------------------------------------------
\subsection{Color}

Please refer to the author guidelines on the \confName\ \confYear\ web page for a discussion of the use of color in your document.

If you use color in your plots, please keep in mind that a significant subset of reviewers and readers may have a color vision deficiency; red-green blindness is the most frequent kind.
Hence avoid relying only on color as the discriminative feature in plots (such as red \vs green lines), but add a second discriminative feature to ease disambiguation.

%------------------------------------------------------------------------
\section{Final copy}

You must include your signed IEEE copyright release form when you submit your finished paper.
We MUST have this form before your paper can be published in the proceedings.

Please direct any questions to the production editor in charge of these proceedings at the IEEE Computer Society Press:
\url{https://www.computer.org/about/contact}.

%%%%%%%%% REFERENCES
{\small
\bibliographystyle{ieee_fullname}
\bibliography{egbib}
}

\end{document}

### 2021-09-15 latex/robdml.tex
tex; start

@@
 \usepackage{booktabs}
+
+\usepackage{microtype}
+\usepackage{xcolor}
+\newcommand{\oo}[1]{\textcolor{orange}{#1}}
 
@@
 \begin{abstract}
-   The ABSTRACT is to be in fully justified italicized text, at the top of the left-hand column, below the author and affiliation information.
-   Use the word ``Abstract'' as the title, in 12-point Times, boldface type, centered relative to the column, initially capitalized.
-   The abstract is to be in 10-point, single-spaced type.
-   Leave two blank lines after the Abstract, then begin the main text.
-   Look at previous CVPR abstracts to get a feel for style and length.
+	Deep metric learning models, being vulnerable to adversarial
+	attacks, have safety and security implications in applications.
+	%
+	Improving the adversarial robustness of a model against the attacks becomes
+	an important problem.
+	%
+	The existing defense methods are based on adversarial training.
+	%
+	However, they \oo{(1) robustness (2) speed/cost. (3) sampling matters.}
+	%
+	In this paper, we \oo{TBD}.
+	%
+	The proposed method is validated on three commonly
+	used deep metric learning datasets, namely CUB-200-2011, Cars-196,
+	and Stanford Online Product.
+	%
+	Comprehensive experimental results show our method outperforms
+	the existing defense methods.
 \end{abstract}
@@
 \section{Introduction}
-\label{sec:intro}
+\label{sec:1}
 
-Please follow the steps outlined below when submitting your manuscript to the IEEE Computer Society Press.
-This style guide now has several important modifications (for example, you are no longer warned against the use of sticky tape to attach your artwork to the paper), so all authors should read this new version.
+\section{Related Works}
+\label{sec:2}
 
-%-------------------------------------------------------------------------
-\subsection{Language}
+\section{Our Approach}
+\label{sec:3}
 
-All manuscripts must be in English.
+\section{Experiments}
+\label{sec:4}
 
-\subsection{Dual submission}
+\section{Discussions}
+\label{sec:5}
 
-Please refer to the author guidelines on the \confName\ \confYear\ web page for a
-discussion of the policy on dual submissions.
+\section{Conclusion}
+\label{sec:6}
 
-\subsection{Paper length}
-Papers, excluding the references section, must be no longer than eight pages in length.
-The references section will not be included in the page count, and there is no limit on the length of the references section.
-For example, a paper of eight pages with two pages of references would have a total length of 10 pages.
-{\bf There will be no extra page charges for \confName\ \confYear.}
-
-Overlength papers will simply not be reviewed.
-This includes papers where the margins and formatting are deemed to have been significantly altered from those laid down by this style guide.
-Note that this \LaTeX\ guide already sets figure captions and references in a smaller font.
-The reason such papers will not be reviewed is that there is no provision for supervised revisions of manuscripts.
-The reviewing process cannot determine the suitability of the paper for presentation in eight pages if it is reviewed in eleven.
-
-%-------------------------------------------------------------------------
-\subsection{The ruler}
-The \LaTeX\ style defines a printed ruler which should be present in the version submitted for review.
-The ruler is provided in order that reviewers may comment on particular lines in the paper without circumlocution.
-If you are preparing a document using a non-\LaTeX\ document preparation system, please arrange for an equivalent ruler to appear on the final output pages.
-The presence or absence of the ruler should not change the appearance of any other content on the page.
-The camera-ready copy should not contain a ruler.
-(\LaTeX\ users may use options of cvpr.sty to switch between different versions.)
-
-Reviewers:
-note that the ruler measurements do not align well with lines in the paper --- this turns out to be very difficult to do well when the paper contains many figures and equations, and, when done, looks ugly.
-Just use fractional references (\eg, this line is $087.5$), although in most cases one would expect that the approximate location will be adequate.
-
-\subsection{Paper ID}
-Make sure that the Paper ID from the submission system is visible in the version submitted for review (replacing the ``*****'' you see in this document).
-If you are using the \LaTeX\ template, \textbf{make sure to update paper ID in the appropriate place in the tex file}.
-
-\subsection{Mathematics}
-
-Please number all of your sections and displayed equations as in these examples:
-\begin{equation}
-  E = m\cdot c^2
-  \label{eq:important}
-\end{equation}
-and
-\begin{equation}
-  v = a\cdot t.
-  \label{eq:also-important}
-\end{equation}
-It is important for readers to be able to refer to any particular equation.
-Just because you did not refer to it in the text does not mean some future reader might not need to refer to it.
-It is cumbersome to have to use circumlocutions like ``the equation second from the top of page 3 column 1''.
-(Note that the ruler will not be present in the final copy, so is not an alternative to equation numbers).
-All authors will benefit from reading Mermin's description of how to write mathematics:
-\url{http://www.pamitc.org/documents/mermin.pdf}.
-
-\subsection{Blind review}
-
-Many authors misunderstand the concept of anonymizing for blind review.
-Blind review does not mean that one must remove citations to one's own work---in fact it is often impossible to review a paper unless the previous citations are known and available.
-
-Blind review means that you do not use the words ``my'' or ``our'' when citing previous work.
-That is all.
-(But see below for tech reports.)
-
-Saying ``this builds on the work of Lucy Smith [1]'' does not say that you are Lucy Smith;
-it says that you are building on her work.
-If you are Smith and Jones, do not say ``as we show in [7]'', say ``as Smith and Jones show in [7]'' and at the end of the paper, include reference 7 as you would any other cited work.
-
-An example of a bad paper just asking to be rejected:
-\begin{quote}
-\begin{center}
-    An analysis of the frobnicatable foo filter.
-\end{center}
-
-   In this paper we present a performance analysis of our previous paper [1], and show it to be inferior to all previously known methods.
-   Why the previous paper was accepted without this analysis is beyond me.
-
-   [1] Removed for blind review
-\end{quote}
-
-An example of an acceptable paper:
-\begin{quote}
-\begin{center}
-     An analysis of the frobnicatable foo filter.
-\end{center}
-
-   In this paper we present a performance analysis of the  paper of Smith \etal [1], and show it to be inferior to all previously known methods.
-   Why the previous paper was accepted without this analysis is beyond me.
-
-   [1] Smith, L and Jones, C. ``The frobnicatable foo filter, a fundamental contribution to human knowledge''. Nature 381(12), 1-213.
-\end{quote}
-
-If you are making a submission to another conference at the same time, which covers similar or overlapping material, you may need to refer to that submission in order to explain the differences, just as you would if you had previously published related work.
-In such cases, include the anonymized parallel submission~\cite{Authors14} as supplemental material and cite it as
-\begin{quote}
-[1] Authors. ``The frobnicatable foo filter'', F\&G 2014 Submission ID 324, Supplied as supplemental material {\tt fg324.pdf}.
-\end{quote}
-
-Finally, you may feel you need to tell the reader that more details can be found elsewhere, and refer them to a technical report.
-For conference submissions, the paper must stand on its own, and not {\em require} the reviewer to go to a tech report for further details.
-Thus, you may say in the body of the paper ``further details may be found in~\cite{Authors14b}''.
-Then submit the tech report as supplemental material.
-Again, you may not assume the reviewers will read this material.
-
-Sometimes your paper is about a problem which you tested using a tool that is widely known to be restricted to a single institution.
-For example, let's say it's 1969, you have solved a key problem on the Apollo lander, and you believe that the CVPR70 audience would like to hear about your
-solution.
-The work is a development of your celebrated 1968 paper entitled ``Zero-g frobnication: How being the only people in the world with access to the Apollo lander source code makes us a wow at parties'', by Zeus \etal.
-
-You can handle this paper like any other.
-Do not write ``We show how to improve our previous work [Anonymous, 1968].
-This time we tested the algorithm on a lunar lander [name of lander removed for blind review]''.
-That would be silly, and would immediately identify the authors.
-Instead write the following:
-\begin{quotation}
-\noindent
-   We describe a system for zero-g frobnication.
-   This system is new because it handles the following cases:
-   A, B.  Previous systems [Zeus et al. 1968] did not  handle case B properly.
-   Ours handles it by including a foo term in the bar integral.
-
-   ...
-
-   The proposed system was integrated with the Apollo lunar lander, and went all the way to the moon, don't you know.
-   It displayed the following behaviours, which show how well we solved cases A and B: ...
-\end{quotation}
-As you can see, the above text follows standard scientific convention, reads better than the first version, and does not explicitly name you as the authors.
-A reviewer might think it likely that the new paper was written by Zeus \etal, but cannot make any decision based on that guess.
-He or she would have to be sure that no other authors could have been contracted to solve problem B.
-\medskip
-
-\noindent
-FAQ\medskip\\
-{\bf Q:} Are acknowledgements OK?\\
-{\bf A:} No.  Leave them for the final copy.\medskip\\
-{\bf Q:} How do I cite my results reported in open challenges?
-{\bf A:} To conform with the double-blind review policy, you can report results of other challenge participants together with your results in your paper.
-For your results, however, you should not identify yourself and should not mention your participation in the challenge.
-Instead present your results referring to the method proposed in your paper and draw conclusions based on the experimental comparison to other results.\medskip\\
-
-\begin{figure}[t]
-  \centering
-  \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
-
-   \caption{Example of caption.
-   It is set in Roman so that mathematics (always set in Roman: $B \sin A = A \sin B$) may be included without an ugly clash.}
-   \label{fig:onecol}
-\end{figure}
-
-\subsection{Miscellaneous}
-
-\noindent
-Compare the following:\\
-\begin{tabular}{ll}
- \verb'$conf_a$' &  $conf_a$ \\
- \verb'$\mathit{conf}_a$' & $\mathit{conf}_a$
-\end{tabular}\\
-See The \TeX book, p165.
-
-The space after \eg, meaning ``for example'', should not be a sentence-ending space.
-So \eg is correct, {\em e.g.} is not.
-The provided \verb'\eg' macro takes care of this.
-
-When citing a multi-author paper, you may save space by using ``et alia'', shortened to ``\etal'' (not ``{\em et.\ al.}'' as ``{\em et}'' is a complete word).
-If you use the \verb'\etal' macro provided, then you need not worry about double periods when used at the end of a sentence as in Alpher \etal.
-However, use it only when there are three or more authors.
-Thus, the following is correct:
-   ``Frobnication has been trendy lately.
-   It was introduced by Alpher~\cite{Alpher02}, and subsequently developed by
-   Alpher and Fotheringham-Smythe~\cite{Alpher03}, and Alpher \etal~\cite{Alpher04}.''
-
-This is incorrect: ``... subsequently developed by Alpher \etal~\cite{Alpher03} ...'' because reference~\cite{Alpher03} has just two authors.
-
-% Update the cvpr.cls to do the following automatically.
-% For this citation style, keep multiple citations in numerical (not
-% chronological) order, so prefer \cite{Alpher03,Alpher02,Authors14} to
-% \cite{Alpher02,Alpher03,Authors14}.
-
-\begin{figure*}
-  \centering
-  \begin{subfigure}{0.68\linewidth}
-    \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-    \caption{An example of a subfigure.}
-    \label{fig:short-a}
-  \end{subfigure}
-  \hfill
-  \begin{subfigure}{0.28\linewidth}
-    \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-    \caption{Another example of a subfigure.}
-    \label{fig:short-b}
-  \end{subfigure}
-  \caption{Example of a short caption, which should be centered.}
-  \label{fig:short}
-\end{figure*}
-
-%------------------------------------------------------------------------
-\section{Formatting your paper}
-\label{sec:formatting}
-
-All text must be in a two-column format.
-The total allowable size of the text area is $6\frac78$ inches (17.46 cm) wide by $8\frac78$ inches (22.54 cm) high.
-Columns are to be $3\frac14$ inches (8.25 cm) wide, with a $\frac{5}{16}$ inch (0.8 cm) space between them.
-The main title (on the first page) should begin 1 inch (2.54 cm) from the top edge of the page.
-The second and following pages should begin 1 inch (2.54 cm) from the top edge.
-On all pages, the bottom margin should be $1\frac{1}{8}$ inches (2.86 cm) from the bottom edge of the page for $8.5 \times 11$-inch paper;
-for A4 paper, approximately $1\frac{5}{8}$ inches (4.13 cm) from the bottom edge of the
-page.
-
-%-------------------------------------------------------------------------
-\subsection{Margins and page numbering}
-
-All printed material, including text, illustrations, and charts, must be kept
-within a print area $6\frac{7}{8}$ inches (17.46 cm) wide by $8\frac{7}{8}$ inches (22.54 cm)
-high.
-%
-Page numbers should be in the footer, centered and $\frac{3}{4}$ inches from the bottom of the page.
-The review version should have page numbers, yet the final version submitted as camera ready should not show any page numbers.
-The \LaTeX\ template takes care of this when used properly.
-
-%-------------------------------------------------------------------------
-\subsection{Type style and fonts}
-
-Wherever Times is specified, Times Roman may also be used.
-If neither is available on your word processor, please use the font closest in
-appearance to Times to which you have access.
-
-MAIN TITLE.
-Center the title $1\frac{3}{8}$ inches (3.49 cm) from the top edge of the first page.
-The title should be in Times 14-point, boldface type.
-Capitalize the first letter of nouns, pronouns, verbs, adjectives, and adverbs;
-do not capitalize articles, coordinate conjunctions, or prepositions (unless the title begins with such a word).
-Leave two blank lines after the title.
-
-AUTHOR NAME(s) and AFFILIATION(s) are to be centered beneath the title
-and printed in Times 12-point, non-boldface type.
-This information is to be followed by two blank lines.
-
-The ABSTRACT and MAIN TEXT are to be in a two-column format.
-
-MAIN TEXT.
-Type main text in 10-point Times, single-spaced.
-Do NOT use double-spacing.
-All paragraphs should be indented 1 pica (approx.~$\frac{1}{6}$ inch or 0.422 cm).
-Make sure your text is fully justified---that is, flush left and flush right.
-Please do not place any additional blank lines between paragraphs.
-
-Figure and table captions should be 9-point Roman type as in \cref{fig:onecol,fig:short}.
-Short captions should be centred.
-
-\noindent Callouts should be 9-point Helvetica, non-boldface type.
-Initially capitalize only the first word of section titles and first-, second-, and third-order headings.
-
-FIRST-ORDER HEADINGS.
-(For example, {\large \bf 1. Introduction}) should be Times 12-point boldface, initially capitalized, flush left, with one blank line before, and one blank line after.
-
-SECOND-ORDER HEADINGS.
-(For example, { \bf 1.1. Database elements}) should be Times 11-point boldface, initially capitalized, flush left, with one blank line before, and one after.
-If you require a third-order heading (we discourage it), use 10-point Times, boldface, initially capitalized, flush left, preceded by one blank line, followed by a period and your text on the same line.
-
-%-------------------------------------------------------------------------
-\subsection{Footnotes}
-
-Please use footnotes\footnote{This is what a footnote looks like.
-It often distracts the reader from the main flow of the argument.} sparingly.
-Indeed, try to avoid footnotes altogether and include necessary peripheral observations in the text (within parentheses, if you prefer, as in this sentence).
-If you wish to use a footnote, place it at the bottom of the column on the page on which it is referenced.
-Use Times 8-point type, single-spaced.
-
-%-------------------------------------------------------------------------
-\subsection{Cross-references}
-
-For the benefit of author(s) and readers, please use the
-{\small\begin{verbatim}
-  \cref{...}
-\end{verbatim}}  command for cross-referencing to figures, tables, equations, or sections.
-This will automatically insert the appropriate label alongside the cross-reference as in this example:
-\begin{quotation}
-  To see how our method outperforms previous work, please see \cref{fig:onecol} and \cref{tab:example}.
-  It is also possible to refer to multiple targets as once, \eg~to \cref{fig:onecol,fig:short-a}.
-  You may also return to \cref{sec:formatting} or look at \cref{eq:also-important}.
-\end{quotation}
-If you do not wish to abbreviate the label, for example at the beginning of the sentence, you can use the
-{\small\begin{verbatim}
-  \Cref{...}
-\end{verbatim}}
-command. Here is an example:
-\begin{quotation}
-  \Cref{fig:onecol} is also quite important.
-\end{quotation}
-
-%-------------------------------------------------------------------------
-\subsection{References}
-
-List and number all bibliographical references in 9-point Times, single-spaced, at the end of your paper.
-When referenced in the text, enclose the citation number in square brackets, for
-example~\cite{Authors14}.
-Where appropriate, include page numbers and the name(s) of editors of referenced books.
-When you cite multiple papers at once, please make sure that you cite them in numerical order like this \cite{Alpher02,Alpher03,Alpher05,Authors14b,Authors14}.
-If you use the template as advised, this will be taken care of automatically.
-
-\begin{table}
-  \centering
-  \begin{tabular}{@{}lc@{}}
-    \toprule
-    Method & Frobnability \\
-    \midrule
-    Theirs & Frumpy \\
-    Yours & Frobbly \\
-    Ours & Makes one's heart Frob\\
-    \bottomrule
-  \end{tabular}
-  \caption{Results.   Ours is better.}
-  \label{tab:example}
-\end{table}
-
-%-------------------------------------------------------------------------
-\subsection{Illustrations, graphs, and photographs}
-
-All graphics should be centered.
-In \LaTeX, avoid using the \texttt{center} environment for this purpose, as this adds potentially unwanted whitespace.
-Instead use
-{\small\begin{verbatim}
-  \centering
-\end{verbatim}}
-at the beginning of your figure.
-Please ensure that any point you wish to make is resolvable in a printed copy of the paper.
-Resize fonts in figures to match the font in the body text, and choose line widths that render effectively in print.
-Readers (and reviewers), even of an electronic copy, may choose to print your paper in order to read it.
-You cannot insist that they do otherwise, and therefore must not assume that they can zoom in to see tiny details on a graphic.
-
-When placing figures in \LaTeX, it's almost always best to use \verb+\includegraphics+, and to specify the figure width as a multiple of the line width as in the example below
-{\small\begin{verbatim}
-   \usepackage{graphicx} ...
-   \includegraphics[width=0.8\linewidth]
-                   {myfile.pdf}
-\end{verbatim}
-}
-
-%-------------------------------------------------------------------------
-\subsection{Color}
-
-Please refer to the author guidelines on the \confName\ \confYear\ web page for a discussion of the use of color in your document.
-
-If you use color in your plots, please keep in mind that a significant subset of reviewers and readers may have a color vision deficiency; red-green blindness is the most frequent kind.
-Hence avoid relying only on color as the discriminative feature in plots (such as red \vs green lines), but add a second discriminative feature to ease disambiguation.
-
-%------------------------------------------------------------------------
-\section{Final copy}
-
-You must include your signed IEEE copyright release form when you submit your finished paper.
-We MUST have this form before your paper can be published in the proceedings.
-
-Please direct any questions to the production editor in charge of these proceedings at the IEEE Computer Society Press:
-\url{https://www.computer.org/about/contact}.
+\cite{Authors14}
 

### 2021-09-17 latex/robdml.tex
u

@@
 \newcommand{\oo}[1]{\textcolor{orange}{#1}}
+\include{math_commands.tex}
 
@@
 
-\author{Mo Zhou ~~~~~~~ Vishal M. Patel\\
+\author{Mo Zhou ~~~~~~~ Vishal Patel\\
 Johns Hopkins University\\
@@
 
+% what is deep metric learning
+
+Given a set of data points, a metric gives a distance value between each pair
+of them, while Deep Metric Learning (DML) aims to learn such a metric
+leveraging the representational power of deep neural networks.
+%
+DML has been extensively studied~[], and has a wide range of applications
+such as image retrieval~[] and face recognition~[].
+
+% why defense in deep metric learning
+
+Despite the improvements of this field thanks to the advancement of deep neural
+networks, recent research works suggest that DML models are vulnerable to
+adversarial attacks, where an imperceptible perturbation could incur unexpected
+or covertly manipulated results~[].
+%
+Such vulnerability poses safety, security, and fairness concerns in the
+applications of DML.
+%
+For example, impersonation or recognition evation are possible for DML-based
+face-identification system~[].
+%
+Thus, defending a DML model against adversarial attacks and improving its
+adversarial robustness could be an important problem.
+
+% existing methods & problem
+existing methods and problem.
+
+% for problem 1
+solution to problem 1
+
+% for problem 2
+solution to problem 2
+
+% evaluation and conclusion
+experimetal evaluations
+
+% contributions
+In brief, our contribusions include:
+
 \section{Related Works}

### 2021-09-17 latex/robdml.tex
u

@@
 %
-Thus, defending a DML model against adversarial attacks and improving its
-adversarial robustness could be an important problem.
+To counter the attacks (or reducing the vulnerability), it is important to
+design defense methods to improve the adversarial robustness of DML models.
 
 % existing methods & problem
-existing methods and problem.
+A series of defense methods for DML are proposed~[], inspired by the Madry's
+adversarial training method~[], as it is kown as one of the most effective
+defense methods for deep neural network classifiers.
+%
+However, it has been noted that
+%
+(1) the direct adoptation of Madry's defense will easily lead to model collapse
+due to producing very hard sample triplets;
+%
+(2) \oo{the sota defense lacks ()};
+%
+and (3) the adversarial training procedure is very time-consuming compared
+to the training process of a regular DML model.
 
 % for problem 1
+Triplet hardness still matters in adversarial training for deep metric
+learning.
+%
+propose hardness manipulation for.
 solution to problem 1
@@
 % for problem 2
+ACT and amdsemi have distinct characteristics.
 solution to problem 2
+
+% for problem 3
+update of advtrain acceleration.
+solution to problem 3
 
@@
 In brief, our contribusions include:
+%
+\begin{enumerate}
+	%
+	\item Hardness manipulation and the finding. better robustness.
+		%
+	\item Combine and even better.
+		%
+	\item Accelerate and reduce the cost for reproducing and applying.
+		%
+\end{enumerate}
 

### 2021-09-30 latex/appendix.tex
make lyx table only

\appendix

\section{Notes}

\subsection{To be investigated}

\begin{enumerate}

	\item [WIP]
		Sampling also matters in adversarial training for deep metric learning.

		[source hardness and destination hardness] different source sampling
		strategy and different destination sampling strategy. attack
		destination. DML loss not that sensitive to sampling? or generic
		advtrain method for DML? | still investigating

	\item [WIP] 7-step PGD and better aligned comparison: compare when
		these methods reach similar retrieval performance.

	\item Adversarial training (does not allow any distance moving) may
		encourage collapse (a trivial solution to the requirement). What if we
		loosen the requirement and convert it into a new constraint? For
		instance, \[
			L_{loosen}(a,p,n)=L_{base}(a,p,n)+\lambda_{1}L(a,\tilde{a},p)+\lambda_{2}L_{triplet}(a,\tilde{a},n)
		\] where the $L_{base}$ can be either $L_{triplet}$, $L_{rest}$, or
		$L_{act}$. Question: should we do this for every sample? i.e., \[
			L_{loosen}(a,p,n)=L_{base}(a,p,n)+\sum_{x\in\{a,p,n\}}L(x,\tilde{x},n_{x})
		\]

	\item ?  what about other types of metric learining loss functions? |
		investigating (we first make the most classical method work)

	\item ?  effectiveness of AMD Semi is to be verified. | as effective
		as ACT, reaches slightly higher ERS. But performs worse than ACT on
		some attacks, while performs better one some other attacks. | needs to
		be interpreted.

	\item faster training (algorithm tweak) FAT/other | postpone

	\item ? can we learn a good destination distribution? | too
		complicated? not necessary currently.

	\item 1. APGD as the optimization algorithm? | postpone

	\item 1. ? mixing amdsemi and act for adversarial training. They are good
		at different aspects.

	\item verify model collapse

	\item [\cmark] what if we use stopat for RAMD? | similar effect to amdsemi.
		misguiding gradient does not significantly affect AMD defense. So it
		is not quite necessary.

	\item [\cmark] \checkmark dynamically changing schedule for amdsemi? |
		looks good | the sqrt scheme works the best. (gradually increasing the
		hardness makes sense)

	\item [\cmark] implement FAT for faster exp iteration | works on toy
		dataset. too prone to collapse. if we try to avoid model collapse, the
		adversarial robustness will decrease significantly.

	\item [\cmark] (codecheck) does amd really honour the pgditer parameter? |
		direct adoptation of madry defense is really prone to model collapse.

\end{enumerate}

\subsection{Discarded or Rejected}

\begin{enumerate}

	\item \xmark
		MSE attack? | TMA is already close enough to it.

\end{enumerate}

### 2021-09-30 latex/appendix.tex
app

@@
 
-\begin{enumerate}
+\begin{itemize}
 
-	\item [WIP]
+	\item [*]
 		Sampling also matters in adversarial training for deep metric learning.
@@
 
-	\item [WIP] 7-step PGD and better aligned comparison: compare when
+	\item [*] 7-step PGD and better aligned comparison: compare when
 		these methods reach similar retrieval performance.
@@
 
-\end{enumerate}
+\end{itemize}
 

### 2021-09-30 latex/robdml.tex
tex
make lyx table only

@@
 \include{math_commands.tex}
+\usepackage{pifont}
+\newcommand{\cmark}{\ding{51}}
+\newcommand{\xmark}{\ding{55}}
 
@@
 	%
-	\item Hardness manipulation and the finding. better robustness.
+	\item Hardness manipulation is proposed for the adversarial training
+		of triplet-based deep metric learning models, which avoids model
+		collapse in the typical min-max adversarial training setting.
+		\oo{We discover that blah}.
+		Our proposed method achieves higher adversarial robustness compared
+		to the state-of-the-art.
 		%
@@
 \end{enumerate}
+
+To be investigated: (1) hardness manipulation and analysis of sample
+hardness to adversarial trainining of a deep metric learning model.
+(2) faster adversarial training by adopting the idea of free adversarial
+training. (3) other metric learning loss functions. / free adversarial
+training?
 
@@
 
+\subsection{Evaluation Protocol}
+
+\textbf{Dataset.}
+
 \section{Discussions}
 \label{sec:5}
+
+1. adversarial training speed.
 
@@
 
+\input{appendix.tex}
+
 \end{document}

### 2021-09-30 latex/robdml.tex
tex

@@
 adversarial attacks, where an imperceptible perturbation could incur unexpected
-or covertly manipulated results~[].
+or covertly manipulated results~\cite{advrank}.
 %
@@
 
-To be investigated: (1) hardness manipulation and analysis of sample
-hardness to adversarial trainining of a deep metric learning model.
-(2) faster adversarial training by adopting the idea of free adversarial
-training. (3) other metric learning loss functions. / free adversarial
-training?
-
 \section{Related Works}
 \label{sec:2}
+
+\textbf{Adversarial Attack.}
+
+\textbf{Adversarial Defense.}
+
+\textbf{Deep Metric Learning.}
+\cite{advrank,advorder,robrank}
 

### 2021-09-30 latex/appendix.tex
tex

@@
 
-	\item [*]
-		Sampling also matters in adversarial training for deep metric learning.
+	\item [*] Sampling also matters in adversarial training for deep metric learning.
 
@@
 
-	\item [*] 7-step PGD and better aligned comparison: compare when
-		these methods reach similar retrieval performance.
+	\item [*] 7-step PGD (as well as 16-step PGD) and better aligned comparison:
+		compare when these methods reach similar retrieval performance.
+		Meanwhile we can do experiments much faster.
 
@@
 
+	\item [?] Combine and even better. | Mixing ACT and AMDsemi does result
+		in clearly better results. It's on par with AMDsemi.
+
 	\item [\cmark] what if we use stopat for RAMD? | similar effect to amdsemi.

### 2021-09-30 latex/robdml.tex
tex

@@
 Given a set of data points, a metric gives a distance value between each pair
-of them, while Deep Metric Learning (DML) aims to learn such a metric
-leveraging the representational power of deep neural networks.
+of them.
 %
-DML has been extensively studied~[], and has a wide range of applications
-such as image retrieval~[] and face recognition~[].
+Deep Metric Learning (DML) aims to learn such a metric between two inputs (\eg,
+images) leveraging the representational power of deep neural networks.
+%
+DML has been extensively studied~[], and has a wide range of applications such
+as image retrieval~[] and face recognition~[].
 
@@
 		%
-	\item Combine and even better.
-		%
-	\item Accelerate and reduce the cost for reproducing and applying.
-		%
 \end{enumerate}
@@
 \label{sec:4}
+
+1. hardness manipulation, comparison with state-of-the-art.
 

### 2021-09-30 latex/appendix.tex
tex

@@
+\newpage
 \appendix
@@
 		advtrain method for DML? | still investigating
+
+	\item [\cmark] \checkmark dynamically changing schedule for amdsemi? |
+		looks good | the sqrt scheme works the best. (gradually increasing the
+		hardness makes sense)
 
@@
 
-	\item faster training (algorithm tweak) FAT/other | postpone
-
 	\item ? can we learn a good destination distribution? | too
@@
 	\item [?] Combine and even better. | Mixing ACT and AMDsemi does result
-		in clearly better results. It's on par with AMDsemi.
-
-	\item [\cmark] what if we use stopat for RAMD? | similar effect to amdsemi.
-		misguiding gradient does not significantly affect AMD defense. So it
-		is not quite necessary.
-
-	\item [\cmark] \checkmark dynamically changing schedule for amdsemi? |
-		looks good | the sqrt scheme works the best. (gradually increasing the
-		hardness makes sense)
-
-	\item [\cmark] implement FAT for faster exp iteration | works on toy
-		dataset. too prone to collapse. if we try to avoid model collapse, the
-		adversarial robustness will decrease significantly.
+		in clearly better results. It's on par with AMDsemi. Are they really
+		that different?
 
@@
 
-\subsection{Discarded or Rejected}
+\subsection{Done, Discarded or Rejected}
 
@@
 
-	\item \xmark
-		MSE attack? | TMA is already close enough to it.
+	\item [\xmark] MSE attack? | TMA is already close enough to it.
+
+	\item [\xmark] Faster training (algorithm tweak) based FAT/other | this is
+		a dead end. ACT has a different loss function to the outer minimization
+		problem, and hence result in different gradient and we cannot reuse
+		these gradients for algorithms like free adversarial training.
+		Re-calculating the gradients we need would simple double the
+		computational cost of the algorithm and diminish the gain from Free
+		Adversarial Training. We are no longer using the core benefit of FAT in
+		this way. In contrast, the AMD / AMDhm formulation can benefit from
+		this setup. | Further experiments suggest very weak robustness and the
+		models are very prone to collapse due to the non-zero initial delta
+		(results in too hard adversarial example).  | gradient approximation
+		does not look convincing. triplet gradient and ACT gradient does not
+		look convertible.
+
+	\item [\cmark] implement FAT for faster exp iteration | works on toy
+		dataset. too prone to collapse. if we try to avoid model collapse, the
+		adversarial robustness will decrease significantly.
+
+	\item [\cmark] what if we use stopat for RAMD? | similar effect to amdsemi.
+		misguiding gradient does not significantly affect AMD defense. So it
+		is not quite necessary.
 

### 2021-09-30 latex/robdml.tex
tex

@@
 \begin{abstract}
-	Deep metric learning models, being vulnerable to adversarial
-	attacks, have safety and security implications in applications.
-	%
-	Improving the adversarial robustness of a model against the attacks becomes
-	an important problem.
-	%
-	The existing defense methods are based on adversarial training.
-	%
-	However, they \oo{(1) robustness (2) speed/cost. (3) sampling matters.}
+	% background
+	Deep metric learning, being vulnerable to adversarial
+	attacks, has safety and security implications in its applications.
+	% importance
+	To counter these attacks, it is important to design adversarial
+	defense methods to improve adversarial robustness of deep metric learning.
+	% insight
+	However, as deep metric model with triplet loss is prone to collapse with
+	excessively hard samples, the previous methods refrain from using the
+	classical min-max adversarial training paradigm, but also suffer from
+	inefficiency.
+	% our proposal
+	In this paper, we argue that the sampling strategy has a significant
+	impact on the adversarial training for triplet-based deep metric learning.
+	% solution 1
+	\oo{
+	Based on this, we propose Hardness Manipulation 
+	TODO
+	However, they the influence of triplet sampling strategy during
+	adversarial training, 
+	(1) robustness (2) speed/cost. (3) sampling matters.}
 	%
@@
 		%
+	\item Gradual Adversary.
+		%
+	\item Benchmark existing metric learning loss functions with adversarial
+		training for future reference.
 \end{enumerate}
@@
 \label{sec:3}
+
+\subsection{Hardness Manipulation}
+
+\subsection{Gradual Adversary}
 

### 2021-10-01 latex/robdml.tex
tex

@@
 	% importance
-	To counter these attacks, it is important to design adversarial
-	defense methods to improve adversarial robustness of deep metric learning.
+	It is crucial to improve adversarial robustness of deep
+	metric learning.
 	% insight
@@
 	inefficiency.
-	% our proposal
-	In this paper, we argue that the sampling strategy has a significant
-	impact on the adversarial training for triplet-based deep metric learning.
+	% our finding
+	In this paper, we reveal a significant impact of triplet sampling strategy
+	on the adversarial training.
 	% solution 1
-	\oo{
-	Based on this, we propose Hardness Manipulation 
-	TODO
-	However, they the influence of triplet sampling strategy during
-	adversarial training, 
-	(1) robustness (2) speed/cost. (3) sampling matters.}
-	%
-	In this paper, we \oo{TBD}.
-	%
+	Based on this, Hardness Manipulation is proposed to adversarially perturb
+	a given triplet into a specified hardness level in min-max adversarial
+	training, instead of creating hardest triplets rendering model collapse.
+	% solution 2
+	To further improve the model performance, we propose a Gradual
+	Adversary to dynamicly change the hardness level to balance metric
+	learning and adversarial learning.
+	% Experiment
 	The proposed method is validated on three commonly
@@
 	and Stanford Online Product.
-	%
+	% Conclusion
 	Comprehensive experimental results show our method outperforms
-	the existing defense methods.
+	the existing defense methods, while achieving clearly higher
+	efficiency at a lower training cost.
 \end{abstract}
@@
 %
-DML has been extensively studied~[], and has a wide range of applications such
-as image retrieval~[] and face recognition~[].
+DML has been extensively studied~\cite{revisiting}, and has a
+wide range of applications such
+as image retrieval~\cite{imagesim2} and face recognition~\cite{facenet}.
 
@@
 adversarial attacks, where an imperceptible perturbation could incur unexpected
-or covertly manipulated results~\cite{advrank}.
+or covertly manipulated results~\cite{advrank,advorder}.
 %
@@
 For example, impersonation or recognition evation are possible for DML-based
-face-identification system~[].
+face-identification system.
 %
@@
 % existing methods & problem
-A series of defense methods for DML are proposed~[], inspired by the Madry's
-adversarial training method~[], as it is kown as one of the most effective
-defense methods for deep neural network classifiers.
+Several defense methods for DML are proposed in the
+literature~\cite{advrank,robrank}, inspired by the Madry's adversarial training
+method~\cite{madry}, as it is kown as one of the most effective defense methods
+for deep neural network classifiers.
 %
@@
 %
-(1) the direct adoptation of Madry's defense will easily lead to model collapse
-due to producing very hard sample triplets;
+(1) the robustness level achieved by the existing methods is still insufficient
+to counter the attacks;
 %
-(2) \oo{the sota defense lacks ()};
+(2) the direct adoptation of Madry's min-max adversarial training~\cite{madry} will easily
+lead to model collapse due to producing very hard sample triplets;
 %
-and (3) the adversarial training procedure is very time-consuming compared
-to the training process of a regular DML model.
+(3) the adversarial training procedure is very time-consuming compared to
+the training process of a regular DML model, but existing defense methods
+are incompatible to acceleration methods like Free Adversarial Training~\cite{freeat}.
 

### 2021-10-01 latex/robdml.tex
tex

@@
 \newcommand{\xmark}{\ding{55}}
+\usepackage{enumitem}
 
@@
 
-% for problem 1
-Triplet hardness still matters in adversarial training for deep metric
-learning.
+%% for problem 1
+%Triplet hardness still matters in adversarial training for deep metric
+%learning.
+%%
+%propose hardness manipulation for.
+%solution to problem 1
 %
-propose hardness manipulation for.
-solution to problem 1
-
-% for problem 2
-ACT and amdsemi have distinct characteristics.
-solution to problem 2
-
-% for problem 3
-update of advtrain acceleration.
-solution to problem 3
-
-% evaluation and conclusion
-experimetal evaluations
+%% for problem 2
+%ACT and amdsemi have distinct characteristics.
+%solution to problem 2
+%
+%% for problem 3
+%update of advtrain acceleration.
+%solution to problem 3
+%
+%% evaluation and conclusion
+%experimetal evaluations
 
 % contributions
-In brief, our contribusions include:
+%In brief, our contribusions include:
+In this MLSP project, we plan to make the following contributions:
 %
-\begin{enumerate}
+\begin{enumerate}[noitemsep]
 	%
-	\item Hardness manipulation is proposed for the adversarial training
-		of triplet-based deep metric learning models, which avoids model
-		collapse in the typical min-max adversarial training setting.
-		\oo{We discover that blah}.
-		Our proposed method achieves higher adversarial robustness compared
-		to the state-of-the-art.
+	\item {\textit{Hardness Manipulation}} is proposed for the adversarial
+		training of triplet-based deep metric learning models, which avoids
+		model collapse in the typical min-max adversarial training setting.
+		The proposed method achieves higher adversarial robustness compared to
+		the state-of-the-art, and is more computationally efficient.
 		%
-	\item Gradual Adversary.
+	\item \textit{Gradual Adversary} is proposed to dynamically adjust the
+		destination hardness less for Hardness Manipulation during the
+		adversarial training process in order to balance the metric learning
+		and adversarial learning.
 		%
-	\item Benchmark existing metric learning loss functions with adversarial
-		training for future reference.
+	\item Revise and incorporate the state-of-the-art adversarial training
+		acceleration method (\ie, Free Adversarial Training~\cite{freeat},
+		which is designed for classification) into adversarial training of 
+		deep metric learning models. It will greatly improve the efficiency
+		of adversarial training.
+		%
+	\item Benchmark of existing metric learning loss functions under
+		adversarial training scenario, and analyze their different
+		characteristics for future reference.
+		%
+	\item Explore the possibility of proposing a new metric learning loss
+		function oriented for adversarial training, starting from scratch or
+		from an existing metric learning loss.
+		%
 \end{enumerate}
@@
 
-1. hardness manipulation, comparison with state-of-the-art.
+\textbf{Dataset.}
 
-\subsection{Evaluation Protocol}
-
-\textbf{Dataset.}
+\textbf{Experiment Settings.}
 
@@
 
-1. adversarial training speed.
+%1. adversarial training speed.
+
+% PGD-7 PGD-16
 

### 2021-10-01 latex/robdml.tex
tex

@@
 \textbf{Adversarial Attack.}
+%
+Szegedy \etal~\cite{l-bfgs} find misclassification of DNN can be triggered by
+an imperceptible adversarial perturbation to the input image.
+%
+Ian \etal~\cite{fgsm} speculate the reason is that DNN being locally linear
+with respect to the adversarial perturbation.
+%
+A series of following works attempt to more efficiently compromise the DNNs,
+such as BIM~\cite{i-fgsm}, C\&W~\cite{cw}, PGD~\cite{madry}, and
+APGD~\cite{apgd}.
+%
+These attacks are based on the first-order gradient of the classification loss
+with respect to the input image, and hence rely on the white-box assumption
+that the model architecture and parameters are accessible to the attacker,
+which is impractical for real-world attacks.
+%
+Subsequently, black-box attack methods are developed into two types:
+transferrability-based attacks and query-based attacks.
+%
+Transferrability-based attacks relies on the observation that image-agnostic
+(will take effect when applied to any image) and model-agnostic (will take
+effect when applied to any model) adversarial perturbation are possible.
+%
+Query-based attacks only need the logit score output or the label output from a
+classifier, based on which the gradient could be estimated from the response to
+repetitive queries in order to figure out the adversarial perturbation.
 
 \textbf{Adversarial Defense.}
+%
+To battle against the attacks, some early defense
+methods create a gradient masking effect, namely making it hard for the attacker
+to find a good gradient, but it gives a false sense of security~\cite{obfuscated}.
+%
+Defensive distillation~[] can be compromised by C\&W~\cite{cw}.
+%
+Ensemble of weak defenses is insufficient~[].
+%
+Defense can also be implemented as preprocessing~[] or reconstructing~[] the input
+image, or a randomized process inside the network~[].
+%
+However, it is noted that various defense methods are still susceptible to
+adaptive attack~\cite{adaptive}.
+%
+Among the proposed defense methods, adversarial training has been empirically
+found effective~[][], and it consistently retains adversarial robustness
+for the model.
 
 \textbf{Deep Metric Learning.}
-\cite{advrank,advorder,robrank}
+%
+A wide range of application problem such as image retrieval~\cite{imagesim2},
+cross-modal retrieval~\cite{ladderloss}, and face recognition~\cite{facenet}
+can be formularized as a deep metric learning problem.
+%
+Deep metric learning has been found vulnerable to adversarial attacks as
+well~\cite{advrank,advorder}, which will result in undesired
+implications on safety, security, or fairness of a deep metric learning
+application.
+%
+In contrast, the defense methods for enhancing the adversarial robustness of deep
+metric learning are less explored.
+%
+Mo \etal~\cite{advrank} present an adversarial training method with adversarial
+examples maximizing the embedding move distance off its original location.
+%
+Anti-Collapse Triplet defense~\cite{robrank} forces the model
+to separate collapsed positive and negative samples in order to learn
+robust features.
+%
+However, the existing defense methods refrain from adopting Madry's min-max
+adversarial training paradigm due to the model being too easy to collapse
+with excessively hard adversarial samples.
 

### 2021-10-01 latex/robdml.tex
tex

@@
 %
-Transferrability-based attacks relies on the observation that image-agnostic
+Transferrability-based attacks~\cite{di-fgsm,universal} relies on the observation that image-agnostic
 (will take effect when applied to any image) and model-agnostic (will take
@@
 %
-Query-based attacks only need the logit score output or the label output from a
+Query-based attacks~\cite{nes-atk,spsa-atk} only need the logit score output or the label output from a
 classifier, based on which the gradient could be estimated from the response to
@@
 %
-Defensive distillation~[] can be compromised by C\&W~\cite{cw}.
+Defensive distillation~\cite{distill2} can be compromised by C\&W~\cite{cw}.
 %
-Ensemble of weak defenses is insufficient~[].
+Ensemble of weak defenses is insufficient~\cite{ensembleweak}.
 %
-Defense can also be implemented as preprocessing~[] or reconstructing~[] the input
-image, or a randomized process inside the network~[].
+Defense can also be implemented as preprocessing~\cite{deflecting} the input
+image, or a randomized process inside the network~\cite{self-ensemble}.
 %
@@
 Among the proposed defense methods, adversarial training has been empirically
-found effective~[][], and it consistently retains adversarial robustness
+found effective~\cite{bilateral,advtrain-triplet,benchmarking}, and it consistently retains adversarial robustness
 for the model.

### 2021-10-01 latex/robdml.tex
tex

@@
 	attacks, has safety and security implications in its applications.
-	% importance
-	It is crucial to improve adversarial robustness of deep
-	metric learning.
+	% 
+	Owing to the significance of this issue, a series of defense methods
+	are proposed to improve its adversarial robustness.
 	% insight
-	However, as deep metric model with triplet loss is prone to collapse with
-	excessively hard samples, the previous methods refrain from using the
-	classical min-max adversarial training paradigm, but also suffer from
-	inefficiency.
+	However, as a model with triplet loss is prone to collapse with
+	excessively hard samples, the existing methods refrain from using the
+	classical min-max adversarial training paradigm, and hence suffer from
+	inefficient learning from a strong adversary.
 	% our finding

### 2021-10-01 latex/robdml.tex
tex

@@
 %
-Mo \etal~\cite{advrank} present an adversarial training method with adversarial
+Zhou \etal~\cite{advrank} present an adversarial training method with adversarial
 examples maximizing the embedding move distance off its original location.
 %
-Anti-Collapse Triplet defense~\cite{robrank} forces the model
+Anti-Collapse Triplet~\cite{robrank} forces the model
 to separate collapsed positive and negative samples in order to learn

### 2021-10-02 latex/appendix.tex
lyx

@@
 
+	\item [!] revise HM. align dap dan directly instead of the loss.
+
+	\item [!] re-design Gradual Adversary for HM based on that for the amdsemi.
+
+	\item [!] difference between EST, ACT, AMD/ AMDsemi.
+		Other methods (than HM) cannot effectively learn from the strongest
+		adversary as the inner maximization is indirectly (and not guaranteed).
+		HM follows the min-max paradigm (can be incorporated into FAT etc).
+		Both ACT and HM stops at a specific point.
+
 	\item [*] Sampling also matters in adversarial training for deep metric learning.
@@
 		advtrain method for DML? | still investigating
-
-	\item [\cmark] \checkmark dynamically changing schedule for amdsemi? |
-		looks good | the sqrt scheme works the best. (gradually increasing the
-		hardness makes sense)
 
@@
 		\]
+
+	\item [?] adversarial training that does not allow embedding move may
+		encourage model collapse. Maybe we just apply some loosened restrction
+		such as aap? i.e. $(a,\tilde{a},p;\gamma=0)$.
 
@@
 
-	\item [\cmark] (codecheck) does amd really honour the pgditer parameter? |
-		direct adoptation of madry defense is really prone to model collapse.
-
 \end{itemize}
@@
 \begin{enumerate}
+
+	\item [\cmark] \checkmark dynamically changing schedule for amdsemi? |
+		looks good | the sqrt scheme works the best. (gradually increasing the
+		hardness makes sense)
+
+	\item [\cmark] (codecheck) does amd really honour the pgditer parameter? |
+		direct adoptation of madry defense is really prone to model collapse.
 

### 2021-10-03 latex/appendix.tex
tex

@@
 
-	\item [!] revise HM. align dap dan directly instead of the loss.
-
-	\item [!] re-design Gradual Adversary for HM based on that for the amdsemi.
+	\item [*] re-design Gradual Adversary for HM based on that for the amdsemi. |
+		\[
+			(1-\frac{\text{prev\_loss}|_0^{2+\beta}}{2+\beta}) \times
+			(\phi - H_\text{dst})\mathbb{I}\{\phi > H_\text{dst}\}
+		\]
+		So that for triplets that are not hard enoguh, when
+		$prevloss \rightarrow 0$, $E[H_\text{dst}]\rightarrow \phi$.
 
@@
 		Both ACT and HM stops at a specific point.
+
+	\item [?] does the new generic HM work under FAT?
 
@@
 
+	\item [\cmark] revise HM. align dap dan directly instead of the loss.
+
 	\item [\cmark] \checkmark dynamically changing schedule for amdsemi? |

### 2021-10-03 latex/appendix.tex
tex

@@
 
-\section{Notes}
+\section{My Memo}
 
@@
 	\item [?] does the new generic HM work under FAT?
+		Previous FAT leads to collapse because (even if in the amdsemi +fat
+		experiment due to implementation issue) the delta is going to be universal
+		so that for every input $x$ it will increase $H[L(x)]$ as much as possible.
+		This is too prone to lead to collpase. Can we reuse the gradient for 
+		Hardness Manipulation then? We linearly scale down the delta?
+		We want to minimize $E[|H_{src}(x)-H_{dst}(x)|]$ (to a specified hardness).
+
+	\item [?] benchmark other metric learning loss functions for adversarial
+		training. Can HM or GradualAdversary be adopted for other loss functions?
 

### 2021-10-03 latex/robdml.tex
tex

@@
 		%
+		This method makes min-max training feaisble, and hence the incorporation
+		into free adversarial training and boost learning efficiency.
+		%
+		(initial condition)
+		%
 	\item \textit{Gradual Adversary} is proposed to dynamically adjust the
@@
 		and adversarial learning.
+		%
+		(terminal condition)
+		%
+	\item Inter-ID structure constraint. ((aa~p) + (pp~a))/2
+		(cross-id repelling)
+		existing methods only care inter-class separation, but not
+		intra-class (inter-id) separation, because we may get a 6-element
+		set (a,a~,p,p~,n,n~) from the original triplet.
 		%

### 2021-10-04 latex/appendix.tex
tex

@@
 
+\subsection{Lessons Learned}
+
 \subsection{To be investigated}
@@
 
-	\item [*] re-design Gradual Adversary for HM based on that for the amdsemi. |
+	\item [*] Re-design Gradual Adversary (Linear Addition)
 		\[
-			(1-\frac{\text{prev\_loss}|_0^{2+\beta}}{2+\beta}) \times
-			(\phi - H_\text{dst})\mathbb{I}\{\phi > H_\text{dst}\}
+			(1-\frac{l_{t-1}|_0^{U_L}}{U_L}) \times U_H
 		\]
-		So that for triplets that are not hard enoguh, when
-		$prevloss \rightarrow 0$, $E[H_\text{dst}]\rightarrow \phi$.
+		Increase $E[H]$ to $E[H]+\alpha U_H$. $E[H]$ is expected to decrease
+		with a well-learned model. So without GA, the strength of adversary
+		will decrease.
 
@@
 
+	\item [\xmark] re-design Gradual Adversary for HM based on that for the amdsemi. |
+		\[
+			(1-\frac{\text{prev\_loss}|_0^{2+\beta}}{2+\beta}) \times
+			(\phi - H_\text{dst})\mathbb{I}\{\phi > H_\text{dst}\}
+		\]
+		So that for triplets that are not hard enoguh, when
+		$prevloss \rightarrow 0$, $E[H_\text{dst}]\rightarrow \phi$.
+		| This has a weak effect. Redesign required.
+
 	\item [\cmark] revise HM. align dap dan directly instead of the loss.

### 2021-10-05 latex/appendix.tex
merge FAT attemp #1 into tex

@@
 \section{My Memo}
-
-\subsection{Lessons Learned}
 
@@
 
-\subsection{Done, Discarded or Rejected}
+\subsection{Lessons Learned}
+
+\begin{table*}
+\resizebox{1.0\linewidth}{!}{
+\begin{tabular}{|c|c|c|c|c|cccc|ccccc|ccccc|c|}
+\hline
+dataset & model & loss & num\_rep & comment & \multicolumn{1}{c|}{R1} & \multicolumn{1}{c|}{R2} & \multicolumn{1}{c|}{mAP} & NMI & \multicolumn{1}{c|}{CA+} & \multicolumn{1}{c|}{CA-} & \multicolumn{1}{c|}{QA+} & \multicolumn{1}{c|}{QA-} & TMA & \multicolumn{1}{c|}{ES:D} & \multicolumn{1}{c|}{ES:R} & \multicolumn{1}{c|}{LTM} & \multicolumn{1}{c|}{GTM} & GTT & ERS\tabularnewline
+\hline
+\hline
+fashion & rc2f2fatamd & tripletN & 1 & want delta & 84.0 & 90.6 & 78.7 & 75.3 & 3.9 & 69.3 & 7.4 & 81.7 & 0.960 & 0.959 & 19.8 & 8.1 & 12.1 & 0.0 & 16.8\tabularnewline
+\hline
+ &  &  & 2 & want delta & 82.7 & 89.7 & 75.9 & 73.7 & 15.1 & 35.6 & 23.4 & 48.0 & 0.905 & 0.598 & 9.4 & 27.9 & 17.9 & 0.0 & 32.8\tabularnewline
+\hline
+ &  &  & 4 & want delta & 80.3 & 88.4 & 73.5 & 71.7 & 20.7 & 27.8 & 29.7 & 37.6 & 0.920 & 0.345 & 31.0 & 29.5 & 20.1 & 0.0 & 40.7\tabularnewline
+\hline
+ &  &  & 8 & want delta & 79.1 & 87.1 & 70.7 & 68.7 & 23.3 & 25.2 & 31.8 & 29.8 & 0.925 & 0.225 & 44.6 & 26.2 & 25.3 & 0.0 & 44.7\tabularnewline
+\hline
+ & rc2f2fatnone &  & 1 & zero delta & 87.8 & 92.9 & 83.2 & 79.8 & 0.7 & 98.6 & 0.2 & 96.5 & 0.994 & 1.548 & 0.0 & 1.4 & 7.2 & 0.0 & 3.9\tabularnewline
+\hline
+ &  &  & 2 & zero delta & 85.8 &  &  &  &  &  &  &  &  &  &  &  &  &  & \tabularnewline
+\hline
+ &  &  & 4 & zero delta & 84.7 & 91.0 & 79.0 & 75.4 & 0.8 & 93.9 & 0.3 & 91.8 & 0.994 & 1.435 & 1.2 & 3.8 & 14.8 & 0.0 & 6.5\tabularnewline
+\hline
+ &  &  & 8 & zero delta & 81.0 &  &  &  &  &  &  &  &  &  &  &  &  &  & \tabularnewline
+\hline
+cub & rres18fatnone & tripletN & 1 & zero delta & 52.9 & 64.4 & 33.4 & 59.5 & 0.1 & 100.0 & 0.1 & 99.9 & 0.882 & 1.797 & 0.0 & 0.0 & 20.1 & 0.0 & 4.3\tabularnewline
+\hline
+ & rres18fatamd & tripletN & 1 & wants delta & 51.5 & 63.2 & 32.7 & 59.8 & 0.0 & 100.0 & 0.2 & 99.7 & 0.886 & 1.783 & 0.0 & 0.0 & 18.0 & 0.0 & 4.1\tabularnewline
+\hline
+ &  &  & 2 &  & 46.0 & 56.8 & 27.9 & 53.8 & 1.3 & 93.7 & 0.7 & 92.8 & 0.915 & 1.009 & 1.2 & 0.1 & 17.2 & 0.0 & 9.4\tabularnewline
+\hline
+ &  &  & 4 &  & Coll &  &  &  &  &  &  &  &  &  &  &  &  &  & \tabularnewline
+\hline
+ &  &  & 8 &  & Coll &  &  &  &  &  &  &  &  &  &  &  &  &  & \tabularnewline
+\hline
+ & rres18fatamdsemi & tripletN & 4 & decay0.5 & 44.1 & 55.6 & 26.1 & 53.1 & 1.5 & 92.3 & 0.9 & 91.3 & 0.916 & 1.004 & 1.3 & 0.2 & 17.2 & 0.0 & 9.8\tabularnewline
+\hline
+ & (too weak) &  & 8 & decay0.25 & omitted &  &  &  &  &  &  &  &  &  &  &  &  &  & \tabularnewline
+\hline
+ & (too weak) &  & 8 & decay0.0 & 48.7 & 60.6 & 29.0 & 56.3 & 0.1 & 100.0 & 0.3 & 99.5 & 0.895 & 1.733 & 0.0 & 0.0 & 16.8 & 0.0 & 4.2\tabularnewline
+\hline
+\end{tabular}
+}
+\caption{(freeze) FAT attempt \#1 debugging and sanity. This version seeks
+for universal perturbation for increasing E\_x{[}Loss{]} as much as
+possible.}
+\end{table*}
 

### 2021-10-05 latex/sort-hardness.tex
tables

\begin{table}
\resizebox{\columnwidth}{!}{
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
Dataset & Random (r) & Semihard (m) & Softhard (s) & Distance (d) & Hardest (h)\tabularnewline
\hline 
\hline 
MNIST & -0.24 & -0.12 & -0.05 & 0.02 & 0.02\tabularnewline
\hline 
Fashion & -0.32 & -0.12 & -0.04 & 0.03 & 0.03\tabularnewline
\hline 
CUB & -0.15 & -0.13 & -0.10 & 0.04 & 0.05\tabularnewline
\hline 
CARS &  &  &  &  & \tabularnewline
\hline 
SOP &  &  &  &  & \tabularnewline
\hline 
\end{tabular}
}
\caption{(freeze) Sorting Hardness using average loss of first several (we
set 5) iterations.}
\end{table}

### 2021-10-05 latex/robdml.tex
tex
tables

@@
 \usepackage{enumitem}
+\usepackage{multirow}
+\newcommand{\uline}[1]{\underline{#1}}
 
@@
 
-% what is deep metric learning
+% background and insight.
 
@@
 wide range of applications such
-as image retrieval~\cite{imagesim2} and face recognition~\cite{facenet}.
-
-% why defense in deep metric learning
-
+as image retrieval~\cite{imagesim2} and face recognition~\cite{facenet,domainface}.
+%
 Despite the improvements of this field thanks to the advancement of deep neural
@@
 
-%% for problem 1
-%Triplet hardness still matters in adversarial training for deep metric
-%learning.
-%%
-%propose hardness manipulation for.
-%solution to problem 1
-%
-%% for problem 2
-%ACT and amdsemi have distinct characteristics.
-%solution to problem 2
-%
-%% for problem 3
-%update of advtrain acceleration.
-%solution to problem 3
-%
-%% evaluation and conclusion
-%experimetal evaluations
+% for problem 1
+\oo{[1. Hardness Manipulation]}
+Triplet hardness still matters in adversarial training for deep metric
+learning.
+
+% for problem 2
+\oo{[2. Gradual Adversary]}
+The expectation of hardness will decrease during the training process,
+compared to that from the beginning phase.
+
+\oo{[3. Intra-Class Structure]}
+Given a triplet of samples, we may eventually get up to 6 samples avaiable
+for adversarial training. There could be some kind of hierarchy.
+
+\oo{[4. Free Adversarial Metric Learining]}
+Extension of FAT to adversarial deep metric learning.
+
+% evaluation and conclusion
+\oo{[experimetal evaluations]}
+To validate the effectiveness of the proposed method, we conduct experiments
+on three commonly used dataset, namely CUB-200-2011, Cars-196, and Stanford
+Online Product. \oo{the results suggest that}
+
+\begin{figure}
+	\oo{[diagram]}
+	\caption{\oo{Diagram demonstrating the core idea}}
+\end{figure}
 
 % contributions
-%In brief, our contribusions include:
-In this MLSP project, we plan to make the following contributions:
+In brief, our contribusions include:
 %
@@
 
+\oo{[Deep metric learning problem setup]}
+
+In Deep Metric Learning (DML)~\cite{revisiting,dmlreality}, an embedding
+function $\phi:\mathcal{X}\mapsto \Phi \subseteq \mathbb{R}^D$ is learned to
+map data points $X\in\mathcal{X}$ into an embedding space $\Phi$, where the
+output of $\phi(\cdot)$ is usually normalized to the real unit hypersphere for
+regularization purpose.
+%
+With a predefined distance function $d(\cdot,\cdot)$, it allows us to measure
+the distance between $X_i$ and $X_j$ as
+$d_\phi(X_i,X_j)=d(\phi(X_i),\phi(X_j))$.
+%
+Various loss functions for learning the underlying embedding function have been
+proposed~\cite{revisiting,dmlreality}, where the triplet loss~\cite{facenet}
+remain to be a strong and widely used baseline that could reach
+state-of-the-art performance with appropriate triplet sampling strategy.
+
+\oo{[Quick review of existing defense methods]}
+
 \subsection{Hardness Manipulation}
@@
 \subsection{Gradual Adversary}
+
+\subsection{Intra-Class Structure}
 

### 2021-10-05 latex/robdml.tex
tex

@@
 %
-Transferrability-based attacks~\cite{di-fgsm,universal} relies on the observation that image-agnostic
-(will take effect when applied to any image) and model-agnostic (will take
-effect when applied to any model) adversarial perturbation are possible.
+Transferrability-based attacks~\cite{di-fgsm,universal} relies on the
+observation that image-agnostic (will take effect when applied to any image)
+and model-agnostic (will take effect when applied to any model) adversarial
+perturbation are possible.
 %
-Query-based attacks~\cite{nes-atk,spsa-atk} only need the logit score output or the label output from a
-classifier, based on which the gradient could be estimated from the response to
-repetitive queries in order to figure out the adversarial perturbation.
+Query-based attacks~\cite{nes-atk,spsa-atk} only need the logit score output or
+the label output from a classifier, based on which the gradient could be
+estimated from the response to repetitive queries in order to figure out the
+adversarial perturbation.
 
@@
 %
-To battle against the attacks, some early defense
-methods create a gradient masking effect, namely making it hard for the attacker
-to find a good gradient, but it gives a false sense of security~\cite{obfuscated}.
+To battle against the attacks, some early defense methods create a gradient
+masking effect, namely making it hard for the attacker to find a good gradient,
+but it gives a false sense of security~\cite{obfuscated}.
 %
@@
 Among the proposed defense methods, adversarial training has been empirically
-found effective~\cite{bilateral,advtrain-triplet,benchmarking}, and it consistently retains adversarial robustness
-for the model.
+found effective~\cite{bilateral,advtrain-triplet,benchmarking}, and it
+consistently retains adversarial robustness for the model.
 
@@
 Deep metric learning has been found vulnerable to adversarial attacks as
-well~\cite{advrank,advorder}, which will result in undesired
-implications on safety, security, or fairness of a deep metric learning
-application.
+well~\cite{advrank,advorder}, which will result in undesired implications on
+safety, security, or fairness of a deep metric learning application.
 %
-In contrast, the defense methods for enhancing the adversarial robustness of deep
-metric learning are less explored.
+In contrast, the defense methods for enhancing the adversarial robustness of
+deep metric learning are less explored.
 %
-Zhou \etal~\cite{advrank} present an adversarial training method with adversarial
-examples maximizing the embedding move distance off its original location.
+Zhou \etal~\cite{advrank} present an adversarial training method with
+adversarial examples maximizing the embedding move distance off its original
+location.
 %
-Anti-Collapse Triplet~\cite{robrank} forces the model
-to separate collapsed positive and negative samples in order to learn
-robust features.
+Anti-Collapse Triplet~\cite{robrank} forces the model to separate collapsed
+positive and negative samples in order to learn robust features.
 %
 However, the existing defense methods refrain from adopting Madry's min-max
-adversarial training paradigm due to the model being too easy to collapse
-with excessively hard adversarial samples.
+adversarial training paradigm due to the model being too easy to collapse with
+excessively hard adversarial samples.
 
@@
 \label{sec:3}
-
-\oo{[Deep metric learning problem setup]}
 
@@
 
+Similar to what have been found for the classifiers, recent
+works~\cite{robrank,advrank,advorder} also suggest that the embedding function
+$\phi(\cdot)$ in DML is vulnerable to adversarial attacks.
+%
+Specifically, an imperceptible adversarial perturbation $r$ is added to the
+input image $X$ ($\|r\|_p \leq \varepsilon$, $X+r\in \mathcal{X}$), so that its
+embedding vector $\tilde{\vx}=\phi(X+r)$ will be moved off its original
+location towards other positions to fulfill the attacker's goal.
+
+Although attacks against DML has been widely studied~\cite{advrank,advorder},
+the defense methods for improving adversarial robustness is much less explored.
+%
+As adversarial training~\cite{madry} remains to be one of the most effective
+defense for classification, existing defense methods for DML are also adversarial
+training-based.
+
 \oo{[Quick review of existing defense methods]}
+EST~\cite{advrank} and ACT~\cite{robrank}. Their issues.
 
@@
 \subsection{Intra-Class Structure}
+
+\subsection{\oo{Free Adversarial DML?}}
+
+\subsection{\oo{Benchmark other DML loss?}}
 

### 2021-10-05 latex/robdml.tex
tex
svg

@@
 
+\begin{figure}[t]
+	\includegraphics[width=1.0\columnwidth]{introdiag.pdf}
+	\caption{\oo{Performance plot with aligned conditions.
+	(1) robustness and r1 under the same training cost;
+	(2) r1 and training cost for reaching similar robustness;
+	(3) training cost and robustness for reaching similar r1.}}
+\end{figure}
+
 % existing methods & problem
@@
 Online Product. \oo{the results suggest that}
-
-\begin{figure}
-	\oo{[diagram]}
-	\caption{\oo{Diagram demonstrating the core idea}}
-\end{figure}
 
@@
 state-of-the-art performance with appropriate triplet sampling strategy.
+%
+Given a triplet of image embeddings (anchor $\va=\phi(X_a)$, positive sample
+$\vp=\phi(X_p)$, negative sample $\vn=\phi(X_n)$), the triplet loss is defined
+as:
+%
+$
+%
+	L_\text{trip}(\va, \vp, \vn; \gamma) = \max(0, d(\va, \vp) - d(\va, \vn) +
+	\gamma),
+%
+$
+%
+where $\gamma$ is a predefined margin parameter.
 
@@
 As adversarial training~\cite{madry} remains to be one of the most effective
-defense for classification, existing defense methods for DML are also adversarial
-training-based.
-
-\oo{[Quick review of existing defense methods]}
-EST~\cite{advrank} and ACT~\cite{robrank}. Their issues.
+defense for classification, existing defense methods for DML are also
+adversarial training-based.
+%
+Embedding-Shifted Triplet (EST)~\cite{advrank} adopts adversarial counterpars
+of $\va,\vp,\vn$ with maximum embedding move distance off their original
+locations, \ie,
+$L_\text{EST}=L_\text{trip}(\tilde{\va},\tilde{\vp},\tilde{\vn};\gamma)$ where
+$\tilde{\va}=\phi(X+r^*)$, $r^*=\arg\max_{r}d_\phi(X+r, X)$.
+%
+Anti-Collapse Triplet (ACT)~\cite{robrank} collapses the embedding vectors
+of positive and negative sample, and enforces the model to separate them
+apart, \ie, $L_\text{ACT}=L_\text{trip}(\va, \overrightarrow{\vp},
+\overleftarrow{\vn};\gamma)$, where $[\overrightarrow{\vp},\overleftarrow{\vn}]
+=[\phi(X_p+r_p^*), \phi(X_n+r_n^*)]$, and $[r_p^*,r_n^*]=\arg\min_{r_p,r_n}
+d_\phi(X_p+r_p, X_n+r_n)$.
+%
+\oo{Their issues.}
 

### 2021-10-05 latex/robdml.tex
tex

@@
 %
-Anti-Collapse Triplet (ACT)~\cite{robrank} collapses the embedding vectors
-of positive and negative sample, and enforces the model to separate them
-apart, \ie, $L_\text{ACT}=L_\text{trip}(\va, \overrightarrow{\vp},
+Anti-Collapse Triplet (ACT)~\cite{robrank} collapses the embedding vectors of
+positive and negative sample, and enforces the model to separate them apart,
+\ie, $L_\text{ACT}=L_\text{trip}(\va, \overrightarrow{\vp},
 \overleftarrow{\vn};\gamma)$, where $[\overrightarrow{\vp},\overleftarrow{\vn}]
@@
 %
-\oo{Their issues.}
+However, compared to the standard min-max adversarial training
+paradigm~\cite{madry}, these methods merely indirectly increase the loss value,
+and thus, suffer from inefficient learning because the adversary is not strong
+enough.
+%
+\oo{Furthermore, min-max form -- free adversarial training}.
 
 \subsection{Hardness Manipulation}
+
+Given an anchor image $X_a$, we sample a positive image $X_p^S$ (in the same
+class as the anchor) and a negative image $X_n^S$ (in different class as the
+anchor) with a certain sampling strategy (\eg, semi-hard~\cite{facenet}).
+%
+For convenience we call this triplet as ``source triplet''.
+%
+Then its \emph{hardness} is defined as
+$H(X_a,X_p^S,X_n^S)=d_\phi(X_a,X_p^S)-d_\phi(X_a,X_n^S)$, which is an internal
+part of the triplet loss.
+
+In the traditional min-max adversarial training setting~\cite{madry}, the inner
+``max'' problem should maximize $H(X_a,X_p^S,X_n^S)$ and hence maximize the triplet
+loss.
+%
+However, existing defense methods~\cite{advorder,robrank} refrain from adopting
+such paradigm because the model will quickly collapse with excessively hard
+triplets~\cite{facenet}, and adopt relatively weak adversaries instead
+(inefficient in gaining robustness).
 

### 2021-10-06 fat-attempt-1.tex
move

\begin{table*}
\resizebox{1.0\linewidth}{!}{
\begin{tabular}{|c|c|c|c|c|cccc|ccccc|ccccc|c|}
\hline
dataset & model & loss & num\_rep & comment & \multicolumn{1}{c|}{R1} & \multicolumn{1}{c|}{R2} & \multicolumn{1}{c|}{mAP} & NMI & \multicolumn{1}{c|}{CA+} & \multicolumn{1}{c|}{CA-} & \multicolumn{1}{c|}{QA+} & \multicolumn{1}{c|}{QA-} & TMA & \multicolumn{1}{c|}{ES:D} & \multicolumn{1}{c|}{ES:R} & \multicolumn{1}{c|}{LTM} & \multicolumn{1}{c|}{GTM} & GTT & ERS\tabularnewline
\hline
\hline
fashion & rc2f2fatamd & tripletN & 1 & want delta & 84.0 & 90.6 & 78.7 & 75.3 & 3.9 & 69.3 & 7.4 & 81.7 & 0.960 & 0.959 & 19.8 & 8.1 & 12.1 & 0.0 & 16.8\tabularnewline
\hline
 &  &  & 2 & want delta & 82.7 & 89.7 & 75.9 & 73.7 & 15.1 & 35.6 & 23.4 & 48.0 & 0.905 & 0.598 & 9.4 & 27.9 & 17.9 & 0.0 & 32.8\tabularnewline
\hline
 &  &  & 4 & want delta & 80.3 & 88.4 & 73.5 & 71.7 & 20.7 & 27.8 & 29.7 & 37.6 & 0.920 & 0.345 & 31.0 & 29.5 & 20.1 & 0.0 & 40.7\tabularnewline
\hline
 &  &  & 8 & want delta & 79.1 & 87.1 & 70.7 & 68.7 & 23.3 & 25.2 & 31.8 & 29.8 & 0.925 & 0.225 & 44.6 & 26.2 & 25.3 & 0.0 & 44.7\tabularnewline
\hline
 & rc2f2fatnone &  & 1 & zero delta & 87.8 & 92.9 & 83.2 & 79.8 & 0.7 & 98.6 & 0.2 & 96.5 & 0.994 & 1.548 & 0.0 & 1.4 & 7.2 & 0.0 & 3.9\tabularnewline
\hline
 &  &  & 2 & zero delta & 85.8 &  &  &  &  &  &  &  &  &  &  &  &  &  & \tabularnewline
\hline
 &  &  & 4 & zero delta & 84.7 & 91.0 & 79.0 & 75.4 & 0.8 & 93.9 & 0.3 & 91.8 & 0.994 & 1.435 & 1.2 & 3.8 & 14.8 & 0.0 & 6.5\tabularnewline
\hline
 &  &  & 8 & zero delta & 81.0 &  &  &  &  &  &  &  &  &  &  &  &  &  & \tabularnewline
\hline
cub & rres18fatnone & tripletN & 1 & zero delta & 52.9 & 64.4 & 33.4 & 59.5 & 0.1 & 100.0 & 0.1 & 99.9 & 0.882 & 1.797 & 0.0 & 0.0 & 20.1 & 0.0 & 4.3\tabularnewline
\hline
 & rres18fatamd & tripletN & 1 & wants delta & 51.5 & 63.2 & 32.7 & 59.8 & 0.0 & 100.0 & 0.2 & 99.7 & 0.886 & 1.783 & 0.0 & 0.0 & 18.0 & 0.0 & 4.1\tabularnewline
\hline
 &  &  & 2 &  & 46.0 & 56.8 & 27.9 & 53.8 & 1.3 & 93.7 & 0.7 & 92.8 & 0.915 & 1.009 & 1.2 & 0.1 & 17.2 & 0.0 & 9.4\tabularnewline
\hline
 &  &  & 4 &  & Coll &  &  &  &  &  &  &  &  &  &  &  &  &  & \tabularnewline
\hline
 &  &  & 8 &  & Coll &  &  &  &  &  &  &  &  &  &  &  &  &  & \tabularnewline
\hline
 & rres18fatamdsemi & tripletN & 4 & decay0.5 & 44.1 & 55.6 & 26.1 & 53.1 & 1.5 & 92.3 & 0.9 & 91.3 & 0.916 & 1.004 & 1.3 & 0.2 & 17.2 & 0.0 & 9.8\tabularnewline
\hline
 & (too weak) &  & 8 & decay0.25 & omitted &  &  &  &  &  &  &  &  &  &  &  &  &  & \tabularnewline
\hline
 & (too weak) &  & 8 & decay0.0 & 48.7 & 60.6 & 29.0 & 56.3 & 0.1 & 100.0 & 0.3 & 99.5 & 0.895 & 1.733 & 0.0 & 0.0 & 16.8 & 0.0 & 4.2\tabularnewline
\hline
\end{tabular}
}
\caption{(freeze) FAT attempt \#1 debugging and sanity. This version seeks
for universal perturbation for increasing E\_x{[}Loss{]} as much as
possible.}
\end{table*}

### 2021-10-06 introplot.py
introplot.py

@@ -1,0 +1,84 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import rich
+c = rich.get_console()
+
+data = {
+        #'N/A': (53.9, 1.0, 3.8),
+        #'EST': (8.5, 33.0, 5.3),
+        'ACT': (
+            (27.5, 28.6, 33.3),
+            (33.0, 17.0, 8.0),
+            (33.9, 34.7, 27.3),
+            ),
+        'amdsemi': (
+            (25.6, 25.1, 28.0),
+            (33.0, 17.0, 8.0),
+            (38.0, 36.6, 33.5),
+            ),
+        'amdsemi+aap0': (26.2, 9.0, 40.0),
+        'hml2rm': (27.4, 9.0, 32.9),
+        'hml2rmi': (25.2, 9.0, 39.8),
+        }
+
+plt.figure()
+
+plt.subplot(1,2,1)
+for (name, (r1, cost, ers)) in data.items():
+    c.print(name, r1, cost, ers)
+
+    color = 'k'
+    if name == 'EST':
+        color = 'b'
+    if name == 'ACT':
+        color = 'r'
+    plt.plot(cost, ers, f'-{color}o')
+    if isinstance(cost, float):
+        plt.annotate(name, xy=(cost, ers))
+    elif isinstance(cost, tuple):
+        plt.annotate(name, xy=(cost[0], ers[0]))
+plt.xlabel('Training Cost')
+plt.ylabel('Robustness (ERS)')
+plt.xscale('log', base=2)
+#plt.axis('equal')
+
+#plt.subplot(2,2,2)
+#for (name, (r1, cost, ers)) in data.items():
+#    c.print(name, r1, cost, ers)
+#
+#    color = 'k'
+#    if name == 'EST':
+#        color = 'b'
+#    if name == 'ACT':
+#        color = 'r'
+#    plt.plot(cost, r1, f'-{color}o')
+#    if isinstance(cost, float):
+#        plt.annotate(name, xy=(cost, r1))
+#    elif isinstance(cost, tuple):
+#        plt.annotate(name, xy=(cost[0], r1[0]))
+#plt.xlabel('Training Cost')
+#plt.ylabel('Recall@1 (R@1)')
+#plt.xscale('log', base=2)
+
+
+plt.subplot(1,2,2)
+for (name, (r1, cost, ers)) in data.items():
+    c.print(name, r1, cost, ers)
+
+    color = 'k'
[…]

### 2021-10-06 introplot.py
introplot.py

@@ -80,5 +80,5 @@ plt.ylabel('Recall@1 (R@1)')
 #plt.axis('equal')
 
 
-plt.tight_layout()
+#plt.tight_layout()
 plt.show()

### 2021-10-06 introplot.py
introplot.py: transpose subplot 2

@@ -70,13 +70,13 @@ for (name, (r1, cost, ers)) in data.items():
         color = 'b'
     if name == 'ACT':
         color = 'r'
-    plt.plot(ers, r1, f'-{color}o')
+    plt.plot(r1, ers, f'-{color}o')
     if isinstance(ers, float):
-        plt.annotate(name, xy=(ers, r1))
+        plt.annotate(name, xy=(r1, ers))
     elif isinstance(ers, tuple):
-        plt.annotate(name, xy=(ers[0], r1[0]))
-plt.xlabel('Robustness (ERS)')
-plt.ylabel('Recall@1 (R@1)')
+        plt.annotate(name, xy=(r1[0], ers[0]))
+plt.ylabel('Robustness (ERS)')
+plt.xlabel('Recall@1 (R@1)')
 #plt.axis('equal')
 
 

### 2021-10-06 introplot.py
py

@@ -7,9 +7,9 @@ data = {
         #'N/A': (53.9, 1.0, 3.8),
         #'EST': (8.5, 33.0, 5.3),
         'ACT': (
-            (27.5, 28.6, 33.3),
-            (33.0, 17.0, 8.0),
-            (33.9, 34.7, 27.3),
+            (27.5, 28.6, 33.3, 38.4),
+            (33.0, 17.0, 8.0, 5.0),
+            (33.9, 34.7, 27.3, 13.9),
             ),
         'amdsemi': (
             (25.6, 25.1, 28.0),
@@ -77,6 +77,7 @@ for (name, (r1, cost, ers)) in data.items():
         plt.annotate(name, xy=(r1[0], ers[0]))
 plt.ylabel('Robustness (ERS)')
 plt.xlabel('Recall@1 (R@1)')
+plt.gca().invert_xaxis()
 #plt.axis('equal')
 
 

### 2021-10-06 appendix.tex
tex

--- 2021-10-04 latex/appendix.tex
@@
 		\[
-			(1-\frac{l_{t-1}|_0^{U_L}}{U_L}) \times U_H
+			\big(1-\frac{\text{Clip}_0^{U_L}[l_{t-1}]}{U_L} \big)\times U_H
 		\]
@@
 		instance, \[
-			L_{loosen}(a,p,n)=L_{base}(a,p,n)+\lambda_{1}L(a,\tilde{a},p)+\lambda_{2}L_{triplet}(a,\tilde{a},n)
+			L=L_{base}(a,p,n)+\lambda_{1}L(a,\tilde{a},p)+\lambda_{2}L_{triplet}(a,\tilde{a},n)
 		\] where the $L_{base}$ can be either $L_{triplet}$, $L_{rest}$, or
@@
 
-	\item ? can we learn a good destination distribution? | too
-		complicated? not necessary currently.
-
 	\item 1. APGD as the optimization algorithm? | postpone
-
-	\item 1. ? mixing amdsemi and act for adversarial training. They are good
-		at different aspects.
 
@@
 
-	\item [?] Combine and even better. | Mixing ACT and AMDsemi does result
+\end{itemize}
+
+\subsection{Lessons Learned}
+
+\input{direct-amd.tex}
+
+\input{sort-hardness.tex}
+
+\input{fat-attempt-1.tex}
+
+\input{amdsemi.tex}
+
+\begin{enumerate}
+
+	\item [\cmark] HM method: KL, L2, L2+threshold. L2 is $\|H_s-H_d\|^2$.
+		In L2 the adversarial sample may vibrate around the boundary due to
+		the minimum perturbation precision limit of $1/255$. The attacker
+		may turn to reduce the hardness when $H_s>H_d$. We don't want that
+		to happen.  L2+threshold (ET) is $\|\min(0,H_s-H_d)\|^2$. In this case,
+		the adversarial example will not vibrate around the boundary, and will
+		automatically stop when $H_s>H_d$.
+
+	\item [\xmark] mixing amdsemi and act for adversarial training. They are good
+		at different aspects. | not necessary for now. harms novelty.
+
+	\item [\xmark] Combine and even better. | Mixing ACT and AMDsemi does result
 		in clearly better results. It's on par with AMDsemi. Are they really
@@
 
-\end{itemize}
-
-\subsection{Done, Discarded or Rejected}
-
-\begin{enumerate}
+	\item [\xmark] can we learn a good destination distribution? | too
+		complicated? not necessary currently.
 

### 2021-10-06 introplot.py
introplot

@@ -21,9 +21,9 @@ data = {
         'hml2rmi': (25.2, 9.0, 39.8),
         }
 
-plt.figure()
+plt.figure(figsize=[10.8, 4.8])
 
-plt.subplot(1,2,1)
+ax = plt.subplot(1,2,1)
 for (name, (r1, cost, ers)) in data.items():
     c.print(name, r1, cost, ers)
 
@@ -39,8 +39,14 @@ for (name, (r1, cost, ers)) in data.items():
         plt.annotate(name, xy=(cost[0], ers[0]))
 plt.xlabel('Training Cost')
 plt.ylabel('Robustness (ERS)')
-plt.xscale('log', base=2)
+plt.xscale('log', base=2, basex=2)
 #plt.axis('equal')
+#plt.axis('square')
+
+ax.annotate('↖ Better', xy=(0.05, 0.95), xycoords='axes fraction',
+        bbox=dict(boxstyle="round,pad=0.3", fc="white", ec="k", lw=2))
+ax.annotate('↘ Worse', xy=(0.80, 0.05), xycoords='axes fraction',
+        bbox=dict(boxstyle="round,pad=0.3", fc="white", ec="k", lw=2))
 
 #plt.subplot(2,2,2)
 #for (name, (r1, cost, ers)) in data.items():
@@ -61,7 +67,7 @@ plt.xscale('log', base=2)
 #plt.xscale('log', base=2)
 
 
-plt.subplot(1,2,2)
+ax = plt.subplot(1,2,2)
 for (name, (r1, cost, ers)) in data.items():
     c.print(name, r1, cost, ers)
 
@@ -79,7 +85,13 @@ plt.ylabel('Robustness (ERS)')
 plt.xlabel('Recall@1 (R@1)')
 plt.gca().invert_xaxis()
 #plt.axis('equal')
+#plt.axis('square')
 
+ax.annotate('↖ Better', xy=(0.05, 0.95), xycoords='axes fraction',
+        bbox=dict(boxstyle="round,pad=0.3", fc="white", ec="k", lw=2))
+ax.annotate('↘ Worse', xy=(0.80, 0.05), xycoords='axes fraction',
+        bbox=dict(boxstyle="round,pad=0.3", fc="white", ec="k", lw=2))
 
 #plt.tight_layout()
-plt.show()
+#plt.show()
+plt.savefig('introplot.svg')

### 2021-10-06 introplot.py
svg

@@ -17,7 +17,11 @@ data = {
             (38.0, 36.6, 33.5),
             ),
         'amdsemi+aap0': (26.2, 9.0, 40.0),
-        'hml2rm': (27.4, 9.0, 32.9),
+        'hml2rm': (
+            (27.4, 29.0),
+            (9.0, 5.0),
+            (32.9, 30.8),
+            ),
         'hml2rmi': (25.2, 9.0, 39.8),
         }
 

### 2021-10-06 robdml.tex
move
introplot
tex

--- 2021-10-05 latex/robdml.tex
@@
 \newcommand{\uline}[1]{\underline{#1}}
+
+%\DeclareMathOperator*{\argmax}{arg\,max}
+%\DeclareMathOperator*{\argmin}{arg\,min}
 
@@
 \begin{figure}[t]
-	\includegraphics[width=1.0\columnwidth]{introdiag.pdf}
+	\includegraphics[width=1.0\columnwidth]{introplot.pdf}
 	\caption{\oo{Performance plot with aligned conditions.
@@
 %
-For convenience we call this triplet as ``source triplet''.
+% For convenience we call this triplet as ``source triplet''.
 %
@@
 part of the triplet loss.
+%
+For convenience we call this as ``source hardness'', denoted as $H_S$.
 
@@
 (inefficient in gaining robustness).
+
+In this paper, we argue that the hardness of triplet matters in adversarial
+training for DML.
+%
+The model does not collapse with EST or ACT because the expectation of hardness,
+\ie, $E[H]$ will be close to zero.
+%
+While the variance $\text{Var}[H]$ for EST is higher, and that for ACT is lower.
+
+Instead of directly maximizing the source hardness, we propose to stop the
+maximization process when the adversarial examples reach a certain level of
+hardness in order to avoid model collapse.
+%
+Based on the same anchor image $X_a$, we sample another positive image $X_p^D$
+and negative image $X_n^D$ with a different triplet sampling strategy, and
+we call its hardness as ``destination hardness'', denoted as $H_D$.
+
+Then, we want change (increase)
+the hardness level from $H_S$ into $H_D$, by finding adversarial examples for
+$(X_a, X_p^S, X_n^S)$.
+%
+We denote the the hardness of adversarial examples as
+$\tilde{H}_S=H(X_a{+}r_a, X_p^S{+}r_p, X_n^S{+}r_n)$.
+%
+This is named as \emph{Hardness Manipulation} (HM), which is implemented as 
+follows:
+%
+\begin{equation}
+	%
+	\argmin_{r_a,r_p,r_n} \|\min(0, \tilde{H}_S-H_D)\|^2.
+	%
+\end{equation}
 

### 2021-10-06 robdml.tex
tex

@@
 
-Then, we want change (increase)
-the hardness level from $H_S$ into $H_D$, by finding adversarial examples for
-$(X_a, X_p^S, X_n^S)$.
+Then, we want change (increase) the hardness level from $H_S$ into $H_D$, by
+finding adversarial examples for $(X_a, X_p^S, X_n^S)$.
 %
-We denote the the hardness of adversarial examples as
-$\tilde{H}_S=H(X_a{+}r_a, X_p^S{+}r_p, X_n^S{+}r_n)$.
+Note, it is not expected to lower the hardness during the attack, namely
+$E[H_D]$ should be greater or equal to $E[H_S]$.
+%
+We denote the the hardness of adversarial examples as $\tilde{H}_S=H(X_a{+}r_a,
+X_p^S{+}r_p, X_n^S{+}r_n)$.
 %
@@
 	%
+	\bar{r}_a, \bar{r}_p, \bar{r}_n =
 	\argmin_{r_a,r_p,r_n} \|\min(0, \tilde{H}_S-H_D)\|^2.
 	%
+	\label{eq:hm}
+	%
 \end{equation}
+%
+The $\min(0,\cdot)$ part in \cref{eq:hm} truncates the gradient when $H_S>H_D$,
+preventing $H_S$ from being reduced.
+%
+The optimization problem can be solved by projected gradient
+descent~\cite{madry}.
+%
+And the resulting adversarial examples are used for adversarially training
+the DML model:
+%
+$L_\text{trip}(\phi(X_a+\bar{r}_a), \phi(X_p^S+\bar{r}_p),
+\phi(X_n^S+\bar{r}_n))$.
 

### 2021-10-06 introplot.py
svg

@@ -23,6 +23,7 @@ data = {
             (32.9, 30.8),
             ),
         'hml2rmi': (25.2, 9.0, 39.8),
+        'hmetrm': (34.9, 5.0, 25.6),
         }
 
 plt.figure(figsize=[10.8, 4.8])

### 2021-10-06 introplot.py
py

@@ -7,9 +7,9 @@ data = {
         #'N/A': (53.9, 1.0, 3.8),
         #'EST': (8.5, 33.0, 5.3),
         'ACT': (
-            (27.5, 28.6, 33.3, 38.4),
-            (33.0, 17.0, 8.0, 5.0),
-            (33.9, 34.7, 27.3, 13.9),
+            (27.5, 28.6, 33.3, 38.4, 46.5),
+            (33.0, 17.0, 8.0, 5.0, 3.0),
+            (33.9, 34.7, 27.3, 13.9, 5.8),
             ),
         'amdsemi': (
             (25.6, 25.1, 28.0),

### 2021-10-06 robdml.tex
tex
u

@@
 	%
-	\bar{r}_a, \bar{r}_p, \bar{r}_n =
-	\argmin_{r_a,r_p,r_n} \|\min(0, \tilde{H}_S-H_D)\|^2.
+	\bar{r}_a, \bar{r}_p, \bar{r}_n = \argmin_{r_a,r_p,r_n} \|\min(0,
+	\tilde{H}_S-H_D)\|^2.
 	%
@@
 The $\min(0,\cdot)$ part in \cref{eq:hm} truncates the gradient when $H_S>H_D$,
-preventing $H_S$ from being reduced.
+automatically stopping the optimization.
+%
+This is because $H_S$ will be reduced once greater than $H_D$ in standard Mean
+Square Error.
 %
@@
 %
-And the resulting adversarial examples are used for adversarially training
-the DML model:
+And the resulting adversarial examples are used for adversarially training the
+DML model:
 %
@@
 \subsection{Gradual Adversary}
+
+During the training process, the strength of adversary will gradually decrease,
+because the expectation of the destination hardness $E[H_D]$ is expected to
+decrease with a model being trained.
+
+\[
+	\big(1-\frac{\text{Clip}_0^{U_L}[l_{t-1}]}{U_L} \big)\times
+	(U_H + (H_D - H_S).relu())
+\]
 

### 2021-10-07 introplot.py
lyx

@@ -11,19 +11,23 @@ data = {
             (33.0, 17.0, 8.0, 5.0, 3.0),
             (33.9, 34.7, 27.3, 13.9, 5.8),
             ),
-        'amdsemi': (
-            (25.6, 25.1, 28.0),
-            (33.0, 17.0, 8.0),
-            (38.0, 36.6, 33.5),
+        #'amdsemi': (
+        #    (25.6, 25.1, 28.0),
+        #    (33.0, 17.0, 8.0),
+        #    (38.0, 36.6, 33.5),
+        #    ),
+        #'amdsemi+aap0': (26.2, 9.0, 40.0),
+        #'hml2rm': (
+        #    (27.4, 29.0),
+        #    (9.0, 5.0),
+        #    (32.9, 30.8),
+        #    ),
+        #'hml2rmi': (25.2, 9.0, 39.8),
+        'hmetrm': (
+            (28.3, 34.9),
+            (9.0, 5.0,),
+            (37.2, 25.6),
             ),
-        'amdsemi+aap0': (26.2, 9.0, 40.0),
-        'hml2rm': (
-            (27.4, 29.0),
-            (9.0, 5.0),
-            (32.9, 30.8),
-            ),
-        'hml2rmi': (25.2, 9.0, 39.8),
-        'hmetrm': (34.9, 5.0, 25.6),
         }
 
 plt.figure(figsize=[10.8, 4.8])
@@ -33,10 +37,8 @@ for (name, (r1, cost, ers)) in data.items():
     c.print(name, r1, cost, ers)
 
     color = 'k'
-    if name == 'EST':
-        color = 'b'
     if name == 'ACT':
-        color = 'r'
+        color = 'm'
     plt.plot(cost, ers, f'-{color}o')
     if isinstance(cost, float):
         plt.annotate(name, xy=(cost, ers))
@@ -77,10 +79,8 @@ for (name, (r1, cost, ers)) in data.items():
     c.print(name, r1, cost, ers)
 
     color = 'k'
-    if name == 'EST':
-        color = 'b'
     if name == 'ACT':
-        color = 'r'
+        color = 'm'
     plt.plot(r1, ers, f'-{color}o')
     if isinstance(ers, float):
         plt.annotate(name, xy=(r1, ers))

### 2021-10-07 introplot.py
lyx

@@ -24,9 +24,9 @@ data = {
         #    ),
         #'hml2rmi': (25.2, 9.0, 39.8),
         'hmetrm': (
-            (28.3, 34.9),
-            (9.0, 5.0,),
-            (37.2, 25.6),
+            (27.1, 28.3, 34.9),
+            (17.0, 9.0, 5.0,),
+            (40.0, 37.2, 25.6),
             ),
         }
 

### 2021-10-07 introplot.py
lyx

@@ -24,9 +24,9 @@ data = {
         #    ),
         #'hml2rmi': (25.2, 9.0, 39.8),
         'hmetrm': (
-            (27.1, 28.3, 34.9),
-            (17.0, 9.0, 5.0,),
-            (40.0, 37.2, 25.6),
+            (27.1, 28.3, 34.9, 39.2),
+            (17.0, 9.0, 5.0, 3.0),
+            (40.0, 37.2, 25.6, 14.0),
             ),
         }
 

### 2021-10-07 introplot.py
svg

@@ -3,6 +3,12 @@ import matplotlib.pyplot as plt
 import rich
 c = rich.get_console()
 
+plt.rcParams['font.family'] = 'serif'
+#plt.rcParams['font.serif'] = 'Times New Roman; Noto Sans'
+plt.rcParams['font.serif'] = 'FreeSerif'
+#plt.rcParams['font.serif'] = 'Linux Libertine O'
+plt.rcParams['font.size'] = 12
+
 data = {
         #'N/A': (53.9, 1.0, 3.8),
         #'EST': (8.5, 33.0, 5.3),
@@ -46,14 +52,16 @@ for (name, (r1, cost, ers)) in data.items():
         plt.annotate(name, xy=(cost[0], ers[0]))
 plt.xlabel('Training Cost')
 plt.ylabel('Robustness (ERS)')
-plt.xscale('log', base=2, basex=2)
+plt.xscale('log', base=2)
 #plt.axis('equal')
 #plt.axis('square')
 
-ax.annotate('↖ Better', xy=(0.05, 0.95), xycoords='axes fraction',
-        bbox=dict(boxstyle="round,pad=0.3", fc="white", ec="k", lw=2))
-ax.annotate('↘ Worse', xy=(0.80, 0.05), xycoords='axes fraction',
-        bbox=dict(boxstyle="round,pad=0.3", fc="white", ec="k", lw=2))
+ax.annotate('↖ Better', xy=(0.04, 0.92), xycoords='axes fraction',
+        bbox=dict(boxstyle="round,pad=0.3", fc="white", ec="k", lw=2),
+        size=14)
+ax.annotate('↘ Worse', xy=(0.77, 0.06), xycoords='axes fraction',
+        bbox=dict(boxstyle="round,pad=0.3", fc="white", ec="k", lw=2),
+        size=14)
 
 #plt.subplot(2,2,2)
 #for (name, (r1, cost, ers)) in data.items():
@@ -87,15 +95,17 @@ for (name, (r1, cost, ers)) in data.items():
     elif isinstance(ers, tuple):
         plt.annotate(name, xy=(r1[0], ers[0]))
 plt.ylabel('Robustness (ERS)')
-plt.xlabel('Recall@1 (R@1)')
+plt.xlabel('Recall@1')
 plt.gca().invert_xaxis()
 #plt.axis('equal')
 #plt.axis('square')
 
[…]

### 2021-10-07 introplot.py
svg

@@ -7,7 +7,7 @@ plt.rcParams['font.family'] = 'serif'
 #plt.rcParams['font.serif'] = 'Times New Roman; Noto Sans'
 plt.rcParams['font.serif'] = 'FreeSerif'
 #plt.rcParams['font.serif'] = 'Linux Libertine O'
-plt.rcParams['font.size'] = 12
+plt.rcParams['font.size'] = 14
 
 data = {
         #'N/A': (53.9, 1.0, 3.8),

### 2021-10-07 appendix.tex
tex

@@
 
-	\item [*] Re-design Gradual Adversary (Linear Addition)
+	\item [GA] Re-design Gradual Adversary (Linear Addition)
 		\[
@@
 
-	\item [!] difference between EST, ACT, AMD/ AMDsemi.
+	\item [M] difference between EST, ACT, AMD/ AMDsemi.
 		Other methods (than HM) cannot effectively learn from the strongest
@@
 
-	\item [?] does the new generic HM work under FAT?
-		Previous FAT leads to collapse because (even if in the amdsemi +fat
-		experiment due to implementation issue) the delta is going to be universal
-		so that for every input $x$ it will increase $H[L(x)]$ as much as possible.
-		This is too prone to lead to collpase. Can we reuse the gradient for 
-		Hardness Manipulation then? We linearly scale down the delta?
-		We want to minimize $E[|H_{src}(x)-H_{dst}(x)|]$ (to a specified hardness).
-
-	\item [?] benchmark other metric learning loss functions for adversarial
-		training. Can HM or GradualAdversary be adopted for other loss functions?
-
-	\item [*] Sampling also matters in adversarial training for deep metric learning.
+	\item [M] Sampling also matters in adversarial training for deep metric learning.
 
@@
 
-	\item [*] 7-step PGD (as well as 16-step PGD) and better aligned comparison:
-		compare when these methods reach similar retrieval performance.
-		Meanwhile we can do experiments much faster.
-
-	\item Adversarial training (does not allow any distance moving) may
+	\item [ICS] Adversarial training (does not allow any distance moving) may
 		encourage collapse (a trivial solution to the requirement). What if we
@@
 
-	\item [?] adversarial training that does not allow embedding move may
+	\item [ICS] adversarial training that does not allow embedding move may
 		encourage model collapse. Maybe we just apply some loosened restrction
@@
 
-	\item ?  what about other types of metric learining loss functions? |
+	\item [?] verify model collapse. are the parameters really going towards zero?
+
+	\item [T] does the new generic HM work under FAT?
+		Previous FAT leads to collapse because (even if in the amdsemi +fat
+		experiment due to implementation issue) the delta is going to be universal
+		so that for every input $x$ it will increase $H[L(x)]$ as much as possible.
+		This is too prone to lead to collpase. Can we reuse the gradient for 
+		Hardness Manipulation then? We linearly scale down the delta?
+		We want to minimize $E[|H_{src}(x)-H_{dst}(x)|]$ (to a specified hardness).
+
+	\item [T] APGD as the optimization algorithm? | postpone
+
+	\item [T] benchmark other metric learning loss functions for adversarial
+		training. Can HM or GradualAdversary be adopted for other loss functions?
+
+	\item [T]  what about other types of metric learining loss functions? |
 		investigating (we first make the most classical method work)
-
-	\item ?  effectiveness of AMD Semi is to be verified. | as effective
-		as ACT, reaches slightly higher ERS. But performs worse than ACT on
-		some attacks, while performs better one some other attacks. | needs to
-		be interpreted.
-
-	\item 1. APGD as the optimization algorithm? | postpone
-
-	\item verify model collapse
 
@@
 \begin{enumerate}
+
+	\item [-] effectiveness of AMD Semi is to be verified. | as effective
+		as ACT, reaches slightly higher ERS. But performs worse than ACT on
+		some attacks, while performs better one some other attacks. | needs to
+		be interpreted.
+
+	\item [\cmark] 7-step PGD (as well as 16-step PGD) and better aligned comparison:
+		compare when these methods reach similar retrieval performance.
+		Meanwhile we can do experiments much faster.
 

### 2021-10-07 introplot.py
lyx

@@ -44,7 +44,7 @@ for (name, (r1, cost, ers)) in data.items():
 
     color = 'k'
     if name == 'ACT':
-        color = 'm'
+        color = 'b'
     plt.plot(cost, ers, f'-{color}o')
     if isinstance(cost, float):
         plt.annotate(name, xy=(cost, ers))
@@ -88,7 +88,7 @@ for (name, (r1, cost, ers)) in data.items():
 
     color = 'k'
     if name == 'ACT':
-        color = 'm'
+        color = 'b'
     plt.plot(r1, ers, f'-{color}o')
     if isinstance(ers, float):
         plt.annotate(name, xy=(r1, ers))

### 2021-10-07 tab-desth.tex
tex

\begin{table}
\resizebox{\columnwidth}{!}{
\begin{tabular}{c|cc|cc|cc|cc|cc}

	\toprule

\multirow{2}{*}{\backslashbox{$H_S$}{$H_D$}} & \multicolumn{2}{c|}{Random} & \multicolumn{2}{c|}{Semihard} & \multicolumn{2}{c|}{Softhard} & \multicolumn{2}{c|}{Distance} & \multicolumn{2}{c|}{Hardest}\tabularnewline
\cline{2-11} \cline{3-11} \cline{4-11} \cline{5-11} \cline{6-11} \cline{7-11} \cline{8-11} \cline{9-11} \cline{10-11} \cline{11-11} 
 & R@1 & ERS & R@1 & ERS & R@1 & ERS & R@1 & ERS & R@1 & ERS\tabularnewline

	\midrule

Random & \uline{53.9} & \uline{3.8} & 27.4 & 32.9 & \multicolumn{2}{c|}{Collapse} & \multicolumn{2}{c|}{Collapse} & \multicolumn{2}{c|}{Collapse}\tabularnewline
\hline 
Semihard & 46.9 & 4.1 & - & - & \multicolumn{2}{c|}{Collapse} & \multicolumn{2}{c|}{Collapse} & \multicolumn{2}{c|}{Collapse}\tabularnewline
\hline 
Softhard &  &  &  &  & - & - & \multicolumn{2}{c|}{Collapse} & \multicolumn{2}{c|}{Collapse}\tabularnewline
\hline 
Distance &  &  &  &  &  &  & - & - & 52.1 & 4.7\tabularnewline
\hline 
Hardest &  &  &  &  &  &  &  &  & \uline{48.9} & \uline{5.0}\tabularnewline

	\bottomrule
\end{tabular}
}

\caption{Hardness Manipulation: Source hardness v.s. Destination hardness for
amdsemi on CUB Dataset. (R@1, ERS for each cell). Diagonal = does
not attack}
\label{tab:desth}

\end{table}

### 2021-10-07 introplot.py
u

@@ -42,10 +42,10 @@ ax = plt.subplot(1,2,1)
 for (name, (r1, cost, ers)) in data.items():
     c.print(name, r1, cost, ers)
 
-    color = 'k'
     if name == 'ACT':
-        color = 'b'
-    plt.plot(cost, ers, f'-{color}o')
+        plt.plot(cost, ers, f'-o', 'color', 'tab:blue')
+    else:
+        plt.plot(cost, ers, f'-ok')
     if isinstance(cost, float):
         plt.annotate(name, xy=(cost, ers))
     elif isinstance(cost, tuple):
@@ -86,10 +86,10 @@ ax = plt.subplot(1,2,2)
 for (name, (r1, cost, ers)) in data.items():
     c.print(name, r1, cost, ers)
 
-    color = 'k'
     if name == 'ACT':
-        color = 'b'
-    plt.plot(r1, ers, f'-{color}o')
+        plt.plot(r1, ers, f'-o', 'color', 'tab:blue')
+    else:
+        plt.plot(r1, ers, '-ok')
     if isinstance(ers, float):
         plt.annotate(name, xy=(r1, ers))
     elif isinstance(ers, tuple):

### 2021-10-07 introplot.py
svg

@@ -2,32 +2,17 @@ import numpy as np
 import matplotlib.pyplot as plt
 import rich
 c = rich.get_console()
-
 plt.rcParams['font.family'] = 'serif'
-#plt.rcParams['font.serif'] = 'Times New Roman; Noto Sans'
 plt.rcParams['font.serif'] = 'FreeSerif'
-#plt.rcParams['font.serif'] = 'Linux Libertine O'
 plt.rcParams['font.size'] = 14
 
 data = {
-        #'N/A': (53.9, 1.0, 3.8),
-        #'EST': (8.5, 33.0, 5.3),
         'ACT': (
             (27.5, 28.6, 33.3, 38.4, 46.5),
             (33.0, 17.0, 8.0, 5.0, 3.0),
             (33.9, 34.7, 27.3, 13.9, 5.8),
             ),
-        #'amdsemi': (
-        #    (25.6, 25.1, 28.0),
-        #    (33.0, 17.0, 8.0),
-        #    (38.0, 36.6, 33.5),
-        #    ),
         #'amdsemi+aap0': (26.2, 9.0, 40.0),
-        #'hml2rm': (
-        #    (27.4, 29.0),
-        #    (9.0, 5.0),
-        #    (32.9, 30.8),
-        #    ),
         #'hml2rmi': (25.2, 9.0, 39.8),
         'hmetrm': (
             (27.1, 28.3, 34.9, 39.2),
@@ -43,9 +28,9 @@ for (name, (r1, cost, ers)) in data.items():
     c.print(name, r1, cost, ers)
 
     if name == 'ACT':
-        plt.plot(cost, ers, f'-o', 'color', 'tab:blue')
+        plt.plot(cost, ers, f'-o', color='tab:blue')
     else:
-        plt.plot(cost, ers, f'-ok')
+        plt.plot(cost, ers, f'-o', color='k')
     if isinstance(cost, float):
         plt.annotate(name, xy=(cost, ers))
     elif isinstance(cost, tuple):
@@ -87,15 +72,15 @@ for (name, (r1, cost, ers)) in data.items():
     c.print(name, r1, cost, ers)
 
     if name == 'ACT':
-        plt.plot(r1, ers, f'-o', 'color', 'tab:blue')
+        plt.plot(r1, ers, f'-o', color='tab:blue')
     else:
-        plt.plot(r1, ers, '-ok')
+        plt.plot(r1, ers, f'-o', color='k')
[…]

### 2021-10-07 robdml.tex
tex

@@
 \newcommand{\uline}[1]{\underline{#1}}
+\usepackage{slashbox}
+\usepackage{booktabs}
 
@@
 %
-	L_\text{trip}(\va, \vp, \vn; \gamma) = \max(0, d(\va, \vp) - d(\va, \vn) +
+	L_\text{T}(\va, \vp, \vn; \gamma) = \max(0, d(\va, \vp) - d(\va, \vn) +
 	\gamma),
@@
 locations, \ie,
-$L_\text{EST}=L_\text{trip}(\tilde{\va},\tilde{\vp},\tilde{\vn};\gamma)$ where
+$L_\text{EST}=L_\text{T}(\tilde{\va},\tilde{\vp},\tilde{\vn};\gamma)$ where
 $\tilde{\va}=\phi(X+r^*)$, $r^*=\arg\max_{r}d_\phi(X+r, X)$.
@@
 positive and negative sample, and enforces the model to separate them apart,
-\ie, $L_\text{ACT}=L_\text{trip}(\va, \overrightarrow{\vp},
+\ie, $L_\text{ACT}=L_\text{T}(\va, \overrightarrow{\vp},
 \overleftarrow{\vn};\gamma)$, where $[\overrightarrow{\vp},\overleftarrow{\vn}]
@@
 \subsection{Hardness Manipulation}
+
+\oo{[illust fig]}
 
@@
 %
-$L_\text{trip}(\phi(X_a+\bar{r}_a), \phi(X_p^S+\bar{r}_p),
+$L_\text{T}(\phi(X_a+\bar{r}_a), \phi(X_p^S+\bar{r}_p),
 \phi(X_n^S+\bar{r}_n))$.
@@
 \subsection{Gradual Adversary}
+
+\oo{[illust fig]}
 
@@
 
-\subsection{Intra-Class Structure}
+\subsection{Intra-Class Structure Constraint}
 
-\subsection{\oo{Free Adversarial DML?}}
-
-\subsection{\oo{Benchmark other DML loss?}}
+\oo{[illust fig]}
 
@@
 
-\textbf{Dataset.}
+To validate the effectiveness of our proposed defense, we conduct experiments
+on three commonly used DML datasets: CUB-200~\cite{cub200}, Cars-196~\cite{cars196},
+and Stanford-Online-Products (SOP)~\cite{sop}.
+%
+We follow the same experiment setup of the state-of-the-art work~\cite{robrank}
+for ease of comparison.
+%
+The setup is also consistent to standard DML~\cite{revisiting}.
 
-\textbf{Experiment Settings.}
+Specifically, we train a ResNet-18~\cite{resnet} with the output dimension of
+the last layer changed to $N=512$.
+%
+The margin $\gamma$ in triplet loss is set as $0.2$ by default.
+%
+The model is trained with Adam optimizer with learning rate $1.0\times 10^{-3}$
+for $150$ epochs, with mini-batch size set as $112$.
+
+For adversarial training, we adopt the perturbation budget of
+$\varepsilon=8/255$ in infinity norm ($p=\infty$).
+%
+Projected Gradient Descent (PGD)~\cite{madry} is used for creating adversarial
+examples, with a maximum step number set as $\eta=8$ by default.\footnote{
+Instead of $\eta=32$ as in \cite{robrank} in order to control time consumption.}
+%
+Step size for PGD is set as $\alpha=1/255$.
+
+The model performance on benign (\ie, unperturbed) examples is measured in
+Recall@1 (R@1), Recall@2 (R@2), mAP and NMI
+following~\cite{revisiting,robrank}.
+%
+The adversarial robustness of a model is measured in Empirical Robustness Score
+(ERS)~\cite{robrank}, which is a normalized score (the higher the better) from
+an ensemble of existing white-box attacks against DML or their simplified
+white-box counterparts.
+%
+As adversarial training will not cause gradient masking~\cite{obfuscated},
+the performance of white-box attack can be regarded as the upper bound of the
+corresponding black-box attack.
+%
+An adversarially trained DML model that is empirically robust to the ensemble
+is expected to be robust in other scenarios as well.
+
+\oo{Concretely, the ensemble of attack for computing ERS includes.}
+
+\subsection{Selection of Destination Hardness}
+
+\input{tab-desth.tex}
+
+Hardness sorting.
+
+Hardness selection \cref{tab:desth}.
 

### 2021-10-08 introplot.py
lyx

@@ -15,9 +15,9 @@ data = {
         #'amdsemi+aap0': (26.2, 9.0, 40.0),
         #'hml2rmi': (25.2, 9.0, 39.8),
         'hmetrm': (
-            (27.1, 28.3, 34.9, 39.2),
-            (17.0, 9.0, 5.0, 3.0),
-            (40.0, 37.2, 25.6, 14.0),
+            (27.0, 27.1, 28.3, 34.9, 39.2),
+            (33.0, 17.0, 9.0, 5.0, 3.0),
+            (40.3, 40.0, 37.2, 25.6, 14.0),
             ),
         }
 

### 2021-10-08 robdml.tex
tex

@@
 
+In literature, a series of triplet sampling strategies exist, such as random,
+semi-hard~\cite{facenet}, soft-hard[], distance[], and hardest sampling.
+%
+Any of these can be selected for source triplet and destination triplet.
+
+As the samples will not become adversarial once $H_S>H_D$ (zero perturbation in
+this case according to \cref{eq:hm}, an effective combination of source and
+destination sampling strategy should make the expectation of source hardness
+less than the source hardness, \ie, $E[H_S]<E[H_D]$.
+%
+Our empirical observation on $E[H]$ from randomly initialized
+model suggests a sorting of ``random'' $<$ ``semi-hard'' $<$ ``soft-hard'' $<$
+``distance'' $<$ ``hardest''.
+%
+Namely, the source sampling strategy should be ahead of the destination
+sampling strategy in this list.
+
 Hardness sorting.

### 2021-10-08 appendix.tex
tex
u
lyx

@@
 
-	\item [GA] Re-design Gradual Adversary (Linear Addition)
-		\[
-			\big(1-\frac{\text{Clip}_0^{U_L}[l_{t-1}]}{U_L} \big)\times U_H
-		\]
-		Increase $E[H]$ to $E[H]+\alpha U_H$. $E[H]$ is expected to decrease
-		with a well-learned model. So without GA, the strength of adversary
-		will decrease.
+	\item [HM] do we fix the anchor like ACT? | marginal. Queued.
 
@@
 
+	\item [T] Face verification (biometrics) and DML robustness.
+
+	\item [T] Unsup learning with DML robustness.
+
 	\item [T] APGD as the optimization algorithm? | postpone
@@
 \begin{enumerate}
+
+	\item [\xmark] What if we truncate $H_D$. Clamp it with $\min=-\gamma$.
+		| clipping leads to negative effect on fashion-mnist. (ghmetrm 8)
+
+	\item [\xmark] Re-design Gradual Adversary (Linear Addition)
+		\[
+			\big(1-\frac{\text{Clip}_0^{U_L}[l_{t-1}]}{U_L} \big)\times U_H
+		\]
+		Increase $E[H]$ to $E[H]+\alpha U_H$. $E[H]$ is expected to decrease
+		with a well-learned model. So without GA, the strength of adversary
+		will decrease. | Linear GA has a negative effect as observed on
+		Fashion-MNIST.
 

### 2021-10-08 robdml.tex
tex
u

@@
 as image retrieval~\cite{imagesim2} and face recognition~\cite{facenet,domainface}.
-%
+
 Despite the improvements of this field thanks to the advancement of deep neural
@@
 	(3) training cost and robustness for reaching similar r1.}}
+	\label{fig:introplot}
 \end{figure}
@@
 %
-(2) the direct adoptation of Madry's min-max adversarial training~\cite{madry} will easily
+(2) the direct adaptation of Madry's min-max adversarial training~\cite{madry} will easily
 lead to model collapse due to producing very hard sample triplets;
@@
 
-% for problem 1
-\oo{[1. Hardness Manipulation]}
+% inspiration.
+Recall that a DML model is already prone to collapse with very hard but not
+adversarially purturbed sample triplets~\cite{facenet}.
+%
+To overcome this issue, various triplet sampling strategies, such as
+semi-hard~\cite{facenet} and distance~\cite{distance} are proposed to provide
+effective negative examples to facilitate metric learning while avoiding model
+collapse.
+%
+In the classical min-max adversarial training, the adversarial example triplet
+created by maximizing the triplet loss value can incur model collapse more
+easily than unperturbed sample triplets.
+%
+
+In this paper, we propose Hardness Manipulation (HM) to create adversarial
+examples for increasing their hardness towards that of a harder sample triplet.
+%
+%
+%
 Triplet hardness still matters in adversarial training for deep metric
@@
 
-\subsection{Selection of Destination Hardness}
+\subsection{Selection of Source/Destination Hardness}
 
@@
 
-Hardness sorting.
+To figure out an appropriate combination for further experiments, we try
+every possible combination and compare their R@1 and ERS performance, as
+shown in \cref{tab:desth}.
+%
+\oo{The table suggests that}
 
-Hardness selection \cref{tab:desth}.
+\subsection{Comparison with State-of-the-art}
+
+\oo{experiment, 8 step by default}
+Number of PGD Steps $\eta$.
+\cref{fig:introplot}
 
@@
 \label{sec:5}
-
-%1. adversarial training speed.
-
-% PGD-7 PGD-16
 

### 2021-10-08 robdml.tex
tex

@@
 %
-In the classical min-max adversarial training, the adversarial example triplet
-created by maximizing the triplet loss value can incur model collapse more
-easily than unperturbed sample triplets.
+In the typical min-max adversarial training~\cite{madry}, the adversarial
+example triplet created by maximizing the triplet loss value can incur model
+collapse more easily than unperturbed sample triplets.
+%
+But what if we do not maximize the triplet loss value to the theoretical upper
+bound, but merely increase it towards a value that could be caused by
+a known, unperturbed and harder sample triplet?
+
+% HM
+In this paper, we propose Hardness Manipulation (HM) to make adversarially
+training a DML model with triplet loss feasible without model collapse,
+so the model could efficiently learn from a strong adversary.
+%
+First, we sample two triplets, namely ``source triplet'' and ``destination
+triplet'' with the same anchor example but in two different pre-defined
+sampling strategy.
+%
+The ``destination triplet'' is expected to result in a higher loss value.
 %
 
-In this paper, we propose Hardness Manipulation (HM) to create adversarial
+create adversarial
 examples for increasing their hardness towards that of a harder sample triplet.

### 2021-10-08 robdml.tex
tex

@@
 In this paper, we propose Hardness Manipulation (HM) to make adversarially
-training a DML model with triplet loss feasible without model collapse,
-so the model could efficiently learn from a strong adversary.
+training a DML model with triplet loss feasible without model collapse, so the
+model could efficiently learn from a strong adversary.
 %
-First, we sample two triplets, namely ``source triplet'' and ``destination
-triplet'' with the same anchor example but in two different pre-defined
-sampling strategy.
+Assume there are two data triplets, namely ``source triplet'' and ``destination
+triplet'' with the same anchor example, but sampled using different triplet
+sampling strategies.
 %
-The ``destination triplet'' is expected to result in a higher loss value.
+And the ``destination triplet'' is expected to result in a higher loss value
+than another.
 %
+HM aims at creating adversarial examples of the ``source triplet'', that would
+increase the corresponding loss value until that of the unperturbed
+``destination triplet''.
+%
+This can also be interpreted as maximizing the loss value but ``stops early''
+at a certain point.
+%
+The resulting perturbed ``source triplet'' can be used for adversarial
+training of the model.
 

### 2021-10-12 appendix.tex
u
tex

@@
 \begin{itemize}
-
-	\item [HM] do we fix the anchor like ACT? | marginal. Queued.
-
-	\item [M] difference between EST, ACT, AMD/ AMDsemi.
-		Other methods (than HM) cannot effectively learn from the strongest
-		adversary as the inner maximization is indirectly (and not guaranteed).
-		HM follows the min-max paradigm (can be incorporated into FAT etc).
-		Both ACT and HM stops at a specific point.
-
-	\item [M] Sampling also matters in adversarial training for deep metric learning.
-
-		[source hardness and destination hardness] different source sampling
-		strategy and different destination sampling strategy. attack
-		destination. DML loss not that sensitive to sampling? or generic
-		advtrain method for DML? | still investigating
 
@@
 
+	\item [\xmark] do we fix the anchor like ACT? | negative result observed
+		on fashion-mnist (rhetrm).
+
 	\item [\xmark] What if we truncate $H_D$. Clamp it with $\min=-\gamma$.
 		| clipping leads to negative effect on fashion-mnist. (ghmetrm 8)
+		Not every triplet is useful in this regard. Not all of them have to
+		contribute to the final gradient.
 

### 2021-10-12 robdml.tex
tex

@@
 %%%%%%%%% TITLE - PLEASE UPDATE
-\title{Enhancing Adversarial Robustness for Deep Metric Learning}
+\title{Efficiently Enhancing Adversarial Robustness for Deep Metric Learning}
 
@@
 
-create adversarial
-examples for increasing their hardness towards that of a harder sample triplet.
-%
-%
-%
-Triplet hardness still matters in adversarial training for deep metric
-learning.
-
 % for problem 2
@@
 on three commonly used dataset, namely CUB-200-2011, Cars-196, and Stanford
-Online Product. \oo{the results suggest that}
+Online Product. Our conclusions are:
+%
+(1) Triplet sampling strategy is vital for adversarial training of tripet-loss
+based DML models.
+%
+\oo{the results suggest that}
 
@@
 
-\cite{Authors14}
+HM follows the min-max paradigm, (can be incorporated into FAT etc).
+Both ACT and HM stops at a specific point.
 

### 2021-10-12 introplot.py
py

@@ -19,6 +19,7 @@ data = {
             (33.0, 17.0, 9.0, 5.0, 3.0),
             (40.3, 40.0, 37.2, 25.6, 14.0),
             ),
+        'bugfix hmetrm': (27.0, 9.0, 35.1),
         }
 
 plt.figure(figsize=[10.8, 4.8])

### 2021-10-13 tab-desth.tex
tex

@@
 \resizebox{\columnwidth}{!}{
+\setlength{\tabcolsep}{0.3em}
 \begin{tabular}{c|cc|cc|cc|cc|cc}
-
 	\toprule
@@
 
-Random & \uline{53.9} & \uline{3.8} & 27.4 & 32.9 & \multicolumn{2}{c|}{Collapse} & \multicolumn{2}{c|}{Collapse} & \multicolumn{2}{c|}{Collapse}\tabularnewline
+Random & \cellcolor{black!10} 53.9 & \cellcolor{black!10}3.8 & 27.0 & 35.1 & \multicolumn{2}{c|}{Collapse} & \multicolumn{2}{c|}{Collapse} & \multicolumn{2}{c|}{Collapse}\tabularnewline
 \hline
-Semihard & 46.9 & 4.1 & - & - & \multicolumn{2}{c|}{Collapse} & \multicolumn{2}{c|}{Collapse} & \multicolumn{2}{c|}{Collapse}\tabularnewline
+Semihard & 43.9 & 5.4 & \cellcolor{black!10}44.0 & \cellcolor{black!10}5.0 & \multicolumn{2}{c|}{Collapse} & \multicolumn{2}{c|}{Collapse} & \multicolumn{2}{c|}{Collapse}\tabularnewline
 \hline
-Softhard &  &  &  &  & - & - & \multicolumn{2}{c|}{Collapse} & \multicolumn{2}{c|}{Collapse}\tabularnewline
+Softhard & 48.3 & 13.7 & 38.4 & 29.6 & \cellcolor{black!10}55.7 & \cellcolor{black!10}6.2 & \multicolumn{2}{c|}{Collapse} & \multicolumn{2}{c|}{Collapse}\tabularnewline
 \hline
-Distance &  &  &  &  &  &  & - & - & 52.1 & 4.7\tabularnewline
+Distance & 52.7 & 4.8 & 50.7 & 4.8 & \multicolumn{2}{c|}{Collapse} & \cellcolor{black!10}51.4 & \cellcolor{black!10}4.9 & 54.7 & 5.4\tabularnewline
 \hline
-Hardest &  &  &  &  &  &  &  &  & \uline{48.9} & \uline{5.0}\tabularnewline
+Hardest & 51.0 & 4.7 & 52.2 & 4.8 & \multicolumn{2}{c|}{Collapse} & 52.6 & 5.1 & \cellcolor{black!10}48.9 & \cellcolor{black!10}5.0\tabularnewline
 
@@
 
-\caption{Hardness Manipulation: Source hardness v.s. Destination hardness for
-amdsemi on CUB Dataset. (R@1, ERS for each cell). Diagonal = does
-not attack}
+\caption{Combinations of Source/Destination Hardness.
+	%
+	Experiments are conducted on CUB Dataset.
+	%
+	Models on the diagonal do not use adversarial examples
+	due to destination being unchanged.
+	%
+}
 \label{tab:desth}

### 2021-10-13 tab-desth.tex
tex

@@
 
-\multirow{2}{*}{\backslashbox{$H_S$}{$H_D$}} & \multicolumn{2}{c|}{Random} & \multicolumn{2}{c|}{Semihard} & \multicolumn{2}{c|}{Softhard} & \multicolumn{2}{c|}{Distance} & \multicolumn{2}{c|}{Hardest}\tabularnewline
+\multirow{2}{*}{\backslashbox{$H_S$}{$H_D$}} & \multicolumn{2}{c|}{Random} & \multicolumn{2}{c|}{Semihard} & \multicolumn{2}{c|}{Softhard} & \multicolumn{2}{c|}{Distance} & \multicolumn{2}{c}{Hardest}\tabularnewline
 \cline{2-11} \cline{3-11} \cline{4-11} \cline{5-11} \cline{6-11} \cline{7-11} \cline{8-11} \cline{9-11} \cline{10-11} \cline{11-11} 
@@
 
-Random & \cellcolor{black!10} 53.9 & \cellcolor{black!10}3.8 & 27.0 & 35.1 & \multicolumn{2}{c|}{Collapse} & \multicolumn{2}{c|}{Collapse} & \multicolumn{2}{c|}{Collapse}\tabularnewline
+Random & \cellcolor{black!10} 53.9 & \cellcolor{black!10}3.8 & 27.0 & 35.1 & \multicolumn{2}{c|}{Collapse} & \multicolumn{2}{c|}{Collapse} & \multicolumn{2}{c}{Collapse}\tabularnewline
 \hline
-Semihard & 43.9 & 5.4 & \cellcolor{black!10}44.0 & \cellcolor{black!10}5.0 & \multicolumn{2}{c|}{Collapse} & \multicolumn{2}{c|}{Collapse} & \multicolumn{2}{c|}{Collapse}\tabularnewline
+Semihard & 43.9 & 5.4 & \cellcolor{black!10}44.0 & \cellcolor{black!10}5.0 & \multicolumn{2}{c|}{Collapse} & \multicolumn{2}{c|}{Collapse} & \multicolumn{2}{c}{Collapse}\tabularnewline
 \hline
-Softhard & 48.3 & 13.7 & 38.4 & 29.6 & \cellcolor{black!10}55.7 & \cellcolor{black!10}6.2 & \multicolumn{2}{c|}{Collapse} & \multicolumn{2}{c|}{Collapse}\tabularnewline
+Softhard & 48.3 & 13.7 & 38.4 & 29.6 & \cellcolor{black!10}55.7 & \cellcolor{black!10}6.2 & \multicolumn{2}{c|}{Collapse} & \multicolumn{2}{c}{Collapse}\tabularnewline
 \hline

### 2021-10-13 robdml.tex
tex

@@
 \usepackage{booktabs}
+\usepackage{colortbl}
 
@@
 \[
-	\big(1-\frac{\text{Clip}_0^{U_L}[l_{t-1}]}{U_L} \big)\times
-	(U_H + (H_D - H_S).relu())
+	\big(1-\text{Clip}_0^{U_L}[l_{t-1}]/U_L \big)\times
+	U_H
 \]
@@
 To validate the effectiveness of our proposed defense, we conduct experiments
-on three commonly used DML datasets: CUB-200~\cite{cub200}, Cars-196~\cite{cars196},
+on three commonly used DML datasets: CUB-200-2011~\cite{cub200}, Cars-196~\cite{cars196},
 and Stanford-Online-Products (SOP)~\cite{sop}.
@@
 
-\subsection{Selection of Source/Destination Hardness}
+\subsection{Selection of Source \& Destination Hardness}
 
@@
 
-In literature, a series of triplet sampling strategies exist, such as random,
-semi-hard~\cite{facenet}, soft-hard[], distance[], and hardest sampling.
+% 1. possible combinations
+
+In literature, various triplet sampling strategies exist, such as random,
+semihard~\cite{facenet}, softhard[], distance~\cite{distance}, and the hardest negative sampling
+(\ie, the negative sample with the largest loss value).
 %
-Any of these can be selected for source triplet and destination triplet.
+Although any of them can be selected for source or destination hardness for HM,
+not all the possible combinations are expected to be effective or efficient.
+%
+In order to figure out an empirically good combination of source and destination
+hardness, we adversarially train models on the CUB-200-2011 dataset with
+every possible combination, and compare their R@1 and ERS performance in
+\cref{tab:desth}.
+
+% 2. hypothesis
 
@@
 
+\subsection{Effectiveness of HM}
+
+HM + different pgditer
+CUB, 2 4 8 16 32
+
+8; empirically selected as the base for further ablation study.
+
+\oo{experiment, 8 step by default}
+
+\subsection{Effectiveness of GA}
+
+\subsection{Effectiveness of ICS}
+
 \subsection{Comparison with State-of-the-art}
 
-\oo{experiment, 8 step by default}
+CUB 8 32
+
+CARS 8 32
+
+SOP 8 32
+
 Number of PGD Steps $\eta$.
@@
 
+(optional) ICS for ACT?
+
 \section{Conclusion}
@@
 Both ACT and HM stops at a specific point.
+
+\oo{In potential of future works}
+Deep metric learning on adversarial example is also used for improving
+adversarial robustness for deep classifiers~\cite{mao2019metric}.
 

### 2021-10-13 robdml.tex
tex

@@
 To validate the effectiveness of our proposed defense, we conduct experiments
-on three commonly used DML datasets: CUB-200-2011~\cite{cub200}, Cars-196~\cite{cars196},
-and Stanford-Online-Products (SOP)~\cite{sop}.
+on three commonly used DML datasets: CUB-200-2011 (CUB)~\cite{cub200}, Cars-196
+(CARS)~\cite{cars196}, and Stanford-Online-Products (SOP)~\cite{sop}.
 %
@@
 
-Specifically, we train a ResNet-18~\cite{resnet} with the output dimension of
+Specifically, we train a ResNet-18 (RN18)~\cite{resnet} with the output dimension of
 the last layer changed to $N=512$.
@@
 In literature, various triplet sampling strategies exist, such as random,
-semihard~\cite{facenet}, softhard[], distance~\cite{distance}, and the hardest negative sampling
-(\ie, the negative sample with the largest loss value).
+semihard~\cite{facenet}, softhard~\cite{revisiting}, distance~\cite{distance}, and the hardest
+negative sampling (\ie, the negative sample with the largest loss value).
 %
@@
 %
-In order to figure out an empirically good combination of source and destination
-hardness, we adversarially train models on the CUB-200-2011 dataset with
+In order to figure out an empirically good combination of source and
+destination hardness, we adversarially train RN18 models on the CUB dataset with
 every possible combination, and compare their R@1 and ERS performance in

### 2021-10-13 tab-desth.tex
tex

@@
 
-\caption{Combinations of Source/Destination Hardness.
+	\caption{Combinations of Source \& Destination Hardness.
 	%
-	Experiments are conducted on CUB Dataset.
+	Experiments are conducted on CUB Dataset with RN18 model.
 	%
-	Models on the diagonal do not use adversarial examples
-	due to destination being unchanged.
+	The last-epoch performance is reported instead of the peak performance.
+	%
+	Original data is used when the source and destination hardness are the
+	same, as shown on the diagonal line of the table.
 	%

### 2021-10-13 robdml.tex
tex

@@
 In literature, various triplet sampling strategies exist, such as random,
-semihard~\cite{facenet}, softhard~\cite{revisiting}, distance~\cite{distance}, and the hardest
-negative sampling (\ie, the negative sample with the largest loss value).
+semihard~\cite{facenet}, softhard~\cite{revisiting}, distance~\cite{distance},
+and the hardest negative sampling (\ie, the negative sample with the largest
+loss value).
 %
@@
 In order to figure out an empirically good combination of source and
-destination hardness, we adversarially train RN18 models on the CUB dataset with
-every possible combination, and compare their R@1 and ERS performance in
+destination hardness, we adversarially train RN18 models on the CUB dataset
+with every possible combination, and compare their R@1 and ERS performance in
 \cref{tab:desth}.
+%
+Note, these methods are empirically sorted by their expectation of hardness
+$E[H]$, in the ascending order: random, semihard, softhard, distance, and
+hardest.
 
@@
 less than the source hardness, \ie, $E[H_S]<E[H_D]$.
-%
-Our empirical observation on $E[H]$ from randomly initialized
-model suggests a sorting of ``random'' $<$ ``semi-hard'' $<$ ``soft-hard'' $<$
-``distance'' $<$ ``hardest''.
 %

### 2021-10-13 robdml.tex
tex

@@
 
+Recall that triplet-based model is already prone to collapse with very hard
+examples, even if they are unperturbed.
+%
+Similarly, the model is expected to collapse with excessively hard adversarial
+examples as well.
+%
+As shown in the last three columns of \cref{tab:desth}, almost all combinations
+will result in model collapse as long as the destination hardness is softhard,
+distance, or hardest.
+%
+The only exception is the combination of distance and hardest.
+%
+We speculate the  \oo{TODO}
+The $E[H]$ of distance and hardest sampling are empirically observed very close.
+%
+
+And the model can be easier to collapse with adversarially perturbed hard
+examples
+
 As the samples will not become adversarial once $H_S>H_D$ (zero perturbation in
@@
 
-\subsection{Effectiveness of HM}
+The proposed hardness manipulation is effective.
+
+\subsection{Efficiency of Hardness Manipulation}
 

### 2021-10-13 robdml.tex
tex

@@
 %
-We speculate the  \oo{TODO}
-The $E[H]$ of distance and hardest sampling are empirically observed very close.
+We empirically observe that the $E[H]$ of distance and hardest sampling are
+very close to each other, which means the attack will be rather weak.
 %
-
-And the model can be easier to collapse with adversarially perturbed hard
-examples
+The model does not collapse in this case, but the robustness gain is negligible
+as well.
 

### 2021-10-13 robdml.tex
tex

@@
 
-% 2. hypothesis
+% 2. table: left and right
 
@@
 as well.
+
+% 3. table: upper and lower
+
+For cases in the upper triangular of \cref{tab:desth}, $E[H_S] < E[H_D]$,
+which means most triplets will be turned into adversarial example by HM
+to increase the hardness.
+%
+Although most of such cases end up with model collapse, the preliminary 
+result suggests that HM from random to semihard is effective in significantly
+improve the robustness without model collapse, at an expected cost on the R@1
+performance on benign examples.
 

### 2021-10-13 robdml.tex
tex

@@
 
-For cases in the upper triangular of \cref{tab:desth}, $E[H_S] < E[H_D]$,
+For cases in upper triangular of \cref{tab:desth}, $E[H_S] \leqslant E[H_D]$,
 which means most triplets will be turned into adversarial example by HM
@@
 
-As the samples will not become adversarial once $H_S>H_D$ (zero perturbation in
-this case according to \cref{eq:hm}, an effective combination of source and
-destination sampling strategy should make the expectation of source hardness
-less than the source hardness, \ie, $E[H_S]<E[H_D]$.
+For cases in lower triangular of \cref{tab:desth}, $E[H_S] \geqslant E[H_D]$,
+which means most tirplet will not be turned into adversarial according to
+\cref{eq:hm}.
 %
-Namely, the source sampling strategy should be ahead of the destination
-sampling strategy in this list.
+In such cases, the model will not be able to effectively learn from a strong
+adversary, and hence will behave as if no defense is equipped.
+%
+As an exception, HM from softhard to semihard can also lead to relatively high
+adversarial robustness.
+%
+Due to the high variance of hardness of softhard sampling strategy, the
+hardness of a notable portion of triplets will be less than that of semihard,
+and hence HM will create some adversarial examples for training.
+%
+In other words, HM in this case can be interpreted as mixing some unperturbed
+softhard triplets and some semihard adversarial triplets.
 
@@
 The proposed hardness manipulation is effective.
+\oo{todo: table of first and second order central moment}
 

### 2021-10-13 robdml.tex
tex

@@
 hardest.
+%
+\oo{todo: table of first and second order central moment}
 
@@
 
-To figure out an appropriate combination for further experiments, we try
-every possible combination and compare their R@1 and ERS performance, as
-shown in \cref{tab:desth}.
+% 4. summary
+
+In summary, according to \cref{tab:desth}, HM from random to semihard, or from
+softhard to semihard are two choices that can effectively lead to robust
+DML model.
 %
-\oo{The table suggests that}
-
-The proposed hardness manipulation is effective.
-\oo{todo: table of first and second order central moment}
+The subsequent experiments will be based on the two choices.
 

### 2021-10-13 tab-hsort.tex
tex

\begin{table}
\resizebox{\columnwidth}{!}{
	\setlength{\tabcolsep}{0.9em}
\begin{tabular}{c|c|c|c|c|c}
\toprule
 & Random & Semihard & Softhard & Distance & Hardest\tabularnewline
\midrule
$E[H]$ & $-0.164$ & $-0.126$ & $-0.085$ & $0.043$ & $0.044$\tabularnewline
$\text{Var}[H]$ & $0.00035$ & $0.00013$ & $0.00122$ & $0.00021$ & $0.00021$\tabularnewline
\bottomrule
\end{tabular}
}

\caption{Expectation and Variance. 1000 batches.}

\end{table}

### 2021-10-14 robdml.tex
tex

@@
 Then its \emph{hardness} is defined as
-$H(X_a,X_p^S,X_n^S)=d_\phi(X_a,X_p^S)-d_\phi(X_a,X_n^S)$, which is an internal
+%
+\begin{equation}
+%
+H(X_a^S,X_p^S,X_n^S)=d_\phi(X_a,X_p^S)-d_\phi(X_a,X_n^S),
+%
+\end{equation}
+%
+which is an internal
 part of the triplet loss.
@@
 
+\input{tab-hsort.tex}
+
 \input{tab-desth.tex}
@@
 $E[H]$, in the ascending order: random, semihard, softhard, distance, and
-hardest.
-%
-\oo{todo: table of first and second order central moment}
+hardest, as shown in \cref{tab:hsort}.
 

### 2021-10-14 tab-hmeff.tex
tex

\begin{table*}
\resizebox{\linewidth}{!}{
	\setlength{\tabcolsep}{0.2em}
\begin{tabular}{cccc|cccc|ccccc|ccccc|c}
\hline 
\multicolumn{1}{c|}{\multirow{2}{*}{\textbf{Dataset}}} & \multicolumn{1}{c|}{\multirow{2}{*}{\textbf{Model}}} & \multicolumn{1}{c|}{\multirow{2}{*}{\textbf{Loss}}} & \multirow{2}{*}{\textbf{Defense}} & \multicolumn{4}{c|}{\textbf{Benign Example}} & \multicolumn{10}{c|}{\textbf{White-Box Attacks for Robustness Evaluation}} & \multirow{2}{*}{\textbf{ERS$\uparrow$}}\tabularnewline
\cline{5-18} \cline{6-18} \cline{7-18} \cline{8-18} \cline{9-18} \cline{10-18} \cline{11-18} \cline{12-18} \cline{13-18} \cline{14-18} \cline{15-18} \cline{16-18} \cline{17-18} \cline{18-18} 
 &  &  &  & R@1$\uparrow$ & R@2$\uparrow$ & mAP$\uparrow$ & NMI$\uparrow$ & CA+$\uparrow$ & CA-$\downarrow$ & QA+$\uparrow$ & QA-$\downarrow$ & TMA$\downarrow$ & ES:D$\downarrow$ & ES:R$\uparrow$ & LTM$\uparrow$ & GTM$\uparrow$ & GTT$\uparrow$ & \tabularnewline
\hline 
\hline 
CUB & RN18 & Triplet & N/A & 53.9 & 66.4 & 26.1 & 59.5 & 0.0 & 100.0 & 0.0 & 99.9 & 0.883 & 1.762 & 0.0 & 0.0 & 14.1 & 0.0 & 3.8\tabularnewline
\hline 
 &  &  & ACT ($\eta=2$) & 46.5 & 58.4 & 29.1 & 55.6 & 0.6 & 98.9 & 0.4 & 98.1 & 0.837 & 1.666 & 0.2 & 0.2 & 19.6 & 0.0 & 5.8\tabularnewline
 &  &  & ACT ($\eta=4$) & 38.4 & 49.8 & 22.8 & 49.7 & 4.6 & 81.9 & 2.8 & 80.5 & 0.695 & 1.366 & 2.9 & 2.3 & 18.8 & 0.1 & 13.9\tabularnewline
 &  &  & ACT ($\eta=8$) & 30.6 & 40.1 & 16.5 & 45.6 & 13.7 & 46.8 & 12.6 & 39.3 & 0.547 & 0.902 & 13.6 & 9.8 & 21.9 & 1.3 & 31.3\tabularnewline
 &  &  & ACT ($\eta=16$) & \uline{28.6} & \uline{38.7} & \uline{15.1} & \uline{43.7} & \uline{15.8} & \uline{37.9} & \uline{16.0} & \uline{31.5} & \uline{0.496} & \uline{0.834} & \uline{11.3} & \uline{9.8} & \uline{21.2} & \uline{2.1} & \uline{34.7}\tabularnewline
 &  &  & ACT ($\eta=32$) & 27.5 & 38.2 & 12.2 & 43.0 & 15.5 & 37.7 & 15.1 & 32.2 & 0.472 & 0.821 & 11.1 & 9.4 & 14.9 & 1.0 & 33.9\tabularnewline
\hline 
 &  &  & HM:R$\rightarrow$M ($\eta=2$) &  &  &  &  &  &  &  &  &  &  &  &  &  &  & \tabularnewline
 &  &  & HM:R$\rightarrow$M ($\eta=4$) &  &  &  &  &  &  &  &  &  &  &  &  &  &  & \tabularnewline
 &  &  & HM:R$\rightarrow$M ($\eta=8$) &  &  &  &  &  &  &  &  &  &  &  &  &  &  & \tabularnewline
 &  &  & HM:R$\rightarrow$M ($\eta=16$) &  &  &  &  &  &  &  &  &  &  &  &  &  &  & \tabularnewline
 &  &  & HM:R$\rightarrow$M ($\eta=32$) &  &  &  &  &  &  &  &  &  &  &  &  &  &  & \tabularnewline
\hline 
 &  &  & HM:S$\rightarrow$M ($\eta=2$) &  &  &  &  &  &  &  &  &  &  &  &  &  &  & \tabularnewline
 &  &  & HM:S$\rightarrow$M ($\eta=4$) &  &  &  &  &  &  &  &  &  &  &  &  &  &  & \tabularnewline
 &  &  & HM:S$\rightarrow$M ($\eta=8$) &  &  &  &  &  &  &  &  &  &  &  &  &  &  & \tabularnewline
 &  &  & HM:S$\rightarrow$M ($\eta=16$) &  &  &  &  &  &  &  &  &  &  &  &  &  &  & \tabularnewline
 &  &  & HM:S$\rightarrow$M ($\eta=32$) &  &  &  &  &  &  &  &  &  &  &  &  &  &  & \tabularnewline
\end{tabular}
}

\caption{Efficiency of Hardness Manipulation for Adversarial Training.}
\label{tab:hmeff}
\end{table*}

### 2021-10-14 introplot.py
svg

@@ -8,18 +8,24 @@ plt.rcParams['font.size'] = 14
 
 data = {
         'ACT': (
-            (27.5, 28.6, 33.3, 38.4, 46.5),
-            (33.0, 17.0, 8.0, 5.0, 3.0),
-            (33.9, 34.7, 27.3, 13.9, 5.8),
+            (27.5, 28.6, 30.6, 38.4, 46.5),
+            (33.0, 17.0, 9.0, 5.0, 3.0),
+            (33.9, 34.7, 31.3, 13.9, 5.8),
             ),
         #'amdsemi+aap0': (26.2, 9.0, 40.0),
         #'hml2rmi': (25.2, 9.0, 39.8),
-        'hmetrm': (
+        'hmetrm(bug)': (
             (27.0, 27.1, 28.3, 34.9, 39.2),
             (33.0, 17.0, 9.0, 5.0, 3.0),
             (40.3, 40.0, 37.2, 25.6, 14.0),
             ),
-        'bugfix hmetrm': (27.0, 9.0, 35.1),
+        'hmetrm': (
+            (23.1, 23.8, 27.0, 30.7),
+            (33.0, 17.0, 9.0, 5.0),
+            (38.0, 38.0, 35.1, 27.1),
+            ),
+        'hmetsm': (38.4, 9.0, 29.6),
+
         }
 
 plt.figure(figsize=[10.8, 4.8])

### 2021-10-14 introplot.py
lyx

@@ -20,9 +20,9 @@ data = {
             (40.3, 40.0, 37.2, 25.6, 14.0),
             ),
         'hmetrm': (
-            (23.1, 23.8, 27.0, 30.7),
-            (33.0, 17.0, 9.0, 5.0),
-            (38.0, 38.0, 35.1, 27.1),
+            (23.1, 23.8, 27.0, 30.7, 34.3),
+            (33.0, 17.0, 9.0, 5.0, 3.0),
+            (38.0, 38.0, 35.1, 27.1, 18.1),
             ),
         'hmetsm': (38.4, 9.0, 29.6),
 

### 2021-10-14 introplot.py
svg

@@ -24,8 +24,11 @@ data = {
             (33.0, 17.0, 9.0, 5.0, 3.0),
             (38.0, 38.0, 35.1, 27.1, 18.1),
             ),
-        'hmetsm': (38.4, 9.0, 29.6),
-
+        'hmetsm': (
+            (38.4, 40.6, 44.5),
+            (9.0, 5.0, 3.0),
+            (29.6, 22.1, 11.6),
+            ),
         }
 
 plt.figure(figsize=[10.8, 4.8])
@@ -35,7 +38,11 @@ for (name, (r1, cost, ers)) in data.items():
     c.print(name, r1, cost, ers)
 
     if name == 'ACT':
+        plt.plot(cost, ers, f'-o', color='dimgray')
+    elif name == 'hmetrm':
         plt.plot(cost, ers, f'-o', color='tab:blue')
+    elif name == 'hmetsm':
+        plt.plot(cost, ers, f'-o', color='tab:red')
     else:
         plt.plot(cost, ers, f'-o', color='k')
     if isinstance(cost, float):
@@ -55,31 +62,16 @@ ax.annotate('↘ Worse', xy=(0.77, 0.06), xycoords='axes fraction',
         bbox=dict(boxstyle="round,pad=0.3", fc="white", ec="k", lw=2),
         size=14)
 
-#plt.subplot(2,2,2)
-#for (name, (r1, cost, ers)) in data.items():
-#    c.print(name, r1, cost, ers)
-#
-#    color = 'k'
-#    if name == 'EST':
-#        color = 'b'
-#    if name == 'ACT':
-#        color = 'r'
-#    plt.plot(cost, r1, f'-{color}o')
-#    if isinstance(cost, float):
-#        plt.annotate(name, xy=(cost, r1))
-#    elif isinstance(cost, tuple):
-#        plt.annotate(name, xy=(cost[0], r1[0]))
-#plt.xlabel('Training Cost')
-#plt.ylabel('Recall@1 (R@1)')
-#plt.xscale('log', base=2)
-
-
 ax = plt.subplot(1,2,2)
 for (name, (r1, cost, ers)) in data.items():
     c.print(name, r1, cost, ers)
 
     if name == 'ACT':
+        plt.plot(r1, ers, f'-o', color='dimgray')
+    elif name == 'hmetrm':
         plt.plot(r1, ers, f'-o', color='tab:blue')
+    elif name == 'hmetsm':
[…]

### 2021-10-14 introplot.py
lyx

@@ -29,6 +29,11 @@ data = {
             (9.0, 5.0, 3.0),
             (29.6, 22.1, 11.6),
             ),
+        'hmix': (
+            (37.8, 42.7),
+            (5.0, 3.0),
+            (21.7, 12.5),
+            ),
         }
 
 plt.figure(figsize=[10.8, 4.8])
@@ -43,6 +48,8 @@ for (name, (r1, cost, ers)) in data.items():
         plt.plot(cost, ers, f'-o', color='tab:blue')
     elif name == 'hmetsm':
         plt.plot(cost, ers, f'-o', color='tab:red')
+    elif name == 'hmix':
+        plt.plot(cost, ers, f'-o', color='deeppink')
     else:
         plt.plot(cost, ers, f'-o', color='k')
     if isinstance(cost, float):
@@ -72,6 +79,8 @@ for (name, (r1, cost, ers)) in data.items():
         plt.plot(r1, ers, f'-o', color='tab:blue')
     elif name == 'hmetsm':
         plt.plot(r1, ers, f'-o', color='tab:red')
+    elif name == 'hmix':
+        plt.plot(r1, ers, f'-o', color='deeppink')
     else:
         plt.plot(r1, ers, f'-o', color='k')
     if isinstance(ers, float):

### 2021-10-14 introplot.py
lyx

@@ -30,9 +30,9 @@ data = {
             (29.6, 22.1, 11.6),
             ),
         'hmix': (
-            (37.8, 42.7),
-            (5.0, 3.0),
-            (21.7, 12.5),
+            (32.3, 32.5, 37.8, 42.7),
+            (17.0, 9.0, 5.0, 3.0),
+            (33.1, 31.8, 21.7, 12.5),
             ),
         }
 

### 2021-10-14 introplot.py
lyx

@@ -25,9 +25,9 @@ data = {
             (38.0, 38.0, 35.1, 27.1, 18.1),
             ),
         'hmetsm': (
-            (38.4, 40.6, 44.5),
-            (9.0, 5.0, 3.0),
-            (29.6, 22.1, 11.6),
+            (36.0, 38.4, 40.6, 44.5),
+            (17.0, 9.0, 5.0, 3.0),
+            (36.2, 29.6, 22.1, 11.6),
             ),
         'hmix': (
             (32.3, 32.5, 37.8, 42.7),
@@ -43,13 +43,13 @@ for (name, (r1, cost, ers)) in data.items():
     c.print(name, r1, cost, ers)
 
     if name == 'ACT':
-        plt.plot(cost, ers, f'-o', color='dimgray')
+        plt.plot(cost, ers, f'.-', color='dimgray')
     elif name == 'hmetrm':
-        plt.plot(cost, ers, f'-o', color='tab:blue')
+        plt.plot(cost, ers, f'v-', color='tab:blue')
     elif name == 'hmetsm':
-        plt.plot(cost, ers, f'-o', color='tab:red')
+        plt.plot(cost, ers, f'^-', color='tab:red')
     elif name == 'hmix':
-        plt.plot(cost, ers, f'-o', color='deeppink')
+        plt.plot(cost, ers, f'h-', color='deeppink')
     else:
         plt.plot(cost, ers, f'-o', color='k')
     if isinstance(cost, float):
@@ -74,13 +74,13 @@ for (name, (r1, cost, ers)) in data.items():
     c.print(name, r1, cost, ers)
 
     if name == 'ACT':
-        plt.plot(r1, ers, f'-o', color='dimgray')
+        plt.plot(r1, ers, f'.-', color='dimgray')
     elif name == 'hmetrm':
-        plt.plot(r1, ers, f'-o', color='tab:blue')
+        plt.plot(r1, ers, f'v-', color='tab:blue')
     elif name == 'hmetsm':
-        plt.plot(r1, ers, f'-o', color='tab:red')
+        plt.plot(r1, ers, f'^-', color='tab:red')
     elif name == 'hmix':
-        plt.plot(r1, ers, f'-o', color='deeppink')
+        plt.plot(r1, ers, f'h-', color='deeppink')
     else:
         plt.plot(r1, ers, f'-o', color='k')
     if isinstance(ers, float):

### 2021-10-14 introplot.py
lyx

@@ -34,6 +34,9 @@ data = {
             (17.0, 9.0, 5.0, 3.0),
             (33.1, 31.8, 21.7, 12.5),
             ),
+        'hmix0.8': (
+            29.1, 9.0, 33.9,
+            ),
         }
 
 plt.figure(figsize=[10.8, 4.8])

### 2021-10-14 robdml.tex
tex
svg

@@
 %%%%%%%%% TITLE - PLEASE UPDATE
-\title{Efficiently Enhancing Adversarial Robustness for Deep Metric Learning}
+\title{Enhancing Adversarial Robustness for Deep Metric Learning}
 
@@
 \subsection{Hardness Manipulation}
+\label{sec:31}
 
-\oo{[illust fig]}
+\begin{figure}
+	\includegraphics[width=\columnwidth]{hmillust.pdf}
+	\caption{Illustration of Hardness Manipulation.}
+	\label{fig:hm}
+\end{figure}
 
@@
 
+Note, the design of HM is flexible, and not coupled with specific sampling
+strategy.
+%
+In other words, any existing or future triplet sampling strategy can
+be adopted in HM.
+
 \subsection{Gradual Adversary}
+\label{sec:32}
 
@@
 \subsection{Intra-Class Structure Constraint}
+\label{sec:33}
 
@@
 
+\input{tab-hmeff.tex}
 % 1. possible combinations
@@
 CUB, 2 4 8 16 32
+\cref{tab:hmeff}
 
@@
 
-\subsection{Effectiveness of GA}
+\subsection{Effectiveness of GA and ICS}
 
-\subsection{Effectiveness of ICS}
+Put together for easier comparison.
 

### 2021-10-14 appendix.tex
svg
tex

@@
 \begin{itemize}
+
+	\item [ICS] should investigate other metric learning loss functions and see
+		how they deal with hierarchy. e.g. MS, LSS, GLift, quadrup, etc.
+
+	\item [GA] Also scale the $H_D-H_S$ part?
+		(1) $$ H_\mathsf{GA} \leftarrow (H_\mathsf{D} + U - H_\mathsf{S}) * nL $$
+		(2) $$ H_\mathsf{GA} \leftarrow H_\mathsf{D} + U * nL $$
+		(3) pure GA for ablation $$ H_\mathsf{GA} \leftarrow U * nL $$
+		interpret with lessons learned from HM matrix.
 

### 2021-10-14 robdml.tex
svg
tex

@@
 
+\cref{fig:hm}
+
 Given an anchor image $X_a$, we sample a positive image $X_p^S$ (in the same
@@
 %
-For convenience we call this as ``source hardness'', denoted as $H_S$.
+For convenience we call this as ``source hardness'', denoted as $H_\mathsf{S}$.
 
@@
 and negative image $X_n^D$ with a different triplet sampling strategy, and
-we call its hardness as ``destination hardness'', denoted as $H_D$.
+we call its hardness as ``destination hardness'', denoted as $H_\mathsf{D}$.
 
-Then, we want change (increase) the hardness level from $H_S$ into $H_D$, by
+Then, we want change (increase) the hardness level from $H_\mathsf{S}$ into $H_\mathsf{D}$, by
 finding adversarial examples for $(X_a, X_p^S, X_n^S)$.
@@
 Note, it is not expected to lower the hardness during the attack, namely
-$E[H_D]$ should be greater or equal to $E[H_S]$.
+$E[H_\mathsf{D}]$ should be greater or equal to $E[H_\mathsf{S}]$.
 %
@@
 	\bar{r}_a, \bar{r}_p, \bar{r}_n = \argmin_{r_a,r_p,r_n} \|\min(0,
-	\tilde{H}_S-H_D)\|^2.
+	\tilde{H}_\mathsf{S}-H_\mathsf{D})\|^2.
 	%
@@
 %
-The $\min(0,\cdot)$ part in \cref{eq:hm} truncates the gradient when $H_S>H_D$,
+The $\min(0,\cdot)$ part in \cref{eq:hm} truncates the gradient when $H_\mathsf{S}>H_\mathsf{D}$,
 automatically stopping the optimization.
 %
-This is because $H_S$ will be reduced once greater than $H_D$ in standard Mean
+This is because $H_\mathsf{S}$ will be reduced once greater than $H_\mathsf{D}$ in standard Mean
 Square Error.
@@
 
+\oo{uses gradient for maximization. Maxim is $HM(H_\mathsf{S}, 2)$.}
+
 Note, the design of HM is flexible, and not coupled with specific sampling
@@
 
-\oo{[illust fig]}
+\begin{figure}
+	\includegraphics[width=\columnwidth]{gaillust.pdf}
+	\caption{Illustration of Gradual Adversary.}
+	\label{fig:ga}
+\end{figure}
+
+\cref{fig:ga}
 
 During the training process, the strength of adversary will gradually decrease,
-because the expectation of the destination hardness $E[H_D]$ is expected to
+because the expectation of the destination hardness $E[H_\mathsf{D}]$ is expected to
 decrease with a model being trained.
@@
 
-For cases in upper triangular of \cref{tab:desth}, $E[H_S] \leqslant E[H_D]$,
+For cases in upper triangular of \cref{tab:desth}, $E[H_\mathsf{S}] \leqslant E[H_\mathsf{D}]$,
 which means most triplets will be turned into adversarial example by HM
@@
 
-For cases in lower triangular of \cref{tab:desth}, $E[H_S] \geqslant E[H_D]$,
+For cases in lower triangular of \cref{tab:desth}, $E[H_\mathsf{S}] \geqslant E[H_\mathsf{D}]$,
 which means most tirplet will not be turned into adversarial according to

### 2021-10-14 introplot.py
svg

@@ -34,9 +34,8 @@ data = {
             (17.0, 9.0, 5.0, 3.0),
             (33.1, 31.8, 21.7, 12.5),
             ),
-        'hmix0.8': (
-            29.1, 9.0, 33.9,
-            ),
+        'hmix0.8': (29.1, 9.0, 33.9),
+        'hmix0.6': (31.7, 9.0, 32.1),
         }
 
 plt.figure(figsize=[10.8, 4.8])

### 2021-10-15 introplot.py
lyx

@@ -36,6 +36,7 @@ data = {
             ),
         'hmix0.8': (29.1, 9.0, 33.9),
         'hmix0.6': (31.7, 9.0, 32.1),
+        'G4': (34.4, 9.0, 36.7),
         }
 
 plt.figure(figsize=[10.8, 4.8])

### 2021-10-15 robdml.tex
u

@@
 be adopted in HM.
+%
+or even a pseudo hardness function $g(\cdot)$ as long as we have a strong
+prior knowledge on what the destination hardness should be.
 
@@
 
+strong example when the embedding space is not in good shape.
+
 \[
@@
 \]
+
+\begin{equation}
+	%
+	g_\mathsf{B}(H(\cdots)) = H(\cdots) + \xi \cdot \bar{\ell}_{t-1}
+	%
+\end{equation}
+
+\begin{equation}
+	%
+	g_\mathsf{SGA}() = -\gamma \cdot \bar{\ell}_{t-1}
+	%
+\end{equation}
 
@@
 \oo{Concretely, the ensemble of attack for computing ERS includes.}
+
+This section is organized in logical order where a group of experiments
+or ablation study
+provides clues for the next group of experiment.
+%
+Hence, the comparison to the state-of-the-art works are put at the last
+subsection.
 

### 2021-10-15 introplot.py
svg: no hmix

@@ -29,13 +29,6 @@ data = {
             (17.0, 9.0, 5.0, 3.0),
             (36.2, 29.6, 22.1, 11.6),
             ),
-        'hmix': (
-            (32.3, 32.5, 37.8, 42.7),
-            (17.0, 9.0, 5.0, 3.0),
-            (33.1, 31.8, 21.7, 12.5),
-            ),
-        'hmix0.8': (29.1, 9.0, 33.9),
-        'hmix0.6': (31.7, 9.0, 32.1),
         'G4': (34.4, 9.0, 36.7),
         }
 

### 2021-10-15 tab-hmeff.tex
tex

@@
 	\setlength{\tabcolsep}{0.2em}
-\begin{tabular}{cccc|cccc|ccccc|ccccc|c}
+
+\begin{tabular}{cc|cccc|ccccc|ccccc|c}
 \hline 
-\multicolumn{1}{c|}{\multirow{2}{*}{\textbf{Dataset}}} & \multicolumn{1}{c|}{\multirow{2}{*}{\textbf{Model}}} & \multicolumn{1}{c|}{\multirow{2}{*}{\textbf{Loss}}} & \multirow{2}{*}{\textbf{Defense}} & \multicolumn{4}{c|}{\textbf{Benign Example}} & \multicolumn{10}{c|}{\textbf{White-Box Attacks for Robustness Evaluation}} & \multirow{2}{*}{\textbf{ERS$\uparrow$}}\tabularnewline
-\cline{5-18} \cline{6-18} \cline{7-18} \cline{8-18} \cline{9-18} \cline{10-18} \cline{11-18} \cline{12-18} \cline{13-18} \cline{14-18} \cline{15-18} \cline{16-18} \cline{17-18} \cline{18-18} 
- &  &  &  & R@1$\uparrow$ & R@2$\uparrow$ & mAP$\uparrow$ & NMI$\uparrow$ & CA+$\uparrow$ & CA-$\downarrow$ & QA+$\uparrow$ & QA-$\downarrow$ & TMA$\downarrow$ & ES:D$\downarrow$ & ES:R$\uparrow$ & LTM$\uparrow$ & GTM$\uparrow$ & GTT$\uparrow$ & \tabularnewline
+\multicolumn{1}{c|}{\multirow{2}{*}{\textbf{Dataset}}} & \multirow{2}{*}{\textbf{Defense}} & \multicolumn{4}{c|}{\textbf{Benign Example}} & \multicolumn{10}{c|}{\textbf{White-Box Attacks for Robustness Evaluation}} & \multirow{2}{*}{\textbf{ERS$\uparrow$}}\tabularnewline
+\cline{3-16} \cline{4-16} \cline{5-16} \cline{6-16} \cline{7-16} \cline{8-16} \cline{9-16} \cline{10-16} \cline{11-16} \cline{12-16} \cline{13-16} \cline{14-16} \cline{15-16} \cline{16-16} 
+ &  & R@1$\uparrow$ & R@2$\uparrow$ & mAP$\uparrow$ & NMI$\uparrow$ & CA+$\uparrow$ & CA-$\downarrow$ & QA+$\uparrow$ & QA-$\downarrow$ & TMA$\downarrow$ & ES:D$\downarrow$ & ES:R$\uparrow$ & LTM$\uparrow$ & GTM$\uparrow$ & GTT$\uparrow$ & \tabularnewline
 \hline 
 \hline 
-CUB & RN18 & Triplet & N/A & 53.9 & 66.4 & 26.1 & 59.5 & 0.0 & 100.0 & 0.0 & 99.9 & 0.883 & 1.762 & 0.0 & 0.0 & 14.1 & 0.0 & 3.8\tabularnewline
+CUB & N/A & 53.9 & 66.4 & 26.1 & 59.5 & 0.0 & 100.0 & 0.0 & 99.9 & 0.883 & 1.762 & 0.0 & 0.0 & 14.1 & 0.0 & 3.8\tabularnewline
 \hline 
- &  &  & ACT ($\eta=2$) & 46.5 & 58.4 & 29.1 & 55.6 & 0.6 & 98.9 & 0.4 & 98.1 & 0.837 & 1.666 & 0.2 & 0.2 & 19.6 & 0.0 & 5.8\tabularnewline
- &  &  & ACT ($\eta=4$) & 38.4 & 49.8 & 22.8 & 49.7 & 4.6 & 81.9 & 2.8 & 80.5 & 0.695 & 1.366 & 2.9 & 2.3 & 18.8 & 0.1 & 13.9\tabularnewline
- &  &  & ACT ($\eta=8$) & 30.6 & 40.1 & 16.5 & 45.6 & 13.7 & 46.8 & 12.6 & 39.3 & 0.547 & 0.902 & 13.6 & 9.8 & 21.9 & 1.3 & 31.3\tabularnewline
- &  &  & ACT ($\eta=16$) & \uline{28.6} & \uline{38.7} & \uline{15.1} & \uline{43.7} & \uline{15.8} & \uline{37.9} & \uline{16.0} & \uline{31.5} & \uline{0.496} & \uline{0.834} & \uline{11.3} & \uline{9.8} & \uline{21.2} & \uline{2.1} & \uline{34.7}\tabularnewline
- &  &  & ACT ($\eta=32$) & 27.5 & 38.2 & 12.2 & 43.0 & 15.5 & 37.7 & 15.1 & 32.2 & 0.472 & 0.821 & 11.1 & 9.4 & 14.9 & 1.0 & 33.9\tabularnewline
+ & ACT ($\eta=2$) & 46.5 & 58.4 & 29.1 & 55.6 & 0.6 & 98.9 & 0.4 & 98.1 & 0.837 & 1.666 & 0.2 & 0.2 & 19.6 & 0.0 & 5.8\tabularnewline
+ & ACT ($\eta=4$) & 38.4 & 49.8 & 22.8 & 49.7 & 4.6 & 81.9 & 2.8 & 80.5 & 0.695 & 1.366 & 2.9 & 2.3 & 18.8 & 0.1 & 13.9\tabularnewline
+ & ACT ($\eta=8$) & 30.6 & 40.1 & 16.5 & 45.6 & 13.7 & 46.8 & 12.6 & 39.3 & 0.547 & 0.902 & 13.6 & 9.8 & 21.9 & 1.3 & 31.3\tabularnewline
+ & ACT ($\eta=16$) & \uline{28.6} & \uline{38.7} & \uline{15.1} & \uline{43.7} & \uline{15.8} & \uline{37.9} & \uline{16.0} & \uline{31.5} & \uline{0.496} & \uline{0.834} & \uline{11.3} & \uline{9.8} & \uline{21.2} & \uline{2.1} & \uline{34.7}\tabularnewline
+v7 & ACT ($\eta=16$) & R:V &  &  &  &  &  &  &  &  &  &  &  &  &  & \tabularnewline
+ & ACT ($\eta=32$) & 27.5 & 38.2 & 12.2 & 43.0 & 15.5 & 37.7 & 15.1 & 32.2 & 0.472 & 0.821 & 11.1 & 9.4 & 14.9 & 1.0 & 33.9\tabularnewline
 \hline 
- &  &  & HM:R$\rightarrow$M ($\eta=2$) &  &  &  &  &  &  &  &  &  &  &  &  &  &  & \tabularnewline
- &  &  & HM:R$\rightarrow$M ($\eta=4$) &  &  &  &  &  &  &  &  &  &  &  &  &  &  & \tabularnewline
- &  &  & HM:R$\rightarrow$M ($\eta=8$) &  &  &  &  &  &  &  &  &  &  &  &  &  &  & \tabularnewline
- &  &  & HM:R$\rightarrow$M ($\eta=16$) &  &  &  &  &  &  &  &  &  &  &  &  &  &  & \tabularnewline
- &  &  & HM:R$\rightarrow$M ($\eta=32$) &  &  &  &  &  &  &  &  &  &  &  &  &  &  & \tabularnewline
+ & HM{[}$\mathcal{R},\mathcal{M}${]} ($\eta=2$) & 34.3 & 44.9 & 19.5 & 47.4 & 7.7 & 77.5 & 6.5 & 70.8 & 0.636 & 1.281 & 4.3 & 2.6 & 21.1 & 0.2 & 18.1\tabularnewline
+ & HM$|_{\text{Random}}^{\text{Semihard}}$ ($\eta=4$) & 30.7 & 40.3 & 16.4 & 45.3 & 13.9 & 60.4 & 13.5 & 48.1 & 0.582 & 1.041 & 6.6 & 6.6 & 20.2 & 1.2 & 27.1\tabularnewline
+ & HM$|_{\text{Random}}^{\text{Semihard}}$ ($\eta=8$) & 27.0 & 36.0 & 13.2 & 42.5 & 19.4 & 48.0 & 22.2 & 32.0 & 0.535 & 0.867 & 11.6 & 10.4 & 19.3 & 2.9 & 35.1\tabularnewline
+ & HM$|_{\text{Random}}^{\text{Semihard}}$ ($\eta=16$) & 23.8 & 32.6 & 11.6 & 40.6 & 20.9 & 45.0 & 24.6 & 28.6 & 0.494 & 0.805 & 15.6 & 11.3 & 22.1 & 3.2 & 38.0\tabularnewline
+ & HM$|_{\text{Random}}^{\text{Semihard}}$ ($\eta=32$) & 23.1 & 31.9 & 11.3 & 40.3 & 22.8 & 46.0 & 24.3 & 28.3 & 0.495 & 0.800 & 14.2 & 11.7 & 19.7 & 3.8 & 38.0\tabularnewline
 \hline 
- &  &  & HM:S$\rightarrow$M ($\eta=2$) &  &  &  &  &  &  &  &  &  &  &  &  &  &  & \tabularnewline
- &  &  & HM:S$\rightarrow$M ($\eta=4$) &  &  &  &  &  &  &  &  &  &  &  &  &  &  & \tabularnewline
- &  &  & HM:S$\rightarrow$M ($\eta=8$) &  &  &  &  &  &  &  &  &  &  &  &  &  &  & \tabularnewline
- &  &  & HM:S$\rightarrow$M ($\eta=16$) &  &  &  &  &  &  &  &  &  &  &  &  &  &  & \tabularnewline
- &  &  & HM:S$\rightarrow$M ($\eta=32$) &  &  &  &  &  &  &  &  &  &  &  &  &  &  & \tabularnewline
+ & HM$|_{\text{Softhard}}^{\text{Semihard}}$ ($\eta=2$) & 44.5 & 56.1 & 27.8 & 53.3 & 1.9 & 87.7 & 1.6 & 88.8 & 0.827 & 1.101 & 3.7 & 0.3 & 19.0 & 0.0 & 11.6\tabularnewline
+ & HM$|_{\text{Softhard}}^{\text{Semihard}}$ ($\eta=4$) & 40.6 & 51.8 & 24.2 & 51.0 & 7.3 & 64.1 & 6.3 & 60.9 & 0.715 & 0.894 & 7.9 & 4.4 & 22.8 & 0.2 & 22.1\tabularnewline
+ & HM$|_{\text{Softhard}}^{\text{Semihard}}$ ($\eta=8$) & 38.4 & 49.7 & 22.9 & 50.3 & 10.9 & 50.5 & 10.8 & 44.6 & 0.680 & 0.722 & 13.3 & 11.2 & 25.8 & 1.2 & 29.6\tabularnewline
+ & HM$|_{\text{Softhard}}^{\text{Semihard}}$ ($\eta=16$) & 36.0 & 46.2 & 20.6 & 48.5 & 14.5 & 39.7 & 15.8 & 32.8 & 0.587 & 0.678 & 18.6 & 16.8 & 27.6 & 3.1 & 36.2\tabularnewline
+ & HM$|_{\text{Softhard}}^{\text{Semihard}}$ ($\eta=32$) & Q &  &  &  &  &  &  &  &  &  &  &  &  &  & \tabularnewline
 \end{tabular}
+
 }

### 2021-10-15 robdml.tex
tex

@@
 \subsection{Selection of Source \& Destination Hardness}
+\label{sec:41}
 
@@
 \subsection{Efficiency of Hardness Manipulation}
+\label{sec:42}
 
@@
 
+Conditions for a good source and destination hardness:
+%
+(1) the destination hardness is semihard (or something between semihard
+and softhard, we leave new sampling strategy for future work).
+(2) the source hardness should have high variance and a relatively high mean
+value to ensure number of benign example and number of adversarial example ratio.
+
+\oo{Note, naive combination of benign training and adv train does not lead to better
+result, why?} mix 0.5
+
 \oo{experiment, 8 step by default}
@@
 \subsection{Effectiveness of GA and ICS}
+\label{sec:43}
+
+\input{tab-gaeff.tex}
+
+\cref{tab:gaeff}
 

### 2021-10-16 introplot.py
svg

@@ -7,27 +7,20 @@ plt.rcParams['font.serif'] = 'FreeSerif'
 plt.rcParams['font.size'] = 14
 
 data = {
-        'ACT': (
+        'ACT': ( # [freeze]
             (27.5, 28.6, 30.6, 38.4, 46.5),
             (33.0, 17.0, 9.0, 5.0, 3.0),
             (33.9, 34.7, 31.3, 13.9, 5.8),
             ),
-        #'amdsemi+aap0': (26.2, 9.0, 40.0),
-        #'hml2rmi': (25.2, 9.0, 39.8),
-        'hmetrm(bug)': (
-            (27.0, 27.1, 28.3, 34.9, 39.2),
-            (33.0, 17.0, 9.0, 5.0, 3.0),
-            (40.3, 40.0, 37.2, 25.6, 14.0),
-            ),
-        'hmetrm': (
+        'hmetrm': ( # [freeze]
             (23.1, 23.8, 27.0, 30.7, 34.3),
             (33.0, 17.0, 9.0, 5.0, 3.0),
             (38.0, 38.0, 35.1, 27.1, 18.1),
             ),
-        'hmetsm': (
-            (36.0, 38.4, 40.6, 44.5),
-            (17.0, 9.0, 5.0, 3.0),
-            (36.2, 29.6, 22.1, 11.6),
+        'hmetsm': ( # [freeze]
+            (35.3, 37.4, 38.4, 40.6, 44.5),
+            (33.0, 17.0, 9.0, 5.0, 3.0),
+            (35.7, 34.8, 29.6, 22.1, 11.6),
             ),
         'G4': (34.4, 9.0, 36.7),
         }

### 2021-10-16 tab-hmeff.tex
tab-hmeff (freeze)

@@
 \resizebox{\linewidth}{!}{
-	\setlength{\tabcolsep}{0.2em}
-
+\setlength{\tabcolsep}{0.2em}%
+\renewcommand{\arraystretch}{1.1}
 \begin{tabular}{cc|cccc|ccccc|ccccc|c}
@@
 \hline
- & ACT ($\eta=2$) & 46.5 & 58.4 & 29.1 & 55.6 & 0.6 & 98.9 & 0.4 & 98.1 & 0.837 & 1.666 & 0.2 & 0.2 & 19.6 & 0.0 & 5.8\tabularnewline
+\multirow{5}{*}{CUB} & ACT ($\eta=2$) & 46.5 & 58.4 & 29.1 & 55.6 & 0.6 & 98.9 & 0.4 & 98.1 & 0.837 & 1.666 & 0.2 & 0.2 & 19.6 & 0.0 & 5.8\tabularnewline
  & ACT ($\eta=4$) & 38.4 & 49.8 & 22.8 & 49.7 & 4.6 & 81.9 & 2.8 & 80.5 & 0.695 & 1.366 & 2.9 & 2.3 & 18.8 & 0.1 & 13.9\tabularnewline
  & ACT ($\eta=8$) & 30.6 & 40.1 & 16.5 & 45.6 & 13.7 & 46.8 & 12.6 & 39.3 & 0.547 & 0.902 & 13.6 & 9.8 & 21.9 & 1.3 & 31.3\tabularnewline
- & ACT ($\eta=16$) & \uline{28.6} & \uline{38.7} & \uline{15.1} & \uline{43.7} & \uline{15.8} & \uline{37.9} & \uline{16.0} & \uline{31.5} & \uline{0.496} & \uline{0.834} & \uline{11.3} & \uline{9.8} & \uline{21.2} & \uline{2.1} & \uline{34.7}\tabularnewline
-v7 & ACT ($\eta=16$) & R:V &  &  &  &  &  &  &  &  &  &  &  &  &  & \tabularnewline
+ & ACT ($\eta=16$) & 28.6 & 38.7 & 15.1 & 43.7 & 15.8 & 37.9 & 16.0 & 31.5 & 0.496 & 0.834 & 11.3 & 9.8 & 21.2 & 2.1 & 34.7\tabularnewline
  & ACT ($\eta=32$) & 27.5 & 38.2 & 12.2 & 43.0 & 15.5 & 37.7 & 15.1 & 32.2 & 0.472 & 0.821 & 11.1 & 9.4 & 14.9 & 1.0 & 33.9\tabularnewline
 \hline
- & HM{[}$\mathcal{R},\mathcal{M}${]} ($\eta=2$) & 34.3 & 44.9 & 19.5 & 47.4 & 7.7 & 77.5 & 6.5 & 70.8 & 0.636 & 1.281 & 4.3 & 2.6 & 21.1 & 0.2 & 18.1\tabularnewline
- & HM$|_{\text{Random}}^{\text{Semihard}}$ ($\eta=4$) & 30.7 & 40.3 & 16.4 & 45.3 & 13.9 & 60.4 & 13.5 & 48.1 & 0.582 & 1.041 & 6.6 & 6.6 & 20.2 & 1.2 & 27.1\tabularnewline
- & HM$|_{\text{Random}}^{\text{Semihard}}$ ($\eta=8$) & 27.0 & 36.0 & 13.2 & 42.5 & 19.4 & 48.0 & 22.2 & 32.0 & 0.535 & 0.867 & 11.6 & 10.4 & 19.3 & 2.9 & 35.1\tabularnewline
- & HM$|_{\text{Random}}^{\text{Semihard}}$ ($\eta=16$) & 23.8 & 32.6 & 11.6 & 40.6 & 20.9 & 45.0 & 24.6 & 28.6 & 0.494 & 0.805 & 15.6 & 11.3 & 22.1 & 3.2 & 38.0\tabularnewline
- & HM$|_{\text{Random}}^{\text{Semihard}}$ ($\eta=32$) & 23.1 & 31.9 & 11.3 & 40.3 & 22.8 & 46.0 & 24.3 & 28.3 & 0.495 & 0.800 & 14.2 & 11.7 & 19.7 & 3.8 & 38.0\tabularnewline
+\multirow{5}{*}{CUB} & HM{[}$\mathcal{R},\mathcal{M}${]} ($\eta=2$) & 34.3 & 44.9 & 19.5 & 47.4 & 7.7 & 77.5 & 6.5 & 70.8 & 0.636 & 1.281 & 4.3 & 2.6 & 21.1 & 0.2 & 18.1\tabularnewline
+ & HM{[}$\mathcal{R},\mathcal{M}${]} ($\eta=4$) & 30.7 & 40.3 & 16.4 & 45.3 & 13.9 & 60.4 & 13.5 & 48.1 & 0.582 & 1.041 & 6.6 & 6.6 & 20.2 & 1.2 & 27.1\tabularnewline
+ & HM{[}$\mathcal{R},\mathcal{M}${]} ($\eta=8$) & 27.0 & 36.0 & 13.2 & 42.5 & 19.4 & 48.0 & 22.2 & 32.0 & 0.535 & 0.867 & 11.6 & 10.4 & 19.3 & 2.9 & 35.1\tabularnewline
+ & HM{[}$\mathcal{R},\mathcal{M}${]} ($\eta=16$) & 23.8 & 32.6 & 11.6 & 40.6 & 20.9 & 45.0 & 24.6 & 28.6 & 0.494 & 0.805 & 15.6 & 11.3 & 22.1 & 3.2 & 38.0\tabularnewline
+ & HM{[}$\mathcal{R},\mathcal{M}${]} ($\eta=32$) & 23.1 & 31.9 & 11.3 & 40.3 & 22.8 & 46.0 & 24.3 & 28.3 & 0.495 & 0.800 & 14.2 & 11.7 & 19.7 & 3.8 & 38.0\tabularnewline
 \hline
- & HM$|_{\text{Softhard}}^{\text{Semihard}}$ ($\eta=2$) & 44.5 & 56.1 & 27.8 & 53.3 & 1.9 & 87.7 & 1.6 & 88.8 & 0.827 & 1.101 & 3.7 & 0.3 & 19.0 & 0.0 & 11.6\tabularnewline
- & HM$|_{\text{Softhard}}^{\text{Semihard}}$ ($\eta=4$) & 40.6 & 51.8 & 24.2 & 51.0 & 7.3 & 64.1 & 6.3 & 60.9 & 0.715 & 0.894 & 7.9 & 4.4 & 22.8 & 0.2 & 22.1\tabularnewline
- & HM$|_{\text{Softhard}}^{\text{Semihard}}$ ($\eta=8$) & 38.4 & 49.7 & 22.9 & 50.3 & 10.9 & 50.5 & 10.8 & 44.6 & 0.680 & 0.722 & 13.3 & 11.2 & 25.8 & 1.2 & 29.6\tabularnewline
- & HM$|_{\text{Softhard}}^{\text{Semihard}}$ ($\eta=16$) & 36.0 & 46.2 & 20.6 & 48.5 & 14.5 & 39.7 & 15.8 & 32.8 & 0.587 & 0.678 & 18.6 & 16.8 & 27.6 & 3.1 & 36.2\tabularnewline
- & HM$|_{\text{Softhard}}^{\text{Semihard}}$ ($\eta=32$) & Q &  &  &  &  &  &  &  &  &  &  &  &  &  & \tabularnewline
+\multirow{5}{*}{CUB} & HM{[}$\mathcal{S},\mathcal{M}${]} ($\eta=2$) & 44.5 & 56.1 & 27.8 & 53.3 & 1.9 & 87.7 & 1.6 & 88.8 & 0.827 & 1.101 & 3.7 & 0.3 & 19.0 & 0.0 & 11.6\tabularnewline
+ & HM{[}$\mathcal{S},\mathcal{M}${]} ($\eta=4$) & 40.6 & 51.8 & 24.2 & 51.0 & 7.3 & 64.1 & 6.3 & 60.9 & 0.715 & 0.894 & 7.9 & 4.4 & 22.8 & 0.2 & 22.1\tabularnewline
+ & HM{[}$\mathcal{S},\mathcal{M}${]} ($\eta=8$) & 38.4 & 49.7 & 22.9 & 50.3 & 10.9 & 50.5 & 10.8 & 44.6 & 0.680 & 0.722 & 13.3 & 11.2 & 25.8 & 1.2 & 29.6\tabularnewline
+ & HM{[}$\mathcal{S},\mathcal{M}${]} ($\eta=16$) & 37.4 & 47.3 & 21.0 & 48.2 & 14.4 & 42.0 & 14.8 & 34.7 & 0.599 & 0.693 & 17.5 & 14.4 & 26.5 & 2.4 & 34.8\tabularnewline
+ & HM{[}$\mathcal{S},\mathcal{M}${]} ($\eta=32$) & 35.3 & 46.1 & 20.2 & 48.0 & 15.1 & 41.8 & 15.2 & 33.0 & 0.589 & 0.686 & 18.7 & 14.9 & 27.8 & 2.9 & 35.7\tabularnewline
 \end{tabular}

### 2021-10-17 introplot.py
svg

@@ -22,7 +22,11 @@ data = {
             (33.0, 17.0, 9.0, 5.0, 3.0),
             (35.7, 34.8, 29.6, 22.1, 11.6),
             ),
-        'G4': (34.4, 9.0, 36.7),
+        'HM(S,SGA)': (
+            (47.5, 42.7, 35.5),
+            (3.0, 5.0, 9.0),
+            (11.7, 20.8, 35.3),
+            ),
         }
 
 plt.figure(figsize=[10.8, 4.8])
@@ -37,7 +41,7 @@ for (name, (r1, cost, ers)) in data.items():
         plt.plot(cost, ers, f'v-', color='tab:blue')
     elif name == 'hmetsm':
         plt.plot(cost, ers, f'^-', color='tab:red')
-    elif name == 'hmix':
+    elif name == 'HM(S,SGA)':
         plt.plot(cost, ers, f'h-', color='deeppink')
     else:
         plt.plot(cost, ers, f'-o', color='k')
@@ -68,7 +72,7 @@ for (name, (r1, cost, ers)) in data.items():
         plt.plot(r1, ers, f'v-', color='tab:blue')
     elif name == 'hmetsm':
         plt.plot(r1, ers, f'^-', color='tab:red')
-    elif name == 'hmix':
+    elif name == 'HM(S,SGA)':
         plt.plot(r1, ers, f'h-', color='deeppink')
     else:
         plt.plot(r1, ers, f'-o', color='k')

### 2021-10-17 introplot.py
svg

@@ -27,6 +27,11 @@ data = {
             (3.0, 5.0, 9.0),
             (11.7, 20.8, 35.3),
             ),
+        'HM(S,-r/2)': (
+            (44.5, 36.8),
+            (3.0, 9.0),
+            (12.4, 33.8),
+            ),
         }
 
 plt.figure(figsize=[10.8, 4.8])

### 2021-10-17 introplot.py
lyx

@@ -28,9 +28,9 @@ data = {
             (11.7, 20.8, 35.3),
             ),
         'HM(S,-r/2)': (
-            (44.5, 36.8),
-            (3.0, 9.0),
-            (12.4, 33.8),
+            (44.5, 40.0, 36.8),
+            (3.0, 5.0, 9.0),
+            (12.4, 24.7, 33.8),
             ),
         }
 

### 2021-10-18 introplot.py
lyx

@@ -23,9 +23,9 @@ data = {
             (35.7, 34.8, 29.6, 22.1, 11.6),
             ),
         'HM(S,SGA)': (
-            (47.5, 42.7, 35.5),
-            (3.0, 5.0, 9.0),
-            (11.7, 20.8, 35.3),
+            (47.5, 42.7, 38.0, 37.0, 36.5),
+            (3.0, 5.0, 9.0, 17.0, 33.0),
+            (11.7, 20.8, 32.4, 34.5, 35.9),
             ),
         'HM(S,-r/2)': (
             (44.5, 40.0, 36.8),

### 2021-10-19 introplot.py
lyx

@@ -28,9 +28,9 @@ data = {
             (11.7, 20.8, 32.4, 34.5, 35.9),
             ),
         'HM(S,-r/2)': (
-            (44.5, 40.0, 36.8),
-            (3.0, 5.0, 9.0),
-            (12.4, 24.7, 33.8),
+            (44.5, 40.0, 36.8, 35.2),
+            (3.0, 5.0, 9.0, 33.0),
+            (12.4, 24.7, 33.8, 37.0),
             ),
         }
 

### 2021-10-21 tab-hmeff.tex
tex
tab

--- 2021-10-14 tab-hmeff.tex
@@
 \resizebox{\linewidth}{!}{
-	\setlength{\tabcolsep}{0.2em}
-\begin{tabular}{cccc|cccc|ccccc|ccccc|c}
+\setlength{\tabcolsep}{0.4em}%
+\renewcommand{\arraystretch}{1.1}
+\begin{tabular}{c|cc|cccc|ccccc|ccccc|c}
+
+	\toprule
+
+\multirow{2}{*}{\textbf{Dataset}} & \multicolumn{1}{c}{\multirow{2}{*}{\textbf{Defense}}} & \multirow{2}{*}{$\eta$} & \multicolumn{4}{c|}{\textbf{Benign Example}} & \multicolumn{10}{c|}{\textbf{White-Box Attacks for Robustness Evaluation}} & \multirow{2}{*}{\textbf{ERS$\uparrow$}}\tabularnewline
+\cline{4-17} \cline{5-17} \cline{6-17} \cline{7-17} \cline{8-17} \cline{9-17} \cline{10-17} \cline{11-17} \cline{12-17} \cline{13-17} \cline{14-17} \cline{15-17} \cline{16-17} \cline{17-17} 
+ &  &  & R@1$\uparrow$ & R@2$\uparrow$ & mAP$\uparrow$ & NMI$\uparrow$ & CA+$\uparrow$ & CA-$\downarrow$ & QA+$\uparrow$ & QA-$\downarrow$ & TMA$\downarrow$ & ES:D$\downarrow$ & ES:R$\uparrow$ & LTM$\uparrow$ & GTM$\uparrow$ & GTT$\uparrow$ & \tabularnewline
+
+	\midrule
+
+CUB & N/A & N/A & 53.9 & 66.4 & 26.1 & 59.5 & 0.0 & 100.0 & 0.0 & 99.9 & 0.883 & 1.762 & 0.0 & 0.0 & 14.1 & 0.0 & 3.8\tabularnewline
 \hline 
-\multicolumn{1}{c|}{\multirow{2}{*}{\textbf{Dataset}}} & \multicolumn{1}{c|}{\multirow{2}{*}{\textbf{Model}}} & \multicolumn{1}{c|}{\multirow{2}{*}{\textbf{Loss}}} & \multirow{2}{*}{\textbf{Defense}} & \multicolumn{4}{c|}{\textbf{Benign Example}} & \multicolumn{10}{c|}{\textbf{White-Box Attacks for Robustness Evaluation}} & \multirow{2}{*}{\textbf{ERS$\uparrow$}}\tabularnewline
-\cline{5-18} \cline{6-18} \cline{7-18} \cline{8-18} \cline{9-18} \cline{10-18} \cline{11-18} \cline{12-18} \cline{13-18} \cline{14-18} \cline{15-18} \cline{16-18} \cline{17-18} \cline{18-18} 
- &  &  &  & R@1$\uparrow$ & R@2$\uparrow$ & mAP$\uparrow$ & NMI$\uparrow$ & CA+$\uparrow$ & CA-$\downarrow$ & QA+$\uparrow$ & QA-$\downarrow$ & TMA$\downarrow$ & ES:D$\downarrow$ & ES:R$\uparrow$ & LTM$\uparrow$ & GTM$\uparrow$ & GTT$\uparrow$ & \tabularnewline
+\multirow{5}{*}{CUB} & ACT & 2 & 46.5 & 58.4 & 29.1 & 55.6 & 0.6 & 98.9 & 0.4 & 98.1 & 0.837 & 1.666 & 0.2 & 0.2 & 19.6 & 0.0 & 5.8\tabularnewline
+ & ACT & 4 & 38.4 & 49.8 & 22.8 & 49.7 & 4.6 & 81.9 & 2.8 & 80.5 & 0.695 & 1.366 & 2.9 & 2.3 & 18.8 & 0.1 & 13.9\tabularnewline
+ & ACT & 8 & 30.6 & 40.1 & 16.5 & 45.6 & 13.7 & 46.8 & 12.6 & 39.3 & 0.547 & 0.902 & 13.6 & 9.8 & 21.9 & 1.3 & 31.3\tabularnewline
+ & ACT & 16 & 28.6 & 38.7 & 15.1 & 43.7 & 15.8 & 37.9 & 16.0 & 31.5 & 0.496 & 0.834 & 11.3 & 9.8 & 21.2 & 2.1 & 34.7\tabularnewline
+ & ACT & 32 & 27.5 & 38.2 & 12.2 & 43.0 & 15.5 & 37.7 & 15.1 & 32.2 & 0.472 & 0.821 & 11.1 & 9.4 & 14.9 & 1.0 & 33.9\tabularnewline
 \hline 
+\multirow{5}{*}{CUB} & HM{[}$\mathcal{R},\mathcal{M}${]} & 2 & 34.3 & 44.9 & 19.5 & 47.4 & 7.7 & 77.5 & 6.5 & 70.8 & 0.636 & 1.281 & 4.3 & 2.6 & 21.1 & 0.2 & 18.1\tabularnewline
+ & HM{[}$\mathcal{R},\mathcal{M}${]} & 4 & 30.7 & 40.3 & 16.4 & 45.3 & 13.9 & 60.4 & 13.5 & 48.1 & 0.582 & 1.041 & 6.6 & 6.6 & 20.2 & 1.2 & 27.1\tabularnewline
+ & HM{[}$\mathcal{R},\mathcal{M}${]} & 8 & 27.0 & 36.0 & 13.2 & 42.5 & 19.4 & 48.0 & 22.2 & 32.0 & 0.535 & 0.867 & 11.6 & 10.4 & 19.3 & 2.9 & 35.1\tabularnewline
+ & HM{[}$\mathcal{R},\mathcal{M}${]}  & 16 & 23.8 & 32.6 & 11.6 & 40.6 & 20.9 & 45.0 & 24.6 & 28.6 & 0.494 & 0.805 & 15.6 & 11.3 & 22.1 & 3.2 & 38.0\tabularnewline
+ & HM{[}$\mathcal{R},\mathcal{M}${]} & 32 & 23.1 & 31.9 & 11.3 & 40.3 & 22.8 & 46.0 & 24.3 & 28.3 & 0.495 & 0.800 & 14.2 & 11.7 & 19.7 & 3.8 & 38.0\tabularnewline
 \hline 
-CUB & RN18 & Triplet & N/A & 53.9 & 66.4 & 26.1 & 59.5 & 0.0 & 100.0 & 0.0 & 99.9 & 0.883 & 1.762 & 0.0 & 0.0 & 14.1 & 0.0 & 3.8\tabularnewline
-\hline 
- &  &  & ACT ($\eta=2$) & 46.5 & 58.4 & 29.1 & 55.6 & 0.6 & 98.9 & 0.4 & 98.1 & 0.837 & 1.666 & 0.2 & 0.2 & 19.6 & 0.0 & 5.8\tabularnewline
- &  &  & ACT ($\eta=4$) & 38.4 & 49.8 & 22.8 & 49.7 & 4.6 & 81.9 & 2.8 & 80.5 & 0.695 & 1.366 & 2.9 & 2.3 & 18.8 & 0.1 & 13.9\tabularnewline
- &  &  & ACT ($\eta=8$) & 30.6 & 40.1 & 16.5 & 45.6 & 13.7 & 46.8 & 12.6 & 39.3 & 0.547 & 0.902 & 13.6 & 9.8 & 21.9 & 1.3 & 31.3\tabularnewline
- &  &  & ACT ($\eta=16$) & \uline{28.6} & \uline{38.7} & \uline{15.1} & \uline{43.7} & \uline{15.8} & \uline{37.9} & \uline{16.0} & \uline{31.5} & \uline{0.496} & \uline{0.834} & \uline{11.3} & \uline{9.8} & \uline{21.2} & \uline{2.1} & \uline{34.7}\tabularnewline
- &  &  & ACT ($\eta=32$) & 27.5 & 38.2 & 12.2 & 43.0 & 15.5 & 37.7 & 15.1 & 32.2 & 0.472 & 0.821 & 11.1 & 9.4 & 14.9 & 1.0 & 33.9\tabularnewline
-\hline 
- &  &  & HM:R$\rightarrow$M ($\eta=2$) &  &  &  &  &  &  &  &  &  &  &  &  &  &  & \tabularnewline
- &  &  & HM:R$\rightarrow$M ($\eta=4$) &  &  &  &  &  &  &  &  &  &  &  &  &  &  & \tabularnewline
- &  &  & HM:R$\rightarrow$M ($\eta=8$) &  &  &  &  &  &  &  &  &  &  &  &  &  &  & \tabularnewline
- &  &  & HM:R$\rightarrow$M ($\eta=16$) &  &  &  &  &  &  &  &  &  &  &  &  &  &  & \tabularnewline
- &  &  & HM:R$\rightarrow$M ($\eta=32$) &  &  &  &  &  &  &  &  &  &  &  &  &  &  & \tabularnewline
-\hline 
- &  &  & HM:S$\rightarrow$M ($\eta=2$) &  &  &  &  &  &  &  &  &  &  &  &  &  &  & \tabularnewline
- &  &  & HM:S$\rightarrow$M ($\eta=4$) &  &  &  &  &  &  &  &  &  &  &  &  &  &  & \tabularnewline
- &  &  & HM:S$\rightarrow$M ($\eta=8$) &  &  &  &  &  &  &  &  &  &  &  &  &  &  & \tabularnewline
- &  &  & HM:S$\rightarrow$M ($\eta=16$) &  &  &  &  &  &  &  &  &  &  &  &  &  &  & \tabularnewline
- &  &  & HM:S$\rightarrow$M ($\eta=32$) &  &  &  &  &  &  &  &  &  &  &  &  &  &  & \tabularnewline
+\multirow{5}{*}{CUB} & HM{[}$\mathcal{S},\mathcal{M}${]} & 2 & 44.5 & 56.1 & 27.8 & 53.3 & 1.9 & 87.7 & 1.6 & 88.8 & 0.827 & 1.101 & 3.7 & 0.3 & 19.0 & 0.0 & 11.6\tabularnewline
+ & HM{[}$\mathcal{S},\mathcal{M}${]} & 4 & 40.6 & 51.8 & 24.2 & 51.0 & 7.3 & 64.1 & 6.3 & 60.9 & 0.715 & 0.894 & 7.9 & 4.4 & 22.8 & 0.2 & 22.1\tabularnewline
+ & HM{[}$\mathcal{S},\mathcal{M}${]} & 8 & 38.4 & 49.7 & 22.9 & 50.3 & 10.9 & 50.5 & 10.8 & 44.6 & 0.680 & 0.722 & 13.3 & 11.2 & 25.8 & 1.2 & 29.6\tabularnewline
+ & HM{[}$\mathcal{S},\mathcal{M}${]} & 16 & 37.4 & 47.3 & 21.0 & 48.2 & 14.4 & 42.0 & 14.8 & 34.7 & 0.599 & 0.693 & 17.5 & 14.4 & 26.5 & 2.4 & 34.8\tabularnewline
+ & HM{[}$\mathcal{S},\mathcal{M}${]} & 32 & 35.3 & 46.1 & 20.2 & 48.0 & 15.1 & 41.8 & 15.2 & 33.0 & 0.589 & 0.686 & 18.7 & 14.9 & 27.8 & 2.9 & 35.7\tabularnewline
+
+	\bottomrule
+
 \end{tabular}
+
 }
 
-\caption{Efficiency of Hardness Manipulation for Adversarial Training.}
+\caption{Effectiveness of Hardness Manipulation for Adversarial Training.}
 \label{tab:hmeff}

### 2021-10-21 introplot.py
svg

@@ -22,15 +22,15 @@ data = {
             (33.0, 17.0, 9.0, 5.0, 3.0),
             (35.7, 34.8, 29.6, 22.1, 11.6),
             ),
-        'HM(S,SGA)': (
+        'HM(S,SGA)': ( # [freeze]
             (47.5, 42.7, 38.0, 37.0, 36.5),
             (3.0, 5.0, 9.0, 17.0, 33.0),
             (11.7, 20.8, 32.4, 34.5, 35.9),
             ),
-        'HM(S,-r/2)': (
-            (44.5, 40.0, 36.8, 35.2),
-            (3.0, 5.0, 9.0, 33.0),
-            (12.4, 24.7, 33.8, 37.0),
+        'HM(S,-r/2)': ( # [freeze]
+            (44.5, 40.0, 36.8, 35.2, 34.7),
+            (3.0, 5.0, 9.0, 17.0, 33.0),
+            (12.4, 24.7, 33.8, 36.8, 37.0),
             ),
         }
 

### 2021-10-21 robdml.tex
tex

@@
 	% background
-	Deep metric learning, being vulnerable to adversarial
-	attacks, has safety and security implications in its applications.
+	Owing to the significance of the adversarial vulnerability of deep metric
+	learning models, which poses safety and security implications in its
+	applications, a series of defense methods have been proposed to improve its
+	adversarial robustness.
+	% insight
+	In order to avoid model collapse due to excessively hard examples, the
+	existing methods refrain from using the typical min-max adversarial
+	training paradigm, but instead learn from a weak adversary.
+	% our starting point
+	However, we argue that a model can learn from a strong adversary without
+	model collapse, where the key for overall performance is triplet hardness.
+	% HM framework
+	To this end, Hardness Manipulation is proposed to adversarially perturb
+	the training triplet to increase its hardness into a specified level,
+	by referencing other benign triplets, or a pseudo-hardness function.
+	% GA Adversary
+	To further improve the model performance, we propose a Gradual Adversary to
+	dynamicly change the hardness level to balance metric learning and
+	adversarial learning.
+	% Experiment
+	The proposed method is validated on three commonly used deep metric
+	learning datasets, namely CUB-200-2011, Cars-196, and Stanford Online
+	Product.
+	% Conclusion
+	Comprehensive experimental results show our method outperforms the existing
+	defense methods, while achieving clearly higher efficiency at a lower
+	training cost.  
 %
-	Owing to the significance of this issue, a series of defense methods
-	are proposed to improve its adversarial robustness.
-	% insight
-	However, as a model with triplet loss is prone to collapse with
-	excessively hard samples, the existing methods refrain from using the
-	classical min-max adversarial training paradigm, and hence suffer from
-	inefficient learning from a strong adversary.
-	% our finding
-	In this paper, we reveal a significant impact of triplet sampling strategy
-	on the adversarial training.
-	% solution 1
-	Based on this, Hardness Manipulation is proposed to adversarially perturb
-	a given triplet into a specified hardness level in min-max adversarial
-	training, instead of creating hardest triplets rendering model collapse.
-	% solution 2
-	To further improve the model performance, we propose a Gradual
-	Adversary to dynamicly change the hardness level to balance metric
-	learning and adversarial learning.
-	% Experiment
-	The proposed method is validated on three commonly
-	used deep metric learning datasets, namely CUB-200-2011, Cars-196,
-	and Stanford Online Product.
-	% Conclusion
-	Comprehensive experimental results show our method outperforms
-	the existing defense methods, while achieving clearly higher
-	efficiency at a lower training cost.
 \end{abstract}

### 2021-10-21 robdml.tex
tex

@@
 	% our starting point
-	However, we argue that a model can learn from a strong adversary without
-	model collapse, where the key for overall performance is triplet hardness.
+	Conversely, we argue that a model can learn from a strong adversary without
+	collapse, where the key is triplet hardness.
 	% HM framework
-	To this end, Hardness Manipulation is proposed to adversarially perturb
-	the training triplet to increase its hardness into a specified level,
-	by referencing other benign triplets, or a pseudo-hardness function.
+	To this end, Hardness Manipulation is proposed to adversarially perturb the
+	training triplet to increase its hardness into a specified level, by
+	referencing other benign triplets, or a pseudo-hardness function.
 	% GA Adversary
-	To further improve the model performance, we propose a Gradual Adversary to
-	dynamicly change the hardness level to balance metric learning and
-	adversarial learning.
-	% Experiment
-	The proposed method is validated on three commonly used deep metric
-	learning datasets, namely CUB-200-2011, Cars-196, and Stanford Online
-	Product.
-	% Conclusion
-	Comprehensive experimental results show our method outperforms the existing
-	defense methods, while achieving clearly higher efficiency at a lower
-	training cost.  
+	Based on this, Gradual Adversary is proposed as a family of pseudo-hardness
+	functions to overcome problems of referencing other benign triplets, and
+	achieve a better balance in the learning objective.
+	% ICS
+	\oo{ICS}
+	% Experiment and Conclusion
+	Comprehensive experimental results on three commonly used deep metric
+	learning datasets suggest that the proposed method, albeit remains
+	simple, overwhelmingly outperforms the state-of-the-art defense
+	methods in terms of robustness, training cost, as well as recall
+	performance on benign examples.
 %

### 2021-10-21 robdml.tex
abs
tex

@@
 	achieve a better balance in the learning objective.
-	% ICS
-	\oo{ICS}
+	% Intra-Class Structure
+	Besides, a penalty on Intra-Class Structure among benign and adversarial
+	examples, which has been neglected by existing methods, can be used to
+	further improve the model robustness.
 	% Experiment and Conclusion
@@
 
+% motivation of GA : late phase
+
+When benign triplets are used as reference for destination hardness, the
+adversary (\ie, hardness of adversarial triplets) could gradually become weaker
+than it should be in the late phase of training.
+%
+During the training process of a DML model, the expectation of the triplet loss
+$E[L_\text{T}(\cdots)]$ on benign examples is gradually decreasing
+(with the lower bound being zero).
+%
+The corresponding expectation of hardness $E[H(\cdots)]$ will
+decrease as well (with the lower bound being $-\gamma$).
+%
+As a result, $E[H_\mathsf{D}-H_\mathsf{S}]$ will gradually tend to zero,
+indicating a gradually decreasing strength of attack, and inefficiency in
+learning from a strong adversary.
+
+%
+
 \cref{fig:ga}
@@
 	%
-	g_\mathsf{B}(H(\cdots)) = H(\cdots) + \xi \cdot \bar{\ell}_{t-1}
+	g_\mathsf{B}(H(\cdots);\xi) = H(\cdots) + \xi \cdot (1-\bar{\ell}_{t-1})
 	%

### 2021-10-21 robdml.tex
tex

@@
 
+% hardness boosting
+
+Such deficiency in the late training process can be alleviated with a
+pseudo-hardness function that boosts the destination hardness when the loss
+value is low.
 %
+Denoting the loss value from the previous training iteration as $\ell_{t-1}$,
+we first normalize it into $[0,1]$ as $\bar{\ell}_{t-1}=\min(u,\ell_{t-1})/u$,
+where $u$ is a manually specified parameter.
+%
+Note, $u$ is much less than the theoretical upperbound of the loss function,
+in order to avoid excessive hardness boost.
+%
+Then the expectation of destination hardness can be linearly shifted (boosted)
+by a scaled constant by a ``hardness boosting'' pseudo-hardness
+function, \ie,
+%
+\begin{equation}
+	%
+	g_\mathsf{B}(H_\mathsf{D};\xi) = H_\mathsf{D} + \xi \cdot (1-\bar{\ell}_{t-1}).
+	%
+\end{equation}
+%
+And the adversarial examples from $\text{HM}(H_\mathsf{S},g_\mathsf{B}(H_\mathsf{D}))$
+can be used for training.
 
@@
 strong example when the embedding space is not in good shape.
-
-\[
-	\big(1-\text{Clip}_0^{U_L}[l_{t-1}]/U_L \big)\times
-	U_H
-\]
-
-\begin{equation}
-	%
-	g_\mathsf{B}(H(\cdots);\xi) = H(\cdots) + \xi \cdot (1-\bar{\ell}_{t-1})
-	%
-\end{equation}
 

### 2021-10-21 robdml.tex
tex

@@
 
+\cref{fig:ga}
+
 % motivation of GA : late phase
@@
 
-\cref{fig:ga}
+% motivation of GA: early phase
 
-During the training process, the strength of adversary will gradually decrease,
-because the expectation of the destination hardness $E[H_\mathsf{D}]$ is expected to
-decrease with a model being trained.
+However, while the destination hardness is boosted in the late phase of
+training, the adversarial examples may still hamper the learning of a good
+embedding space in the early phase.
+%
+At this point, we argue that learning from a strong adversary in the early
+training phase (\ie, when the embedding space is not ``in-good-shape'') hampers the
+generalization on benign examples.
+%
+In other words, the desired destination hardness should be (1) relatively weak
+in the early training phase, and (2) relatively strong in the late training
+phase.
+%
+We name the family of pseudo-hardness functions that fulfills the two
+conditions as ``Graduate Adversary''.
+%
+Additionally, if we have a strong prior knowledge on ``how hard the destination
+hardness should be'', the pseudo-hardness function can be independent from
+any benign triplet.
 
-strong example when the embedding space is not in good shape.
+% simple graduate adversary
 
+For instance, if we assume that the destination hardness should remain
+in the hardness range of Semihard~\cite{facenet}, the following function
+satisfies the two condictions of Gradual Adversary, dubbed
+``Simple Gradual Adversary'' (SGA):
+%
 \begin{equation}
 	%
-	g_\mathsf{SGA}() = -\gamma \cdot \bar{\ell}_{t-1}
+	g_\mathsf{SGA}() = -\gamma \cdot \bar{\ell}_{t-1} ~ \in [-\gamma,0].
 	%
 \end{equation}
+%
+The design of this function will be empirically supported in the experiments
+section.
+%
+The exploration of other possible pseudo-hardness functions is omitted to 
+keep simplicity.
 

### 2021-10-21 appendix.tex
tex
remove deprecated tabs
appendix

@@
 \appendix
+
+\section{Complete Table for Sec~4.1 Hardness Selection}
 
@@
 \begin{itemize}
+
+	\item [TODO] arxiv 2105.04906 for collapse issue.
+
+	\item [?] Can we learn more from the third and fourth standard moments?
+		Namely skewness and kurtosis.
+
+	\item [M] manuscript notes on SGA.
+
+	\item [\cmark] We don't have to mix HM(R,M) and HM(S,M).
+
+	\item [Q] Is ACT equivalent to $HM(H_\mathsf{S},0)$.
 
@@
 
+	\item [T] Revise and incorporate the state-of-the-art adversarial training
+		acceleration method (\ie, Free Adversarial Training~\cite{freeat},
+		which is designed for classification) into adversarial training of 
+		deep metric learning models. It will greatly improve the efficiency
+		of adversarial training.
+		%
+	\item [T] Benchmark of existing metric learning loss functions under
+		adversarial training scenario, and analyze their different
+		characteristics for future reference.
+		%
+	\item [T] Explore the possibility of proposing a new metric learning loss
+		function oriented for adversarial training, starting from scratch or
+		from an existing metric learning loss.
+		%
 \end{itemize}
@@
 
-\input{direct-amd.tex}
-
-\input{sort-hardness.tex}
-
 \input{fat-attempt-1.tex}
-
-\input{amdsemi.tex}
 

### 2021-10-21 robdml.tex
tex

@@
 %
-DML has been extensively studied~\cite{revisiting}, and has a
-wide range of applications such
-as image retrieval~\cite{imagesim2} and face recognition~\cite{facenet,domainface}.
+As an extensively studied task~\cite{revisiting}, DML has a wide range of
+applications such as image retrieval~\cite{imagesim2} and face
+recognition~\cite{facenet,domainface}, as well as a wide impact in
+the core idea of other areas such as self-supervised learning~\cite{dmlreality}.
 
@@
 %
-Such vulnerability poses safety, security, and fairness concerns in the
+Such vulnerability raises safety, security, and fairness concerns in the
 applications of DML.
@@
 %
-To counter the attacks (or reducing the vulnerability), it is important to
+To counter the attacks (\ie, mitigating the vulnerability), it is important to
 design defense methods to improve the adversarial robustness of DML models.
@@
 are incompatible to acceleration methods like Free Adversarial Training~\cite{freeat}.
+\oo{rob, time, r1}.
 
@@
 		%
-	\item Revise and incorporate the state-of-the-art adversarial training
-		acceleration method (\ie, Free Adversarial Training~\cite{freeat},
-		which is designed for classification) into adversarial training of 
-		deep metric learning models. It will greatly improve the efficiency
-		of adversarial training.
-		%
-	\item Benchmark of existing metric learning loss functions under
-		adversarial training scenario, and analyze their different
-		characteristics for future reference.
-		%
-	\item Explore the possibility of proposing a new metric learning loss
-		function oriented for adversarial training, starting from scratch or
-		from an existing metric learning loss.
-		%
 \end{enumerate}
+
+The proposed method overwhelmingly outperforms the state-of-the-art defense
+in terms of robustness, training cost, as well as the penalty on benign
+example retrieval.
 
@@
 	%
-	g_\mathsf{B}(H_\mathsf{D};\xi) = H_\mathsf{D} + \xi \cdot (1-\bar{\ell}_{t-1}).
+	g_\mathsf{B}(H_\mathsf{D};\xi,\bar{\ell}_{t-1}) =
+	H_\mathsf{D} + \xi \cdot (1-\bar{\ell}_{t-1}).
 	%
@@
 generalization on benign examples.
-%
+
+% Gradual Adversary
+
 In other words, the desired destination hardness should be (1) relatively weak
@@
 	%
-	g_\mathsf{SGA}() = -\gamma \cdot \bar{\ell}_{t-1} ~ \in [-\gamma,0].
+	g_\mathsf{SGA}(\bar{\ell}_{t-1}) =
+	-\gamma \cdot \bar{\ell}_{t-1} ~ \in [-\gamma,0].
 	%
 \end{equation}
+%
+And the adversarial examples from $\text{HM}(H_\mathsf{S},g_\mathsf{SGA})$
+can be used for adversarial training.
 %
@@
 %
-The exploration of other possible pseudo-hardness functions is omitted to 
-keep simplicity.
+The exploration of other possible pseudo-hardness functions is omitted 
+for simplicity.
 

### 2021-10-22 robdml.tex
tab
tex

@@
 	% background
-	Owing to the significance of the adversarial vulnerability of deep metric
-	learning models, which poses safety and security implications in its
-	applications, a series of defense methods have been proposed to improve its
-	adversarial robustness.
+	Owing to the security implications of adversarial vulnerability, the
+	adversarial robustness of deep metric learning models have to be improved
+	via defense.
 	% insight
@@
 	training triplet to increase its hardness into a specified level, by
-	referencing other benign triplets, or a pseudo-hardness function.
+	referencing another benign triplet or a pseudo-hardness function.
 	% GA Adversary
@@
 	Besides, a penalty on Intra-Class Structure among benign and adversarial
-	examples, which has been neglected by existing methods, can be used to
-	further improve the model robustness.
+	examples can further improve model robustness, which is neglected by
+	previous methods.
 	% Experiment and Conclusion
 	Comprehensive experimental results on three commonly used deep metric
-	learning datasets suggest that the proposed method, albeit remains
-	simple, overwhelmingly outperforms the state-of-the-art defense
-	methods in terms of robustness, training cost, as well as recall
-	performance on benign examples.
+	learning datasets suggest that the proposed method overwhelmingly
+	outperforms the state-of-the-art defense methods in terms of robustness,
+	training cost, as well as recall performance on benign examples, while
+	remains in a simple form.
 %
@@
 Note, $u$ is much less than the theoretical upperbound of the loss function,
-in order to avoid excessive hardness boost.
+in order to avoid excessive hardness boost in the functions introduced below.
 %
@@
 
+\input{tab-ics.tex}
+
 Put together for easier comparison.
@@
 \subsection{Comparison with State-of-the-art}
+
+\input{tab-sota.tex}
 

### 2021-10-22 robdml.tex
tex

@@
 	In order to avoid model collapse due to excessively hard examples, the
-	existing methods refrain from using the typical min-max adversarial
-	training paradigm, but instead learn from a weak adversary.
+	existing methods refrain from using the min-max adversarial
+	training, but instead learns from a weak adversary inefficiently.
 	% our starting point
@@
 applications such as image retrieval~\cite{imagesim2} and face
-recognition~\cite{facenet,domainface}, as well as a wide impact in
+recognition~\cite{facenet,domainface}, as well as a wide influence on
 the core idea of other areas such as self-supervised learning~\cite{dmlreality}.
 
-Despite the improvements of this field thanks to the advancement of deep neural
-networks, recent research works suggest that DML models are vulnerable to
-adversarial attacks, where an imperceptible perturbation could incur unexpected
-or covertly manipulated results~\cite{advrank,advorder}.
+Despite the advancements in this field thanks to deep neural
+networks, recent studies find DML models vulnerable to
+adversarial attacks, where an imperceptible perturbation can incur unexpected
+retrieval, or covertly manipulate the results~\cite{advrank,advorder}.
 %
-Such vulnerability raises safety, security, and fairness concerns in the
-applications of DML.
+Such vulnerability raises security, safety, and fairness concerns in the
+DML applications.
 %
-For example, impersonation or recognition evation are possible for DML-based
-face-identification system.
+For example, impersonation or recognition evation are possible for a
+vulnerable DML-based face-identification system.
 %
-To counter the attacks (\ie, mitigating the vulnerability), it is important to
-design defense methods to improve the adversarial robustness of DML models.
+To counter the attacks (\ie, mitigating the vulnerability), the
+adversarial robustness of DML models has to be improved via defense.
 
@@
 % existing methods & problem
-Several defense methods for DML are proposed in the
-literature~\cite{advrank,robrank}, inspired by the Madry's adversarial training
-method~\cite{madry}, as it is kown as one of the most effective defense methods
-for deep neural network classifiers.
+Several adversarial training-based defense methods for DML are proposed in the
+literature~\cite{advrank,robrank}, which are inspired by the Madry's min-max
+adversarial training~\cite{madry} because it is one of the most effective
+defense methods for deep neural network classifiers.
 %
-However, it has been noted that
+However, it is widely known that such methods always suffer from greatly increased
+training cost and a notable penalty in the model's retrieval performance on
+benign (\ie, unperturbed) examples.
+%
+Meanwhile, the level of robustness that the previous methods have achieved
+is still insufficient.
 %
@@
 %
-(2) the direct adaptation of Madry's min-max adversarial training~\cite{madry} will easily
-lead to model collapse due to producing very hard sample triplets;
+(2) the direct adaptation of Madry's min-max adversarial training~\cite{madry}
+will easily lead to model collapse due to producing very hard sample triplets;
 %
-(3) the adversarial training procedure is very time-consuming compared to
-the training process of a regular DML model, but existing defense methods
-are incompatible to acceleration methods like Free Adversarial Training~\cite{freeat}.
-\oo{rob, time, r1}.
+(3) the adversarial training procedure is very time-consuming compared to the
+training process of a regular DML model, but existing defense methods are
+incompatible to acceleration methods like Free Adversarial
+Training~\cite{freeat}.  \oo{rob, time, r1}.
 

### 2021-10-22 robdml.tex
tex

@@
 	\includegraphics[width=1.0\columnwidth]{introplot.pdf}
-	\caption{\oo{Performance plot with aligned conditions.
-	(1) robustness and r1 under the same training cost;
-	(2) r1 and training cost for reaching similar robustness;
-	(3) training cost and robustness for reaching similar r1.}}
+	\caption{
+		%
+		Comparison in robustness, training time cost, and recall@1 performance
+		between our method and the state-of-the-art method.
+		%
+		Our method performs much better in all the three aspects.
+		%
+	}
 	\label{fig:introplot}

### 2021-10-22 robdml.tex
tex

@@
 
-Given a set of data points, a metric gives a distance value between each pair
-of them.
+Given a set of data points, a \emph{metric} gives a distance value between each
+pair of them.
 %
@@
 applications such as image retrieval~\cite{imagesim2} and face
-recognition~\cite{facenet,domainface}, as well as a wide influence on
-the core idea of other areas such as self-supervised learning~\cite{dmlreality}.
+recognition~\cite{facenet,domainface}, as well as a wide influence on the core
+idea of other areas such as self-supervised learning~\cite{dmlreality}.
 
@@
 To counter the attacks (\ie, mitigating the vulnerability), the
-adversarial robustness of DML models has to be improved via defense.
+\emph{adversarial robustness} of DML models has to be improved via defense.
 
@@
 % existing methods & problem
-Several adversarial training-based defense methods for DML are proposed in the
-literature~\cite{advrank,robrank}, which are inspired by the Madry's min-max
-adversarial training~\cite{madry} because it is one of the most effective
-defense methods for deep neural network classifiers.
+Existing defense methods for DML~\cite{advrank,robrank} are adversarial
+training-based, inspired by Madry's \emph{min-max} adversarial
+training~\cite{madry} because it is one of the most effective methods for deep
+neural network classifiers.
 %
-However, it is widely known that such methods always suffer from greatly increased
-training cost and a notable penalty in the model's retrieval performance on
-benign (\ie, unperturbed) examples.
+Specifically, Madry's method involves a inner problem to \emph{maximize} the
+loss by perturbing the inputs into adversarial examples, and an outer problem
+to \emph{minimize} the loss by updating the model parameters.
+%
+However, in order to avoid model collapse, the existing DML defenses refrain
+from directly adopting such paradigm, but instead use some indirect and
+relatively weak objectives to merely increase the loss value to a certain
+level.
+%
+As a result, the model is not learning from a strong adversary, and suffers
+from low efficiency in gaining robustness within limited time. 
+%
+Furthermore, advertsarial training already suffers from
+significant training time cost (compared to the normal training process).
+%
+Hence, time efficiency in gaining adversarial robustness is an inevitable
+major issue.
+
+We conjecture there is a certain intermediate level of hardness.
+
+notable penalty in the model performance on benign (\ie, unperturbed) examples.
+
+%
+\oo{rev}
 %

### 2021-10-22 robdml.tex
update

@@
 	In order to avoid model collapse due to excessively hard examples, the
-	existing methods refrain from using the min-max adversarial
-	training, but instead learns from a weak adversary inefficiently.
+	existing methods refrain from using the min-max adversarial training, but
+	instead learns from a weak adversary inefficiently.
 	% our starting point
@@
 	% Experiment and Conclusion
-	Comprehensive experimental results on three commonly used deep metric
-	learning datasets suggest that the proposed method overwhelmingly
-	outperforms the state-of-the-art defense methods in terms of robustness,
-	training cost, as well as recall performance on benign examples, while
-	remains in a simple form.
+	Comprehensive experimental results on commonly used deep metric
+	learning datasets suggest that the proposed method, although simple in
+	form, overwhelmingly outperforms the state-of-the-art defense methods in
+	terms of training time cost, robustness, as well as recall performance on
+	benign examples.
 %
@@
 %
-For example, impersonation or recognition evation are possible for a
+For example, impersonation or recognition evasion are possible for a
 vulnerable DML-based face-identification system.
@@
 %
-Furthermore, advertsarial training already suffers from
-significant training time cost (compared to the normal training process).
+Furthermore, adversarial training already suffers from significant training
+time cost (compared to the normal training process).
 %
-Hence, time efficiency in gaining adversarial robustness is an inevitable
-major issue.
+Hence, time efficiency in gaining adversarial robustness
+is an inevitable major issue.
+
+% we argue
+
+As suggested by previous works, an appropriate adversary for the inner
+\emph{maximization} problem should increase the loss to a certain point between
+that of benign examples (\ie, unperturbed examples) and the theoretical upper
+bound.
+%
+What if this point is reached by the strongest adversary, directly and
+efficiently?
+%
+Besides, as the mathematical expectation of loss is also greatly influenced by
+the triplet sampling strategy, we conjecture that the triplet sampling strategy
+and triplet ``hardness'' have a key impact for adversarial training.
 

### 2021-10-22 introplot.py

@@ -4,7 +4,7 @@ import rich
 c = rich.get_console()
 plt.rcParams['font.family'] = 'serif'
 plt.rcParams['font.serif'] = 'FreeSerif'
-plt.rcParams['font.size'] = 14
+plt.rcParams['font.size'] = 15
 
 data = {
         'ACT': ( # [freeze]
@@ -34,7 +34,7 @@ data = {
             ),
         }
 
-plt.figure(figsize=[10.8, 4.8])
+plt.figure(figsize=[10.8, 4.7])
 
 ax = plt.subplot(1,2,1)
 for (name, (r1, cost, ers)) in data.items():
@@ -60,12 +60,12 @@ plt.xscale('log', base=2)
 #plt.axis('equal')
 #plt.axis('square')
 
-ax.annotate('↖ Better', xy=(0.04, 0.92), xycoords='axes fraction',
+ax.annotate('↖ Better', xy=(0.04, 0.91), xycoords='axes fraction',
         bbox=dict(boxstyle="round,pad=0.3", fc="white", ec="k", lw=2),
-        size=14)
-ax.annotate('↘ Worse', xy=(0.77, 0.06), xycoords='axes fraction',
+        size=17)
+ax.annotate('↘ Worse', xy=(0.75, 0.06), xycoords='axes fraction',
         bbox=dict(boxstyle="round,pad=0.3", fc="white", ec="k", lw=2),
-        size=14)
+        size=17)
 
 ax = plt.subplot(1,2,2)
 for (name, (r1, cost, ers)) in data.items():
@@ -91,13 +91,13 @@ plt.gca().invert_xaxis()
 #plt.axis('equal')
 #plt.axis('square')
 
-ax.annotate('↖ Better', xy=(0.04, 0.92), xycoords='axes fraction',
+ax.annotate('↖ Better', xy=(0.04, 0.91), xycoords='axes fraction',
         bbox=dict(boxstyle="round,pad=0.3", fc="white", ec="k", lw=2),
-        size=14)
-ax.annotate('↘ Worse', xy=(0.77, 0.06), xycoords='axes fraction',
+        size=17)
+ax.annotate('↘ Worse', xy=(0.75, 0.06), xycoords='axes fraction',
         bbox=dict(boxstyle="round,pad=0.3", fc="white", ec="k", lw=2),
-        size=14)
+        size=17)
 
-#plt.tight_layout()
+plt.tight_layout(pad=1.0)
 #plt.show()
 plt.savefig('introplot.svg')

### 2021-10-22 robdml.tex
tex

@@
 %
-Meanwhile, the level of robustness that the previous methods have achieved
-is still insufficient.
-%
-(1) the robustness level achieved by the existing methods is still insufficient
-to counter the attacks;
-%
-(2) the direct adaptation of Madry's min-max adversarial training~\cite{madry}
-will easily lead to model collapse due to producing very hard sample triplets;
-%
-(3) the adversarial training procedure is very time-consuming compared to the
-training process of a regular DML model, but existing defense methods are
-incompatible to acceleration methods like Free Adversarial
-Training~\cite{freeat}.  \oo{rob, time, r1}.
-
 % inspiration.
@@
 
+\oo{extend: fat}
+training process of a regular DML model, but existing defense methods are
+incompatible to acceleration methods like Free Adversarial
+Training~\cite{freeat}.
+
 \subsection{Gradual Adversary}

### 2021-10-22 robdml.tex
tex

@@
 %
-What if this point is reached by the strongest adversary, directly and
+What if this point is reached by a strong adversary, directly and
 efficiently?
@@
 and triplet ``hardness'' have a key impact for adversarial training.
+
+% hardness manipulation
+
+In this paper, we first define the ``\emph{hardness}'' of a sample triplet as
+the difference between the anchor-positive distance and the anchor-negative
+distance.
+%
+Then, Hardness Manipulation (HM) is proposed to adversarially perturb a given
+sample triplet and increase its hardness into a specified hardness level.
+%
+HM is implemented as an objective to minimize the L-$2$ norm of the thresholded
+difference between the hardness of the given sample triplet and the specified
+hardness.
+%
+Mathematically, when the objective is optimized using Projected Gradient
+Descent~\cite{madry}, the gradient of HM objective with respect to the
+adversarial perturbation is the same as that of directly \emph{maximizing} the
+triplet loss.
+%
+Thus, the optimization process of HM objective can be interpreted as a direct
+\emph{maximization} process of the loss (indicating a direct strong adversary)
+which stops halfway at the specified hardness level.
+%
+But, how hard should such ``specified level'' be?
+
+by referencing
+another benign (but harder) sample triplet.
+
+make adversarially training a DML model
+with triplet loss feasible without model collapse, so the model could
+efficiently learn from a strong adversary.
+%
+Assume there are two data triplets, namely ``source triplet'' and ``destination
+triplet'' with the same anchor example, but sampled using different triplet
+sampling strategies.
+%
+And the ``destination triplet'' is expected to result in a higher loss value
+than another.
+%
+HM aims at creating adversarial examples of the ``source triplet'', that would
+increase the corresponding loss value until that of the unperturbed
+``destination triplet''.
+%
+This can also be interpreted as maximizing the loss value but ``stops early''
+at a certain point.
+%
+The resulting perturbed ``source triplet'' can be used for adversarial training
+of the model.
 
@@
 a known, unperturbed and harder sample triplet?
-
-% HM
-In this paper, we propose Hardness Manipulation (HM) to make adversarially
-training a DML model with triplet loss feasible without model collapse, so the
-model could efficiently learn from a strong adversary.
-%
-Assume there are two data triplets, namely ``source triplet'' and ``destination
-triplet'' with the same anchor example, but sampled using different triplet
-sampling strategies.
-%
-And the ``destination triplet'' is expected to result in a higher loss value
-than another.
-%
-HM aims at creating adversarial examples of the ``source triplet'', that would
-increase the corresponding loss value until that of the unperturbed
-``destination triplet''.
-%
-This can also be interpreted as maximizing the loss value but ``stops early''
-at a certain point.
-%
-The resulting perturbed ``source triplet'' can be used for adversarial
-training of the model.
 
@@
 	%
-	\bar{r}_a, \bar{r}_p, \bar{r}_n = \argmin_{r_a,r_p,r_n} \|\min(0,
-	\tilde{H}_\mathsf{S}-H_\mathsf{D})\|^2.
+	\bar{r}_a, \bar{r}_p, \bar{r}_n = \argmin_{r_a,r_p,r_n} \big\|\min(0,
+	\tilde{H}_\mathsf{S} - H_\mathsf{D}) \big\|_2^2.
 	%
@@
 \phi(X_n^S+\bar{r}_n))$.
+
+\begin{align}
+	&
+	\sign \big\{
+		-\frac{\partial}{\partial r} \big\| \min(0, 
+		\tilde{H}_\mathsf{S} - H_\mathsf{D}) \big\|_2^2
+	\big\}
+	\\
+	=&
+	\sign \big\{
+		-2(\tilde{H}_\mathsf{S}-H_\mathsf{D})
+		\frac{\partial }{\partial r} \tilde{H}_\mathsf{S} \big\}
+	=
+	\sign \big\{
+		\frac{\partial}{\partial r} \tilde{H}_\mathsf{S}
+		\big\}
+\end{align}
 

### 2021-10-22 robdml.tex
tex

@@
 Then, Hardness Manipulation (HM) is proposed to adversarially perturb a given
-sample triplet and increase its hardness into a specified hardness level.
+sample triplet and increase its hardness into a specified destination hardness level.
 %
@@
 difference between the hardness of the given sample triplet and the specified
-hardness.
+destination hardness.
 %
@@
 \emph{maximization} process of the loss (indicating a direct strong adversary)
-which stops halfway at the specified hardness level.
+which stops halfway at the specified destination hardness level.
 %
-But, how hard should such ``specified level'' be?
+But, how hard should such ``destination hardness'' be?
 
-by referencing
-another benign (but harder) sample triplet.
+% how hard? benign destination reference
 
-make adversarially training a DML model
-with triplet loss feasible without model collapse, so the model could
-efficiently learn from a strong adversary.
+Recall that the model is already prone to collapse with excessively hard
+benign triplets, let alone adversarial examples.
 %
-Assume there are two data triplets, namely ``source triplet'' and ``destination
-triplet'' with the same anchor example, but sampled using different triplet
-sampling strategies.
-%
-And the ``destination triplet'' is expected to result in a higher loss value
-than another.
-%
-HM aims at creating adversarial examples of the ``source triplet'', that would
-increase the corresponding loss value until that of the unperturbed
-``destination triplet''.
-%
-This can also be interpreted as maximizing the loss value but ``stops early''
-at a certain point.
-%
-The resulting perturbed ``source triplet'' can be used for adversarial training
-of the model.
-
-We conjecture there is a certain intermediate level of hardness.
-
-notable penalty in the model performance on benign (\ie, unperturbed) examples.
-
-%
-\oo{rev}
-%
-% inspiration.
-Recall that a DML model is already prone to collapse with very hard but not
-adversarially purturbed sample triplets~\cite{facenet}.
-%
-To overcome this issue, various triplet sampling strategies, such as
-semi-hard~\cite{facenet} and distance~\cite{distance} are proposed to provide
-effective negative examples to facilitate metric learning while avoiding model
-collapse.
-%
-In the typical min-max adversarial training~\cite{madry}, the adversarial
-example triplet created by maximizing the triplet loss value can incur model
-collapse more easily than unperturbed sample triplets.
-%
-But what if we do not maximize the triplet loss value to the theoretical upper
-bound, but merely increase it towards a value that could be caused by
-a known, unperturbed and harder sample triplet?
+Thus, intuitively, the destination hardness can be that of another benign
+triplet which is harder than the given triplet (\eg, a Semihard~\cite{facenet}
+triplet).
 
@@
 \cref{fig:hm}
+
+by referencing
+another benign (but harder) sample triplet.
+
+make adversarially training a DML model
+with triplet loss feasible without model collapse, so the model could
+efficiently learn from a strong adversary.
+%
+Assume there are two data triplets, namely ``source triplet'' and ``destination
+triplet'' with the same anchor example, but sampled using different triplet
+sampling strategies.
+%
+And the ``destination triplet'' is expected to result in a higher loss value
+than another.
+%
+HM aims at creating adversarial examples of the ``source triplet'', that would
+increase the corresponding loss value until that of the unperturbed
+``destination triplet''.
+%
+This can also be interpreted as maximizing the loss value but ``stops early''
+at a certain point.
+%
+The resulting perturbed ``source triplet'' can be used for adversarial training
+of the model.
 

### 2021-10-23 robdml.tex
tex

@@
 	To this end, Hardness Manipulation is proposed to adversarially perturb the
-	training triplet to increase its hardness into a specified level, by
-	referencing another benign triplet or a pseudo-hardness function.
+	training triplet to increase its hardness into a specified level, according
+	to another benign triplet or a pseudo-hardness function.
 	% GA Adversary
@@
 % existing methods & problem
+
 Existing defense methods for DML~\cite{advrank,robrank} are adversarial
@@
 
-% we argue
+% we argue / insight
 
@@
 Then, Hardness Manipulation (HM) is proposed to adversarially perturb a given
-sample triplet and increase its hardness into a specified destination hardness level.
+sample triplet and increase its hardness into a specified \emph{destination}
+hardness level.
 %
@@
 difference between the hardness of the given sample triplet and the specified
-destination hardness.
+\emph{destination} hardness.
 %
@@
 \emph{maximization} process of the loss (indicating a direct strong adversary)
-which stops halfway at the specified destination hardness level.
+which stops halfway at the specified \emph{destination} hardness level.
 %
-But, how hard should such ``destination hardness'' be?
+But, how hard should such ``\emph{destination} hardness'' be?
 
-% how hard? benign destination reference
+% how hard? benign destination
 
-Recall that the model is already prone to collapse with excessively hard
-benign triplets, let alone adversarial examples.
+Recall that the model is already prone to collapse with excessively hard benign
+triplets, let alone adversarial examples.
 %
-Thus, intuitively, the destination hardness can be that of another benign
-triplet which is harder than the given triplet (\eg, a Semihard~\cite{facenet}
-triplet).
+Thus, intuitively, the \emph{destination} hardness can be that of another
+benign triplet which is harder than the given triplet (\eg, a
+Semihard~\cite{facenet} triplet).
+%
+However, in the late phase of training, the expectation of the loss, as well as
+the corresponding \emph{hardness} of a given triplet will be small, which means
+the \emph{destination} hardness will be close to that of the sample triplet for
+training.
+%
+This leads to weak attacks, and inefficient learning from a weak adversary.
+%
+Besides, we speculate a strong adversary in the early phase of DML training may
+hinder the model from learning good embeddings, and hence influence the
+eventual performance on benign examples.
+%
+Based on these, a \emph{destination} hardness calculated from benign examples
+may not be the best choice.
+%
+A better \emph{destination} hardness should be able to balance the training
+objectives in the early and late phases of training.
+
+% Gradual Adversary
 
@@
 	&
-	\sign \big\{
+	\sign\big\{
 		-\frac{\partial}{\partial r} \big\| \min(0, 
@@
 	=&
-	\sign \big\{
+	\sign\big\{
 		-2(\tilde{H}_\mathsf{S}-H_\mathsf{D})
@@
 	=
-	\sign \big\{
+	\sign\big\{
 		\frac{\partial}{\partial r} \tilde{H}_\mathsf{S}

### 2021-10-23 robdml.tex
tex

@@
 
-% for problem 2
-\oo{[2. Gradual Adversary]}
-The expectation of hardness will decrease during the training process,
-compared to that from the beginning phase.
+To this end, we propose Graduate Adversary, a family of pseudo-hardness
+functions which can be used as the \emph{destination} hardness in HM.
+%
+Any function that leads to a relatively weak adversary in the early training
+phase, and a relatively strong adversary in the late training phase belongs to
+this family.
+%
+As an example, we design a ``Simple Graduate Adversary'' (SGA) pseudo-hardness
+function as the linearly scaled negative triplet margin, incorporating a strong
+assumption that the \emph{destination} hardness should remain Semihard.
+%
+Empirical observation will show the advantage of such pseudo-hardness
+functions.
 
@@
 
-\oo{[4. Free Adversarial Metric Learining]}
-Extension of FAT to adversarial deep metric learning.
-
 % evaluation and conclusion
-\oo{[experimetal evaluations]}
-To validate the effectiveness of the proposed method, we conduct experiments
-on three commonly used dataset, namely CUB-200-2011, Cars-196, and Stanford
-Online Product. Our conclusions are:
+We conduct experiments
+on three commonly used DML dataset, namely CUB-200-2011~\cite{cub200}, Cars-196~\cite{cars196}, and Stanford
+Online Product~\cite{sop}.
+%
+The proposed method overwhelmingly outperforms the state-of-the-art defense
+in terms of robustness, training cost, as well as the penalty on benign
+example retrieval.
+%
+Our conclusions are:
 %
@@
 %
-\oo{the results suggest that}
+\oo{...}
 
@@
 %
-\begin{enumerate}[noitemsep]
+\begin{enumerate}[nosep, noitemsep, leftmargin=*]
 	%
-	\item {\textit{Hardness Manipulation}} is proposed for the adversarial
-		training of triplet-based deep metric learning models, which avoids
-		model collapse in the typical min-max adversarial training setting.
-		The proposed method achieves higher adversarial robustness compared to
-		the state-of-the-art, and is more computationally efficient.
+	\item {\textit{Hardness Manipulation}} (HM) is proposed as a flexible tool
+		to create adversarial triplets with increased hardness for
+		subsequent adversarial training.
 		%
-		This method makes min-max training feaisble, and hence the incorporation
-		into free adversarial training and boost learning efficiency.
+		It is more efficient than previous adversarial training methods of DML.
 		%
-		(initial condition)
+	\item \textit{Gradual Adversary} is proposed as a family of pseudo-hardness
+		functions for \emph{Hardness Manipulation}, which can balance the
+		training objectives during the training process.
 		%
-	\item \textit{Gradual Adversary} is proposed to dynamically adjust the
-		destination hardness less for Hardness Manipulation during the
-		adversarial training process in order to balance the metric learning
-		and adversarial learning.
+		A linear function named Simple Graduate Adversary (SGA) is designed as
+		an example.
 		%
-		(terminal condition)
-		%
-	\item Inter-ID structure constraint. ((aa~p) + (pp~a))/2
-		(cross-id repelling)
-		existing methods only care inter-class separation, but not
-		intra-class (inter-id) separation, because we may get a 6-element
-		set (a,a~,p,p~,n,n~) from the original triplet.
+	\item \oo{TODO} Inter-ID structure constraint. ((aa~p) + (pp~a))/2
+		(cross-id repelling) existing methods only care inter-class separation,
+		but not intra-class (inter-id) separation, because we may get a
+		6-element set (a,a~,p,p~,n,n~) from the original triplet.
 		%
 \end{enumerate}
-
-The proposed method overwhelmingly outperforms the state-of-the-art defense
-in terms of robustness, training cost, as well as the penalty on benign
-example retrieval.
 
@@
 Training~\cite{freeat}.
+
+\oo{[4. Free Adversarial Metric Learining]}
+Extension of FAT to adversarial deep metric learning.
 

### 2021-10-24 robdml.tex
tex

@@
 %
-A series of following works attempt to more efficiently compromise the DNNs,
-such as BIM~\cite{i-fgsm}, C\&W~\cite{cw}, PGD~\cite{madry}, and
-APGD~\cite{apgd}.
+Subsequent studies can compromise the DNNs more effectively, such as
+BIM~\cite{i-fgsm}, PGD~\cite{madry}, and APGD~\cite{apgd}, which are
+unanimously based on the first-order gradient of the loss, and rely on the
+white-box assumption of fully accessible model details.
 %
-These attacks are based on the first-order gradient of the classification loss
-with respect to the input image, and hence rely on the white-box assumption
-that the model architecture and parameters are accessible to the attacker,
-which is impractical for real-world attacks.
-%
-Subsequently, black-box attack methods are developed into two types:
-transferrability-based attacks and query-based attacks.
-%
-Transferrability-based attacks~\cite{di-fgsm,universal} relies on the
-observation that image-agnostic (will take effect when applied to any image)
-and model-agnostic (will take effect when applied to any model) adversarial
-perturbation are possible.
-%
-Query-based attacks~\cite{nes-atk,spsa-atk} only need the logit score output or
-the label output from a classifier, based on which the gradient could be
-estimated from the response to repetitive queries in order to figure out the
-adversarial perturbation.
+In contrast, query-based black-box attacks~\cite{nes-atk,spsa-atk} are more
+practical for real-world scenarios, as they requires the least amount of
+information from the model for estimating the gradients.
 
@@
 
-\textbf{Deep Metric Learning.}
+\textbf{Deep Metric Learning DML.}
 %
@@
 excessively hard adversarial samples.
+
+\textbf{Attacks in DML.}
+%
+Similar to what have been found for the classifiers, recent
+works~\cite{robrank,advrank,advorder} also suggest that the embedding function
+$\phi(\cdot)$ in DML is vulnerable to adversarial attacks.
+%
+Specifically, an imperceptible adversarial perturbation $r$ is added to the
+input image $X$ ($\|r\|_p \leq \varepsilon$, $X+r\in \mathcal{X}$), so that its
+embedding vector $\tilde{\vx}=\phi(X+r)$ will be moved off its original
+location towards other positions to fulfill the attacker's goal.
+
+\textbf{Defenses in DML.}
+%
+Although attacks against DML has been widely studied~\cite{advrank,advorder},
+the defense methods for improving adversarial robustness is much less explored.
+%
+As adversarial training~\cite{madry} remains to be one of the most effective
+defense for classification, existing defense methods for DML are also
+adversarial training-based.
+%
+Embedding-Shifted Triplet (EST)~\cite{advrank} adopts adversarial counterpars
+of $\va,\vp,\vn$ with maximum embedding move distance off their original
+locations, \ie,
+$L_\text{EST}=L_\text{T}(\tilde{\va},\tilde{\vp},\tilde{\vn};\gamma)$ where
+$\tilde{\va}=\phi(X+r^*)$, $r^*=\arg\max_{r}d_\phi(X+r, X)$.
+%
+Anti-Collapse Triplet (ACT)~\cite{robrank} collapses the embedding vectors of
+positive and negative sample, and enforces the model to separate them apart,
+\ie, $L_\text{ACT}=L_\text{T}(\va, \overrightarrow{\vp},
+\overleftarrow{\vn};\gamma)$, where $[\overrightarrow{\vp},\overleftarrow{\vn}]
+=[\phi(X_p+r_p^*), \phi(X_n+r_n^*)]$, and $[r_p^*,r_n^*]=\arg\min_{r_p,r_n}
+d_\phi(X_p+r_p, X_n+r_n)$.
+%
+However, compared to the standard min-max adversarial training
+paradigm~\cite{madry}, these methods merely indirectly increase the loss value,
+and thus, suffer from inefficient learning because the adversary is not strong
+enough.
+%
+\oo{Furthermore, min-max form -- free adversarial training}.
 
@@
 where $\gamma$ is a predefined margin parameter.
-
-Similar to what have been found for the classifiers, recent
-works~\cite{robrank,advrank,advorder} also suggest that the embedding function
-$\phi(\cdot)$ in DML is vulnerable to adversarial attacks.
-%
-Specifically, an imperceptible adversarial perturbation $r$ is added to the
-input image $X$ ($\|r\|_p \leq \varepsilon$, $X+r\in \mathcal{X}$), so that its
-embedding vector $\tilde{\vx}=\phi(X+r)$ will be moved off its original
-location towards other positions to fulfill the attacker's goal.
-
-Although attacks against DML has been widely studied~\cite{advrank,advorder},
-the defense methods for improving adversarial robustness is much less explored.
-%
-As adversarial training~\cite{madry} remains to be one of the most effective
-defense for classification, existing defense methods for DML are also
-adversarial training-based.
-%
-Embedding-Shifted Triplet (EST)~\cite{advrank} adopts adversarial counterpars
-of $\va,\vp,\vn$ with maximum embedding move distance off their original
-locations, \ie,
-$L_\text{EST}=L_\text{T}(\tilde{\va},\tilde{\vp},\tilde{\vn};\gamma)$ where
-$\tilde{\va}=\phi(X+r^*)$, $r^*=\arg\max_{r}d_\phi(X+r, X)$.
-%
-Anti-Collapse Triplet (ACT)~\cite{robrank} collapses the embedding vectors of
-positive and negative sample, and enforces the model to separate them apart,
-\ie, $L_\text{ACT}=L_\text{T}(\va, \overrightarrow{\vp},
-\overleftarrow{\vn};\gamma)$, where $[\overrightarrow{\vp},\overleftarrow{\vn}]
-=[\phi(X_p+r_p^*), \phi(X_n+r_n^*)]$, and $[r_p^*,r_n^*]=\arg\min_{r_p,r_n}
-d_\phi(X_p+r_p, X_n+r_n)$.
-%
-However, compared to the standard min-max adversarial training
-paradigm~\cite{madry}, these methods merely indirectly increase the loss value,
-and thus, suffer from inefficient learning because the adversary is not strong
-enough.
-%
-\oo{Furthermore, min-max form -- free adversarial training}.
 
@@
 
+\begin{equation}
+	L_\text{ICS} = \lambda \cdot L_\text{T}(
+	\va, \tilde{\va}, \vp; 0)
+\end{equation}
+
 \section{Experiments}

### 2021-10-24 robdml.tex
tex

@@
 %
-To battle against the attacks, some early defense methods create a gradient
-masking effect, namely making it hard for the attacker to find a good gradient,
-but it gives a false sense of security~\cite{obfuscated}.
+To battle against the attacks, some early defenses incur gradient masking
+effect, but it gives a false sense of security~\cite{obfuscated}.
 %
-Defensive distillation~\cite{distill2} can be compromised by C\&W~\cite{cw}.
+Defensive distillation~\cite{distill2} can be compromised~\cite{cw}.
 %
-Ensemble of weak defenses is insufficient~\cite{ensembleweak}.
+Ensemble of weak defenses is not robust~\cite{ensembleweak}.
 %
-Defense can also be implemented as preprocessing~\cite{deflecting} the input
-image, or a randomized process inside the network~\cite{self-ensemble}.
+Other forms of defenses are also proposed, such as input
+preprocessing~\cite{deflecting}, or a randomization inside the
+network~\cite{self-ensemble}.
 %
-However, it is noted that various defense methods are still susceptible to
-adaptive attack~\cite{adaptive}.
+But various defense methods are still susceptible to adaptive
+attack~\cite{adaptive}.
 %
-Among the proposed defense methods, adversarial training has been empirically
-found effective~\cite{bilateral,advtrain-triplet,benchmarking}, and it
-consistently retains adversarial robustness for the model.
+Of all defenses, adversarial training remains to be one of the most
+effective method~\cite{bilateral,advtrain-triplet,benchmarking}, and it
+consistently show promising empirical robustness,
+although suffering from significant training time cost and a lower performance
+on benign examples.
 

### 2021-10-24 robdml.tex
tex

@@
 
-\subsection{Intra-Class Structure Constraint}
+\subsection{Intra-Class Structure}
 \label{sec:33}
 
-\oo{[illust fig]}
+% motivation
 
+During adversarial training, the adversarial counterpart of each given sample
+triplet is fed to the model, and the triplet loss will enforce a good
+\emph{inter-class} structure.
+%
+Since the anchor, positive sample, and their adversarial counterpart belongs to
+the same class, it should be noted that the \emph{intra-class} structure can be
+enforced as well, and This has been neglected by the existing DML defenses.
+%
+\emph{Intra-class} structure is also important for robustness besides the
+\emph{inter-class} structure, because the attack may attempt to change the
+rankings of samples in the same class~\cite{advrank}.
+
+% Solution
+
+We propose an additional loss function term to enforce such \emph{intra-class}
+structure, as shown in \oo{Fig.~[].}
+%
+Specifically, the anchor $\va$ and its adversarial counterpart $\tilde{\va}$
+are separated from the positve sample $\vp$ by reusing the triplet loss,
+\ie,
+%
 \begin{equation}
 	L_\text{ICS} = \lambda \cdot L_\text{T}(
-	\va, \tilde{\va}, \vp; 0)
+	\va, \tilde{\va}, \vp; 0),
 \end{equation}
+%
+where $\lambda$ is a constant hyper-parameter for controlling the importance
+of this term.
+%
+$L_\text{ICS}$ can be added to the original loss function for adversarial training.
 

### 2021-10-24 robdml.tex
tex

@@
 where $\lambda$ is a constant hyper-parameter for controlling the importance
-of this term.
+of this term, and the margin here is set as zero to avoid negative effect.
 %
-$L_\text{ICS}$ can be added to the original loss function for adversarial training.
+The $L_\text{ICS}$ penalty term can be appended to the loss function for
+adversarial training.
 

### 2021-10-24 robdml.tex
tex

--- 2021-10-24 robdml.tex
@@
 %
-where $\lambda$ is a constant hyper-parameter for controlling the importance
-of this term.
+where $\lambda$ is a constant weight for this loss term,
+and the margin is set as zero to avoid negative effect.
 %
-$L_\text{ICS}$ can be added to the original loss function for adversarial training.
+The $L_\text{ICS}$ term can be added to the loss function for
+adversarial training.
 

### 2021-10-24 robdml.tex
tex

@@
 
-To validate the effectiveness of our proposed defense, we conduct experiments
+% evaluation: dataset
+
+To validate the proposed defense, we conduct experiments
 on three commonly used DML datasets: CUB-200-2011 (CUB)~\cite{cub200}, Cars-196
@@
 %
-We follow the same experiment setup of the state-of-the-art work~\cite{robrank}
+We follow the same experiment setup as the state-of-the-art work~\cite{robrank}
 for ease of comparison.
+
+% evaluation: configuration
+
+Specifically, we (adversarially) train imagenet-initialized ResNet-18
+(RN18)~\cite{resnet} with the output dimension of the last layer changed to
+$N=512$.
 %
-The setup is also consistent to standard DML~\cite{revisiting}.
-
-Specifically, we train a ResNet-18 (RN18)~\cite{resnet} with the output dimension of
-the last layer changed to $N=512$.
+The margin $\gamma$ in triplet loss is $0.2$ by default.
 %
-The margin $\gamma$ in triplet loss is set as $0.2$ by default.
-%
-The model is trained with Adam optimizer with learning rate $1.0\times 10^{-3}$
-for $150$ epochs, with mini-batch size set as $112$.
+Adam~\cite{adam} optimizer is used for parameter updates, with a learning rate
+as $1.0\times 10^{-3}$ for $150$ epochs, and a mini-batch size of $112$.
 
@@
 Step size for PGD is set as $\alpha=1/255$.
+%
+The setup is also consistent to standard DML~\cite{revisiting}.
 

### 2021-10-24 robdml.tex
tex

@@
 (RN18)~\cite{resnet} with the output dimension of the last layer changed to
-$N=512$.
+$N{=}512$.
 %
@@
 %
+The setup is also consistent to standard DML~\cite{revisiting}.
+%
 Adam~\cite{adam} optimizer is used for parameter updates, with a learning rate
-as $1.0\times 10^{-3}$ for $150$ epochs, and a mini-batch size of $112$.
-
-For adversarial training, we adopt the perturbation budget of
-$\varepsilon=8/255$ in infinity norm ($p=\infty$).
+as $1.0{\times}10^{-3}$ for $150$ epochs, and a mini-batch size of $112$.
 %
-Projected Gradient Descent (PGD)~\cite{madry} is used for creating adversarial
-examples, with a maximum step number set as $\eta=8$ by default.\footnote{
-Instead of $\eta=32$ as in \cite{robrank} in order to control time consumption.}
+Adversarial examples are created under the perturbation budget
+$\varepsilon{=}8/255$ in infinity norm, using the
+Projected Gradient Descent (PGD)~\cite{madry} method with step size $\alpha{=}1/255$ 
+and a default maximum step number $\eta{=}8$.
 %
-Step size for PGD is set as $\alpha=1/255$.
-%
-The setup is also consistent to standard DML~\cite{revisiting}.
 
@@
 The adversarial robustness of a model is measured in Empirical Robustness Score
-(ERS)~\cite{robrank}, which is a normalized score (the higher the better) from
-an ensemble of existing white-box attacks against DML or their simplified
-white-box counterparts.
+(ERS)~\cite{robrank}, a normalized score (the higher the better) from
+an ensemble of existing attacks against DML or their simplified white-box
+alternatives.
 %
-As adversarial training will not cause gradient masking~\cite{obfuscated},
-the performance of white-box attack can be regarded as the upper bound of the
-corresponding black-box attack.
-%
-An adversarially trained DML model that is empirically robust to the ensemble
-is expected to be robust in other scenarios as well.
+Since adversarial training is not gradient masking~\cite{obfuscated}, the
+performance of white-box attack can be regarded as the upper bound of the
+black-box attacks, and thus a model that is empirically robust to the ensemble
+of white-box attacks is expected to be robust in general.
 
 \oo{Concretely, the ensemble of attack for computing ERS includes.}
+%
+Further details can be found in the supplementary.
 

### 2021-10-24 appendix.tex
tex

@@
 \appendix
+
+\section{More Details Explained}
+
+In this section, we provide more details on the reasons of our design,
+additional details of our implementation, as well as more discussions
+on questions that are unsuitable for the main part of manuscript.
+
+\begin{enumerate}[noitemsep]
+	\item Only aap in ICS?
+	\item Why not aa~p~ in ICS?
+	\item Have you tried FAT?
+	\item What if we mix HM(RM) and HM(SM)?
+	\item Another example for the GA pseudo-hardness function family?
+	\item Why not ResNet-50?
+\end{enumerate}
+
+\section{Visualizations}
+
+Visualize robustness through the image retrieval task.
 

### 2021-10-24 robdml.tex
tex

@@
 
-This section is organized in logical order where a group of experiments
-or ablation study
-provides clues for the next group of experiment.
+In this section, we first carry out parameter search for the components of the
+proposed method, in order to illustrate their effectiveness.
 %
-Hence, the comparison to the state-of-the-art works are put at the last
-subsection.
+The comparison with the state-of-the-art DML defense methods will be presented in the end.
 

### 2021-10-24 appendix.tex
tex

@@
 
-\begin{enumerate}[noitemsep]
-	\item Only aap in ICS?
+\begin{enumerate}[noitemsep, label={Q.{\arabic*}}]
+		%
+	\item {\it There is only $L_\text{T}(\va, \tilde{\va}, \vp)$ in the ICS
+		term.  Is it possible to introduce any other triplet combinations among
+		the six samples (\ie, three benign and three adversarial)?}\\
+		%
+		A: We have tried some other combinations, and they are either not
+		effective, or causing negative effects.
+		%
+		In particular, adding $L_\text{T}(\va, \vp, \vn)$ on top of the
+		adversarial training loss
+		$L_\text{T}(\tilde{\va},\tilde{\vp},\tilde{\vn})$ can improve
+		performance on benign examples, but will drastically reduce model
+		robustness.
+
 	\item Why not aa~p~ in ICS?
+		less adversarial, further.
 	\item Have you tried FAT?

### 2021-10-24 robdml.tex
tex

@@
 \input{tab-hmeff.tex}
+
 % 1. possible combinations
 
-In literature, various triplet sampling strategies exist, such as random,
-semihard~\cite{facenet}, softhard~\cite{revisiting}, distance~\cite{distance},
-and the hardest negative sampling (\ie, the negative sample with the largest
-loss value).
+Although any of the existing triplet sampling strategies, such as Random,
+Semihard~\cite{facenet}, Softhard~\cite{revisiting},
+Distance-weighted~\cite{distance}, and the within-batch Hardest negative
+sampling method, can be selected for source and destination hardness,
+not all combinations are effective and efficient.
 %
-Although any of them can be selected for source or destination hardness for HM,
-not all the possible combinations are expected to be effective or efficient.
-%
+In this subsection, we find a proper combination empirically.
+
+% 2. sort sampling strategies
+
+As HM is expected to increase the hardness of the source triplet, we first sort
+the triplet sampling methods according to their approximated mean hardness of
+$1000$ mini-batches from CUB dataset with an imagenet-initialized RN18 model,
+as shown in~\cref{tab:hsort}.
+
 In order to figure out an empirically good combination of source and

### 2021-10-24 robdml.tex
tex

@@
 Distance-weighted~\cite{distance}, and the within-batch Hardest negative
-sampling method, can be selected for source and destination hardness,
-not all combinations are effective and efficient.
+sampling method, can be selected for source hardness $H_\mathsf{S}$ and
+destination hardness $H_\mathsf{D}$, not all combinations are effective and
+efficient.
 %
-In this subsection, we find a proper combination empirically.
+In this subsection, we find a proper combination empirically as a baseline for
+further experiments.
 
@@
 as shown in~\cref{tab:hsort}.
-
-In order to figure out an empirically good combination of source and
-destination hardness, we adversarially train RN18 models on the CUB dataset
-with every possible combination, and compare their R@1 and ERS performance in
-\cref{tab:desth}.
 %
-Note, these methods are empirically sorted by their expectation of hardness
-$E[H]$, in the ascending order: random, semihard, softhard, distance, and
-hardest, as shown in \cref{tab:hsort}.
+Then we adversarially train models on the CUB dataset with all possible
+combinations, and summarize their R@1 and ERS performance in \cref{tab:desth}.
 

### 2021-10-24 appendix.tex
tex
uy

@@
 		%
-	\item {\it There is only $L_\text{T}(\va, \tilde{\va}, \vp)$ in the ICS
+	\item \ul{\it There is only $L_\text{T}(\va, \tilde{\va}, \vp)$ in the ICS
 		term.  Is it possible to introduce any other triplet combinations among
@@
 	\item What if we mix HM(RM) and HM(SM)?
+		works but not good enough.
 	\item Another example for the GA pseudo-hardness function family?
+		sqaure and sqrt.
 	\item Why not ResNet-50?
+		ttx and video memory.
+	\item fix the anchor like ACT?
+		not quite helpful. not necessary.
+	\item Why compare in theoretical time cost instead of walltime cost?
+		Walltime cost does not precisely indicate the true efficiency
+		of a defense method, and may even result in unfair comparison.
+		isolate the discrepancy from implementation and engineering tricks,
+		as well as software / hardware differences.
 \end{enumerate}

### 2021-10-25 tab-desth.tex
tex
lyx

@@
 \resizebox{\columnwidth}{!}{
-\setlength{\tabcolsep}{0.3em}
+\setlength{\tabcolsep}{0.36em}
 \begin{tabular}{c|cc|cc|cc|cc|cc}
@@
 
-\multirow{2}{*}{\backslashbox{$H_S$}{$H_D$}} & \multicolumn{2}{c|}{Random} & \multicolumn{2}{c|}{Semihard} & \multicolumn{2}{c|}{Softhard} & \multicolumn{2}{c|}{Distance} & \multicolumn{2}{c}{Hardest}\tabularnewline
+	\multirow{2}{*}{\backslashbox{$H_\mathsf{S}$}{$H_\mathsf{D}$}} & \multicolumn{2}{c|}{Random} & \multicolumn{2}{c|}{Semihard} & \multicolumn{2}{c|}{Softhard} & \multicolumn{2}{c|}{Distance} & \multicolumn{2}{c}{Hardest}\tabularnewline
 \cline{2-11} \cline{3-11} \cline{4-11} \cline{5-11} \cline{6-11} \cline{7-11} \cline{8-11} \cline{9-11} \cline{10-11} \cline{11-11} 
@@
 
-Random & \cellcolor{black!10} 53.9 & \cellcolor{black!10}3.8 & 27.0 & 35.1 & \multicolumn{2}{c|}{Collapse} & \multicolumn{2}{c|}{Collapse} & \multicolumn{2}{c}{Collapse}\tabularnewline
+Random & \cellcolor{black!10}53.9 & \cellcolor{black!10}3.8 & 27.0 & 35.1 & \multicolumn{2}{c|}{Collapse} & \multicolumn{2}{c|}{Collapse} & \multicolumn{2}{c}{Collapse}\tabularnewline
 \hline

### 2021-10-25 tab-hmeff.tex
lyx

@@
 \resizebox{\linewidth}{!}{
-\setlength{\tabcolsep}{0.4em}%
-\renewcommand{\arraystretch}{1.1}
+\setlength{\tabcolsep}{0.48em}%
+\renewcommand{\arraystretch}{1.05}
+
 \begin{tabular}{c|cc|cccc|ccccc|ccccc|c}
@@
 
-\multirow{2}{*}{\textbf{Dataset}} & \multicolumn{1}{c}{\multirow{2}{*}{\textbf{Defense}}} & \multirow{2}{*}{$\eta$} & \multicolumn{4}{c|}{\textbf{Benign Example}} & \multicolumn{10}{c|}{\textbf{White-Box Attacks for Robustness Evaluation}} & \multirow{2}{*}{\textbf{ERS$\uparrow$}}\tabularnewline
+\multirow{2}{*}{\textbf{Dataset}} & \multirow{2}{*}{\textbf{Defense}} & \multirow{2}{*}{$\eta$} & \multicolumn{4}{c|}{\textbf{Benign Example}} & \multicolumn{10}{c|}{\textbf{White-Box Attacks for Robustness Evaluation}} & \multirow{2}{*}{\textbf{ERS$\uparrow$}}\tabularnewline
 \cline{4-17} \cline{5-17} \cline{6-17} \cline{7-17} \cline{8-17} \cline{9-17} \cline{10-17} \cline{11-17} \cline{12-17} \cline{13-17} \cline{14-17} \cline{15-17} \cline{16-17} \cline{17-17}
@@
 
-CUB & N/A & N/A & 53.9 & 66.4 & 26.1 & 59.5 & 0.0 & 100.0 & 0.0 & 99.9 & 0.883 & 1.762 & 0.0 & 0.0 & 14.1 & 0.0 & 3.8\tabularnewline
+CUB & N/A{[}$\mathcal{R}${]} & N/A & 53.9 & 66.4 & 26.1 & 59.5 & 0.0 & 100.0 & 0.0 & 99.9 & 0.883 & 1.762 & 0.0 & 0.0 & 14.1 & 0.0 & 3.8\tabularnewline
 \hline
-\multirow{5}{*}{CUB} & ACT & 2 & 46.5 & 58.4 & 29.1 & 55.6 & 0.6 & 98.9 & 0.4 & 98.1 & 0.837 & 1.666 & 0.2 & 0.2 & 19.6 & 0.0 & 5.8\tabularnewline
- & ACT & 4 & 38.4 & 49.8 & 22.8 & 49.7 & 4.6 & 81.9 & 2.8 & 80.5 & 0.695 & 1.366 & 2.9 & 2.3 & 18.8 & 0.1 & 13.9\tabularnewline
- & ACT & 8 & 30.6 & 40.1 & 16.5 & 45.6 & 13.7 & 46.8 & 12.6 & 39.3 & 0.547 & 0.902 & 13.6 & 9.8 & 21.9 & 1.3 & 31.3\tabularnewline
- & ACT & 16 & 28.6 & 38.7 & 15.1 & 43.7 & 15.8 & 37.9 & 16.0 & 31.5 & 0.496 & 0.834 & 11.3 & 9.8 & 21.2 & 2.1 & 34.7\tabularnewline
- & ACT & 32 & 27.5 & 38.2 & 12.2 & 43.0 & 15.5 & 37.7 & 15.1 & 32.2 & 0.472 & 0.821 & 11.1 & 9.4 & 14.9 & 1.0 & 33.9\tabularnewline
+\multirow{5}{*}{CUB} & ACT{[}$\mathcal{R}${]} & 2 & 46.5 & 58.4 & 29.1 & 55.6 & 0.6 & 98.9 & 0.4 & 98.1 & 0.837 & 1.666 & 0.2 & 0.2 & 19.6 & 0.0 & 5.8\tabularnewline
+ & ACT{[}$\mathcal{R}${]} & 4 & 38.4 & 49.8 & 22.8 & 49.7 & 4.6 & 81.9 & 2.8 & 80.5 & 0.695 & 1.366 & 2.9 & 2.3 & 18.8 & 0.1 & 13.9\tabularnewline
+ & ACT{[}$\mathcal{R}${]} & 8 & 30.6 & 40.1 & 16.5 & 45.6 & 13.7 & 46.8 & 12.6 & 39.3 & 0.547 & 0.902 & 13.6 & 9.8 & 21.9 & 1.3 & 31.3\tabularnewline
+ & ACT{[}$\mathcal{R}${]} & 16 & 28.6 & 38.7 & 15.1 & 43.7 & 15.8 & 37.9 & 16.0 & 31.5 & 0.496 & 0.834 & 11.3 & 9.8 & 21.2 & 2.1 & 34.7\tabularnewline
+ & ACT{[}$\mathcal{R}${]} & 32 & 27.5 & 38.2 & 12.2 & 43.0 & 15.5 & 37.7 & 15.1 & 32.2 & 0.472 & 0.821 & 11.1 & 9.4 & 14.9 & 1.0 & 33.9\tabularnewline
+\hline
+\multirow{5}{*}{CUB} & ACT{[}$\mathcal{S}${]} & 2 & 53.0 & 65.1 & 34.7 & 59.9 & 0.0 & 100.0 & 0.0 & 99.8 & 0.877 & 1.637 & 0.0 & 0.0 & 20.4 & 0.0 & 5.1\tabularnewline
+ & ACT{[}$\mathcal{S}${]} & 4 & 49.3 & 61.0 & 31.5 & 56.6 & 0.6 & 97.6 & 0.2 & 98.1 & 0.799 & 1.485 & 0.3 & 0.2 & 18.9 & 0.0 & 7.1\tabularnewline
+ & ACT{[}$\mathcal{S}${]} & 8 & 42.8 & 54.7 & 26.6 & 53.3 & 4.8 & 72.8 & 2.7 & 73.3 & 0.619 & 1.148 & 8.3 & 4.9 & 23.5 & 0.3 & 18.7\tabularnewline
+ & ACT{[}$\mathcal{S}${]} & 16 & 40.5 & 51.6 & 24.8 & 51.7 & 6.7 & 62.1 & 4.9 & 60.6 & 0.566 & 1.014 & 12.4 & 8.6 & 22.5 & 0.9 & 23.7\tabularnewline
+ & ACT{[}$\mathcal{S}${]} & 32 & 39.4 & 50.2 & 18.6 & 51.3 & 6.8 & 61.5 & 5.2 & 60.4 & 0.506 & 1.032 & 12.8 & 11.3 & 17.7 & 0.3 & 24.2\tabularnewline
 \hline

### 2021-10-25 appendix.tex
lyx
tex

@@
 		%
-		In particular, adding $L_\text{T}(\va, \vp, \vn)$ on top of the
+		In particular, (1) adding $L_\text{T}(\va, \vp, \vn)$ on top of the
 		adversarial training loss
@@
 		performance on benign examples, but will drastically reduce model
-		robustness.
+		robustness;
+		%
+		(2) $L_\text{T}(\vp, \tilde{\vp}, \va)$ \oo{is duplicated, not necessary.}
+		%
+		(3) $L_\text{T}(\va, \tilde{\va}, \tilde{\vn})$ no distinct difference.
+		%
+		(4) $L_\text{T}(\va, \vp, \tilde{\vn})$ leads to better performance
+		on benign examples, but drastically reduce robustness.
 
@@
 		as well as software / hardware differences.
+	\item full data sheet for tab 2?
+		\cref{tab:srcdest}
 \end{enumerate}
+
+\input{tab-srcdest.tex}
 

### 2021-10-25 robdml.tex
tex

@@
 \usepackage{colortbl}
+\usepackage{soul}
 
@@
 
-\subsection{Efficiency of Hardness Manipulation}
+\subsection{Effectiveness of Hardness Manipulation}
 \label{sec:42}
+
+Why G4 so promising?
+
+RM = random original (not representative for what the model should learn) plus semihard adv ex (strong advex)
+
+SM = softhard original (selective) plus semihard adv ex (strong adv)
+
+Ignore $H_D$
+
+1. source triplet affects p[erformance regardless of the attack method used for adversarial training.
+
+2. as long as a portion of semihard adversarial example is provided. fully explore the range of semihard.
 

### 2021-10-25 robdml.tex
tex

@@
 
-\section{Discussions}
+\section{Conclusion}
 \label{sec:5}
 
-(optional) ICS for ACT?
-
-\section{Conclusion}
-\label{sec:6}
-
-HM follows the min-max paradigm, (can be incorporated into FAT etc).
-Both ACT and HM stops at a specific point.
+Adversarial robustness is important for DML applications, but
+the existing defenses still suffer from low efficiency and low
+performance.
+%
+In this paper, 
+Hardness Manipulation is proposed as as a flexible tool to create
+adversarial examples for more efficient adversarial training.
+%
+Meanwhile, Gradual Adversary is proposed as a family of pseudo-hardness
+functions to better balance the training objectives.
+%
+Besides, an Intra-Class Structure penalty is proposed to enforce better
+embedding structure for higher robustness.
+%
+According to experimental evaluations, the proposed method overwhelmingly
+outperforms the state-of-the-art defenses.
 

### 2021-10-25 introplot.py
svg

@@ -7,10 +7,15 @@ plt.rcParams['font.serif'] = 'FreeSerif'
 plt.rcParams['font.size'] = 15
 
 data = {
-        'ACT': ( # [freeze]
+        'ACT[R]': ( # [freeze]
             (27.5, 28.6, 30.6, 38.4, 46.5),
             (33.0, 17.0, 9.0, 5.0, 3.0),
             (33.9, 34.7, 31.3, 13.9, 5.8),
+            ),
+        'ACT[S]': ( # [freeze]
+            (53.0, 49.3, 42.8, 40.5, 39.4),
+            (3.0, 5.0, 9.0, 17.0, 33.0),
+            (5.1, 7.1, 18.7, 23.7, 24.2),
             ),
         'hmetrm': ( # [freeze]
             (23.1, 23.8, 27.0, 30.7, 34.3),
@@ -40,16 +45,18 @@ ax = plt.subplot(1,2,1)
 for (name, (r1, cost, ers)) in data.items():
     c.print(name, r1, cost, ers)
 
-    if name == 'ACT':
-        plt.plot(cost, ers, f'.-', color='dimgray')
+    if name == 'ACT[R]':
+        plt.plot(cost, ers, marker='v', linestyle=':', color='dimgray')
+    elif name == 'ACT[S]':
+        plt.plot(cost, ers, marker='^', linestyle=':', color='dimgray')
     elif name == 'hmetrm':
-        plt.plot(cost, ers, f'v-', color='tab:blue')
+        plt.plot(cost, ers, marker='v', linestyle='-.', color='tab:blue')
     elif name == 'hmetsm':
-        plt.plot(cost, ers, f'^-', color='tab:red')
+        plt.plot(cost, ers, marker='^', linestyle='-.', color='tab:red')
     elif name == 'HM(S,SGA)':
-        plt.plot(cost, ers, f'h-', color='deeppink')
+        plt.plot(cost, ers, marker='h', linestyle='-', color='deeppink')
     else:
-        plt.plot(cost, ers, f'-o', color='k')
+        plt.plot(cost, ers, marker='+', linestyle='-.', color='k')
     if isinstance(cost, float):
         plt.annotate(name, xy=(cost, ers))
     elif isinstance(cost, tuple):
@@ -71,8 +78,10 @@ ax = plt.subplot(1,2,2)
 for (name, (r1, cost, ers)) in data.items():
     c.print(name, r1, cost, ers)
 
[…]

### 2021-10-25 robdml.tex
tex

@@
 	Owing to the security implications of adversarial vulnerability, the
-	adversarial robustness of deep metric learning models have to be improved
+	adversarial robustness of deep metric learning models has to be improved
 	via defense.
@@
 	In order to avoid model collapse due to excessively hard examples, the
-	existing methods refrain from using the min-max adversarial training, but
+	existing defenses refrain from using the min-max adversarial training, but
 	instead learns from a weak adversary inefficiently.
@@
 	learning datasets suggest that the proposed method, although simple in
-	form, overwhelmingly outperforms the state-of-the-art defense methods in
+	its form, overwhelmingly outperforms the state-of-the-art defense methods in
 	terms of training time cost, robustness, as well as recall performance on
@@
 from directly adopting such paradigm, but instead use some indirect and
-relatively weak objectives to merely increase the loss value to a certain
-level.
+relatively weak objectives to increase the loss value to a certain level.
 %
@@
 Furthermore, adversarial training already suffers from significant training
-time cost (compared to the normal training process).
+cost (compared to the normal training process).
 %
-Hence, time efficiency in gaining adversarial robustness
-is an inevitable major issue.
+Hence, efficiency in gaining adversarial robustness is an inevitable major
+issue for DML defense methods.
 
@@
 which stops halfway at the specified \emph{destination} hardness level.
-%
-But, how hard should such ``\emph{destination} hardness'' be?
 
@@
 
+Then, how hard should such ``\emph{destination} hardness'' be?
+%
 Recall that the model is already prone to collapse with excessively hard benign
@@
 %
-However, in the late phase of training, the expectation of the loss, as well as
-the corresponding \emph{hardness} of a given triplet will be small, which means
-the \emph{destination} hardness will be close to that of the sample triplet for
-training.
+However, in the late phase of training, the
+expectation of \emph{destination} hardness of another benign triplet
+will be small, and close to the \emph{hardness} expectation of the given triplet.
 %
@@
 %
-Empirical observation will show the advantage of such pseudo-hardness
-functions.
+%Empirical observation will show the advantage of such pseudo-hardness
+%functions.
+
+% Intra-Class Structure
+
+Besides, a sample triplet will be augmented into a sextuplet (benign and
+adversarial examples) during adversarial training, where a \emph{intra-class}
+structure can be enforced.
+%
+Such structure has been neglected by existing methods, but some existing
+attacks aims to change the sample rankings in the same class~\cite{advrank}.
+%
+Hence, we propose a simple \emph{intra-class} structure penalty term for
+adversarial training, which is expected to improve robustness.
 
@@
 consistently show promising empirical robustness,
-although suffering from significant training time cost and a lower performance
+although suffering from significant training cost and a lower performance
 on benign examples.
@@
 (ERS)~\cite{robrank}, a normalized score (the higher the better) from
-an ensemble of existing attacks against DML or their simplified white-box
+an collection of existing attacks against DML or their simplified white-box
 alternatives.
@@
 performance of white-box attack can be regarded as the upper bound of the
-black-box attacks, and thus a model that is empirically robust to the ensemble
+black-box attacks, and thus a model that is empirically robust to the collection
 of white-box attacks is expected to be robust in general.
 
-\oo{Concretely, the ensemble of attack for computing ERS includes.}
+\oo{Concretely, the collection of attack for computing ERS includes.}
 %

### 2021-10-25 robdml.tex
tex

@@
 
-\oo{[3. Intra-Class Structure]}
-Given a triplet of samples, we may eventually get up to 6 samples avaiable
-for adversarial training. There could be some kind of hierarchy.
-
 % evaluation and conclusion
-We conduct experiments
-on three commonly used DML dataset, namely CUB-200-2011~\cite{cub200}, Cars-196~\cite{cars196}, and Stanford
-Online Product~\cite{sop}.
+The experiments are conducted on three commonly used DML datasets, namely
+CUB-200-2011~\cite{cub200}, Cars-196~\cite{cars196}, and Stanford Online
+Product~\cite{sop}.
 %
-The proposed method overwhelmingly outperforms the state-of-the-art defense
-in terms of robustness, training cost, as well as the penalty on benign
+The proposed method overwhelmingly outperforms the state-of-the-art defense in
+terms of training cost, robustness, as well as the performance on benign
 example retrieval.
-%
-Our conclusions are:
-%
-(1) Triplet sampling strategy is vital for adversarial training of tripet-loss
-based DML models.
-%
-\oo{...}
 
 % contributions
-In brief, our contribusions include:
+In brief, our contribusions includes:
 %
@@
 		%
-	\item \oo{TODO} Inter-ID structure constraint. ((aa~p) + (pp~a))/2
-		(cross-id repelling) existing methods only care inter-class separation,
-		but not intra-class (inter-id) separation, because we may get a
-		6-element set (a,a~,p,p~,n,n~) from the original triplet.
+	\item \textit{Intra-Class Structure} penalty is proposed to further improve
+		the robustness of a DML model, while such possibility is neglected by
+		existing methods. 
 		%

### 2021-10-25 appendix.tex
tex

@@
 \begin{itemize}
+
+	\item [T] Sam's idea is interesting. By incorporating the idea of
+		on-manifold adversarial example to adversarial training, the
+		performance on benign example is greatly improved.
+		%
+		That idea can be interpreted as to be selective on the adversarial
+		example used for trianing.
+		%
+		Here, in our observation, we are also selective on the adversarial
+		examples used for training.
+		%
+		Is there anything in common?
+
+	\item [T] Face recognition methods such as ArcFace can be used for
+		metric learning.
+		%
+		We have an opportunity of smooth transition to defense for face
+		recognition methods.
+		%
+		Is defense for face recognition missing from the literature?
 

### 2021-10-25 robdml.tex
tex

@@
 
-\textbf{Deep Metric Learning DML.}
+\textbf{Deep Metric Learning.}
 %
-A wide range of application problem such as image retrieval~\cite{imagesim2},
+A wide range of applications such as image retrieval~\cite{imagesim2},
 cross-modal retrieval~\cite{ladderloss}, and face recognition~\cite{facenet}
-can be formularized as a deep metric learning problem.
+can be formulated as Deep Metric Learning.
 %
-Deep metric learning has been found vulnerable to adversarial attacks as
-well~\cite{advrank,advorder}, which will result in undesired implications on
-safety, security, or fairness of a deep metric learning application.
-%
-In contrast, the defense methods for enhancing the adversarial robustness of
-deep metric learning are less explored.
-%
-Zhou \etal~\cite{advrank} present an adversarial training method with
-adversarial examples maximizing the embedding move distance off its original
-location.
-%
-Anti-Collapse Triplet~\cite{robrank} forces the model to separate collapsed
-positive and negative samples in order to learn robust features.
-%
-However, the existing defense methods refrain from adopting Madry's min-max
-adversarial training paradigm due to the model being too easy to collapse with
-excessively hard adversarial samples.
+A well-designed loss function is crucial for DML performance~\cite{dmlreality}.
+As suggested by recent study, the classical triplet loss could reach
+state-of-the-art performance with an appropriate triplet sampling
+strategy~\cite{revisiting}.
 
@@
 %
-Similar to what have been found for the classifiers, recent
-works~\cite{robrank,advrank,advorder} also suggest that the embedding function
-$\phi(\cdot)$ in DML is vulnerable to adversarial attacks.
+DML has been found vulnerable to adversarial attacks as
+well~\cite{advrank,advorder,robrank}, which raises concerns on
+safety, security, or fairness for a DML application.
 %
+The existing attacks aims to completely subvert the image retrieval results~[][][],
+or covertly alter the top-ranking results without being abnormal~[][][][].
+
+%
+\textbf{Defenses in DML.} Compared to attacks, defense methods for DML are less
+explored.
+%
+Zhou \etal~\cite{advrank} present Embedding Shifted Triplet (EST), an
+adversarial training method using adversarial examples with maximized embedding
+move distance off their original locations.
+%
+Anti-Collapse Triplet (ACT)~\cite{robrank} forces the model to separate
+collapsed positive and negative samples in order to learn robust features,
+which achieves the state-of-the-art robustness.
+%
+However, the existing defense methods suffer from low efficiency as a
+relatively weak adversary is used in order to avoid model collapse.
+
+\section{Our Approach}
+\label{sec:3}
+
 Specifically, an imperceptible adversarial perturbation $r$ is added to the
@@
 
-\textbf{Defenses in DML.}
-%
-Although attacks against DML has been widely studied~\cite{advrank,advorder},
-the defense methods for improving adversarial robustness is much less explored.
-%
-As adversarial training~\cite{madry} remains to be one of the most effective
-defense for classification, existing defense methods for DML are also
-adversarial training-based.
 %
@@
 \oo{Furthermore, min-max form -- free adversarial training}.
-
-\section{Our Approach}
-\label{sec:3}
 

### 2021-10-25 robdml.tex
tex

@@
 
+In Deep Metric Learning (DML)~\cite{revisiting,dmlreality}, an embedding
+function $\phi:\mathcal{X}\mapsto \Phi \subseteq \mathbb{R}^D$ is learned to
+map data points $X\in\mathcal{X}$ into an embedding space $\Phi$, which is usually
+normalized to the real unit hypersphere for regularization.
+%
+With a predefined distance function $d(\cdot,\cdot)$, which is usually the
+Euclidean distance, we can measure the distance between $X_i$ and $X_j$ as
+$d_\phi(X_i,X_j)=d(\phi(X_i),\phi(X_j))$.
+%
+In a typical setting, the triplet loss~\cite{facenet} can be used to learn the
+embedding function, and it could reach the state-of-the-art performance with an
+appropriate triplet sampling strategy~\cite{revisiting}.
+
+Given a triplet of image embeddings (anchor $\va=\phi(X_a)$, positive sample
+$\vp=\phi(X_p)$, negative sample $\vn=\phi(X_n)$), the triplet loss is defined
+as:
+%
+$
+%
+	L_\text{T}(\va, \vp, \vn; \gamma) = \max(0, d(\va, \vp) - d(\va, \vn) +
+	\gamma),
+%
+$
+%
+where $\gamma$ is a predefined margin parameter.
+
 Specifically, an imperceptible adversarial perturbation $r$ is added to the
@@
 \oo{Furthermore, min-max form -- free adversarial training}.
-
-In Deep Metric Learning (DML)~\cite{revisiting,dmlreality}, an embedding
-function $\phi:\mathcal{X}\mapsto \Phi \subseteq \mathbb{R}^D$ is learned to
-map data points $X\in\mathcal{X}$ into an embedding space $\Phi$, where the
-output of $\phi(\cdot)$ is usually normalized to the real unit hypersphere for
-regularization purpose.
-%
-With a predefined distance function $d(\cdot,\cdot)$, it allows us to measure
-the distance between $X_i$ and $X_j$ as
-$d_\phi(X_i,X_j)=d(\phi(X_i),\phi(X_j))$.
-%
-Various loss functions for learning the underlying embedding function have been
-proposed~\cite{revisiting,dmlreality}, where the triplet loss~\cite{facenet}
-remain to be a strong and widely used baseline that could reach
-state-of-the-art performance with appropriate triplet sampling strategy.
-%
-Given a triplet of image embeddings (anchor $\va=\phi(X_a)$, positive sample
-$\vp=\phi(X_p)$, negative sample $\vn=\phi(X_n)$), the triplet loss is defined
-as:
-%
-$
-%
-	L_\text{T}(\va, \vp, \vn; \gamma) = \max(0, d(\va, \vp) - d(\va, \vn) +
-	\gamma),
-%
-$
-%
-where $\gamma$ is a predefined margin parameter.
 

### 2021-10-25 robdml.tex
tex

@@
 
+% Background DML formulation
+
 In Deep Metric Learning (DML)~\cite{revisiting,dmlreality}, an embedding
 function $\phi:\mathcal{X}\mapsto \Phi \subseteq \mathbb{R}^D$ is learned to
-map data points $X\in\mathcal{X}$ into an embedding space $\Phi$, which is usually
+map data points $\mX\in\mathcal{X}$ into an embedding space $\Phi$, which is usually
 normalized to the real unit hypersphere for regularization.
@@
 With a predefined distance function $d(\cdot,\cdot)$, which is usually the
-Euclidean distance, we can measure the distance between $X_i$ and $X_j$ as
-$d_\phi(X_i,X_j)=d(\phi(X_i),\phi(X_j))$.
+Euclidean distance, we can measure the distance between $\mX_i$ and $\mX_j$ as
+$d_\phi(\mX_i,\mX_j)=d(\phi(\mX_i),\phi(\mX_j))$.
 %
@@
 
-Given a triplet of image embeddings (anchor $\va=\phi(X_a)$, positive sample
-$\vp=\phi(X_p)$, negative sample $\vn=\phi(X_n)$), the triplet loss is defined
-as:
+% Background Triplet loss
+
+Given a sample triplet of anchor, positive, negative images, \ie, $\mA, \mP,
+\mN \in \mathcal{X}$, we first calculate their embeddings with $\phi(\cdot)$
+as $\va, \vp, \vn$, respectively.
+%
+Then the triplet loss~\cite{facenet} is defined as:
 %

### 2021-10-25 robdml.tex
tex

@@
 Given a sample triplet of anchor, positive, negative images, \ie, $\mA, \mP,
-\mN \in \mathcal{X}$, we first calculate their embeddings with $\phi(\cdot)$
-as $\va, \vp, \vn$, respectively.
+\mN \in \mathcal{X}$, we first calculate their embeddings with $\phi(\cdot)$ as
+$\va, \vp, \vn$, respectively.
 %
@@
 where $\gamma$ is a predefined margin parameter.
-
-Specifically, an imperceptible adversarial perturbation $r$ is added to the
-input image $X$ ($\|r\|_p \leq \varepsilon$, $X+r\in \mathcal{X}$), so that its
-embedding vector $\tilde{\vx}=\phi(X+r)$ will be moved off its original
-location towards other positions to fulfill the attacker's goal.
+%
+To attack the DML model, an imperceptible adversarial perturbation $\vr$ is
+added to the input image $\mX$, which is subject to $\|\vr\|_p \leq
+\varepsilon$ and $\mX+\vr\in \mathcal{X}$, so that its embedding vector
+$\tilde{\vx}=\phi(\mX+\vr)$ will be moved off its original location to 
+other positions to fulfill the attacker's goal~[][][][][].
 

### 2021-10-25 appendix.tex
tex

@@
 		\cref{tab:srcdest}
+
+	\item Details of existing defense methods?
+
+%
+Embedding-Shifted Triplet (EST)~\cite{advrank} adopts adversarial counterpars
+of $\va,\vp,\vn$ with maximum embedding move distance off their original
+locations, \ie,
+$L_\text{EST}=L_\text{T}(\tilde{\va},\tilde{\vp},\tilde{\vn};\gamma)$ where
+$\tilde{\va}=\phi(X+r^*)$, $r^*=\arg\max_{r}d_\phi(X+r, X)$.
+%
+Anti-Collapse Triplet (ACT)~\cite{robrank} collapses the embedding vectors of
+positive and negative sample, and enforces the model to separate them apart,
+\ie, $L_\text{ACT}=L_\text{T}(\va, \overrightarrow{\vp},
+\overleftarrow{\vn};\gamma)$, where $[\overrightarrow{\vp},\overleftarrow{\vn}]
+=[\phi(X_p+r_p^*), \phi(X_n+r_n^*)]$, and $[r_p^*,r_n^*]=\arg\min_{r_p,r_n}
+d_\phi(X_p+r_p, X_n+r_n)$.
+%
+However, compared to the standard min-max adversarial training
+paradigm~\cite{madry}, these methods merely indirectly increase the loss value,
+and thus, suffer from inefficient learning because the adversary is not strong
+enough.
+
 \end{enumerate}

### 2021-10-25 robdml.tex
tex

@@
 \usepackage{soul}
+\usepackage{comment}
 
@@
 \varepsilon$ and $\mX+\vr\in \mathcal{X}$, so that its embedding vector
-$\tilde{\vx}=\phi(\mX+\vr)$ will be moved off its original location to 
-other positions to fulfill the attacker's goal~[][][][][].
-
+$\tilde{\vx}=\phi(\mX+\vr)$ will be moved off its original location to other
+positions to fulfill the attacker's goal~[][][][][].
 %
-Embedding-Shifted Triplet (EST)~\cite{advrank} adopts adversarial counterpars
-of $\va,\vp,\vn$ with maximum embedding move distance off their original
-locations, \ie,
-$L_\text{EST}=L_\text{T}(\tilde{\va},\tilde{\vp},\tilde{\vn};\gamma)$ where
-$\tilde{\va}=\phi(X+r^*)$, $r^*=\arg\max_{r}d_\phi(X+r, X)$.
+To defend against the attacks, the DML model can be adversarially trained to
+reduce the effect of attacks~\cite{advrank,robrank}.
 %
-Anti-Collapse Triplet (ACT)~\cite{robrank} collapses the embedding vectors of
-positive and negative sample, and enforces the model to separate them apart,
-\ie, $L_\text{ACT}=L_\text{T}(\va, \overrightarrow{\vp},
-\overleftarrow{\vn};\gamma)$, where $[\overrightarrow{\vp},\overleftarrow{\vn}]
-=[\phi(X_p+r_p^*), \phi(X_n+r_n^*)]$, and $[r_p^*,r_n^*]=\arg\min_{r_p,r_n}
-d_\phi(X_p+r_p, X_n+r_n)$.
-%
-However, compared to the standard min-max adversarial training
-paradigm~\cite{madry}, these methods merely indirectly increase the loss value,
-and thus, suffer from inefficient learning because the adversary is not strong
-enough.
-%
-\oo{Furthermore, min-max form -- free adversarial training}.
+The most important metrics for a good defense is training cost, adversarial
+robustness, and performance on benign examples.
 

### 2021-10-25 robdml.tex
tex

@@
 
-\cref{fig:hm}
-
-by referencing
-another benign (but harder) sample triplet.
-
-make adversarially training a DML model
-with triplet loss feasible without model collapse, so the model could
-efficiently learn from a strong adversary.
-%
-Assume there are two data triplets, namely ``source triplet'' and ``destination
-triplet'' with the same anchor example, but sampled using different triplet
-sampling strategies.
-%
-And the ``destination triplet'' is expected to result in a higher loss value
-than another.
-%
-HM aims at creating adversarial examples of the ``source triplet'', that would
-increase the corresponding loss value until that of the unperturbed
-``destination triplet''.
-%
-This can also be interpreted as maximizing the loss value but ``stops early''
-at a certain point.
-%
-The resulting perturbed ``source triplet'' can be used for adversarial training
-of the model.
-
-Given an anchor image $X_a$, we sample a positive image $X_p^S$ (in the same
-class as the anchor) and a negative image $X_n^S$ (in different class as the
-anchor) with a certain sampling strategy (\eg, semi-hard~\cite{facenet}).
-%
-% For convenience we call this triplet as ``source triplet''.
-%
-Then its \emph{hardness} is defined as
+Given an image triplet ($\mA$, $\mP$, $\mN$) sampled with a certain sampling
+strategy (\eg, semi-hard~\cite{facenet}) within a mini-batch, we define its
+\emph{hardness} as a scalar:
 %
@@
 %
-H(X_a^S,X_p^S,X_n^S)=d_\phi(X_a,X_p^S)-d_\phi(X_a,X_n^S),
+H(\mA,\mP,\mN)=d_\phi(\mA,\mP)-d_\phi(\mA,\mN),
 %
@@
 %
-which is an internal
-part of the triplet loss.
+which is an internal part of the triplet loss.
 %
-For convenience we call this as ``source hardness'', denoted as $H_\mathsf{S}$.
+For convenience we call this triplet as ``\emph{source} triplet'', and the
+corresponding $H(\cdots)$ value as ``\emph{source} hardness'', denoted as
+$H_\mathsf{S}$.
 
@@
 \end{equation}
+
+\cref{fig:hm}
 %
@@
 
+%
+Assume there are two data triplets, namely ``source triplet'' and ``destination
+triplet'' with the same anchor example, but sampled using different triplet
+sampling strategies.
+%
+And the ``destination triplet'' is expected to result in a higher loss value
+than another.
+%
+HM aims at creating adversarial examples of the ``source triplet'', that would
+increase the corresponding loss value until that of the unperturbed
+``destination triplet''.
+%
+This can also be interpreted as maximizing the loss value but ``stops early''
+at a certain point.
+%
+The resulting perturbed ``source triplet'' can be used for adversarial training
+of the model.
 \subsection{Gradual Adversary}

### 2021-10-25 robdml.tex
tex

@@
 Recall that the model is already prone to collapse with excessively hard benign
-triplets, let alone adversarial examples.
+triplets~\cite{facenet}, let alone adversarial examples.
 %
@@
 
+% define hardness
+
 Given an image triplet ($\mA$, $\mP$, $\mN$) sampled with a certain sampling
@@
 
-In the traditional min-max adversarial training setting~\cite{madry}, the inner
-``max'' problem should maximize $H(X_a,X_p^S,X_n^S)$ and hence maximize the triplet
-loss.
+% define hardness manipulation
+
+Then, \emph{Hardness Manipulation} (HM) aims to increase the \emph{source} hardness
+$H_\mathsf{S}$ into a specified ``\emph{destination} hardness'' $H_\mathsf{D}$,
+by finding adversarial examples of the source triplet $(\mA, \mP, \mN)$, \ie,
+$(\mA + \hat{\vr}_a, \mP + \hat{\vr}_p, \mN + \hat{\vr}_n)$,
+where $(\hat{\vr}_a, \hat{\vr}_p, \hat{\vr}_n)$ are the adversarial perturbations.
 %
-However, existing defense methods~\cite{advorder,robrank} refrain from adopting
-such paradigm because the model will quickly collapse with excessively hard
-triplets~\cite{facenet}, and adopt relatively weak adversaries instead
-(inefficient in gaining robustness).
+If we denote the hardness of the adversarially perturbed \emph{source} triplet
+as $\tilde{H}_\mathsf{S}$, the HM can be implemented as follows:
+%
+\begin{equation}
+	%
+	\hat{\vr}_a, \hat{\vr}_p, \hat{\vr}_n = \argmin_{r_a,r_p,r_n} \big\|\max(0,
+	H_\mathsf{D} - \tilde{H}_\mathsf{S} ) \big\|_2^2.
+	%
+	\label{eq:hm}
+	%
+\end{equation}
 
-In this paper, we argue that the hardness of triplet matters in adversarial
-training for DML.
-%
-The model does not collapse with EST or ACT because the expectation of hardness,
-\ie, $E[H]$ will be close to zero.
-%
-While the variance $\text{Var}[H]$ for EST is higher, and that for ACT is lower.
-
-Instead of directly maximizing the source hardness, we propose to stop the
-maximization process when the adversarial examples reach a certain level of
-hardness in order to avoid model collapse.
-%
-Based on the same anchor image $X_a$, we sample another positive image $X_p^D$
-and negative image $X_n^D$ with a different triplet sampling strategy, and
-we call its hardness as ``destination hardness'', denoted as $H_\mathsf{D}$.
-
-Then, we want change (increase) the hardness level from $H_\mathsf{S}$ into $H_\mathsf{D}$, by
-finding adversarial examples for $(X_a, X_p^S, X_n^S)$.
 %
@@
 %
-We denote the the hardness of adversarial examples as $\tilde{H}_S=H(X_a{+}r_a,
-X_p^S{+}r_p, X_n^S{+}r_n)$.
 %
-This is named as \emph{Hardness Manipulation} (HM), which is implemented as
-follows:
-%
-\begin{equation}
-	%
-	\bar{r}_a, \bar{r}_p, \bar{r}_n = \argmin_{r_a,r_p,r_n} \big\|\min(0,
-	\tilde{H}_\mathsf{S} - H_\mathsf{D}) \big\|_2^2.
-	%
-	\label{eq:hm}
-	%
-\end{equation}
 
@@
 \oo{uses gradient for maximization. Maxim is $HM(H_\mathsf{S}, 2)$.}
+
+In the traditional min-max adversarial training setting~\cite{madry}, the inner
+``max'' problem should maximize $H(X_a,X_p^S,X_n^S)$ and hence maximize the triplet
+loss.
+
+In this paper, we argue that the hardness of triplet matters in adversarial
+training for DML.
+%
+The model does not collapse with EST or ACT because the expectation of hardness,
+\ie, $E[H]$ will be close to zero.
+%
+While the variance $\text{Var}[H]$ for EST is higher, and that for ACT is lower.
+
+Instead of directly maximizing the source hardness, we propose to stop the
+maximization process when the adversarial examples reach a certain level of
+hardness in order to avoid model collapse.
+%
+Based on the same anchor image $X_a$, we sample another positive image $X_p^D$
+and negative image $X_n^D$ with a different triplet sampling strategy, and
+we call its hardness as ``destination hardness'', denoted as $H_\mathsf{D}$.
 

### 2021-10-25 robdml.tex
tex

@@
 
-Then, \emph{Hardness Manipulation} (HM) aims to increase the \emph{source} hardness
-$H_\mathsf{S}$ into a specified ``\emph{destination} hardness'' $H_\mathsf{D}$,
-by finding adversarial examples of the source triplet $(\mA, \mP, \mN)$, \ie,
-$(\mA + \hat{\vr}_a, \mP + \hat{\vr}_p, \mN + \hat{\vr}_n)$,
-where $(\hat{\vr}_a, \hat{\vr}_p, \hat{\vr}_n)$ are the adversarial perturbations.
+Then, \emph{Hardness Manipulation} (HM) aims to increase the \emph{source}
+hardness $H_\mathsf{S}$ into a specified ``\emph{destination} hardness''
+$H_\mathsf{D}$, by finding adversarial examples of the source triplet $(\mA,
+\mP, \mN)$, \ie, $(\mA + {\vr}_a, \mP + {\vr}_p, \mN + {\vr}_n)$, where
+$({\vr}_a, {\vr}_p, {\vr}_n)$ are the adversarial perturbations.
 %
@@
 	%
-	\hat{\vr}_a, \hat{\vr}_p, \hat{\vr}_n = \argmin_{r_a,r_p,r_n} \big\|\max(0,
-	H_\mathsf{D} - \tilde{H}_\mathsf{S} ) \big\|_2^2.
+	\hat{\vr}_a, \hat{\vr}_p, \hat{\vr}_n = \argmin_{\vr_a,\vr_p,\vr_n}
+	\Big\|\max(0, H_\mathsf{D} - \tilde{H}_\mathsf{S} ) \Big\|_2^2.
 	%
@@
 \end{equation}
-
 %
-Note, it is not expected to lower the hardness during the attack, namely
-$E[H_\mathsf{D}]$ should be greater or equal to $E[H_\mathsf{S}]$.
+The $\max(0,\cdot)$ part in \cref{eq:hm} truncates the gradient when
+$H_\mathsf{S}>H_\mathsf{D}$, automatically stopping the optimization, because
+$H_\mathsf{S}$ is not desired to be reduced once being greater than
+$H_\mathsf{D}$.
 %
-%
-
-\cref{fig:hm}
-%
-The $\min(0,\cdot)$ part in \cref{eq:hm} truncates the gradient when $H_\mathsf{S}>H_\mathsf{D}$,
-automatically stopping the optimization.
-%
-This is because $H_\mathsf{S}$ will be reduced once greater than $H_\mathsf{D}$ in standard Mean
-Square Error.
+The \cref{eq:hm} is written in the L-$2$ norm form instead of the standard Mean Squared
+Error because HM can be directly extended into vector form for a
+mini-batch.
 %
@@
 \phi(X_n^S+\bar{r}_n))$.
+
+\cref{fig:hm}
+%
+Note, it is not expected to lower the hardness during the attack, namely
+$E[H_\mathsf{D}]$ should be greater or equal to $E[H_\mathsf{S}]$.
+%
+%
 

### 2021-10-25 robdml.tex
tex

@@
 	\hat{\vr}_a, \hat{\vr}_p, \hat{\vr}_n = \argmin_{\vr_a,\vr_p,\vr_n}
-	\Big\|\max(0, H_\mathsf{D} - \tilde{H}_\mathsf{S} ) \Big\|_2^2.
+	\big\|\max(0, H_\mathsf{D} - \tilde{H}_\mathsf{S} ) \big\|_2^2.
 	%
@@
 %
-The optimization problem can be solved by projected gradient
-descent~\cite{madry}.
+The optimization problem can be solved by Projected Gradient
+Descent (PGD)~\cite{madry}.
 %
@@
 %
-$L_\text{T}(\phi(X_a+\bar{r}_a), \phi(X_p^S+\bar{r}_p),
-\phi(X_n^S+\bar{r}_n))$.
+$L_\text{T}(\phi(\mA+\hat{\vr}_a), \phi(\mP+\hat{\vr}_p),
+\phi(\mN+\hat{\vr}_n))$.
+%
+We abbreviate the adversarial training with adversarial examples created through
+this way as $\text{HM}[H_\mathsf{S},H_\mathsf{D}]$ in the following text.
 
-\cref{fig:hm}
+% strong adversary
+
+Note, in the PGD case, the sign of negative gradient of the HM objective with
+respect to an adversarial perturbation $\vr$ is equivalent to the sign of
+gradient for directly maximizing the hardness $\tilde{H}_\mathsf{S}$ (hence
+maximizing $L_\text{T}$), \ie,
 %
-Note, it is not expected to lower the hardness during the attack, namely
-$E[H_\mathsf{D}]$ should be greater or equal to $E[H_\mathsf{S}]$.
-%
-%
-
 \begin{align}
-	&
+	\Delta \vr
+	=&
 	\sign\big\{
-		-\frac{\partial}{\partial r} \big\| \min(0, 
-		\tilde{H}_\mathsf{S} - H_\mathsf{D}) \big\|_2^2
+		-\frac{\partial}{\partial \vr} \big\| \max(0, 
+		H_\mathsf{D} - \tilde{H}_\mathsf{S} ) \big\|_2^2
 	\big\}
@@
 	\sign\big\{
-		-2(\tilde{H}_\mathsf{S}-H_\mathsf{D})
-		\frac{\partial }{\partial r} \tilde{H}_\mathsf{S} \big\}
+		2(H_\mathsf{D} - \tilde{H}_\mathsf{S})
+		\frac{\partial }{\partial \vr} \tilde{H}_\mathsf{S} \big\}
 	=
 	\sign\big\{
-		\frac{\partial}{\partial r} \tilde{H}_\mathsf{S}
-		\big\}
+		\frac{\partial}{\partial \vr} \tilde{H}_\mathsf{S}
+		\big\},
 \end{align}
+%
+assuming that $H_\mathsf{D}>\tilde{H}_\mathsf{S}$.
+%
+And the perturbation $\vr$ is updated as $\vr \leftarrow \vr + \alpha \Delta \vr$
+by PGD, where $\alpha$ is a step size parameter.
+%
+Thus, the optimization of HM objective can be interpreted as directly
+maximizing $\tilde{H}_\mathsf{S}$, but stops very early once it reaches
+$H_\mathsf{D}$.
+%
+This means the model learns from an efficient adversary during adversarial
+training with HM.
+
+Instead of directly maximizing the source hardness, we propose to stop the
+maximization process when the adversarial examples reach a certain level of
+hardness in order to avoid model collapse.
 
@@
 
-Instead of directly maximizing the source hardness, we propose to stop the
-maximization process when the adversarial examples reach a certain level of
-hardness in order to avoid model collapse.
+\cref{fig:hm}
+%
+Note, it is not expected to lower the hardness during the attack, namely
+$E[H_\mathsf{D}]$ should be greater or equal to $E[H_\mathsf{S}]$.
+%
+%
+
 %

### 2021-10-26 robdml.tex
tex

@@
 
-\begin{figure}
-	\includegraphics[width=\columnwidth]{hmillust.pdf}
-	\caption{Illustration of Hardness Manipulation.}
-	\label{fig:hm}
-\end{figure}
-
 % define hardness
@@
 Given an image triplet ($\mA$, $\mP$, $\mN$) sampled with a certain sampling
-strategy (\eg, semi-hard~\cite{facenet}) within a mini-batch, we define its
+strategy (\eg, Random) within a mini-batch, we define its
 \emph{hardness} as a scalar:
@@
 this way as $\text{HM}[H_\mathsf{S},H_\mathsf{D}]$ in the following text.
+%
+And the overall procedure of HM is illustrated in \cref{fig:hm}.
+
+\begin{figure}
+	\includegraphics[width=\columnwidth]{hmillust.pdf}
+	\caption{Illustration of Hardness Manipulation.}
+	\label{fig:hm}
+\end{figure}
 
@@
 
-Instead of directly maximizing the source hardness, we propose to stop the
-maximization process when the adversarial examples reach a certain level of
-hardness in order to avoid model collapse.
+Since the same $\Delta\vr$ can be used for both minimizing the HM objective
+and maximizing the triplet loss, one potential advantage of HM is that
+the gradients during the training process can be reused for creating
+adversarial examples for much faster adversarial training, according to 
+Free Adversarial Training~\cite{freeat}.
+%
+We leave this for future exploration.
 
-\oo{uses gradient for maximization. Maxim is $HM(H_\mathsf{S}, 2)$.}
+% selection of destination hardness
 
-In the traditional min-max adversarial training setting~\cite{madry}, the inner
-``max'' problem should maximize $H(X_a,X_p^S,X_n^S)$ and hence maximize the triplet
-loss.
+\textbf{Destination Hardness} $H_\mathsf{D}$.
+%
+$\text{HM}[H_\mathsf{S},H_\mathsf{D}]$ is a very flexible method as various
+\emph{destination} hardness $H_\mathsf{D}$ can be used, \eg, a constant, the
+hardness of another benign triplet, or even a pseudo-hardness function.
+%
+The case of maximizing the triplet loss is equivalent to
+$\text{HM}[H_\mathsf{S},2+\gamma]$, where $2+\gamma$ is the 
+upperbound of triplet loss.
 
-In this paper, we argue that the hardness of triplet matters in adversarial
-training for DML.
+As pushing $\tilde{H}_\mathsf{S}$ towards the upperbound will easily lead to
+model collapse, a valid $H_D\mathsf{D}$ should be choosed within the interval
+$[H_\mathsf{S},2+\gamma]$ without rendering model collapse.
 %
-The model does not collapse with EST or ACT because the expectation of hardness,
-\ie, $E[H]$ will be close to zero.
+Thus, intuitively, $H_\mathsf{D}$ can be the hardness of another benign triplet
+(with the same anchor) sampled with a strategy with a higher hardness
+expectation, \ie, $E[H_\mathsf{D}] > E[H_\mathsf{S}]$.
 %
-While the variance $\text{Var}[H]$ for EST is higher, and that for ACT is lower.
+Or at least the $\text{Var}[H_\mathsf{D}]$ of such sampling strategy has to be
+large enough in order to create valid adversarial examples.
+%
+For instance, $H_\mathsf{D}$ can be the hardness of a Semihard~\cite{facenet}
+triplet when the \emph{source} triplet is sampled with Random sampler.
+%
+Predictably, the model performance will be significantly influenced by the
+triplet sampling strategies we chose for $H_\mathsf{D}$ in this case.
+%
+For convenience of further discussion, we denote the hardness of a Random
+triplet, Semihard triplet, and Softhard triplet as $\mathcal{R}$,
+$\mathcal{M}$, $\mathcal{S}$, respectively.
 
-\cref{fig:hm}
-%
-Note, it is not expected to lower the hardness during the attack, namely
-$E[H_\mathsf{D}]$ should be greater or equal to $E[H_\mathsf{S}]$.
-%
-%
+If we have a strong prior knowledge on what the \emph{destination} hardness
+should be, we can even use a pseudo-hardness function $g(\cdot)$, which is a
+customized scalar function.
 
-%
-Based on the same anchor image $X_a$, we sample another positive image $X_p^D$
-and negative image $X_n^D$ with a different triplet sampling strategy, and
-we call its hardness as ``destination hardness'', denoted as $H_\mathsf{D}$.
-
-Note, the design of HM is flexible, and not coupled with specific sampling
-strategy.
-%
-In other words, any existing or future triplet sampling strategy can
-be adopted in HM.
-%
-or even a pseudo hardness function $g(\cdot)$ as long as we have a strong
-prior knowledge on what the destination hardness should be.
-
-\oo{extend: fat}
-training process of a regular DML model, but existing defense methods are
-incompatible to acceleration methods like Free Adversarial
-Training~\cite{freeat}.
-
-\oo{[4. Free Adversarial Metric Learining]}
-Extension of FAT to adversarial deep metric learning.
-
-%
-Assume there are two data triplets, namely ``source triplet'' and ``destination
-triplet'' with the same anchor example, but sampled using different triplet
-sampling strategies.
-%
-And the ``destination triplet'' is expected to result in a higher loss value
-than another.
-%
-HM aims at creating adversarial examples of the ``source triplet'', that would
-increase the corresponding loss value until that of the unperturbed
-``destination triplet''.
-%
-This can also be interpreted as maximizing the loss value but ``stops early''
-at a certain point.
-%
-The resulting perturbed ``source triplet'' can be used for adversarial training
-of the model.
 \subsection{Gradual Adversary}

### 2021-10-26 appendix.tex
u

@@
 \begin{itemize}
+
+	\item [\xmark] Multicard DDP and single card training leads to different
+		performance, regardless of the exact model of GPUs.
+		%
+		According to the observation, single card training leadss to a lower
+		recall performance and a higher robustness score.
+		%
+		More efficient? This should be ok.
+		%
+		But be careful when doing ablation studies as this will greatly
+		interfere with the conclusions.
 

### 2021-10-26 robdml.tex
tex

@@
 As pushing $\tilde{H}_\mathsf{S}$ towards the upperbound will easily lead to
-model collapse, a valid $H_D\mathsf{D}$ should be choosed within the interval
+model collapse, a valid $H_\mathsf{D}$ should be choosed within the interval
 $[H_\mathsf{S},2+\gamma]$ without rendering model collapse.
@@
 If we have a strong prior knowledge on what the \emph{destination} hardness
-should be, we can even use a pseudo-hardness function $g(\cdot)$, which is a
+should be, we can even use a pseudo-hardness function $g(\cdot)$, \ie, a
 customized scalar function.
@@
 
-\cref{fig:ga}
-
 % motivation of GA : late phase
 
-When benign triplets are used as reference for destination hardness, the
-adversary (\ie, hardness of adversarial triplets) could gradually become weaker
-than it should be in the late phase of training.
+Even if $H_\mathsf{D}$ is calucated from another triplet harder than the
+\emph{source} triplet, the adversary may become weak in the late phase of
+training.
 %
-During the training process of a DML model, the expectation of the triplet loss
-$E[L_\text{T}(\cdots)]$ on benign examples is gradually decreasing
-(with the lower bound being zero).
-%
-The corresponding expectation of hardness $E[H(\cdots)]$ will
-decrease as well (with the lower bound being $-\gamma$).
-%
-As a result, $E[H_\mathsf{D}-H_\mathsf{S}]$ will gradually tend to zero,
-indicating a gradually decreasing strength of attack, and inefficiency in
-learning from a strong adversary.
+The training process of the model aims to reduce the expectation of triplet loss
+$E[L_\text{T}]$ to zero over the distribution of sample triplets,
+and thus the $E[H]$ of any given triplet will eventually tend to $-\gamma$,
+reducing the hardness of adversarial triplets from HM.
 
+\cref{fig:ga}
 % hardness boosting

### 2021-10-26 robdml.tex
tex

@@
 Even if $H_\mathsf{D}$ is calucated from another triplet harder than the
-\emph{source} triplet, the adversary may become weak in the late phase of
-training.
+\emph{source} triplet, the adversarial example may become weak in the late
+phase of training.
 %
-The training process of the model aims to reduce the expectation of triplet loss
-$E[L_\text{T}]$ to zero over the distribution of sample triplets,
-and thus the $E[H]$ of any given triplet will eventually tend to $-\gamma$,
-reducing the hardness of adversarial triplets from HM.
+The optimizer aims to reduce the expectation of triplet
+loss $E[L_\text{T}]$ to zero as possible over the distribution of sample triplets, and thus
+the $E[H]$ of any given triplet will tend to $-\gamma$, reducing the
+hardness of adversarial triplets from HM.
+%
+We speculate this will lower the level of robustness the model could reach.
 
-\cref{fig:ga}
 % hardness boosting
 
-Such deficiency in the late training process can be alleviated with a
-pseudo-hardness function that boosts the destination hardness when the loss
-value is low.
+Intuitively, such deficiency can be alleviated with a \emph{pseudo-hardness}
+function that slightly increase the value of $H_\mathsf{D}$ in the late phase
+of training.
 %
@@
 we first normalize it into $[0,1]$ as $\bar{\ell}_{t-1}=\min(u,\ell_{t-1})/u$,
-where $u$ is a manually specified parameter.
+where $u$ is a manually specified constant.
 %
-Note, $u$ is much less than the theoretical upperbound of the loss function,
-in order to avoid excessive hardness boost in the functions introduced below.
-%
-Then the expectation of destination hardness can be linearly shifted (boosted)
-by a scaled constant by a ``hardness boosting'' pseudo-hardness
-function, \ie,
+Then we can linearly shift the $E[H_\mathsf{D}]$ by a scaled constant $\xi$,
+\ie,
 %
@@
 %
-And the adversarial examples from $\text{HM}(H_\mathsf{S},g_\mathsf{B}(H_\mathsf{D}))$
-can be used for training.
+The deficiency can be alleviated in
+$\text{HM}[H_\mathsf{S},g_\mathsf{B}(H_\mathsf{D})]$.
+
+\cref{fig:ga}
 
@@
 of white-box attacks is expected to be robust in general.
+
+Note, $u$ is much less than the theoretical upperbound of the loss function,
+in order to avoid excessive hardness boost in the functions introduced below.
 

### 2021-10-26 robdml.tex
tex

@@
 
-\cref{fig:ga}
-
 % motivation of GA: early phase
 
-However, while the destination hardness is boosted in the late phase of
-training, the adversarial examples may still hamper the learning of a good
-embedding space in the early phase.
-%
-At this point, we argue that learning from a strong adversary in the early
-training phase (\ie, when the embedding space is not ``in-good-shape'') hampers the
-generalization on benign examples.
+Apart from the deficiency in the late phase of training, we speculate that
+relatively strong adversarial examples may hinder the model from 
+learning good embedding space for the benign examples in the very early phase
+of training, hence influence the model performance on benign examples.
 
@@
 
-In other words, the desired destination hardness should be (1) relatively weak
-in the early training phase, and (2) relatively strong in the late training
-phase.
+Thus, a desired $H_\mathsf{D}$ should be (1) close to $H_\mathsf{S}$ in the
+early training phase (indicated by a large loss value), and (2) clearly higher
+than $H_\mathsf{S}$ in the late training phase (indicated by a small loss
+value).
 %
-We name the family of pseudo-hardness functions that fulfills the two
-conditions as ``Graduate Adversary''.
-%
+We name the two conditions as ``Graduate Adversary'' for 
+pseudo-hardness functions.
+
 Additionally, if we have a strong prior knowledge on ``how hard the destination
-hardness should be'', the pseudo-hardness function can be independent from
-any benign triplet.
+hardness should be'', the pseudo-hardness function can be independent from any
+benign triplet.
 
@@
 section.
+%
+\cref{fig:ga}
 %

### 2021-10-26 robdml.tex
tex

@@
 %
-As an example, we design a ``Simple Graduate Adversary'' (SGA) pseudo-hardness
+As an example, we design a ``Linear Graduate Adversary'' (LGA) pseudo-hardness
 function as the linearly scaled negative triplet margin, incorporating a strong
@@
 		%
-		A linear function named Simple Graduate Adversary (SGA) is designed as
+		A linear function named Linear Graduate Adversary (LGA) is designed as
 		an example.
@@
 
-Thus, a desired $H_\mathsf{D}$ should be (1) close to $H_\mathsf{S}$ in the
+Thus, $H_\mathsf{D}$ should be (1) close to $H_\mathsf{S}$ in the
 early training phase (indicated by a large loss value), and (2) clearly higher
 than $H_\mathsf{S}$ in the late training phase (indicated by a small loss
-value).
+value),
+%
+in order to automatically balance the training objectives (\ie, performance
+on benign examples \emph{v.s.} robustness).
 %
 We name the two conditions as ``Graduate Adversary'' for 
-pseudo-hardness functions.
+pseudo-hardness functions, as illustrated in \cref{fig:ga}.
 
-Additionally, if we have a strong prior knowledge on ``how hard the destination
-hardness should be'', the pseudo-hardness function can be independent from any
-benign triplet.
+% Linear graduate adversary
 
-% simple graduate adversary
-
-For instance, if we assume that the destination hardness should remain
-in the hardness range of Semihard~\cite{facenet}, the following function
-satisfies the two condictions of Gradual Adversary, dubbed
-``Simple Gradual Adversary'' (SGA):
+As an example, we propose a ``Linear Gradual Adversary'' (LGA) pseudo-hardness
+function that is independent to any benign triplets, incorporating an
+assumption that $H_\mathsf{D}$ should remain Semihard~\cite{facenet}, as
+follows:
 %
@@
 	%
-	g_\mathsf{SGA}(\bar{\ell}_{t-1}) =
-	-\gamma \cdot \bar{\ell}_{t-1} ~ \in [-\gamma,0].
+	g_\mathsf{LGA}(\bar{\ell}_{t-1}) = -\gamma \cdot \bar{\ell}_{t-1} ~ \in
+	[-\gamma,0].
 	%
@@
 %
-And the adversarial examples from $\text{HM}(H_\mathsf{S},g_\mathsf{SGA})$
-can be used for adversarial training.
+And the training objectives will be automatically balanced in
+$\text{HM}[H_\mathsf{S},g_\mathsf{LGA}]$.
 %
-The design of this function will be empirically supported in the experiments
-section.
+The design choice of LGA is empirically supported by experimental observations.
 %
-\cref{fig:ga}
+We leave more complex pseudo-hardness functions for future study.
 %
-The exploration of other possible pseudo-hardness functions is omitted 
-for simplicity.
 
@@
 
-During adversarial training, the adversarial counterpart of each given sample
+During adversarial training with HM, the adversarial counterpart of each given sample
 triplet is fed to the model, and the triplet loss will enforce a good

### 2021-10-26 robdml.tex
svg
tex

@@
 
-\textbf{Destination Hardness} $H_\mathsf{D}$.
+\textbf{Destination Hardness}.
 %
-$\text{HM}[H_\mathsf{S},H_\mathsf{D}]$ is a very flexible method as various
-\emph{destination} hardness $H_\mathsf{D}$ can be used, \eg, a constant, the
+$\text{HM}[H_\mathsf{S},H_\mathsf{D}]$ is flexible as various
+types of $H_\mathsf{D}$ can be specified, \eg, a constant, the
 hardness of another benign triplet, or even a pseudo-hardness function.
@@
 $\text{HM}[H_\mathsf{S},2+\gamma]$, where $2+\gamma$ is the 
-upperbound of triplet loss.
+upperbound of loss, while $\text{HM}[H_\mathsf{S},H_\mathsf{S}]$
+is regular DML training.
 
@@
 
+\begin{figure}[t]
+	\includegraphics[width=0.6\columnwidth]{icsapn.pdf}
+	\caption{Intra-Class Structure.}
+	\label{fig:ics}
+\end{figure}
+
 % motivation
@@
 We propose an additional loss function term to enforce such \emph{intra-class}
-structure, as shown in \oo{Fig.~[].}
+structure, as shown in \cref{fig:ics}.
 %

### 2021-10-26 robdml.tex
tex

@@
 	L_\text{ICS} = \lambda \cdot L_\text{T}(
-	\va, \tilde{\va}, \vp; 0),
+	\va, \phi(\mA + \hat{\vr}_a), \vp; 0),
 \end{equation}
@@
 
+\input{tab-hsort.tex}
+
 % evaluation: configuration
@@
 %
-The margin $\gamma$ in triplet loss is $0.2$ by default.
-%
-The setup is also consistent to standard DML~\cite{revisiting}.
+The margin $\gamma$ in triplet loss is $0.2$, which is consistent to standard
+DML~\cite{revisiting}.
 %
@@
 Adversarial examples are created under the perturbation budget
-$\varepsilon{=}8/255$ in infinity norm, using the
-Projected Gradient Descent (PGD)~\cite{madry} method with step size $\alpha{=}1/255$ 
-and a default maximum step number $\eta{=}8$.
+$\varepsilon{=}8/255$ in infinity norm, using PGD~\cite{madry} with step size
+$\alpha{=}1/255$ and a default maximum step number $\eta{=}8$.
 %
+The parameter $u$ is equal to $\gamma$, much less than the upperbound of the
+loss function, in order to avoid excessive hardness boost in pseudo-hardness
+functions $g_\mathsf{B}$ and $g_\mathsf{LGA}$.
 
@@
 an collection of existing attacks against DML or their simplified white-box
-alternatives.
+alternatives optimized with PGD ($\eta=32$ for strong effect).
 %
-Since adversarial training is not gradient masking~\cite{obfuscated}, the
+Since adversarial training is not ``gradient masking''~\cite{obfuscated}, the
 performance of white-box attack can be regarded as the upper bound of the
@@
 of white-box attacks is expected to be robust in general.
-
-Note, $u$ is much less than the theoretical upperbound of the loss function,
-in order to avoid excessive hardness boost in the functions introduced below.
 
@@
 \label{sec:41}
-
-\input{tab-hsort.tex}
 

### 2021-10-26 robdml.tex
tex

@@
 
-\oo{Concretely, the collection of attack for computing ERS includes.}
+Concretely, the collection of attacks for ERS includes:
 %
-Further details can be found in the supplementary.
+(1) CA+, CA-, QA+ and QA-~\cite{advrank}, which move some selected candidates
+towards the topmost or bottommost part of ranking list;
+%
+(2) TMA~[], which increases the cosine similarity between two selected samples;
+%
+(3) ES~[][], which moves the embedding of a sample off its original position as
+distant as possible;
+%
+(4) LTM~[], which perturbs the ranking result by minimizing the distance of
+unmatched pairs while maximizing the distance of matched pairs;
+%
+(5) GTM~\cite{robrank}, which minimizes the distance between query and the
+closest unmatching sample.
+%
+(6) GTT~\cite{robrank}, aims to move the top-$1$ candidate out of the top-$4$
+retrieval results, which is simplified from [].
+%
+The setup of all the attacks for robustness evaluation are unchanged from
+\cite{robrank} for fair comparison.
+%
+Further details can be found in \cite{robrank} and the supplementary.
 
+\begin{comment}
+%
 In this section, we first carry out parameter search for the components of the
@@
 The comparison with the state-of-the-art DML defense methods will be presented in the end.
+%
+\end{comment}
 

### 2021-10-26 robdml.tex
tex

@@
 %
-The parameter $u$ is equal to $\gamma$, much less than the upperbound of the
-loss function, in order to avoid excessive hardness boost in pseudo-hardness
-functions $g_\mathsf{B}$ and $g_\mathsf{LGA}$.
+The parameter $u$ is equal to $\gamma$, much less than the loss upperbound,
+in order to avoid excessive hardness boost in $g_\mathsf{B}$ and $g_\mathsf{LGA}$.
+%
+Parameter $\lambda$ in $L_\text{ICS}$ is $0.5$ by default.
 

### 2021-10-27 introplot.py
svg

@@ -1,12 +1,21 @@
 import numpy as np
 import matplotlib.pyplot as plt
 import rich
+import argparse
 c = rich.get_console()
 plt.rcParams['font.family'] = 'serif'
 plt.rcParams['font.serif'] = 'FreeSerif'
 plt.rcParams['font.size'] = 15
 
-data = {
+ag = argparse.ArgumentParser()
+ag.add_argument('-w', '--whichone', type=int, required=True)
+ag = ag.parse_args()
+
+whichone = ag.whichone
+
+if whichone == 0:
+    # all
+    data = {
         'ACT[R]': ( # [freeze]
             (27.5, 28.6, 30.6, 38.4, 46.5),
             (33.0, 17.0, 9.0, 5.0, 3.0),
@@ -37,7 +46,90 @@ data = {
             (3.0, 5.0, 9.0, 17.0, 33.0),
             (12.4, 24.7, 33.8, 36.8, 37.0),
             ),
-        }
+    }
+elif whichone == 1:
+    # fig 1
+    data = {
+        'ACT[R]': ( # [freeze]
+            (27.5, 28.6, 30.6, 38.4, 46.5),
+            (33.0, 17.0, 9.0, 5.0, 3.0),
+            (33.9, 34.7, 31.3, 13.9, 5.8),
+            ),
+        'ACT[S]': ( # [freeze]
+            (53.0, 49.3, 42.8, 40.5, 39.4),
+            (3.0, 5.0, 9.0, 17.0, 33.0),
+            (5.1, 7.1, 18.7, 23.7, 24.2),
+            ),
+        'HM[R,M]': ( # [freeze]
+            (23.1, 23.8, 27.0, 30.7, 34.3),
+            (33.0, 17.0, 9.0, 5.0, 3.0),
+            (38.0, 38.0, 35.1, 27.1, 18.1),
+            ),
+        'HM[S,M]': ( # [freeze]
+            (35.3, 37.4, 38.4, 40.6, 44.5),
+            (33.0, 17.0, 9.0, 5.0, 3.0),
+            (35.7, 34.8, 29.6, 22.1, 11.6),
+            ),
+        'HM[S,SGA]': ( # [freeze]
+            (47.5, 42.7, 38.0, 37.0, 36.5),
+            (3.0, 5.0, 9.0, 17.0, 33.0),
+            (11.7, 20.8, 32.4, 34.5, 35.9),
+            ),
[…]

### 2021-10-27 introplot.py
svg

@@ -13,29 +13,42 @@ ag = ag.parse_args()
 
 whichone = ag.whichone
 
+ACT_R = {
+    'ACT[R]': ( # [freeze]
+        (27.5, 28.6, 30.6, 38.4, 46.5),
+        (33.0, 17.0, 9.0, 5.0, 3.0),
+        (33.9, 34.7, 31.3, 13.9, 5.8),
+        ),
+}
+ACT_S = {
+    'ACT[S]': ( # [freeze]
+        (53.0, 49.3, 42.8, 40.5, 39.4),
+        (3.0, 5.0, 9.0, 17.0, 33.0),
+        (5.1, 7.1, 18.7, 23.7, 24.2),
+        ),
+}
+HM_RM = {
+    'HM[R,M]': ( # [freeze]
+        (23.1, 23.8, 27.0, 30.7, 34.3),
+        (33.0, 17.0, 9.0, 5.0, 3.0),
+        (38.0, 38.0, 35.1, 27.1, 18.1),
+        ),
+}
+HM_SM = {
+    'HM[S,M]': ( # [freeze]
+        (35.3, 37.4, 38.4, 40.6, 44.5),
+        (33.0, 17.0, 9.0, 5.0, 3.0),
+        (35.7, 34.8, 29.6, 22.1, 11.6),
+        ),
+}
+
 if whichone == 0:
     # all
     data = {
-        'ACT[R]': ( # [freeze]
-            (27.5, 28.6, 30.6, 38.4, 46.5),
-            (33.0, 17.0, 9.0, 5.0, 3.0),
-            (33.9, 34.7, 31.3, 13.9, 5.8),
-            ),
-        'ACT[S]': ( # [freeze]
-            (53.0, 49.3, 42.8, 40.5, 39.4),
-            (3.0, 5.0, 9.0, 17.0, 33.0),
-            (5.1, 7.1, 18.7, 23.7, 24.2),
-            ),
-        'hmetrm': ( # [freeze]
-            (23.1, 23.8, 27.0, 30.7, 34.3),
-            (33.0, 17.0, 9.0, 5.0, 3.0),
-            (38.0, 38.0, 35.1, 27.1, 18.1),
-            ),
-        'hmetsm': ( # [freeze]
-            (35.3, 37.4, 38.4, 40.6, 44.5),
-            (33.0, 17.0, 9.0, 5.0, 3.0),
-            (35.7, 34.8, 29.6, 22.1, 11.6),
[…]

### 2021-10-27 introplot.py
svg

@@ -6,6 +6,8 @@ c = rich.get_console()
 plt.rcParams['font.family'] = 'serif'
 plt.rcParams['font.serif'] = 'FreeSerif'
 plt.rcParams['font.size'] = 15
+plt.rcParams['text.usetex'] = False
+plt.rcParams['mathtext.fallback'] = 'cm'
 
 ag = argparse.ArgumentParser()
 ag.add_argument('-w', '--whichone', type=int, required=True)
@@ -41,6 +43,20 @@ HM_SM = {
         (35.7, 34.8, 29.6, 22.1, 11.6),
         ),
 }
+HM_SSGA = {
+    'HM[S,SGA]': ( # [freeze]
+        (47.5, 42.7, 38.0, 37.0, 36.5),
+        (3.0, 5.0, 9.0, 17.0, 33.0),
+        (11.7, 20.8, 32.4, 34.5, 35.9),
+        ),
+}
+HM_SHM = {
+    'HM[S,-r/2]': ( # [freeze]
+        (44.5, 40.0, 36.8, 35.2, 34.7),
+        (3.0, 5.0, 9.0, 17.0, 33.0),
+        (12.4, 24.7, 33.8, 36.8, 37.0),
+        ),
+}
 
 if whichone == 0:
     # all
@@ -49,32 +65,12 @@ if whichone == 0:
         **ACT_S,
         **HM_RM,
         **HM_SM,
-        'HM(S,SGA)': ( # [freeze]
-            (47.5, 42.7, 38.0, 37.0, 36.5),
-            (3.0, 5.0, 9.0, 17.0, 33.0),
-            (11.7, 20.8, 32.4, 34.5, 35.9),
-            ),
-        'HM(S,-r/2)': ( # [freeze]
-            (44.5, 40.0, 36.8, 35.2, 34.7),
-            (3.0, 5.0, 9.0, 17.0, 33.0),
-            (12.4, 24.7, 33.8, 36.8, 37.0),
-            ),
     }
 elif whichone == 1:
     # fig 1
     data = {
         **ACT_R,
         **ACT_S,
-        'HM[S,SGA]': ( # [freeze]
-            (47.5, 42.7, 38.0, 37.0, 36.5),
-            (3.0, 5.0, 9.0, 17.0, 33.0),
-            (11.7, 20.8, 32.4, 34.5, 35.9),
-            ),
-        'HM[S,-r/2]': ( # [freeze]
[…]

### 2021-10-27 introplot.py
sv

@@ -123,6 +123,16 @@ styledict = {
         'linestyle': '-.',
         'color': 'tab:gray',
     },
+    'EST[R]': {
+        'marker': 'd',
+        'linestyle': ':',
+        'color': 'tab:gray',
+    },
+    'HM[S,SGA]ICS': {
+        'marker': 'o',
+        'linestyle': '-.',
+        'color': 'crimson',
+    },
 }
 
 plt.figure(figsize=[10.8, 4.7])

### 2021-10-27 introplot.py
svg

@@ -71,6 +71,7 @@ elif whichone == 1:
     data = {
         **ACT_R,
         **ACT_S,
+        **HM_SSGA,
     }
 elif whichone == 2:
     # effectiveness of HM
@@ -97,41 +98,49 @@ styledict = {
         'marker': '.',
         'linestyle': ':',
         'color': 'tab:cyan',
+        'linewidth': 2.0,
     },
     'ACT[S]': {
         'marker': '.',
         'linestyle': ':',
         'color': 'tab:orange',
+        'linewidth': 2.0,
     },
     'HM[R,M]': {
         'marker': 'v',
         'linestyle': '-.',
         'color': 'tab:blue',
+        'linewidth': 2.0,
     },
     'HM[S,M]': {
         'marker': '^',
         'linestyle': '-.',
         'color': 'tab:red',
+        'linewidth': 2.0,
     },
     'HM[S,SGA]': {
         'marker': 'h',
         'linestyle': '-',
         'color': 'tab:purple',
+        'linewidth': 2.0,
     },
     'HM[S,-r/2]': {
         'marker': '+',
         'linestyle': '-.',
         'color': 'tab:gray',
+        'linewidth': 2.0,
     },
     'EST[R]': {
         'marker': 'd',
         'linestyle': ':',
         'color': 'tab:gray',
+        'linewidth': 2.0,
     },
     'HM[S,SGA]ICS': {
         'marker': 'o',
         'linestyle': '-.',
         'color': 'crimson',
+        'linewidth': 2.0,
     },
 }
 
@@ -162,6 +171,10 @@ ax.annotate('↘ Worse', xy=(0.75, 0.06), xycoords='axes fraction',
         bbox=dict(boxstyle="round,pad=0.3", fc="white", ec="k", lw=2),
         size=17)
 
+if whichone == 1:
+    ax.legend(['ACT[$\mathcal{R}$]',
+        'ACT[$\mathcal{S}$]',
+        'HM[$\mathcal{S},g_\mathsf{SGA}$]'])
 if whichone == 2:
     ax.legend(['ACT[$\mathcal{R}$]',
         'ACT[$\mathcal{S}$]',
@@ -202,6 +215,10 @@ ax.annotate('↘ Worse', xy=(0.75, 0.06), xycoords='axes fraction',
[…]

### 2021-10-27 sotaplot.py

@@ -1,0 +1,171 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import rich
+import argparse
+c = rich.get_console()
+plt.rcParams['font.family'] = 'serif'
+plt.rcParams['font.serif'] = 'FreeSerif'
+plt.rcParams['font.size'] = 15
+plt.rcParams['text.usetex'] = False
+plt.rcParams['mathtext.fallback'] = 'cm'
+
+data_cub = {
+    'ACT[R]': (
+        (30.6, 27.5), (9.0, 33.0), (31.3, 33.9) ),
+    'HM[S,SGA]': (
+        (38.0, 36.5), (9.0, 33.0), (32.4, 35.9) ),
+}
+data_cars = {
+    'ACT[R]': (
+        (46.8, 43.4), (9.0, 33.0), (39.8, 38.6) ),
+    'HM[S,SGA]': (
+        (63.2, 63.2), (9.0, 9.0), (42.4, 42.4)),
+}
+data_sop = {
+    'ACT[R]': (
+        (45.1, 47.5), (9.0, 33.0), (50.3, 50.8) ),
+    'HM[S,SGA]': (
+        (49.0,), (9.0,), (61.7,)),
+}
+
+styledict = {
+    'ACT[R]': {
+        'marker': '.',
+        'linestyle': ':',
+        'color': 'tab:cyan',
+        'linewidth': 3.0,
+    },
+    'ACT[S]': {
+        'marker': '.',
+        'linestyle': ':',
+        'color': 'tab:orange',
+        'linewidth': 3.0,
+    },
+    'HM[R,M]': {
+        'marker': 'v',
+        'linestyle': '-.',
+        'color': 'tab:blue',
+        'linewidth': 3.0,
+    },
+    'HM[S,M]': {
+        'marker': '^',
+        'linestyle': '-.',
+        'color': 'tab:red',
+        'linewidth': 3.0,
+    },
+    'HM[S,SGA]': {
+        'marker': 'h',
+        'linestyle': '-',
+        'color': 'tab:purple',
+        'linewidth': 3.0,
+    },
+    'HM[S,-r/2]': {
+        'marker': '+',
+        'linestyle': '-.',
+        'color': 'tab:gray',
+        'linewidth': 3.0,
+    },
+    'EST[R]': {
+        'marker': 'd',
+        'linestyle': ':',
[…]

### 2021-10-27 robdml.tex
tex
svg

@@
 	\includegraphics[width=1.0\columnwidth]{introplot.pdf}
+	\vspace{-2.0em}
 	\caption{
@@
 		Comparison in robustness, training time cost, and recall@1 performance
-		between our method and the state-of-the-art method.
+		between our method and the state-of-the-art method (\ie, ``ACT'').
 		%
-		Our method performs much better in all the three aspects.
+		Our method (\ie, ``HM'') performs much better in all the three aspects.
 		%
@@
 
+\begin{figure}[t]
+	\includegraphics[width=\columnwidth]{fighmeff.pdf}
+	\caption{HM eff}
+\end{figure}
+
 Why G4 so promising?
@@
 
+\begin{figure}[t]
+	\includegraphics[width=\columnwidth]{figgaeff.pdf}
+	\caption{GA eff}
+\end{figure}
+
 \input{tab-gaeff.tex}
@@
 \cref{fig:introplot}
+
+\begin{figure}[t]
+	\includegraphics[width=\columnwidth]{sotaplot.pdf}
+	\caption{sota plot}
+\end{figure}
 

### 2021-10-27 robdml.tex
tex

@@
 	\includegraphics[width=1.0\columnwidth]{introplot.pdf}
-	\vspace{-2.0em}
+	%\vspace{-2.0em}
 	\caption{
 		%
-		Comparison in robustness, training time cost, and recall@1 performance
-		between our method and the state-of-the-art method (\ie, ``ACT'').
+		Comparison in Robustness, Training Cost, and Recall@1 Performance
+		between Our Method (\ie, ``HM'') and the State-of-The-Art Method (\ie, ``ACT'').
 		%
-		Our method (\ie, ``HM'') performs much better in all the three aspects.
-		%
+		Best viewed in color.
 	}

### 2021-10-27 robdml.tex
tex

@@
 
-% 1. possible combinations
+% where to start
 
-Although any of the existing triplet sampling strategies, such as Random,
+To validate the effectivenss of HM, we start from using the hardness of another
+benign triplet sampled with a different triplet sampler as $H_\mathsf{D}$, as
+the existing triplet samplers are known not to result in model collapse in
+regular training.
+
+% combinations
+
+Due to the flexibility of HM, any of the existing (and future) triplet samplers
+can be used for calculating $H_\mathsf{S}$ and $H_\mathsf{D}$.
+%
+But not all possible combinations are expected to be effective or efficient in
+terms of adversarial training, as the \emph{source} hardness of a notable
+portion of the given triplets should be increased.
+%
+Thus, we first sort the existing samplers, namely Random,
 Semihard~\cite{facenet}, Softhard~\cite{revisiting},
 Distance-weighted~\cite{distance}, and the within-batch Hardest negative
-sampling method, can be selected for source hardness $H_\mathsf{S}$ and
-destination hardness $H_\mathsf{D}$, not all combinations are effective and
-efficient.
+sampler, based on the approximated mean hardness of their outputs, as shown
+in~\cref{tab:hsort}.
 %
-In this subsection, we find a proper combination empirically as a baseline for
-further experiments.
-
-% 2. sort sampling strategies
-
-As HM is expected to increase the hardness of the source triplet, we first sort
-the triplet sampling methods according to their approximated mean hardness of
-$1000$ mini-batches from CUB dataset with an imagenet-initialized RN18 model,
-as shown in~\cref{tab:hsort}.
-%
-Then we adversarially train models on the CUB dataset with all possible
-combinations, and summarize their R@1 and ERS performance in \cref{tab:desth}.
+Then we adversarially train models on the CUB dataset with all combinations
+respectively, and summarize the R@1 and ERS performance in \cref{tab:desth}.
 

### 2021-10-27 robdml.tex
tex

@@
 \usepackage{comment}
+\usepackage{todonotes}
 
@@
 Semihard~\cite{facenet}, Softhard~\cite{revisiting},
-Distance-weighted~\cite{distance}, and the within-batch Hardest negative
-sampler, based on the approximated mean hardness of their outputs, as shown
-in~\cref{tab:hsort}.
+Distance-weighted~\cite{distance} (\emph{abbr}., Distance), and the
+within-batch Hardest negative sampler, based on the approximated mean hardness
+of their outputs, as shown in~\cref{tab:hsort}.
 %
-Then we adversarially train models on the CUB dataset with all combinations
-respectively, and summarize the R@1 and ERS performance in \cref{tab:desth}.
+Then we adversarially train models on CUB dataset with all combinations
+respectively, and summarize the R@1 and ERS in \cref{tab:desth}.
 
@@
 
-Recall that triplet-based model is already prone to collapse with very hard
-examples, even if they are unperturbed.
+As shown in the last three columns of \cref{tab:desth}, almost all combinations
+lead to model collapse as long as $H_\mathsf{D}$ is calculated from a Softhard,
+Distance, or Hardest triplet.
 %
-Similarly, the model is expected to collapse with excessively hard adversarial
-examples as well.
-%
-As shown in the last three columns of \cref{tab:desth}, almost all combinations
-will result in model collapse as long as the destination hardness is softhard,
-distance, or hardest.
-%
-The only exception is the combination of distance and hardest.
-%
-We empirically observe that the $E[H]$ of distance and hardest sampling are
-very close to each other, which means the attack will be rather weak.
-%
-The model does not collapse in this case, but the robustness gain is negligible
-as well.
+Due to the small $E[H_\mathsf{D}-H_\mathsf{S}]$ in the combination of Distance
+and Hardest triplets, the adversarial examples will be weak and the model does
+collapse, but the robustness gain is negligible.
+
+\todo{Rev}
 
@@
 
-\subsection{Effectiveness of Hardness Manipulation}
+\subsection{Effectiveness of Our Approach}
 \label{sec:42}
@@
 \end{figure}
+
+\noindent\textbf{I. Effectivenss of Hardness Manipulation}.
 
@@
 
-\subsection{Effectiveness of GA and ICS}
-\label{sec:43}
+\noindent\textbf{II. Effectiveness of Gradual Adversary}.
 
@@
 
+\noindent\textbf{III. Effectivenss of Intra-Class Structure}.
+
 \subsection{Comparison with State-of-the-art}
+\label{sec:43}
 

### 2021-10-27 robdml.tex
tex

@@
 collapse, but the robustness gain is negligible.
-
-\todo{Rev}
+%
+Although $E[H]$ of Softhard is less than that of Distance or Hardest,
+some hard adversarial examples are still created due to its large
+$\text{Var}[H]$, which still result in a slow collapse.
 
@@
 
-For cases in upper triangular of \cref{tab:desth}, $E[H_\mathsf{S}] \leqslant E[H_\mathsf{D}]$,
-which means most triplets will be turned into adversarial example by HM
-to increase the hardness.
+For cases in the upper triangular of \cref{tab:desth} where $E[H_\mathsf{S}]
+\leqslant E[H_\mathsf{D}]$, most given triplets will be turned adversarial with
+an increased hardness.
 %
-Although most of such cases end up with model collapse, the preliminary 
-result suggests that HM from random to semihard is effective in significantly
-improve the robustness without model collapse, at an expected cost on the R@1
-performance on benign examples.
+Although most of such cases end up with model collapse, the preliminary result
+suggests that $\text{HM}[\mathcal{R},\mathcal{M}]$ is still effective in
+improving the robustness without model collapse, at an penalty on the R@1.
+
+\todo{R}
 

### 2021-10-27 robdml.tex
tex

@@
 $\text{Var}[H]$, which still result in a slow collapse.
+\todo{merge this para into upper triangular and lower triangular}
 
@@
 
-For cases in lower triangular of \cref{tab:desth}, $E[H_\mathsf{S}] \geqslant E[H_\mathsf{D}]$,
-which means most tirplet will not be turned into adversarial according to
-\cref{eq:hm}.
+For cases in lower triangular of \cref{tab:desth}, where $E[H_\mathsf{S}]
+\geqslant E[H_\mathsf{D}]$, a large portion of given triplets will be
+unchanged according to \cref{eq:hm}, and hence lead to weak robustness.
 %
-In such cases, the model will not be able to effectively learn from a strong
-adversary, and hence will behave as if no defense is equipped.
+As an exception, $\text{HM}[\mathcal{S},\mathcal{M}]$ is still effective in
+improving adversarial robustness, where a notable number of adversarial
+examples are created due the high $\text{Var}[H]$ of Softhard.
 %
-As an exception, HM from softhard to semihard can also lead to relatively high
-adversarial robustness.
 %
-Due to the high variance of hardness of softhard sampling strategy, the
-hardness of a notable portion of triplets will be less than that of semihard,
-and hence HM will create some adversarial examples for training.
 %

### 2021-10-27 introplot.py
svg fig1

@@ -57,6 +57,13 @@ HM_SHM = {
         (12.4, 24.7, 33.8, 36.8, 37.0),
         ),
 }
+HM_SSGAICS = {
+    'HM[S,SGA]ICS': ( # [freeze]
+        (45.2, 41.8, 37.2, 35.5),
+        (3.0, 5.0, 9.0, 17.0),
+        (15.2, 24.6, 33.5, 36.0),
+        ),
+}
 
 if whichone == 0:
     # all
@@ -71,7 +78,7 @@ elif whichone == 1:
     data = {
         **ACT_R,
         **ACT_S,
-        **HM_SSGA,
+        **HM_SSGAICS,
     }
 elif whichone == 2:
     # effectiveness of HM
@@ -89,6 +96,14 @@ elif whichone == 3:
         **HM_SM,
         **HM_SHM,
         **HM_SSGA,
+    }
+elif whichone == 4:
+    # effectivenss of ICS
+    data = {
+        **ACT_R,
+        **ACT_S,
+        **HM_SSGA,
+        **HM_SSGAICS,
     }
 else:
     raise ValueError
@@ -174,7 +189,10 @@ ax.annotate('↘ Worse', xy=(0.75, 0.06), xycoords='axes fraction',
 if whichone == 1:
     ax.legend(['ACT[$\mathcal{R}$]',
         'ACT[$\mathcal{S}$]',
-        'HM[$\mathcal{S},g_\mathsf{SGA}$]'])
+        'HM[$\mathcal{S},g_\mathsf{SGA}$]&ICS'],
+        loc='lower right',
+        bbox_to_anchor=(0.99, 0.12),
+        )
 if whichone == 2:
     ax.legend(['ACT[$\mathcal{R}$]',
         'ACT[$\mathcal{S}$]',
@@ -218,7 +236,10 @@ ax.annotate('↘ Worse', xy=(0.75, 0.06), xycoords='axes fraction',
 if whichone == 1:
     ax.legend(['ACT[$\mathcal{R}$]',
         'ACT[$\mathcal{S}$]',
-        'HM[$\mathcal{S},g_\mathsf{SGA}$]'])
+        'HM[$\mathcal{S},g_\mathsf{SGA}$]&ICS'],
+        loc='lower right',
+        bbox_to_anchor=(0.99, 0.12),
+        )
 if whichone == 2:
     ax.legend(['ACT[$\mathcal{R}$]',
         'ACT[$\mathcal{S}$]',

### 2021-10-27 robdml.tex
svg

@@
 		Comparison in Robustness, Training Cost, and Recall@1 Performance
-		between Our Method (\ie, ``HM'') and the State-of-The-Art Method (\ie, ``ACT'').
+		between Our Method (\ie, ``HM[$\mathcal{S},g_\mathsf{SGA}$]\&ICS'')
+		and the State-of-The-Art Method (\ie, ``ACT[$\mathcal{R}$]'' and
+		``ACT[$\mathcal{S}$]'').
 		%
-		Best viewed in color.
 	}

### 2021-10-27 introplot.py

@@ -192,6 +192,7 @@ if whichone == 1:
         'HM[$\mathcal{S},g_\mathsf{SGA}$]&ICS'],
         loc='lower right',
         bbox_to_anchor=(0.99, 0.12),
+        labelcolor='linecolor',
         )
 if whichone == 2:
     ax.legend(['ACT[$\mathcal{R}$]',
@@ -239,6 +240,7 @@ if whichone == 1:
         'HM[$\mathcal{S},g_\mathsf{SGA}$]&ICS'],
         loc='lower right',
         bbox_to_anchor=(0.99, 0.12),
+        labelcolor='linecolor',
         )
 if whichone == 2:
     ax.legend(['ACT[$\mathcal{R}$]',

### 2021-10-27 introplot.py
svg

@@ -136,18 +136,12 @@ styledict = {
     'HM[S,SGA]': {
         'marker': 'h',
         'linestyle': '-',
-        'color': 'tab:purple',
+        'color': 'darkviolet',
         'linewidth': 2.0,
     },
     'HM[S,-r/2]': {
         'marker': '+',
         'linestyle': '-.',
-        'color': 'tab:gray',
-        'linewidth': 2.0,
-    },
-    'EST[R]': {
-        'marker': 'd',
-        'linestyle': ':',
         'color': 'tab:gray',
         'linewidth': 2.0,
     },
@@ -199,7 +193,9 @@ if whichone == 2:
         'ACT[$\mathcal{S}$]',
         'HM[$\mathcal{R},\mathcal{M}$]',
         'HM[$\mathcal{S},\mathcal{M}$]'],
-        bbox_to_anchor=(0.55,0.5))
+        bbox_to_anchor=(0.55,0.5),
+        labelcolor='linecolor',
+        )
 if whichone == 3:
     ax.legend(['ACT[$\mathcal{R}$]',
         'ACT[$\mathcal{S}$]',
@@ -207,7 +203,18 @@ if whichone == 3:
         'HM[$\mathcal{S},-\gamma/2$]',
         'HM[$\mathcal{S},g_\mathsf{SGA}$]',
         ],
-        bbox_to_anchor=(0.50,0.57))
+        bbox_to_anchor=(0.50,0.57),
+        labelcolor='linecolor',
+        )
+if whichone == 4:
+    ax.legend(['ACT[$\mathcal{R}$]',
+        'ACT[$\mathcal{S}$]',
+        'HM[$\mathcal{S},g_\mathsf{SGA}$]',
+        'HM[$\mathcal{S},g_\mathsf{SGA}$]&ICS'],
+        loc='lower right',
+        bbox_to_anchor=(0.99, 0.12),
+        labelcolor='linecolor',
+        )
 
 ax = plt.subplot(1,2,2)
 for (name, (r1, cost, ers)) in data.items():
@@ -247,7 +254,9 @@ if whichone == 2:
         'ACT[$\mathcal{S}$]',
         'HM[$\mathcal{R},\mathcal{M}$]',
         'HM[$\mathcal{S},\mathcal{M}$]'],
-        bbox_to_anchor=(0.55,0.5))
+        bbox_to_anchor=(0.55,0.5),
+        labelcolor='linecolor',
+        )
[…]

### 2021-10-27 sotaplot.py
svg

@@ -14,18 +14,20 @@ data_cub = {
         (30.6, 27.5), (9.0, 33.0), (31.3, 33.9) ),
     'HM[S,SGA]': (
         (38.0, 36.5), (9.0, 33.0), (32.4, 35.9) ),
+    'HM[S,SGA]ICS': (
+        (37.2, 37.2), (9.0, 33.0), (33.5, 33.5) ),
 }
 data_cars = {
     'ACT[R]': (
         (46.8, 43.4), (9.0, 33.0), (39.8, 38.6) ),
     'HM[S,SGA]': (
-        (63.2, 63.2), (9.0, 9.0), (42.4, 42.4)),
+        (63.2, 62.3), (9.0, 9.0), (42.4, 44.9)),
 }
 data_sop = {
     'ACT[R]': (
         (45.1, 47.5), (9.0, 33.0), (50.3, 50.8) ),
     'HM[S,SGA]': (
-        (49.0,), (9.0,), (61.7,)),
+        (49.0, 49.0), (9.0, 33.0), (61.7, 61.7) ),
 }
 
 styledict = {
@@ -33,49 +35,43 @@ styledict = {
         'marker': '.',
         'linestyle': ':',
         'color': 'tab:cyan',
-        'linewidth': 3.0,
+        'linewidth': 2.0,
     },
     'ACT[S]': {
         'marker': '.',
         'linestyle': ':',
         'color': 'tab:orange',
-        'linewidth': 3.0,
+        'linewidth': 2.0,
     },
     'HM[R,M]': {
         'marker': 'v',
         'linestyle': '-.',
         'color': 'tab:blue',
-        'linewidth': 3.0,
+        'linewidth': 2.0,
     },
     'HM[S,M]': {
         'marker': '^',
         'linestyle': '-.',
         'color': 'tab:red',
-        'linewidth': 3.0,
+        'linewidth': 2.0,
     },
     'HM[S,SGA]': {
         'marker': 'h',
         'linestyle': '-',
-        'color': 'tab:purple',
-        'linewidth': 3.0,
+        'color': 'darkviolet',
+        'linewidth': 2.0,
     },
     'HM[S,-r/2]': {
         'marker': '+',
         'linestyle': '-.',
         'color': 'tab:gray',
-        'linewidth': 3.0,
-    },
-    'EST[R]': {
-        'marker': 'd',
[…]

### 2021-10-28 robdml.tex
svg
sga->lga

--- 2021-10-27 robdml.tex
@@
 		Comparison in Robustness, Training Cost, and Recall@1 Performance
-		between Our Method (\ie, ``HM'') and the State-of-The-Art Method (\ie, ``ACT'').
+		between Our Method (\ie, ``HM[$\mathcal{S},g_\mathsf{LGA}$]\&ICS'')
+		and the State-of-The-Art Method (\ie, ``ACT[$\mathcal{R}$]'' and
+		``ACT[$\mathcal{S}$]'').
 		%
-		Best viewed in color.
 	}
@@
 
+\begin{figure}[t]
+	\includegraphics[width=\columnwidth]{figics.pdf}
+	\caption{ICS eff}
+\end{figure}
+
 \input{tab-gaeff.tex}

### 2021-10-28 introplot.py

@@ -43,8 +43,8 @@ HM_SM = {
         (35.7, 34.8, 29.6, 22.1, 11.6),
         ),
 }
-HM_SSGA = {
-    'HM[S,SGA]': ( # [freeze]
+HM_SLGA = {
+    'HM[S,LGA]': ( # [freeze]
         (47.5, 42.7, 38.0, 37.0, 36.5),
         (3.0, 5.0, 9.0, 17.0, 33.0),
         (11.7, 20.8, 32.4, 34.5, 35.9),
@@ -57,8 +57,8 @@ HM_SHM = {
         (12.4, 24.7, 33.8, 36.8, 37.0),
         ),
 }
-HM_SSGAICS = {
-    'HM[S,SGA]ICS': ( # [freeze]
+HM_SLGAICS = {
+    'HM[S,LGA]ICS': ( # [freeze]
         (45.2, 41.8, 37.2, 35.5),
         (3.0, 5.0, 9.0, 17.0),
         (15.2, 24.6, 33.5, 36.0),
@@ -78,7 +78,7 @@ elif whichone == 1:
     data = {
         **ACT_R,
         **ACT_S,
-        **HM_SSGAICS,
+        **HM_SLGAICS,
     }
 elif whichone == 2:
     # effectiveness of HM
@@ -95,15 +95,15 @@ elif whichone == 3:
         **ACT_S,
         **HM_SM,
         **HM_SHM,
-        **HM_SSGA,
+        **HM_SLGA,
     }
 elif whichone == 4:
     # effectivenss of ICS
     data = {
         **ACT_R,
         **ACT_S,
-        **HM_SSGA,
-        **HM_SSGAICS,
+        **HM_SLGA,
+        **HM_SLGAICS,
     }
 else:
     raise ValueError
@@ -133,7 +133,7 @@ styledict = {
         'color': 'tab:red',
         'linewidth': 2.0,
     },
-    'HM[S,SGA]': {
+    'HM[S,LGA]': {
         'marker': 'h',
         'linestyle': '-',
         'color': 'darkviolet',
@@ -145,7 +145,7 @@ styledict = {
         'color': 'tab:gray',
         'linewidth': 2.0,
     },
-    'HM[S,SGA]ICS': {
+    'HM[S,LGA]ICS': {
         'marker': 'o',
         'linestyle': '-.',
         'color': 'crimson',
[…]

### 2021-10-28 sotaplot.py

@@ -12,21 +12,21 @@ plt.rcParams['mathtext.fallback'] = 'cm'
 data_cub = {
     'ACT[R]': (
         (30.6, 27.5), (9.0, 33.0), (31.3, 33.9) ),
-    'HM[S,SGA]': (
+    'HM[S,LGA]': (
         (38.0, 36.5), (9.0, 33.0), (32.4, 35.9) ),
-    'HM[S,SGA]ICS': (
+    'HM[S,LGA]ICS': (
         (37.2, 37.2), (9.0, 33.0), (33.5, 33.5) ),
 }
 data_cars = {
     'ACT[R]': (
         (46.8, 43.4), (9.0, 33.0), (39.8, 38.6) ),
-    'HM[S,SGA]': (
+    'HM[S,LGA]': (
         (63.2, 62.3), (9.0, 9.0), (42.4, 44.9)),
 }
 data_sop = {
     'ACT[R]': (
         (45.1, 47.5), (9.0, 33.0), (50.3, 50.8) ),
-    'HM[S,SGA]': (
+    'HM[S,LGA]': (
         (49.0, 49.0), (9.0, 33.0), (61.7, 61.7) ),
 }
 
@@ -55,7 +55,7 @@ styledict = {
         'color': 'tab:red',
         'linewidth': 2.0,
     },
-    'HM[S,SGA]': {
+    'HM[S,LGA]': {
         'marker': 'h',
         'linestyle': '-',
         'color': 'darkviolet',
@@ -67,7 +67,7 @@ styledict = {
         'color': 'tab:gray',
         'linewidth': 2.0,
     },
-    'HM[S,SGA]ICS': {
+    'HM[S,LGA]ICS': {
         'marker': 'o',
         'linestyle': '-.',
         'color': 'crimson',
@@ -87,7 +87,7 @@ plt.xlabel('Training Cost')
 plt.ylabel('Robustness (ERS)')
 plt.xscale('log', base=2)
 ax.legend(['ACT[$\mathcal{R}$]',
-        'HM[$\mathcal{S},g_\mathsf{SGA}$]'],
+        'HM[$\mathcal{S},g_\mathsf{LGA}$]'],
         labelcolor='linecolor',
         )
 plt.title('CUB Dataset')
@@ -102,7 +102,7 @@ plt.xlabel('Recall@1')
 plt.ylabel('Robustness (ERS)')
 plt.gca().invert_xaxis()
[…]

### 2021-10-28 robdml.tex
tex
svg

@@
 Or at least the $\text{Var}[H_\mathsf{D}]$ of such sampling strategy has to be
-large enough in order to create valid adversarial examples.
+large enough in order to create a notable number of valid adversarial examples.
 %
@@
 %
-For convenience of further discussion, we denote the hardness of a Random
-triplet, Semihard triplet, and Softhard triplet as $\mathcal{R}$,
+For convenience of further discussion, we denote the hardness of a Random,
+Semihard, and Softhard triplets as $\mathcal{R}$,
 $\mathcal{M}$, $\mathcal{S}$, respectively.
@@
 %
-We follow the same experiment setup as the state-of-the-art work~\cite{robrank}
+We follow the same experiment setup as the state-of-the-art work~\cite{robrank,revisiting}
 for ease of comparison.

### 2021-10-28 introplot.py

@@ -59,9 +59,9 @@ HM_SHM = {
 }
 HM_SLGAICS = {
     'HM[S,LGA]ICS': ( # [freeze]
-        (45.2, 41.8, 37.2, 35.5),
-        (3.0, 5.0, 9.0, 17.0),
-        (15.2, 24.6, 33.5, 36.0),
+        (45.2, 41.8, 37.2, 35.5, 34.9),
+        (3.0, 5.0, 9.0, 17.0, 33.0),
+        (15.2, 24.6, 33.5, 36.0, 36.0),
         ),
 }
 
@@ -136,7 +136,7 @@ styledict = {
     'HM[S,LGA]': {
         'marker': 'h',
         'linestyle': '-',
-        'color': 'darkviolet',
+        'color': 'tab:pink',
         'linewidth': 2.0,
     },
     'HM[S,-r/2]': {

### 2021-10-28 sotaplot.py

@@ -15,13 +15,15 @@ data_cub = {
     'HM[S,LGA]': (
         (38.0, 36.5), (9.0, 33.0), (32.4, 35.9) ),
     'HM[S,LGA]ICS': (
-        (37.2, 37.2), (9.0, 33.0), (33.5, 33.5) ),
+        (37.2, 34.9), (9.0, 33.0), (33.5, 36.0) ),
 }
 data_cars = {
     'ACT[R]': (
         (46.8, 43.4), (9.0, 33.0), (39.8, 38.6) ),
     'HM[S,LGA]': (
-        (63.2, 62.3), (9.0, 9.0), (42.4, 44.9)),
+        (63.2, 62.3), (9.0, 33.0), (42.4, 44.9) ),
+    'HM[S,LGA]ICS': (
+        (60.2, 60.2), (9.0, 33.0), (46.0, 46.0) ),
 }
 data_sop = {
     'ACT[R]': (
@@ -58,7 +60,7 @@ styledict = {
     'HM[S,LGA]': {
         'marker': 'h',
         'linestyle': '-',
-        'color': 'darkviolet',
+        'color': 'tab:pink',
         'linewidth': 2.0,
     },
     'HM[S,-r/2]': {

### 2021-10-29 robdml.tex
remove sotaplot
tex

@@
 
-To validate the effectivenss of HM, we start from using the hardness of another
-benign triplet sampled with a different triplet sampler as $H_\mathsf{D}$, as
-the existing triplet samplers are known not to result in model collapse in
-regular training.
+As discussed in \cref{sec:31}, we start from the $H_\mathsf{D}$ calculated from
+a harder benign triplet sampled in a different strategy, such as Random,
+Semihard~\cite{facenet}, Softhard~\cite{revisiting},
+Distance-weighted~\cite{distance} (\emph{abbr}., Distance), or the within-batch
+Hardest negative sampling strategy, because we know these strategies do not
+result in model collapse in regular training.
 
@@
 
-Due to the flexibility of HM, any of the existing (and future) triplet samplers
-can be used for calculating $H_\mathsf{S}$ and $H_\mathsf{D}$.
+HM is flexible so that any existing or future triplet sampling strategy
+can be used for the source triplet or calculating $H_\mathsf{D}$.
 %
-But not all possible combinations are expected to be effective or efficient in
-terms of adversarial training, as the \emph{source} hardness of a notable
-portion of the given triplets should be increased.
+But not all potential combinations are expected to be effective for HM, as it
+will not create an adversarial triplet when $H_\mathcal{S}\geqslant
+H_\mathcal{D}$.
 %
-Thus, we first sort the existing samplers, namely Random,
-Semihard~\cite{facenet}, Softhard~\cite{revisiting},
-Distance-weighted~\cite{distance} (\emph{abbr}., Distance), and the
-within-batch Hardest negative sampler, based on the approximated mean hardness
-of their outputs, as shown in~\cref{tab:hsort}.
+Thus, we sort the strategies based on the mean hardness of their
+outputs in~\cref{tab:hsort}.
 %
 Then we adversarially train models on CUB dataset with all combinations
-respectively, and summarize the R@1 and ERS in \cref{tab:desth}.
-
-% 2. table: left and right
-
-As shown in the last three columns of \cref{tab:desth}, almost all combinations
-lead to model collapse as long as $H_\mathsf{D}$ is calculated from a Softhard,
-Distance, or Hardest triplet.
-%
-Due to the small $E[H_\mathsf{D}-H_\mathsf{S}]$ in the combination of Distance
-and Hardest triplets, the adversarial examples will be weak and the model does
-collapse, but the robustness gain is negligible.
-%
-Although $E[H]$ of Softhard is less than that of Distance or Hardest,
-some hard adversarial examples are still created due to its large
-$\text{Var}[H]$, which still result in a slow collapse.
-\todo{merge this para into upper triangular and lower triangular}
+respectively, and summarize their R@1 and ERS in \cref{tab:desth}.
 
@@
 For cases in the upper triangular of \cref{tab:desth} where $E[H_\mathsf{S}]
-\leqslant E[H_\mathsf{D}]$, most given triplets will be turned adversarial with
-an increased hardness.
+\leqslant E[H_\mathsf{D}]$, most of the given triplets will be turned
+adversarial.
 %
-Although most of such cases end up with model collapse, the preliminary result
-suggests that $\text{HM}[\mathcal{R},\mathcal{M}]$ is still effective in
-improving the robustness without model collapse, at an penalty on the R@1.
-
-\todo{R}
+Although almost all of them end up with model collapse, the
+$\text{HM}[\mathcal{R},\mathcal{M}]$ is still effective in improving the
+robustness, with an expected performance drop in R@1.
+%
+The combination of Distance and Hardest triplets does not trigger model
+collapse due to the small $E[H_\mathsf{D}-H_\mathsf{S}]$, which leads to weak
+adversarial examples and a negligible robustness gain.
 
 For cases in lower triangular of \cref{tab:desth}, where $E[H_\mathsf{S}]
-\geqslant E[H_\mathsf{D}]$, a large portion of given triplets will be
-unchanged according to \cref{eq:hm}, and hence lead to weak robustness.
+\geqslant E[H_\mathsf{D}]$, a large portion of given triplets will be unchanged
+according to \cref{eq:hm}, and hence lead to weak robustness.
 %
@@
 %
+Although $E[H]$ of Softhard is less than that of Distance or Hardest, some hard
+adversarial examples are still created
 %
+\footnote{Differently, Softhard also samples a
+hard positive instead of a random positive besides a hard negative.
 %
-In other words, HM in this case can be interpreted as mixing some unperturbed
-softhard triplets and some semihard adversarial triplets.
+As a result, the hardness of a small number of Softhard triplets will be 
+greater than that of a given Hardest triplet.}
+%
+due to its large $\text{Var}[H]$, which
+still result in a slow collapse.
+
+In summary, HM creates mini-batches mixing some unperturbed source triplets and
+some adversarial triplets.
+%
+The $\text{HM}[\mathcal{R}, \mathcal{M}]$ and $\text{HM}[\mathcal{S},
+\mathcal{M}]$ achieve such balanced mixtures.
+%
+Empirically, the hardness range of Semihard strategy is appropriate for
+$H_\mathcal{D}$.
+
+\todo{R}
 
@@
 
+\begin{comment}
 \begin{figure}[t]
@@
 \end{figure}
+\end{comment}
 

### 2021-10-29 robdml.tex
tex

@@
 
+% 4. summary
+
 In summary, HM creates mini-batches mixing some unperturbed source triplets and
@@
 %
-Empirically, the hardness range of Semihard strategy is appropriate for
-$H_\mathcal{D}$.
-
-\todo{R}
-
-% 4. summary
-
-In summary, according to \cref{tab:desth}, HM from random to semihard, or from
-softhard to semihard are two choices that can effectively lead to robust
-DML model.
+Subsequent experiments will be based on the two effective combinations.
 %
-The subsequent experiments will be based on the two choices.
+Empirically, the hardness range of Semihard strategy,
+\ie, $[-\gamma,0]$ is appropriate for $H_\mathcal{D}$.
 

### 2021-10-29 tab-desth.tex
tex

@@
 
-Random & \cellcolor{black!10}53.9 & \cellcolor{black!10}3.8 & 27.0 & 35.1 & \multicolumn{2}{c|}{Collapse} & \multicolumn{2}{c|}{Collapse} & \multicolumn{2}{c}{Collapse}\tabularnewline
+Random & \cellcolor{black!7}53.9 & \cellcolor{black!7}3.8 & 27.0 & 35.1 & \multicolumn{2}{c|}{Collapse} & \multicolumn{2}{c|}{Collapse} & \multicolumn{2}{c}{Collapse}\tabularnewline
 \hline
-Semihard & 43.9 & 5.4 & \cellcolor{black!10}44.0 & \cellcolor{black!10}5.0 & \multicolumn{2}{c|}{Collapse} & \multicolumn{2}{c|}{Collapse} & \multicolumn{2}{c}{Collapse}\tabularnewline
+Semihard & 43.9 & 5.4 & \cellcolor{black!7}44.0 & \cellcolor{black!7}5.0 & \multicolumn{2}{c|}{Collapse} & \multicolumn{2}{c|}{Collapse} & \multicolumn{2}{c}{Collapse}\tabularnewline
 \hline
-Softhard & 48.3 & 13.7 & 38.4 & 29.6 & \cellcolor{black!10}55.7 & \cellcolor{black!10}6.2 & \multicolumn{2}{c|}{Collapse} & \multicolumn{2}{c}{Collapse}\tabularnewline
+Softhard & 48.3 & 13.7 & 38.4 & 29.6 & \cellcolor{black!7}55.7 & \cellcolor{black!7}6.2 & \multicolumn{2}{c|}{Collapse} & \multicolumn{2}{c}{Collapse}\tabularnewline
 \hline
-Distance & 52.7 & 4.8 & 50.7 & 4.8 & \multicolumn{2}{c|}{Collapse} & \cellcolor{black!10}51.4 & \cellcolor{black!10}4.9 & 54.7 & 5.4\tabularnewline
+Distance & 52.7 & 4.8 & 50.7 & 4.8 & \multicolumn{2}{c|}{Collapse} & \cellcolor{black!7}51.4 & \cellcolor{black!7}4.9 & 54.7 & 5.4\tabularnewline
 \hline
-Hardest & 51.0 & 4.7 & 52.2 & 4.8 & \multicolumn{2}{c|}{Collapse} & 52.6 & 5.1 & \cellcolor{black!10}48.9 & \cellcolor{black!10}5.0\tabularnewline
+Hardest & 51.0 & 4.7 & 52.2 & 4.8 & \multicolumn{2}{c|}{Collapse} & 52.6 & 5.1 & \cellcolor{black!7}48.9 & \cellcolor{black!7}5.0\tabularnewline
 
@@
 }
-
+%
+	\vspace{-0.5em}
+%
 \caption{Combinations of Source \& Destination Hardness.
 	%
-	Experiments are conducted on CUB Dataset with RN18 model.
+	Evaluated on CUB Dataset with RN18 model.
 	%
@@
 	%
-	Original data is used when the source and destination hardness are the
-	same, as shown on the diagonal line of the table.
+	Models on the diagonal are regularly (instead of adversarially) trained.
 	%

### 2021-10-29 tab-hmeff.tex
tex

@@
 \hline
-\multirow{5}{*}{CUB} & ACT{[}$\mathcal{R}${]} & 2 & 46.5 & 58.4 & 29.1 & 55.6 & 0.6 & 98.9 & 0.4 & 98.1 & 0.837 & 1.666 & 0.2 & 0.2 & 19.6 & 0.0 & 5.8\tabularnewline
- & ACT{[}$\mathcal{R}${]} & 4 & 38.4 & 49.8 & 22.8 & 49.7 & 4.6 & 81.9 & 2.8 & 80.5 & 0.695 & 1.366 & 2.9 & 2.3 & 18.8 & 0.1 & 13.9\tabularnewline
- & ACT{[}$\mathcal{R}${]} & 8 & 30.6 & 40.1 & 16.5 & 45.6 & 13.7 & 46.8 & 12.6 & 39.3 & 0.547 & 0.902 & 13.6 & 9.8 & 21.9 & 1.3 & 31.3\tabularnewline
- & ACT{[}$\mathcal{R}${]} & 16 & 28.6 & 38.7 & 15.1 & 43.7 & 15.8 & 37.9 & 16.0 & 31.5 & 0.496 & 0.834 & 11.3 & 9.8 & 21.2 & 2.1 & 34.7\tabularnewline
- & ACT{[}$\mathcal{R}${]} & 32 & 27.5 & 38.2 & 12.2 & 43.0 & 15.5 & 37.7 & 15.1 & 32.2 & 0.472 & 0.821 & 11.1 & 9.4 & 14.9 & 1.0 & 33.9\tabularnewline
+\multirow{5}{*}{CUB} & ACT{[}$\mathcal{R}${]}\cite{robrank} & 2 & 46.5 & 58.4 & 29.1 & 55.6 & 0.6 & 98.9 & 0.4 & 98.1 & 0.837 & 1.666 & 0.2 & 0.2 & 19.6 & 0.0 & 5.8\tabularnewline
+ & ACT{[}$\mathcal{R}${]}\cite{robrank} & 4 & 38.4 & 49.8 & 22.8 & 49.7 & 4.6 & 81.9 & 2.8 & 80.5 & 0.695 & 1.366 & 2.9 & 2.3 & 18.8 & 0.1 & 13.9\tabularnewline
+ & ACT{[}$\mathcal{R}${]}\cite{robrank} & 8 & 30.6 & 40.1 & 16.5 & 45.6 & 13.7 & 46.8 & 12.6 & 39.3 & 0.547 & 0.902 & 13.6 & 9.8 & 21.9 & 1.3 & 31.3\tabularnewline
+ & ACT{[}$\mathcal{R}${]}\cite{robrank} & 16 & 28.6 & 38.7 & 15.1 & 43.7 & 15.8 & 37.9 & 16.0 & 31.5 & 0.496 & 0.834 & 11.3 & 9.8 & 21.2 & 2.1 & 34.7\tabularnewline
+ & ACT{[}$\mathcal{R}${]}\cite{robrank} & 32 & 27.5 & 38.2 & 12.2 & 43.0 & 15.5 & 37.7 & 15.1 & 32.2 & 0.472 & 0.821 & 11.1 & 9.4 & 14.9 & 1.0 & 33.9\tabularnewline
 \hline
-\multirow{5}{*}{CUB} & ACT{[}$\mathcal{S}${]} & 2 & 53.0 & 65.1 & 34.7 & 59.9 & 0.0 & 100.0 & 0.0 & 99.8 & 0.877 & 1.637 & 0.0 & 0.0 & 20.4 & 0.0 & 5.1\tabularnewline
- & ACT{[}$\mathcal{S}${]} & 4 & 49.3 & 61.0 & 31.5 & 56.6 & 0.6 & 97.6 & 0.2 & 98.1 & 0.799 & 1.485 & 0.3 & 0.2 & 18.9 & 0.0 & 7.1\tabularnewline
- & ACT{[}$\mathcal{S}${]} & 8 & 42.8 & 54.7 & 26.6 & 53.3 & 4.8 & 72.8 & 2.7 & 73.3 & 0.619 & 1.148 & 8.3 & 4.9 & 23.5 & 0.3 & 18.7\tabularnewline
- & ACT{[}$\mathcal{S}${]} & 16 & 40.5 & 51.6 & 24.8 & 51.7 & 6.7 & 62.1 & 4.9 & 60.6 & 0.566 & 1.014 & 12.4 & 8.6 & 22.5 & 0.9 & 23.7\tabularnewline
- & ACT{[}$\mathcal{S}${]} & 32 & 39.4 & 50.2 & 18.6 & 51.3 & 6.8 & 61.5 & 5.2 & 60.4 & 0.506 & 1.032 & 12.8 & 11.3 & 17.7 & 0.3 & 24.2\tabularnewline
+\multirow{5}{*}{CUB} & ACT{[}$\mathcal{S}${]}\cite{robrank} & 2 & 53.0 & 65.1 & 34.7 & 59.9 & 0.0 & 100.0 & 0.0 & 99.8 & 0.877 & 1.637 & 0.0 & 0.0 & 20.4 & 0.0 & 5.1\tabularnewline
+ & ACT{[}$\mathcal{S}${]}\cite{robrank} & 4 & 49.3 & 61.0 & 31.5 & 56.6 & 0.6 & 97.6 & 0.2 & 98.1 & 0.799 & 1.485 & 0.3 & 0.2 & 18.9 & 0.0 & 7.1\tabularnewline
+ & ACT{[}$\mathcal{S}${]}\cite{robrank} & 8 & 42.8 & 54.7 & 26.6 & 53.3 & 4.8 & 72.8 & 2.7 & 73.3 & 0.619 & 1.148 & 8.3 & 4.9 & 23.5 & 0.3 & 18.7\tabularnewline
+ & ACT{[}$\mathcal{S}${]}\cite{robrank} & 16 & 40.5 & 51.6 & 24.8 & 51.7 & 6.7 & 62.1 & 4.9 & 60.6 & 0.566 & 1.014 & 12.4 & 8.6 & 22.5 & 0.9 & 23.7\tabularnewline
+ & ACT{[}$\mathcal{S}${]}\cite{robrank} & 32 & 39.4 & 50.2 & 18.6 & 51.3 & 6.8 & 61.5 & 5.2 & 60.4 & 0.506 & 1.032 & 12.8 & 11.3 & 17.7 & 0.3 & 24.2\tabularnewline
 \hline

### 2021-10-29 tab-hmeff.tex
tex

@@
 
+} \vspace{-0.5em}
+	%
+\caption{Effectiveness of Hardness Manipulation for Adversarial Training.
+%
+The ``$\uparrow$'' mark means ``the higher the better'', while ``$\downarrow$''
+	means the opposite.
+%
+ACT[$\mathcal{R}$] and ACT[$\mathcal{S}$] mean the training triplet is sampled
+	using Random and Softhard strategy, respectively.
+%
 	}
-
-\caption{Effectiveness of Hardness Manipulation for Adversarial Training.}
+	%
 \label{tab:hmeff}
+%
 \end{table*}

### 2021-10-29 robdml.tex
tex

@@
 %
-And the perturbation $\vr$ is updated as $\vr \leftarrow \vr + \alpha \Delta \vr$
-by PGD, where $\alpha$ is a step size parameter.
+And the perturbation $\vr$ is updated as $\vr \leftarrow \vr + \alpha \Delta
+\vr$ by PGD for $\eta$ steps with a step size $\alpha$.
 %
-Thus, the optimization of HM objective can be interpreted as directly
-maximizing $\tilde{H}_\mathsf{S}$, but stops very early once it reaches
-$H_\mathsf{D}$.
+Thus, the optimization of HM objective can be interpreted as direct
+maximization of $\tilde{H}_\mathsf{S}$, which discontinues very early once it
+reaches $H_\mathsf{D}$.
 %
@@
 
+For adversarial training of a DML model, being selective to both benign and
+adversarial training samples is crucial for preventing model collapse, and
+achieving good performance on both kinds of samples.
+%
+Hardness Manipulation is a flexible tool for us to specify such ``selection'',
+and Graduate Adversary is a selection rule for adversarial examples.
+%
+Intra-Class Structure loss helps the model exploit more information from the
+adversarial examples.
+
 \section{Conclusion}

### 2021-10-30 appendix.tex
tex
sga->lga

@@
 
-\section{More Details Explained}
+\section{More Technical Details}
 
@@
 
-\begin{enumerate}[noitemsep, label={Q.{\arabic*}}]
+%\begin{enumerate}[noitemsep, label={Q{\arabic*}.}]
+\begin{enumerate}[noitemsep]
 		%
@@
 
+	\item Loss normalization with $u$?
+
+	\item Hardware and software platform?
+
+	\item Details of EST?
+
+	\item Details of ACT?
 %
@@
 
+	\item Complete Table for Sec~4.1 Hardness Selection?
+
 \end{enumerate}
@@
 
-\section{Complete Table for Sec~4.1 Hardness Selection}
+\section{Miscellaneous}
+
+\textbf{Societal Impact}.
+%
+As encouraged by the author guidelines, we briefly discuss the potential
+societal impact of our work.
+%
+Adversarial attacks may raise security considerations on deep learning
+applications, and hence may have negative impact.
+%
+In contrast, in this manuscript, we focus on defending against the attacks and
+enhancing a model's adversarial robustness, and hence is expected to have a
+positive impact.
+%
+Besides, although adversarial training is not environment-friendly due to its
+high training cost in GPU time, our study has significantly improved the
+adversarial training efficiency compared to the previous works.
+
+\textbf{Limitations}.
+%
+\begin{quote}
+
+Considering the limitations of an approach is an important part of good
+academic scholarship. While many high-quality CVPR papers thoroughly consider
+and discuss limitations, CVPR 2022 aims to emphasize the importance of an
+honest treatment of limitations. Authors are thus explicitly encouraged to
+discuss limitations, ideally by creating a separate "Limitations" (sub-)section
+in their papers.
+
+Such discussion shall point out any strong assumptions and how robust the
+results are to violations of these assumptions (e.g., independence assumptions,
+noiseless settings, model well-specification, asymptotic approximations only
+held locally). Authors need to reflect on how these assumptions might be
+violated in practice and what the implications would be.
+
+The discussion shall also reflect on the scope of their claims, e.g., if the
+authors only tested their approach on a few datasets or did a few runs. In
+general, empirical results often depend on implicit assumptions, which should
+be articulated. The discussion shall reflect on the factors that influence the
+performance of the approach. For example, a recognition algorithm may perform
+poorly when image resolution is low or images are taken in low lighting.
+
+We understand that authors might fear that complete honesty about limitations
+might be used by reviewers as grounds for rejection. It is worth keeping in
+mind that a worse outcome might be if reviewers discover limitations that are
+not acknowledged in the paper. In general, we advise authors to use their best
+judgement and recognize that individual actions in favor of transparency play
+an important role in developing norms that preserve the integrity of the
+community. Reviewers will be specifically instructed to not penalize honesty
+concerning limitations
+
+\end{quote}
 
@@
 
-	\item [M] manuscript notes on SGA.
+	\item [M] manuscript notes on LGA.
 
@@
 
-	\item [\xmark] can we learn a good destination distribution? | too
-		complicated? not necessary currently.
-
 	\item [\xmark] re-design Gradual Adversary for HM based on that for the amdsemi. |

### 2021-10-30 appendix.tex
tex

@@
 
-\textbf{Societal Impact}.
+\textbf{Societal Impact.}
 %
@@
 %
-Adversarial attacks may raise security considerations on deep learning
-applications, and hence may have negative impact.
+Adversarial attacks may raise \uline{security considerations} on deep learning
+applications, and even cause negative effect.
 %
@@
 enhancing a model's adversarial robustness, and hence is expected to have a
-positive impact.
+positive impact instead.
 %
-Besides, although adversarial training is not environment-friendly due to its
-high training cost in GPU time, our study has significantly improved the
+Besides, although adversarial training is not \uline{environment-friendly} due
+to its high training cost in GPU time, our study has significantly improved the
 adversarial training efficiency compared to the previous works.
 
-\textbf{Limitations}.
+\textbf{Limitations.}
 %

### 2021-10-30 robdml.tex
tex

@@
 
+\noindent\textbf{I. Effectivenss of Hardness Manipulation}.
+
+To figure out the efficacy of HM with $H_\mathcal{D}$ calculated from benign
+triplets, we adversarialy train models dataset using $\text{HM}[\mathcal{R},
+\mathcal{M}]$ and $\text{HM}[\mathcal{S}, \mathcal{M}]$ on the CUB dataset,
+with varying PGD steps, \ie, $\eta\in\{2,4,8,16,32\}$, respectively.
+%
+The results can be found in \cref{tab:hmeff}.
+%
+The performance of the state-of-the-art defense, \ie, ACT~\cite{robrank} is
+also provided as a baseline.
+%
+ACT[$\mathcal{R}$] and ACT[$\mathcal{S}$] mean the training
+triplet is sampled using Random and Softhard strategy, respectively.
+%
+
+Why G4 so promising?
+
+RM = random original (not representative for what the model should learn) plus semihard adv ex (strong advex)
+
+SM = softhard original (selective) plus semihard adv ex (strong adv)
+
+Ignore $H_D$
+
+1. source triplet affects p[erformance regardless of the attack method used for adversarial training.
+
+2. as long as a portion of semihard adversarial example is provided. fully explore the range of semihard.
+
+HM + different pgditer
+CUB, 2 4 8 16 32
+\cref{tab:hmeff}
+
+8; empirically selected as the base for further ablation study.
+
+Conditions for a good source and destination hardness:
+%
+(1) the destination hardness is semihard (or something between semihard
+and softhard, we leave new sampling strategy for future work).
+(2) the source hardness should have high variance and a relatively high mean
+value to ensure number of benign example and number of adversarial example ratio.
+
+\oo{Note, naive combination of benign training and adv train does not lead to better
+result, why?} mix 0.5
+
+\oo{experiment, 8 step by default}
+
+\noindent\textbf{II. Effectiveness of Gradual Adversary}.
+
 \begin{figure}[t]
@@
 \end{figure}
-
-\noindent\textbf{I. Effectivenss of Hardness Manipulation}.
-
-Why G4 so promising?
-
-RM = random original (not representative for what the model should learn) plus semihard adv ex (strong advex)
-
-SM = softhard original (selective) plus semihard adv ex (strong adv)
-
-Ignore $H_D$
-
-1. source triplet affects p[erformance regardless of the attack method used for adversarial training.
-
-2. as long as a portion of semihard adversarial example is provided. fully explore the range of semihard.
-
-HM + different pgditer
-CUB, 2 4 8 16 32
-\cref{tab:hmeff}
-
-8; empirically selected as the base for further ablation study.
-
-Conditions for a good source and destination hardness:
-%
-(1) the destination hardness is semihard (or something between semihard
-and softhard, we leave new sampling strategy for future work).
-(2) the source hardness should have high variance and a relatively high mean
-value to ensure number of benign example and number of adversarial example ratio.
-
-\oo{Note, naive combination of benign training and adv train does not lead to better
-result, why?} mix 0.5
-
-\oo{experiment, 8 step by default}
-
-\noindent\textbf{II. Effectiveness of Gradual Adversary}.
 

### 2021-10-30 robdml.tex
tex

@@
 %
-ACT[$\mathcal{R}$] and ACT[$\mathcal{S}$] mean the training
-triplet is sampled using Random and Softhard strategy, respectively.
-%
+ACT[$\mathcal{R}$] and ACT[$\mathcal{S}$] mean the training triplet is sampled
+using Random and Softhard strategy, respectively.
+%
+We also plot curves in \cref{fig:hmeff} based on the robustness, training
+cost~\footnote{Training cost is the number of forward-backward computation
+cycle in each adversarial training iteration, and is calculated as $\eta+1$.},
+as well as the R@1 performance on benign examples to reflect the
+characteristics of these methods.
 
@@
 	\caption{HM eff}
+	\label{fig:hmeff}
 \end{figure}

### 2021-10-30 robdml.tex
tex

@@
 %
-To attack the DML model, an imperceptible adversarial perturbation $\vr$ is
-added to the input image $\mX$, which is subject to $\|\vr\|_p \leq
-\varepsilon$ and $\mX+\vr\in \mathcal{X}$, so that its embedding vector
+To attack the DML model, an imperceptible adversarial perturbation $\vr \in
+\Gamma$ is added to the input image $\mX$, where $\Gamma = \{\vr | \mX+\vr\in
+\mathcal{X},  \|\vr\|_p \leq \varepsilon\}$, so that its embedding vector
 $\tilde{\vx}=\phi(\mX+\vr)$ will be moved off its original location to other
@@
 %
-And the perturbation $\vr$ is updated as $\vr \leftarrow \vr + \alpha \Delta
-\vr$ by PGD for $\eta$ steps with a step size $\alpha$.
+And the perturbation $\vr$ is updated as $\vr \leftarrow \text{Proj}_\Gamma\{\vr + \alpha \Delta
+\vr\}$ by PGD for $\eta$ steps with a step size $\alpha$.
 %

### 2021-10-31 robdml.tex
tex

@@
 
+% What we do
+
 To figure out the efficacy of HM with $H_\mathcal{D}$ calculated from benign
@@
 We also plot curves in \cref{fig:hmeff} based on the robustness, training
-cost~\footnote{Training cost is the number of forward-backward computation
-cycle in each adversarial training iteration, and is calculated as $\eta+1$.},
-as well as the R@1 performance on benign examples to reflect the
+cost\footnote{Training cost is the number of times for forward and backward
+propagation in each adversarial training iteration, which is calculated as
+$\eta+1$.}, as well as the R@1 performance on benign examples to reflect the
 characteristics of these methods.
+
+% first review the sota curve
+
+As shown, k
+
+% then review hm and compare
 
@@
 \begin{figure}[t]
+	%
 	\includegraphics[width=\columnwidth]{fighmeff.pdf}
-	\caption{HM eff}
+	%
+	\caption{Performance of $\text{HM}[\mathcal{R},\mathcal{M}]$
+	%
+	\& $\text{HM}[\mathcal{S},\mathcal{M}]$ in \cref{tab:hmeff}.
+%
+	}
+	%
 	\label{fig:hmeff}
+	%
 \end{figure}

### 2021-10-31 tab-desth.tex
tex

@@
 Random & \cellcolor{black!7}53.9 & \cellcolor{black!7}3.8 & 27.0 & 35.1 & \multicolumn{2}{c|}{Collapse} & \multicolumn{2}{c|}{Collapse} & \multicolumn{2}{c}{Collapse}\tabularnewline
-\hline
+%\hline
 Semihard & 43.9 & 5.4 & \cellcolor{black!7}44.0 & \cellcolor{black!7}5.0 & \multicolumn{2}{c|}{Collapse} & \multicolumn{2}{c|}{Collapse} & \multicolumn{2}{c}{Collapse}\tabularnewline
-\hline
+%\hline
 Softhard & 48.3 & 13.7 & 38.4 & 29.6 & \cellcolor{black!7}55.7 & \cellcolor{black!7}6.2 & \multicolumn{2}{c|}{Collapse} & \multicolumn{2}{c}{Collapse}\tabularnewline
-\hline
+%\hline
 Distance & 52.7 & 4.8 & 50.7 & 4.8 & \multicolumn{2}{c|}{Collapse} & \cellcolor{black!7}51.4 & \cellcolor{black!7}4.9 & 54.7 & 5.4\tabularnewline
-\hline
+%\hline
 Hardest & 51.0 & 4.7 & 52.2 & 4.8 & \multicolumn{2}{c|}{Collapse} & 52.6 & 5.1 & \cellcolor{black!7}48.9 & \cellcolor{black!7}5.0\tabularnewline

### 2021-10-31 robdml.tex
tex

@@
 
-As shown, k
+As shown, ACT[$\mathcal{R}$] can achieve a high ERS, but with a significant
+performance drop in R@1, while ACT[$\mathcal{S}$] can retain a relative high
+R@1, but is much less efficient in gaining robustness.
+%
+Notably, ACT relies on the attack that can successfully pull the adversarial
+positive and negative samples close to each other in order to learn robust
+features~\cite{robrank}.
+%
+As a result, ACT's ERS with a small $\eta$ is relatively low.
 

### 2021-10-31 robdml.tex
tex

--- 2021-10-31 robdml.tex
@@
 
-As shown, k
+As shown, ACT[$\mathcal{R}$] can achieve a high ERS, but with a significant
+performance drop in R@1, while ACT[$\mathcal{S}$] can retain a relative high
+R@1, but is much less efficient in gaining robustness under a fixed training
+cost.
+%
+Notably, ACT relies on the attack that can successfully pull the adversarial
+positive and negative samples close to each other in order to learn robust
+features~\cite{robrank}.
+%
+As a result, ACT's ERS with a small $\eta$ (indicating a weak attack effect) is
+relatively low.
+
+\begin{figure}[t]
+	%
+	\includegraphics[width=\columnwidth]{fighmeff.pdf}
+	%
+	\vspace{-1.5em}
+	%
+	\caption{Performance of $\text{HM}[\mathcal{R},\mathcal{M}]$
+	%
+	\& $\text{HM}[\mathcal{S},\mathcal{M}]$ in \cref{tab:hmeff}.
+%
+	}
+	%
+	\label{fig:hmeff}
+	%
+\end{figure}
 
@@
 
-Why G4 so promising?
-
-RM = random original (not representative for what the model should learn) plus semihard adv ex (strong advex)
-
-SM = softhard original (selective) plus semihard adv ex (strong adv)
-
-Ignore $H_D$
-
-1. source triplet affects p[erformance regardless of the attack method used for adversarial training.
-
-2. as long as a portion of semihard adversarial example is provided. fully explore the range of semihard.
-
-HM + different pgditer
-CUB, 2 4 8 16 32
-\cref{tab:hmeff}
-
-8; empirically selected as the base for further ablation study.
-
-Conditions for a good source and destination hardness:
-%
-(1) the destination hardness is semihard (or something between semihard
-and softhard, we leave new sampling strategy for future work).
-(2) the source hardness should have high variance and a relatively high mean
-value to ensure number of benign example and number of adversarial example ratio.
-
-\oo{Note, naive combination of benign training and adv train does not lead to better
-result, why?} mix 0.5
-
-\oo{experiment, 8 step by default}
+In contrast, HM[$\mathcal{R},\mathcal{M}$] achieves an even higher ERS under
+the same training cost, but with a larger penalty in R@1 compared to
+ACT[$\mathcal{R}$].
+%
+Compared to ACT[$\mathcal{S}$], HM[$\mathcal{S},\mathcal{M}$] is able to retain
+a relatively high R@1, but in a much higher efficiency.
+%
+According to \cref{fig:hmeff}, HM[$\mathcal{R},\mathcal{M}$] achieves the
+highest ERS and efficiency but with the most significant drop in R@1, which is
+not acceptable in applications.
+%
+Apart from that, HM[$\mathcal{S},\mathcal{M}$] achieves a promising result
+in every aspect.
+%
+Its efficiency in gaining robustness is basically on par with
+ACT[$\mathcal{R}$], but can achieve a significantly higher R@1.
+%
+It achieves a balance between ERS and R@1 on par with ACT[$\mathcal{S}$], but
+in a significantly higher efficiency.
+
+% the reasons
+
+Overall, as discussed in \cref{sec:31}, HM uses the same projected gradient as
+to directly maximize the hardness, which endows this method a high efficiency
+in creating strong adversarial examples at a fixed training cost.
+%
+Besides, unlike ACT, HM does not rely on the attack to successfully move the
+embeddings to some specific locations, and hence does not suffer from low
+efficiency when $\eta$ is small.
+%
+HM[$\mathcal{R},\mathcal{M}$] creates training batches with some Random benign
+examples and a large portion of Semihard adversarial examples, and hence
+achieve a high ERS and a relatively low R@1 because the Random triplet sampling
+strategy is not selective for data on which the model cannot generalize well.
+%
+HM[$\mathcal{S},\mathcal{M}$] creates training batches with some Semihard
+adversarial examples and a large portion of Softhard benign examples, and hence
+achieve a relatively high ERS as well as a high R@1 since Softhard sampling
+strategy is selective for the training data.
+%
+Further experiments will be based on HM[$\mathcal{S},\mathcal{M}$].
 
 \noindent\textbf{II. Effectiveness of Gradual Adversary}.
-
-\begin{figure}[t]
-	%
-	\includegraphics[width=\columnwidth]{fighmeff.pdf}
-	%
-	\caption{Performance of $\text{HM}[\mathcal{R},\mathcal{M}]$
-	%
-	\& $\text{HM}[\mathcal{S},\mathcal{M}]$ in \cref{tab:hmeff}.
-%
-	}
-	%
-	\label{fig:hmeff}
-	%
-\end{figure}
 

### 2021-10-31 robdml.tex
tex

@@
 
-\noindent\textbf{I. Effectivenss of Hardness Manipulation}.
-
 % What we do
 
-To figure out the efficacy of HM with $H_\mathcal{D}$ calculated from benign
-triplets, we adversarialy train models dataset using $\text{HM}[\mathcal{R},
+\noindent\textbf{I. Hardness Manipulation.}
+%
+To validate HM with $H_\mathcal{D}$ calculated from benign
+triplets, we adversarially train models using $\text{HM}[\mathcal{R},
 \mathcal{M}]$ and $\text{HM}[\mathcal{S}, \mathcal{M}]$ on the CUB dataset,
@@
 The performance of the state-of-the-art defense, \ie, ACT~\cite{robrank} is
-also provided as a baseline.
+provided as a baseline.
 %
@@
 propagation in each adversarial training iteration, which is calculated as
-$\eta+1$.}, as well as the R@1 performance on benign examples to reflect the
-characteristics of these methods.
+$\eta+1$.}, as well as the R@1 performance on benign examples.
 
@@
 
+\input{tab-gaeff.tex}
+\input{tab-ics.tex}
+
 % the reasons
@@
 
-\noindent\textbf{II. Effectiveness of Gradual Adversary}.
-
 \begin{figure}[t]
+	\vspace{-1em}
 	\includegraphics[width=\columnwidth]{figgaeff.pdf}
+	\vspace{-1.5em}
 	\caption{GA eff}
@@
 \begin{figure}[t]
+	\vspace{-1em}
 	\includegraphics[width=\columnwidth]{figics.pdf}
+	\vspace{-1.5em}
 	\caption{ICS eff}
@@
 
-\input{tab-gaeff.tex}
+\noindent\textbf{II. Gradual Adversary.}
 
@@
 
-\input{tab-ics.tex}
-
-Put together for easier comparison.
-
-\noindent\textbf{III. Effectivenss of Intra-Class Structure}.
+\noindent\textbf{III. Intra-Class Structure.}
+
+\cref{tab:ics}
 

### 2021-11-01 robdml.tex
tex

@@
 	\includegraphics[width=\columnwidth]{figgaeff.pdf}
-	\vspace{-1.5em}
-	\caption{GA eff}
+	\vspace{-1.9em}
+	\caption{Performance of ``HM[$\mathcal{S},g_\mathsf{LGA}$]'' in
+	\cref{tab:gaeff}.}
+	\label{fig:gaeff}
 \end{figure}
+
+\noindent\textbf{II. Gradual Adversary.}
+%
+As discussed in \cref{sec:32}, the HM[$\mathcal{S},\mathcal{M}$] may still suffer
+from the imbalance between learning the embeddings and gaining adversarial
+robustness.
+%
+Hence, we conduct further experiments %with an improved $H_\mathsf{D}$
+following the discussion, as shown in \cref{tab:gaeff} and \cref{fig:gaeff}.
+%
+Compared to HM[$\mathcal{S},\mathcal{M}$], slightly boosting the hardness in
+the late phase of training with $g_\mathsf{B}(\cdot)$ where $\xi{=}0.1$
+benefits the ERS, but results in a notably lower R@1;
+%
+A constant $H_\mathsf{D}$ at the upper bound of Semihard (\ie, $0$; too high
+for both early and late phase) renders model collapse;
+%
+$H_\mathsf{D}$ at the lower bound (\ie, $-\gamma$; too low for the late phase)
+leads to insignificant ERS improvement;
+%
+$H_\mathsf{D}{=}-\gamma/2$ provides a balance between the lower and upper
+bound, but still suffers from inflexibility.
+%
+In contrast, being not susceptible to the problems of other choices,
+HM[$\mathcal{S},g_\mathsf{LGA}$] achieves an ERS on par with
+HM[$\mathcal{S},\mathcal{M}$], but at the lowest R@1 penalty among all choices.
 
@@
 	\includegraphics[width=\columnwidth]{figics.pdf}
-	\vspace{-1.5em}
-	\caption{ICS eff}
+	\vspace{-1.9em}
+	\caption{Performance of ``HM[$\mathcal{S},g_\mathsf{LGA}$]\&ICS'' in \cref{tab:ics}.}
 \end{figure}
-
-\noindent\textbf{II. Gradual Adversary.}
-
-\cref{tab:gaeff}
 

### 2021-11-01 robdml.tex
tex

@@
 \noindent\textbf{III. Intra-Class Structure.}
+%
+Although independent to HM, ACT is incompatible with $L_\text{ICS}$ as it does
+not create an adversarial anchor.
+%
+Thus, we validate this loss term with HM.
+%
+As shown in \cref{tab:ics} and \cref{fig:ics}, $L_\text{ICS}$ consistently
+leads to a higher efficiency in gaining robustness, while retaining a
+good trade-off between ERS and R@1.
 

### 2021-11-01 robdml.tex
tex

@@
 
-\cref{tab:ics}
-
-\subsection{Comparison with State-of-the-art}
+\input{tab-sota.tex}
+
+\subsection{Comparison to State-of-The-Art Defense}
 \label{sec:43}
 
-\input{tab-sota.tex}
+After validating the effectiveness of our proposed method, we conduct
+experiments on three commonly used DML datasets to compare our proposed method
+with the state-of-the-art defense methods, as shown in \cref{tab:sota}.
 

### 2021-11-02 robdml.tex
tex

--- 2021-11-01 robdml.tex
@@
 
-\cref{tab:ics}
-
-\subsection{Comparison with State-of-the-art}
+\input{tab-sota.tex}
+
+\subsection{Comparison to State-of-The-Art Defense}
 \label{sec:43}
 
-\input{tab-sota.tex}
+After validating the effectiveness of our proposed method, we conduct
+experiments on CUB, CARS and SOP to compare our proposed method
+with the state-of-the-art defense methods, \ie, EST~\cite{advrank}
+and ACT~\cite{robrank}, as shown in \cref{tab:sota}.
+
+According to the results, EST[$\mathcal{R}$] achieves a relatively high
+R@1 when $\eta=8$,
 

### 2021-11-02 robdml.tex
tex

@@
 and ACT~\cite{robrank}, as shown in \cref{tab:sota}.
-
-According to the results, EST[$\mathcal{R}$] achieves a relatively high
-R@1 when $\eta=8$,
+%
+An ideal defense method should be able to achieve a high ERS, a high R@1,
+as well as a high efficiency (\ie, being able to gain higher robustness
+under a fixed training cost).
+
+According to the results, EST[$\mathcal{R}$] achieves a relatively high R@1
+when $\eta{=}8$, but suffers from a drastic drop in R@1 when $\eta$ is
+increased to $32$.
+%
+Nevertheless, EST[$\mathcal{R}$] only lead to a moderate robustness in all
+settings compared to other methods.
+%
+Experiments for EST[$\mathcal{S}$] is omitted as it is expected to result
+in even lower ERS based on the observations in previous subsections, and
+EST has been greatly outperformed by ACT~\cite{robrank}.
 

### 2021-11-02 robdml.tex
tex

@@
 
+\oo{regular and max can be expressed as two boundary cases of HM}
+
 % how hard? benign destination
@@
 Experiments for EST[$\mathcal{S}$] is omitted as it is expected to result
-in even lower ERS based on the observations in previous subsections, and
+in even much lower ERS based on the observations in previous subsections, and
 EST has been greatly outperformed by ACT~\cite{robrank}.

### 2021-11-02 robdml.tex
tex

@@
 %
-An ideal defense method should be able to achieve a high ERS, a high R@1,
-as well as a high efficiency (\ie, being able to gain higher robustness
-under a fixed training cost).
+An ideal defense method should be able to achieve a high ERS and a high R@1
+at a low training cost (\ie, $\eta+1$).
+%
+The ability of a method to achieve a high ERS under a fixed training cost
+indicates a high efficiency.
 
@@
 %
-Experiments for EST[$\mathcal{S}$] is omitted as it is expected to result
-in even much lower ERS based on the observations in previous subsections, and
-EST has been greatly outperformed by ACT~\cite{robrank}.
+Experiments for EST[$\mathcal{S}$] is omitted as it is expected to result in
+even much lower ERS based on the observations in previous subsections, and EST
+has been greatly outperformed by ACT~\cite{robrank}.
+%
+Although ACT[$\mathcal{R}$] achieves a relatively high ERS, its R@1 performance
+drop is distinct on every dataset.
+%
+According the previous subsections, ACT[$\mathcal{S}$] can lead to a high R@1,
+but along with a significantly lower ERS.
+%
+Thus, results for ACT[$\mathcal{S}$] are omitted from the table.
+
+It must be acknowledged that the high R@1 performance of our method largely
+stems from the source triplet sampling strategy, namely Softhard, instead of
+our contribution.
+%
+Our core contribution is
+
+minimizing a slightly different objective than the triplet loss.
 

### 2021-11-02 robdml.tex
tex

@@
 		%
-		Comparison in Robustness, Training Cost, and Recall@1 Performance
+		Comparison in Robustness, Training Cost, and Recall@1 
 		between Our Method (\ie, ``HM[$\mathcal{S},g_\mathsf{LGA}$]\&ICS'')
 		and the State-of-The-Art Method (\ie, ``ACT[$\mathcal{R}$]'' and
-		``ACT[$\mathcal{S}$]'').
+		``ACT[$\mathcal{S}$]'') on CUB Dataset.
 		%
@@
 
-It must be acknowledged that the high R@1 performance of our method largely
-stems from the source triplet sampling strategy, namely Softhard, instead of
-our contribution.
-%
-Our core contribution is
-
-minimizing a slightly different objective than the triplet loss.
-
-CUB 8 32
-
-CARS 8 32
-
-SOP 8 32
-
-Number of PGD Steps $\eta$.
-\cref{fig:introplot}
+Apart from that, our method HM[$\mathcal{S},g_\mathsf{LGA}$] out performs the
+previous methods in every aspect, as shown in \cref{fig:introplot} for 
+example.
+%
+Although HM[$\mathcal{R},\mathcal{M}$] and HM[$\mathcal{R},g_\mathsf{LGA}$] can reach
+a higher ERS, they are excluded from comparison because they induce a
+significant performance drop in R@1.
+
+It \emph{must} be acknowledged that the high R@1 performance of our method
+largely stems from the source triplet sampling strategy, namely Softhard,
+instead of our contribution.
+%
+In terms of the overall performance, our method can achieve the highest ERS at
+the lowest performance drop in R@1 under a fixed training cost.
+%
+The existing methods are overwhelmingly outperformed by our method.
 
@@
 adversarial training samples is crucial for preventing model collapse, and
-achieving good performance on both kinds of samples.
+achieving good performance on both types of samples.
 %
@@
 Intra-Class Structure loss helps the model exploit more information from the
-adversarial examples.
+given adversarial examples.
 
@@
 \label{sec:5}
+
+Our core contribution is the improvement in adversarial training efficiency
+through HM.
+%
+Since regular training and the min-max adversarial training can be expressed
+as two boundary cases as HM, Graduate Adversary is modeled as an ``intermediate
+hardness'' the two cases.
+%
+Enforcing the previously neglected Intra-Class Structure is also beneficial
+for model robustness and adversarial training efficiency.
 

### 2021-11-02 robdml.tex
tex

@@
 
+\oo{In potential of future works}
+Deep metric learning on adversarial example is also used for improving
+adversarial robustness for deep classifiers~\cite{mao2019metric}.
+
 \textbf{Adversarial Attack.}
@@
 
+Adversarial robustness is important for DML applications.
+%
 Our core contribution is the improvement in adversarial training efficiency
@@
 %
-Since regular training and the min-max adversarial training can be expressed
-as two boundary cases as HM, Graduate Adversary is modeled as an ``intermediate
-hardness'' the two cases.
-%
-Enforcing the previously neglected Intra-Class Structure is also beneficial
-for model robustness and adversarial training efficiency.
-
-Adversarial robustness is important for DML applications, but
-the existing defenses still suffer from low efficiency and low
-performance.
-%
-In this paper, 
-Hardness Manipulation is proposed as as a flexible tool to create
-adversarial examples for more efficient adversarial training.
-%
-Meanwhile, Gradual Adversary is proposed as a family of pseudo-hardness
-functions to better balance the training objectives.
-%
-Besides, an Intra-Class Structure penalty is proposed to enforce better
-embedding structure for higher robustness.
-%
-According to experimental evaluations, the proposed method overwhelmingly
-outperforms the state-of-the-art defenses.
-
-\oo{In potential of future works}
-Deep metric learning on adversarial example is also used for improving
-adversarial robustness for deep classifiers~\cite{mao2019metric}.
+Since regular training and the min-max adversarial training can be expressed as
+two boundary cases as HM, Graduate Adversary is modeled as an ``intermediate
+hardness'' the two cases, and is effective.
+%
+Enforcing the previously neglected Intra-Class Structure can further improve 
+model robustness and adversarial training efficiency.
+%
+Our method outperforms previous methods.
 

### 2021-11-02 robdml.tex
tex
typo

@@
 % contributions
-In brief, our contribusions includes:
+In brief, our contributions include:
 %
@@
 
+\begin{comment}
 \oo{In potential of future works}
@@
 adversarial robustness for deep classifiers~\cite{mao2019metric}.
+\end{comment}
 
@@
 $\text{HM}[H_\mathsf{S},2+\gamma]$, where $2+\gamma$ is the 
-upperbound of loss, while $\text{HM}[H_\mathsf{S},H_\mathsf{S}]$
+upper bound of loss, while $\text{HM}[H_\mathsf{S},H_\mathsf{S}]$
 is regular DML training.
 
-As pushing $\tilde{H}_\mathsf{S}$ towards the upperbound will easily lead to
-model collapse, a valid $H_\mathsf{D}$ should be choosed within the interval
+As pushing $\tilde{H}_\mathsf{S}$ towards the upper bound will easily lead to
+model collapse, a valid $H_\mathsf{D}$ should be chosen within the interval
 $[H_\mathsf{S},2+\gamma]$ without rendering model collapse.
@@
 
-Even if $H_\mathsf{D}$ is calucated from another triplet harder than the
+Even if $H_\mathsf{D}$ is calculated from another triplet harder than the
 \emph{source} triplet, the adversarial example may become weak in the late
@@
 Specifically, the anchor $\va$ and its adversarial counterpart $\tilde{\va}$
-are separated from the positve sample $\vp$ by reusing the triplet loss,
+are separated from the positive sample $\vp$ by reusing the triplet loss,
 \ie,
@@
 
-Specifically, we (adversarially) train imagenet-initialized ResNet-18
+Specifically, we (adversarially) train ImageNet-initialized ResNet-18
 (RN18)~\cite{resnet} with the output dimension of the last layer changed to
@@
 %
-The parameter $u$ is equal to $\gamma$, much less than the loss upperbound,
+The parameter $u$ is equal to $\gamma$, much less than the loss upper bound,
 in order to avoid excessive hardness boost in $g_\mathsf{B}$ and $g_\mathsf{LGA}$.
@@
 %
-Our core contribution is the improvement in adversarial training efficiency
+In this paper, we improve the efficiency of adversarial training of DML
 through HM.

### 2021-11-04 robdml.tex
svg
tex

@@
 	% background
-	Owing to the security implications of adversarial vulnerability, the
-	adversarial robustness of deep metric learning models has to be improved
-	via defense.
+	Owing to security implications of adversarial vulnerability, adversarial
+	robustness of deep metric learning models has to be improved.
 	% insight
 	In order to avoid model collapse due to excessively hard examples, the
-	existing defenses refrain from using the min-max adversarial training, but
-	instead learns from a weak adversary inefficiently.
+	existing defenses dismiss the min-max adversarial training, but instead
+	learn from a weak adversary inefficiently.
 	% our starting point
-	Conversely, we argue that a model can learn from a strong adversary without
-	collapse, where the key is triplet hardness.
-	% HM framework
-	To this end, Hardness Manipulation is proposed to adversarially perturb the
-	training triplet to increase its hardness into a specified level, according
-	to another benign triplet or a pseudo-hardness function.
+	Conversely, we propose Hardness Manipulation to efficiently perturb the
+	training triplet till a specified level of hardness for adversarial
+	training, according to a harder benign triplet or a pseudo-hardness
+	function.
+	% merit
+	It is flexible as regular training and min-max adversarial training
+	are its boundary cases.
 	% GA Adversary
-	Based on this, Gradual Adversary is proposed as a family of pseudo-hardness
-	functions to overcome problems of referencing other benign triplets, and
-	achieve a better balance in the learning objective.
+	Besides, Gradual Adversary, a family of pseudo-hardness functions is
+	proposed to gradually increase the specified hardness level during training
+	for a better balance between performance and robustness.
 	% Intra-Class Structure
-	Besides, a penalty on Intra-Class Structure among benign and adversarial
-	examples can further improve model robustness, which is neglected by
-	previous methods.
+	Additionally, an Intra-Class Structure loss term among benign and adversarial
+	examples further improves training efficiency and model robustness.
 	% Experiment and Conclusion
-	Comprehensive experimental results on commonly used deep metric
-	learning datasets suggest that the proposed method, although simple in
-	its form, overwhelmingly outperforms the state-of-the-art defense methods in
-	terms of training time cost, robustness, as well as recall performance on
-	benign examples.
+	Comprehensive experimental results suggest that the proposed method,
+	although simple in its form, overwhelmingly outperforms the
+	state-of-the-art defenses in terms of training cost,
+	robustness, as well as performance on benign examples.
 %
@@
 example retrieval.
+
+\begin{figure}
+	\includegraphics[width=\columnwidth]{hmflexible.pdf}
+	\vspace{-1.8em}
+	\caption{Flexibility of Hardness Manipulation.
+	%
+	Regular training and min-max adversarial training are two of its boundary cases.
+	}
+	\label{fig:hmflexible}
+\end{figure}
 

### 2021-11-04 robdml.tex
tex

@@
 %
-As an extensively studied task~\cite{revisiting}, DML has a wide range of
-applications such as image retrieval~\cite{imagesim2} and face
-recognition~\cite{facenet,domainface}, as well as a wide influence on the core
-idea of other areas such as self-supervised learning~\cite{dmlreality}.
-
-Despite the advancements in this field thanks to deep neural
-networks, recent studies find DML models vulnerable to
-adversarial attacks, where an imperceptible perturbation can incur unexpected
-retrieval, or covertly manipulate the results~\cite{advrank,advorder}.
-%
-Such vulnerability raises security, safety, and fairness concerns in the
-DML applications.
-%
-For example, impersonation or recognition evasion are possible for a
-vulnerable DML-based face-identification system.
+As an extensively studied task~\cite{revisiting,dmlreality}, DML has a wide
+range of applications such as image retrieval~\cite{imagesim2} and face
+recognition~\cite{facenet,domainface}, and widely influences some other areas
+such as self-supervised learning~\cite{dmlreality}.
+
+Despite the advancements in this field thanks to deep learning, recent studies
+find DML models vulnerable to adversarial attack, where an imperceptible
+perturbation can incur unexpected retrieval result, or covertly change the
+rankings~\cite{advrank,advorder}.
+%
+Such vulnerability raises security, safety, and fairness concerns in DML
+applications.
+%
+For example, impersonation or recognition evasion are possible on a vulnerable
+DML-based face-identification system.
 %

### 2021-11-04 robdml.tex
page 1

@@
 
-Existing defense methods for DML~\cite{advrank,robrank} are adversarial
-training-based, inspired by Madry's \emph{min-max} adversarial
-training~\cite{madry} because it is one of the most effective methods for deep
-neural network classifiers.
+Existing defense methods~\cite{advrank,robrank} are adversarial training-based,
+inspired by Madry's \emph{min-max} adversarial training~\cite{madry} because it
+is consistently one of the most effective methods for classification task.
 %
@@
 %
-However, in order to avoid model collapse, the existing DML defenses refrain
-from directly adopting such paradigm, but instead use some indirect and
-relatively weak objectives to increase the loss value to a certain level.
-%
-As a result, the model is not learning from a strong adversary, and suffers
-from low efficiency in gaining robustness within limited time. 
-%
-Furthermore, adversarial training already suffers from significant training
-cost (compared to the normal training process).
-%
-Hence, efficiency in gaining adversarial robustness is an inevitable major
-issue for DML defense methods.
+However, in order to avoid model collapse due to excessively hard examples, the
+existing defenses refrain from directly adopting such min-max paradigm, but
+instead replace the inner problem to indirectly increase the loss value to a
+certain level, which suffers from low efficiency and weak adversary (and hence
+weak robustness).
+%
+Since training cost is already a serious issue of adversarial training, the
+efficiency in gaining higher adversarial robustness under a fixed budget is
+inevitable and important for DML defense.
 
@@
 
-As suggested by previous works, an appropriate adversary for the inner
-\emph{maximization} problem should increase the loss to a certain point between
-that of benign examples (\ie, unperturbed examples) and the theoretical upper
-bound.
-%
-What if this point is reached by a strong adversary, directly and
-efficiently?
-%
-Besides, as the mathematical expectation of loss is also greatly influenced by
-the triplet sampling strategy, we conjecture that the triplet sampling strategy
-and triplet ``hardness'' have a key impact for adversarial training.
+Previous works suggest that an appropriate adversary for the inner
+\emph{maximization} problem should increase the loss to an ``intermediate''
+point between that of benign examples (\ie, unperturbed examples) and the
+theoretical upper bound.
+%
+In this paper, we argue such point can be reached by a direct and efficient
+adversary.
+%
+Besides, we conjecture the triplet sampling strategy has a key impact in
+adversarial training, because it is also able to greatly influence the
+mathematical expectation of loss even without adversarial attack.
 

### 2021-11-04 robdml.tex
para

@@
 In this paper, we first define the ``\emph{hardness}'' of a sample triplet as
-the difference between the anchor-positive distance and the anchor-negative
+the difference between the anchor-positive distance and anchor-negative
 distance.
@@
 sample triplet and increase its hardness into a specified \emph{destination}
-hardness level.
-%
-HM is implemented as an objective to minimize the L-$2$ norm of the thresholded
-difference between the hardness of the given sample triplet and the specified
+hardness level for adversarial training.
+%
+The objective of HM is to minimize the L-$2$ norm of the thresholded difference
+between the hardness of the given sample triplet and the specified
 \emph{destination} hardness.
 %
-Mathematically, when the objective is optimized using Projected Gradient
-Descent~\cite{madry}, the gradient of HM objective with respect to the
-adversarial perturbation is the same as that of directly \emph{maximizing} the
-triplet loss.
-%
-Thus, the optimization process of HM objective can be interpreted as a direct
-\emph{maximization} process of the loss (indicating a direct strong adversary)
-which stops halfway at the specified \emph{destination} hardness level.
-
-\oo{regular and max can be expressed as two boundary cases of HM}
+HM is flexible as regular training and min-max adversarial training
+can be expressed as its boundary cases, as shown in \cref{fig:hmflexible}.
+%
+Mathematically, when the HM objective is optimized using Projected Gradient
+Descent~\cite{madry}, the sign of its gradient with respect to the adversarial
+perturbation is the same as that of directly \emph{maximizing} the loss.
+%
+Thus, the optimization of HM objective can be interpreted as a direct and
+efficient \emph{maximization} process of the loss which stops halfway at the
+specified \emph{destination} hardness level, \ie, the ``intermediate'' point.
 

### 2021-11-04 robdml.tex
para

@@
 %
-Thus, intuitively, the \emph{destination} hardness can be that of another
-benign triplet which is harder than the given triplet (\eg, a
-Semihard~\cite{facenet} triplet).
-%
-However, in the late phase of training, the
-expectation of \emph{destination} hardness of another benign triplet
-will be small, and close to the \emph{hardness} expectation of the given triplet.
-%
-This leads to weak attacks, and inefficient learning from a weak adversary.
-%
-Besides, we speculate a strong adversary in the early phase of DML training may
+Thus, intuitively, the \emph{destination} hardness can be the hardness of
+another benign triplet which is moderately harder than the given triplet (\eg,
+a Semihard~\cite{facenet} triplet).
+%
+However, in the late phase of training, the expectation of the difference
+between such \emph{destination} hardness and that of the given triplet will be
+small, leading to weak adversarial examples and inefficient adversarial
+learning.
+%
+Besides, strong adversarial examples in the early phase of training may also
 hinder the model from learning good embeddings, and hence influence the
-eventual performance on benign examples.
-%
-Based on these, a \emph{destination} hardness calculated from benign examples
-may not be the best choice.
-%
-A better \emph{destination} hardness should be able to balance the training
-objectives in the early and late phases of training.
+performance on benign examples.
+%
+Namely, a better \emph{destination} hardness should be able to balance the
+training objectives in the early and late phases of training.
 

### 2021-11-04 robdml.tex
tex

@@
 
-To this end, we propose Graduate Adversary, a family of pseudo-hardness
-functions which can be used as the \emph{destination} hardness in HM.
-%
-Any function that leads to a relatively weak adversary in the early training
-phase, and a relatively strong adversary in the late training phase belongs to
-this family.
-%
-As an example, we design a ``Linear Graduate Adversary'' (LGA) pseudo-hardness
+To this end, Graduate Adversary, a family of pseudo-hardness functions is
+proposed, which can be used as the \emph{destination} hardness.
+%
+A function that leads to relatively weak and relatively strong adversarial
+examples respectively in the early and late phase of training belongs to this
+family.
+%
+As an example, we design a ``Linear Graduate Adversary'' (LGA)
 function as the linearly scaled negative triplet margin, incorporating a strong
-assumption that the \emph{destination} hardness should remain Semihard.
-%
-%Empirical observation will show the advantage of such pseudo-hardness
-%functions.
+prior that the \emph{destination} hardness should remain Semihard
+based on our empirical observation.
 
@@
 
-Besides, a sample triplet will be augmented into a sextuplet (benign and
-adversarial examples) during adversarial training, where a \emph{intra-class}
-structure can be enforced.
-%
-Such structure has been neglected by existing methods, but some existing
-attacks aims to change the sample rankings in the same class~\cite{advrank}.
-%
-Hence, we propose a simple \emph{intra-class} structure penalty term for
-adversarial training, which is expected to improve robustness.
+Additionally, it is noted that a sample triplet will be augmented into a
+sextuplet (both benign and adversarial examples) during adversarial training.
+%
+In this case, the \emph{intra-class} structure can be enforced, has been
+neglected by existing methods.
+%
+Since some existing attacks aim to change the sample rankings in the same
+class~\cite{advrank},
+%
+we propose a simple \emph{intra-class} structure loss term for adversarial
+training, which is expected to further improve robustness.
 
 % evaluation and conclusion
-The experiments are conducted on three commonly used DML datasets, namely
-CUB-200-2011~\cite{cub200}, Cars-196~\cite{cars196}, and Stanford Online
+Comprehensive experiments are conducted on three commonly used DML datasets,
+namely CUB-200-2011~\cite{cub200}, Cars-196~\cite{cars196}, and Stanford Online
 Product~\cite{sop}.
@@
 terms of training cost, robustness, as well as the performance on benign
-example retrieval.
+examples.
 
@@
 	%
-	Regular training and min-max adversarial training are two of its boundary cases.
+	Regular training and min-max adversarial training are its boundary cases.
 	}
@@
 	%
-	\item {\textit{Hardness Manipulation}} (HM) is proposed as a flexible tool
-		to create adversarial triplets with increased hardness for
-		subsequent adversarial training.
-		%
-		It is more efficient than previous adversarial training methods of DML.
-		%
-	\item \textit{Gradual Adversary} is proposed as a family of pseudo-hardness
-		functions for \emph{Hardness Manipulation}, which can balance the
-		training objectives during the training process.
-		%
-		A linear function named Linear Graduate Adversary (LGA) is designed as
-		an example.
-		%
-	\item \textit{Intra-Class Structure} penalty is proposed to further improve
-		the robustness of a DML model, while such possibility is neglected by
-		existing methods. 
+	\item {\textit{Hardness Manipulation}} (HM) is proposed as a flexible and
+		efficient tool to create adversarial example triplets for subsequent
+		adversarial training of DML model.
+		%
+	\item \textit{Linear Gradual Adversary} (LGA) is proposed as a
+		pseudo-hardness function for HM, which incorporates our empirical
+		observations and can balance the training objectives during the
+		training process.
+		%
+	\item \textit{Intra-Class Structure} (ICS) loss term is proposed to further
+		improve the DML model robustness, while such possibility is neglected
+		by existing methods. 
 		%
@@
 %
-Ian \etal~\cite{fgsm} speculate the reason is that DNN being locally linear
-with respect to the adversarial perturbation.
-%
-Subsequent studies can compromise the DNNs more effectively, such as
-BIM~\cite{i-fgsm}, PGD~\cite{madry}, and APGD~\cite{apgd}, which are
-unanimously based on the first-order gradient of the loss, and rely on the
-white-box assumption of fully accessible model details.
-%
-In contrast, query-based black-box attacks~\cite{nes-atk,spsa-atk} are more
-practical for real-world scenarios, as they requires the least amount of
-information from the model for estimating the gradients.
+Ian \etal~\cite{fgsm} attribute the reason to DNN being locally linear with
+respect to the adversarial perturbation.
+%
+Subsequent first-order gradient-based methods can compromise the DNNs more
+effectively under the white-box assumption~\cite{i-fgsm,madry,apgd}.
+%
+In contrast, black-box attacks have been explored by query-based
+methods~\cite{nes-atk,spsa-atk} and transferrability-based methods~[], which
+are more practical for real-world scenarios.
 

### 2021-11-04 robdml.tex
p2

@@
 %
-To battle against the attacks, some early defenses incur gradient masking
-effect, but it gives a false sense of security~\cite{obfuscated}.
-%
-Defensive distillation~\cite{distill2} can be compromised~\cite{cw}.
+To battle against the attacks, some defenses incur gradient masking
+effect, but leads to a false sense of security~\cite{obfuscated}.
+%
+Defensive distillation~\cite{distill2} is compromised~\cite{cw}.
 %
@@
 %
-Other forms of defenses are also proposed, such as input
+Other defenses are also proposed, such as input
 preprocessing~\cite{deflecting}, or a randomization inside the
@@
 %
-But various defense methods are still susceptible to adaptive
-attack~\cite{adaptive}.
-%
-Of all defenses, adversarial training remains to be one of the most
-effective method~\cite{bilateral,advtrain-triplet,benchmarking}, and it
-consistently show promising empirical robustness,
-although suffering from significant training cost and a lower performance
-on benign examples.
+But many defenses are still susceptible to adaptive attack~\cite{adaptive}.
+%
+Of all defenses, adversarial training remains to be one of the most effective
+method~\cite{bilateral,advtrain-triplet,benchmarking}, consistently showing
+promising empirical robustness, although suffers from high training
+cost and a performance drop on benign examples.
 
@@
 %
-A well-designed loss function is crucial for DML performance~\cite{dmlreality}.
-As suggested by recent study, the classical triplet loss could reach
-state-of-the-art performance with an appropriate triplet sampling
-strategy~\cite{revisiting}.
+A well-designed loss function and a proper sampling method are crucial for DML
+performance~\cite{dmlreality}.  As suggested by recent study, the classical
+triplet loss could reach state-of-the-art performance with an appropriate
+triplet sampling strategy~\cite{revisiting}.
 

### 2021-11-04 robdml.tex
sec2

@@
 DML has been found vulnerable to adversarial attacks as
-well~\cite{advrank,advorder,robrank}, which raises concerns on
-safety, security, or fairness for a DML application.
-%
-The existing attacks aims to completely subvert the image retrieval results~[][][],
-or covertly alter the top-ranking results without being abnormal~[][][][].
-
-%
-\textbf{Defenses in DML.} Compared to attacks, defense methods for DML are less
+well~\cite{advrank,advorder,robrank}, which raises concerns on safety,
+security, or fairness for a DML application.
+%
+The existing attacks aims to completely subvert the image retrieval
+results~[][][], or covertly alter the top-ranking results without being
+abnormal~[][][][].
+
+%
+\textbf{Defenses in DML.} Different from attacks, defense methods are less
 explored.
 %
-Zhou \etal~\cite{advrank} present Embedding Shifted Triplet (EST), an
+Embedding Shifted Triplet (EST)~\cite{advrank} is an
 adversarial training method using adversarial examples with maximized embedding
@@
 Anti-Collapse Triplet (ACT)~\cite{robrank} forces the model to separate
-collapsed positive and negative samples in order to learn robust features,
-which achieves the state-of-the-art robustness.
-%
-However, the existing defense methods suffer from low efficiency as a
-relatively weak adversary is used in order to avoid model collapse.
+collapsed positive and negative samples apart in order to learn robust
+features, which achieves the state-of-the-art robustness.
+%
+However, the existing defense methods suffer from low efficiency as the
+inner problem is replaced into a indirect form in order to avoid model collapse.
 

### 2021-11-04 robdml.tex
tex

@@
 In contrast, black-box attacks have been explored by query-based
-methods~\cite{nes-atk,spsa-atk} and transferrability-based methods~[], which
-are more practical for real-world scenarios.
+methods~\cite{nes-atk,spsa-atk} and transferrability-based
+methods~\cite{di-fgsm}, which are more practical for real-world scenarios.
 
@@
 The existing attacks aims to completely subvert the image retrieval
-results~[][][], or covertly alter the top-ranking results without being
-abnormal~[][][][].
+results~\cite{qair,learn-to-misrank,advdpqn,advpattern,flowertower,universalret},
+or covertly alter the top-ranking results without being
+abnormal~\cite{advrank,advorder}.
 

### 2021-11-04 robdml.tex
sec31

@@
 \mathcal{X},  \|\vr\|_p \leq \varepsilon\}$, so that its embedding vector
-$\tilde{\vx}=\phi(\mX+\vr)$ will be moved off its original location to other
-positions to fulfill the attacker's goal~[][][][][].
+$\tilde{\vx}=\phi(\mX+\vr)$ will be moved off its original location towards
+other positions to achieve the attacker's goal.
 %
@@
 The most important metrics for a good defense is training cost, adversarial
-robustness, and performance on benign examples.
+robustness, and performance drop on benign examples.
 
@@
 Given an image triplet ($\mA$, $\mP$, $\mN$) sampled with a certain sampling
-strategy (\eg, Random) within a mini-batch, we define its
-\emph{hardness} as a scalar:
+strategy (\eg, Random) within a mini-batch, we define its \emph{hardness} as a
+scalar which is within $[-2,2]$:
 %
@@
 %
-H(\mA,\mP,\mN)=d_\phi(\mA,\mP)-d_\phi(\mA,\mN),
+H(\mA,\mP,\mN)=d_\phi(\mA,\mP)-d_\phi(\mA,\mN).
 %
@@
 %
-which is an internal part of the triplet loss.
-%
-For convenience we call this triplet as ``\emph{source} triplet'', and the
-corresponding $H(\cdots)$ value as ``\emph{source} hardness'', denoted as
-$H_\mathsf{S}$.
+Clearly, it is an internal part of the triplet loss.
+%
+For convenience, we call this triplet ($\mA$, $\mP$, $\mN$) as ``\emph{source}
+triplet'', and its corresponding hardness value as ``\emph{source}
+hardness'', denoted as $H_\mathsf{S}$.
 
@@
 types of $H_\mathsf{D}$ can be specified, \eg, a constant, the
-hardness of another benign triplet, or even a pseudo-hardness function.
+hardness of another benign triplet, or a pseudo-hardness function.
 %
 The case of maximizing the triplet loss is equivalent to
-$\text{HM}[H_\mathsf{S},2+\gamma]$, where $2+\gamma$ is the 
-upper bound of loss, while $\text{HM}[H_\mathsf{S},H_\mathsf{S}]$
-is regular DML training.
+$\text{HM}[H_\mathsf{S},2]$, where $2$ is the 
+upper bound of hardness, while $\text{HM}[H_\mathsf{S},H_\mathsf{S}]$
+is regular DML training, as shown in \cref{fig:hmflexible}.
 

### 2021-11-04 robdml.tex
tex

@@
 Given an image triplet ($\mA$, $\mP$, $\mN$) sampled with a certain sampling
-strategy (\eg, Random) within a mini-batch, we define its \emph{hardness} as a
-scalar which is within $[-2,2]$:
+strategy (\eg, Random) within a mini-batch, we define its ``\emph{hardness}''
+as a scalar which is within $[-2,2]$:
 %
@@
 For convenience, we call this triplet ($\mA$, $\mP$, $\mN$) as ``\emph{source}
-triplet'', and its corresponding hardness value as ``\emph{source}
-hardness'', denoted as $H_\mathsf{S}$.
+triplet'', and its corresponding hardness value as ``\emph{source} hardness'',
+denoted as $H_\mathsf{S}$.
 
@@
 hardness $H_\mathsf{S}$ into a specified ``\emph{destination} hardness''
-$H_\mathsf{D}$, by finding adversarial examples of the source triplet $(\mA,
-\mP, \mN)$, \ie, $(\mA + {\vr}_a, \mP + {\vr}_p, \mN + {\vr}_n)$, where
-$({\vr}_a, {\vr}_p, {\vr}_n)$ are the adversarial perturbations.
-%
-If we denote the hardness of the adversarially perturbed \emph{source} triplet
-as $\tilde{H}_\mathsf{S}$, the HM can be implemented as follows:
+$H_\mathsf{D}$, by finding adversarial examples of the source triplet, \ie,
+$(\mA{+} {\vr}_a, \mP {+} {\vr}_p, \mN {+} {\vr}_n)$, where $({\vr}_a, {\vr}_p,
+{\vr}_n)$ are the adversarial perturbations.
+%
+Denoting the hardness of the adversarially perturbed \emph{source} triplet
+as $\tilde{H}_\mathsf{S}$, \ie,
+%
+$\tilde{H}_\mathsf{S} = H(\mA{+} {\vr}_a, \mP {+} {\vr}_p, \mN {+} {\vr}_n)$,
+%
+the HM is implemented as:
 %
@@
 $H_\mathsf{S}>H_\mathsf{D}$, automatically stopping the optimization, because
-$H_\mathsf{S}$ is not desired to be reduced once being greater than
-$H_\mathsf{D}$.
-%
-The \cref{eq:hm} is written in the L-$2$ norm form instead of the standard Mean Squared
-Error because HM can be directly extended into vector form for a
+$H_\mathsf{S}$ is not desired to be reduced once it exceeds $H_\mathsf{D}$.
+%
+The \cref{eq:hm} is written in the L-$2$ norm form instead of the standard Mean
+Squared Error because HM can be directly extended into vector form for a
 mini-batch.
 %
-The optimization problem can be solved by Projected Gradient
-Descent (PGD)~\cite{madry}.
+The optimization problem can be solved by Projected Gradient Descent
+(PGD)~\cite{madry}.
 %
 And the resulting adversarial examples are used for adversarially training the
-DML model:
+DML model with
 %
@@
 %
-We abbreviate the adversarial training with adversarial examples created through
-this way as $\text{HM}[H_\mathsf{S},H_\mathsf{D}]$ in the following text.
-%
-And the overall procedure of HM is illustrated in \cref{fig:hm}.
+The overall procedure of HM is illustrated in \cref{fig:hm}.
+%
+For convenience,
+we abbreviate the adversarial training with adversarial examples created
+through this way as $\text{HM}[H_\mathsf{S},H_\mathsf{D}]$ in this paper.
 
@@
 %
-assuming that $H_\mathsf{D}>\tilde{H}_\mathsf{S}$.
-%
-And the perturbation $\vr$ is updated as $\vr \leftarrow \text{Proj}_\Gamma\{\vr + \alpha \Delta
+assuming $H_\mathsf{D}>\tilde{H}_\mathsf{S}$.
+%
+The perturbation $\vr$ is updated as $\vr \leftarrow \text{Proj}_\Gamma\{\vr + \alpha \Delta
 \vr\}$ by PGD for $\eta$ steps with a step size $\alpha$.
@@
 maximization of $\tilde{H}_\mathsf{S}$, which discontinues very early once it
-reaches $H_\mathsf{D}$.
+exceeds $H_\mathsf{D}$.
 %

### 2021-11-05 robdml.tex
tex

@@
 
-\author{Mo Zhou ~~~~~~~ Vishal Patel\\
+\author{Mo Zhou\\
 Johns Hopkins University\\
-{\tt\small mzhou32@jhu.edu ~~ vpatel36@jhu.edu}
+{\tt\small mzhou32@jhu.edu}
+\and
+Vishal Patel\\
+Johns Hopkins University\\
+{\tt\small vpatel36@jhu.edu}
 % For a paper whose authors are all at the same institution,
@@
 	\includegraphics[width=\columnwidth]{hmillust.pdf}
+	\vspace{-1.8em}
 	\caption{Illustration of Hardness Manipulation.}
@@
 
-Note, in the PGD case, the sign of negative gradient of the HM objective with
-respect to an adversarial perturbation $\vr$ is equivalent to the sign of
-gradient for directly maximizing the hardness $\tilde{H}_\mathsf{S}$ (hence
-maximizing $L_\text{T}$), \ie,
+Note, in the PGD case, the sign of negative gradient of the HM objective
+\emph{w.r.t.} an adversarial perturbation $\vr$ is equivalent to the sign of
+gradient for directly maximizing $\tilde{H}_\mathsf{S}$ (hence
+maximizing $L_\text{T}$) when $H_\mathsf{D}>\tilde{H}_\mathsf{S}$, \ie,
 %
@@
 		\frac{\partial}{\partial \vr} \tilde{H}_\mathsf{S}
-		\big\},
+		\big\}.
 \end{align}
 %
-assuming $H_\mathsf{D}>\tilde{H}_\mathsf{S}$.
-%
 The perturbation $\vr$ is updated as $\vr \leftarrow \text{Proj}_\Gamma\{\vr + \alpha \Delta
-\vr\}$ by PGD for $\eta$ steps with a step size $\alpha$.
+\vr\}$ by PGD for $\eta$ steps with a step size $\alpha$, where the ``Proj'' operator
+clips the result into the $\Gamma$ set.
 %
@@
 %
-This means the model learns from an efficient adversary during adversarial
-training with HM.
+With HM, the model can learn from an \emph{efficient} adversary.
 

### 2021-11-05 robdml.tex
tex

@@
 
-As pushing $\tilde{H}_\mathsf{S}$ towards the upper bound will easily lead to
+As pushing $\tilde{H}_\mathsf{S}$ towards the upper bound will easily render
 model collapse, a valid $H_\mathsf{D}$ should be chosen within the interval
-$[H_\mathsf{S},2+\gamma]$ without rendering model collapse.
+$[H_\mathsf{S},2]$.
 %
@@
 %
-Or at least the $\text{Var}[H_\mathsf{D}]$ of such sampling strategy has to be
-large enough in order to create a notable number of valid adversarial examples.
+Or at least the $\text{Var}[H_\mathsf{D}]$ of another benign triplet has to
+be large enough (for a small portion of triplets $H_\mathsf{D}>H_\mathsf{S}$)
+in order to create a notable number of valid adversarial
+examples.
 %
@@
 For convenience of further discussion, we denote the hardness of a Random,
-Semihard, and Softhard triplets as $\mathcal{R}$,
-$\mathcal{M}$, $\mathcal{S}$, respectively.
+Semihard, and Softhard triplets as $\mathcal{R}$, $\mathcal{M}$, $\mathcal{S}$,
+respectively.
 
@@
 %
-The optimizer aims to reduce the expectation of triplet
-loss $E[L_\text{T}]$ to zero as possible over the distribution of sample triplets, and thus
+The optimizer aims to reduce the expectation of 
+loss $E[L_\text{T}]$ towards zero as possible over the distribution of triplets, and thus
 the $E[H]$ of any given triplet will tend to $-\gamma$, reducing the
-hardness of adversarial triplets from HM.
-%
-We speculate this will lower the level of robustness the model could reach.
+hardness of adversarial triplets from HM as $E[H_\mathsf{D}-H_\mathsf{S}]$
+decreases accordingly.
+%
+Weakened adversarial examples are insufficient for robustness.
 
@@
 
-Thus, $H_\mathsf{D}$ should be (1) close to $H_\mathsf{S}$ in the
-early training phase (indicated by a large loss value), and (2) clearly higher
-than $H_\mathsf{S}$ in the late training phase (indicated by a small loss
-value),
-%
-in order to automatically balance the training objectives (\ie, performance
-on benign examples \emph{v.s.} robustness).
-%
-We name the two conditions as ``Graduate Adversary'' for 
-pseudo-hardness functions, as illustrated in \cref{fig:ga}.
+Thus, $H_\mathsf{D}$ should lead to (1) relatively weak adversarial examples in
+the early training phase (indicated by a large loss value), and (2) relatively
+strong adversarial examples in the late training phase (indicated by a small
+loss value),
+%
+in order to automatically balance the training objectives (\ie, performance on
+benign examples \emph{v.s.} robustness).
+%
+A satisfactory pseudo-hardness function is a ``Graduate Adversary'', as
+illustrated in \cref{fig:ga}.
 
@@
 As an example, we propose a ``Linear Gradual Adversary'' (LGA) pseudo-hardness
-function that is independent to any benign triplets, incorporating an
-assumption that $H_\mathsf{D}$ should remain Semihard~\cite{facenet}, as
+function that is independent to any benign triplets, incorporating an empirical
+observation that $H_\mathsf{D}$ should remain Semihard~\cite{facenet}, as
 follows:
@@
 %
-And the training objectives will be automatically balanced in
-$\text{HM}[H_\mathsf{S},g_\mathsf{LGA}]$.
-%
-The design choice of LGA is empirically supported by experimental observations.
-%
-We leave more complex pseudo-hardness functions for future study.
+And the training objectives, namely performance on benign examples and
+robustness will be automatically balanced in
+$\text{HM}[H_\mathsf{S},g_\mathsf{LGA}]$, leading to a better eventual overall
+performance.
+%
+More complicated or non-linear pseudo-hardness functions are left for future study
+for sake of simplicity.
 %

### 2021-11-05 robdml.tex
tex

@@
 
-Adversarial robustness is important for DML applications.
-%
-In this paper, we improve the efficiency of adversarial training of DML
-through HM.
+Adversarial robustness is crucial for DML applications.
+%
+In this paper, we improve adversarial training efficiency through HM.
 %
 Since regular training and the min-max adversarial training can be expressed as
-two boundary cases as HM, Graduate Adversary is modeled as an ``intermediate
-hardness'' the two cases, and is effective.
+two boundary cases of HM, Graduate Adversary has been demonstrated effective as
+an ``intermediate point'' between the two cases.
 %

### 2021-11-05 robdml.tex
tex

@@
 the same class, it should be noted that the \emph{intra-class} structure can be
-enforced as well, and This has been neglected by the existing DML defenses.
+enforced as well, but this has been neglected by the existing DML defenses.
 %
@@
 %
-Specifically, the anchor $\va$ and its adversarial counterpart $\tilde{\va}$
+Specifically, the anchor $\va$ and its adversarial counterpart
 are separated from the positive sample $\vp$ by reusing the triplet loss,
@@
 %
-The $L_\text{ICS}$ term can be added to the loss function for
+The $L_\text{ICS}$ term can be appended to the loss function for
 adversarial training.
@@
 %
-(2) TMA~[], which increases the cosine similarity between two selected samples;
-%
-(3) ES~[][], which moves the embedding of a sample off its original position as
+(2) TMA~\cite{flowertower} which increases the cosine similarity between two selected samples;
+%
+(3) ES~\cite{advrank,advdpqn}, which moves the embedding of a sample off its original position as
 distant as possible;
 %
-(4) LTM~[], which perturbs the ranking result by minimizing the distance of
+(4) LTM~\cite{learn-to-misrank}, which perturbs the ranking result by minimizing the distance of
 unmatched pairs while maximizing the distance of matched pairs;
@@
 (6) GTT~\cite{robrank}, aims to move the top-$1$ candidate out of the top-$4$
-retrieval results, which is simplified from [].
+retrieval results, which is simplified from \cite{qair}.
 %

### 2021-11-06 robdml.tex
tex
svg
p7

@@
 	\includegraphics[width=\columnwidth]{gaillust.pdf}
-	\caption{Illustration of Gradual Adversary.}
+	\caption{Illustration of (Linear) Gradual Adversary.}
 	\label{fig:ga}
@@
 \begin{figure}[t]
-	\includegraphics[width=0.6\columnwidth]{icsapn.pdf}
-	\caption{Intra-Class Structure.}
+	\includegraphics[width=1.0\columnwidth]{icsapn.pdf}
+	\caption{Illustration of Intra-Class Structure Loss Term.}
 	\label{fig:ics}
@@
 Adam~\cite{adam} optimizer is used for parameter updates, with a learning rate
-as $1.0{\times}10^{-3}$ for $150$ epochs, and a mini-batch size of $112$.
+of $1.0{\times}10^{-3}$ for $150$ epochs, and a mini-batch size of $112$.
 %
@@
 %
-The parameter $u$ is equal to $\gamma$, much less than the loss upper bound,
+The parameter $u$ is equal to $\gamma$, much less than the loss upper bound
 in order to avoid excessive hardness boost in $g_\mathsf{B}$ and $g_\mathsf{LGA}$.
 %
-Parameter $\lambda$ in $L_\text{ICS}$ is $0.5$ by default.
+Parameter $\lambda$ for $L_\text{ICS}$ is $0.5$ by default ($0.05$ on SOP).
 
@@
 an collection of existing attacks against DML or their simplified white-box
-alternatives optimized with PGD ($\eta=32$ for strong effect).
+alternatives optimized with PGD ($\eta=32$ for strong attack).
 %
@@
 %
-Further details can be found in \cite{robrank} and the supplementary.
-
-\begin{comment}
-%
-In this section, we first carry out parameter search for the components of the
-proposed method, in order to illustrate their effectiveness.
-%
-The comparison with the state-of-the-art DML defense methods will be presented in the end.
-%
-\end{comment}
+Further details can be found in \cite{robrank} or the supplementary.
 
@@
 As discussed in \cref{sec:31}, we start from the $H_\mathsf{D}$ calculated from
-a harder benign triplet sampled in a different strategy, such as Random,
+a harder benign triplet sampled by a different strategy, such as Random,
 Semihard~\cite{facenet}, Softhard~\cite{revisiting},
@@
 But not all potential combinations are expected to be effective for HM, as it
-will not create an adversarial triplet when $H_\mathcal{S}\geqslant
-H_\mathcal{D}$.
+will not create an adversarial triplet when $H_\mathsf{S}\geqslant
+H_\mathsf{D}$.
 %
@@
 Although $E[H]$ of Softhard is less than that of Distance or Hardest, some hard
-adversarial examples are still created
+adversarial examples are still created%
 %
@@
 
-In summary, HM creates mini-batches mixing some unperturbed source triplets and
+In practice, HM creates mini-batches mixing some unperturbed source triplets and
 some adversarial triplets.
@@
 Empirically, the hardness range of Semihard strategy,
-\ie, $[-\gamma,0]$ is appropriate for $H_\mathcal{D}$.
+\ie, $[-\gamma,0]$ is found appropriate for $H_\mathsf{D}$.
 
@@
 %
-To validate HM with $H_\mathcal{D}$ calculated from benign
+To validate HM with $H_\mathsf{D}$ calculated from benign
 triplets, we adversarially train models using $\text{HM}[\mathcal{R},
@@
 examples and a large portion of Semihard adversarial examples, and hence
-achieve a high ERS and a relatively low R@1 because the Random triplet sampling
-strategy is not selective for data on which the model cannot generalize well.
+achieve a high ERS and a relatively low R@1 because the Random sampling
+strategy is not selective to benign samples on which the model does not generalize well.
 %
@@
 adversarial examples and a large portion of Softhard benign examples, and hence
-achieve a relatively high ERS as well as a high R@1 since Softhard sampling
-strategy is selective for the training data.
+achieve a relatively high ERS and a high R@1 because Softhard sampling
+strategy is selective.
 %
@@
 %
-As discussed in \cref{sec:32}, the HM[$\mathcal{S},\mathcal{M}$] may still suffer
-from the imbalance between learning the embeddings and gaining adversarial
-robustness.
+As discussed in \cref{sec:32}, the HM[$\mathcal{S},\mathcal{M}$] may still
+suffer from the imbalance between learning the embeddings and gaining
+adversarial robustness.
 %
@@
 %
-Compared to HM[$\mathcal{S},\mathcal{M}$], slightly boosting the hardness in
-the late phase of training with $g_\mathsf{B}(\cdot)$ where $\xi{=}0.1$
-benefits the ERS, but results in a notably lower R@1;
+Compared to HM[$\mathcal{S},\mathcal{M}$], slightly boosting the hardness
+training with $g_\mathsf{B}(\cdot)$ where $\xi{=}0.1$ benefits the ERS, but
+results in a notably lower R@1;
 %
 A constant $H_\mathsf{D}$ at the upper bound of Semihard (\ie, $0$; too high
-for both early and late phase) renders model collapse;
+for both the early and the late phase of training) renders model collapse;
 %
@@
 %
-$H_\mathsf{D}{=}-\gamma/2$ provides a balance between the lower and upper
-bound, but still suffers from inflexibility.
-%
-In contrast, being not susceptible to the problems of other choices,
+$H_\mathsf{D}{=}-\gamma/2$ provides a balance in training objectives, but
+still suffers from inflexibility.
+%
+In contrast, being not susceptible to the mentioned problems of other choices,
 HM[$\mathcal{S},g_\mathsf{LGA}$] achieves an ERS on par with
-HM[$\mathcal{S},\mathcal{M}$], but at the lowest R@1 penalty among all choices.
+HM[$\mathcal{S},\mathcal{M}$], but is at the lowest R@1 performance penalty among all choices.
 

### 2021-11-06 robdml.tex
tex

@@
 %
-The ability of a method to achieve a high ERS under a fixed training cost
+The ability of a method to achieve a high ERS under a low training cost
 indicates a high efficiency.
@@
 %
-Nevertheless, EST[$\mathcal{R}$] only lead to a moderate robustness in all
-settings compared to other methods.
-%
-Experiments for EST[$\mathcal{S}$] is omitted as it is expected to result in
+Nevertheless, EST[$\mathcal{R}$] only lead to a moderate robustness
+compared to other methods.
+%
+Experiments for EST[$\mathcal{S}$] are omitted as they are expected to result in
 even much lower ERS based on the observations in previous subsections, and EST
@@
 %
-Thus, results for ACT[$\mathcal{S}$] are omitted from the table.
-
-Apart from that, our method HM[$\mathcal{S},g_\mathsf{LGA}$] out performs the
+Thus, results for ACT[$\mathcal{S}$] are omitted for being insufficiently robust.
+
+Apart from that, our method HM[$\mathcal{S},g_\mathsf{LGA}$] outperforms the
 previous methods in every aspect, as shown in \cref{fig:introplot} for 
@@
 %
-The existing methods are overwhelmingly outperformed by our method.
+The existing methods are overwhelmingly outperformed by our method in overall
+performance.
 
@@
 
-For adversarial training of a DML model, being selective to both benign and
+For adversarial training of a DML model, selectiveness on both benign and
 adversarial training samples is crucial for preventing model collapse, and
@@
 %
-Hardness Manipulation is a flexible tool for us to specify such ``selection'',
-and Graduate Adversary is a selection rule for adversarial examples.
-%
-Intra-Class Structure loss helps the model exploit more information from the
-given adversarial examples.
+HM is a flexible tool for specifying such a ``selection'',
+while LGA is a selection rule for adversarial examples.
+%
+ICS loss term helps the model exploit more information from the
+given sextuplet.
+
+The use of existing assets, limitations and societal impact of our method
+are discussed in supplementary material.
 
@@
 %
-Our method outperforms previous methods.
+%Our method outperforms previous methods.
 

### 2021-11-06 appendix.tex
tex
svg

@@
-\newpage
+\clearpage
 \appendix
+
+\section{Supplementary Information}
+
+\noindent\textbf{I. Potential Societal Impact.}
+
+(1) Security: Adversarial attacks may raise security considerations on deep
+learning applications, and even cause negative effect.
+%
+In contrast, in this manuscript, we focus on defending against the attacks and
+enhancing a model's adversarial robustness, and hence is expected to have a
+positive impact instead.
+
+(2) Environment: Although adversarial training is not environment-friendly due
+to its high training cost (in terms of more intensive computation than regular
+training), our method has significantly improved the adversarial training
+efficiency compared to the previous works (hence is a little bit more
+environment-friendly).
+
+\textbf{Limitations.}
+%
+\begin{quote}
+
+Considering the limitations of an approach is an important part of good
+academic scholarship. While many high-quality CVPR papers thoroughly consider
+and discuss limitations, CVPR 2022 aims to emphasize the importance of an
+honest treatment of limitations. Authors are thus explicitly encouraged to
+discuss limitations, ideally by creating a separate "Limitations" (sub-)section
+in their papers.
+
+Such discussion shall point out any strong assumptions and how robust the
+results are to violations of these assumptions (e.g., independence assumptions,
+noiseless settings, model well-specification, asymptotic approximations only
+held locally). Authors need to reflect on how these assumptions might be
+violated in practice and what the implications would be.
+
+The discussion shall also reflect on the scope of their claims, e.g., if the
+authors only tested their approach on a few datasets or did a few runs. In
+general, empirical results often depend on implicit assumptions, which should
+be articulated. The discussion shall reflect on the factors that influence the
+performance of the approach. For example, a recognition algorithm may perform
+poorly when image resolution is low or images are taken in low lighting.
+
+We understand that authors might fear that complete honesty about limitations
+might be used by reviewers as grounds for rejection. It is worth keeping in
+mind that a worse outcome might be if reviewers discover limitations that are
+not acknowledged in the paper. In general, we advise authors to use their best
+judgement and recognize that individual actions in favor of transparency play
+an important role in developing norms that preserve the integrity of the
+community. Reviewers will be specifically instructed to not penalize honesty
+concerning limitations
+
+\end{quote}
 
@@
 		on benign examples, but drastically reduce robustness.
+
+	\item Gradient in figure 5?
 
@@
 
+	\item Why not wall time as training cost?
+
+	\item the destination hardness is semihard (or something between semihard
+		and softhard, we leave new sampling strategy for future work).
+
+	\item Note, naive combination of benign training and adv train does not lead to better
+result, why? mix 0.5
+
+	\item why experiment, 8 step by default
+
 \end{enumerate}
@@
 Visualize robustness through the image retrieval task.
-
-\section{Miscellaneous}
-
-\textbf{Societal Impact.}
-%
-As encouraged by the author guidelines, we briefly discuss the potential
-societal impact of our work.
-%
-Adversarial attacks may raise \uline{security considerations} on deep learning
-applications, and even cause negative effect.
-%
-In contrast, in this manuscript, we focus on defending against the attacks and
-enhancing a model's adversarial robustness, and hence is expected to have a
-positive impact instead.
-%
-Besides, although adversarial training is not \uline{environment-friendly} due
-to its high training cost in GPU time, our study has significantly improved the
-adversarial training efficiency compared to the previous works.
-
-\textbf{Limitations.}
-%
-\begin{quote}
-
-Considering the limitations of an approach is an important part of good
-academic scholarship. While many high-quality CVPR papers thoroughly consider
-and discuss limitations, CVPR 2022 aims to emphasize the importance of an
-honest treatment of limitations. Authors are thus explicitly encouraged to
-discuss limitations, ideally by creating a separate "Limitations" (sub-)section
-in their papers.
-
-Such discussion shall point out any strong assumptions and how robust the
-results are to violations of these assumptions (e.g., independence assumptions,
-noiseless settings, model well-specification, asymptotic approximations only
-held locally). Authors need to reflect on how these assumptions might be
-violated in practice and what the implications would be.
-
-The discussion shall also reflect on the scope of their claims, e.g., if the
-authors only tested their approach on a few datasets or did a few runs. In
-general, empirical results often depend on implicit assumptions, which should
-be articulated. The discussion shall reflect on the factors that influence the
-performance of the approach. For example, a recognition algorithm may perform
-poorly when image resolution is low or images are taken in low lighting.
-
-We understand that authors might fear that complete honesty about limitations
-might be used by reviewers as grounds for rejection. It is worth keeping in
-mind that a worse outcome might be if reviewers discover limitations that are
-not acknowledged in the paper. In general, we advise authors to use their best
-judgement and recognize that individual actions in favor of transparency play
-an important role in developing norms that preserve the integrity of the
-community. Reviewers will be specifically instructed to not penalize honesty
-concerning limitations
-
-\end{quote}
 

### 2021-11-06 appendix.tex
app

@@
 
-\section{Supplementary Information}
+\section{Additional Information}
 
@@
 
-(1) Security: Adversarial attacks may raise security considerations on deep
-learning applications, and even cause negative effect.
+(1) \ul{Security:} Adversarial attacks may raise security considerations on
+deep learning applications, and even cause negative effect.
 %
@@
 
-(2) Environment: Although adversarial training is not environment-friendly due
-to its high training cost (in terms of more intensive computation than regular
-training), our method has significantly improved the adversarial training
-efficiency compared to the previous works (hence is a little bit more
-environment-friendly).
+(2) \ul{Environment:} Although adversarial training is not
+environment-friendly due to its high training cost (in terms of more intensive
+computation than regular training), our method has significantly improved the
+adversarial training efficiency compared to the previous works (hence is a
+little bit more environment-friendly).
 
-\textbf{Limitations.}
+\noindent\textbf{II. Limitations.}
+
+(1) \ul{The assumption that an ``intermediate point'' exists between regular
+training of DML model and min-max adversarial training of DML model.}
+(discussed in \cref{sec:1}; this is the motivation of HM)
+
+We propose the flexible tool HM where regular training and min-max adversarial
+training are equivalent to its boundary cases.
 %
-\begin{quote}
+By adjusting the destination hardness $H_\mathsf{D}$ in HM, we can obtain
+different results from adversarial training.
+%
+In the experiments section, we empirically search for valid options of the
+destination hardness, and add further improvements (\ie, LGA and ICS) on top of
+them.
+%
+The proposed method has been validated on three commonly used dataset, which
+demonstrates its robustness empirically.
 
-Considering the limitations of an approach is an important part of good
-academic scholarship. While many high-quality CVPR papers thoroughly consider
-and discuss limitations, CVPR 2022 aims to emphasize the importance of an
-honest treatment of limitations. Authors are thus explicitly encouraged to
-discuss limitations, ideally by creating a separate "Limitations" (sub-)section
-in their papers.
+Even if the proposed method stopped working in a new dataset or with some other
+different experimental settings, we can reduce
+the value $H_\mathsf{D}$ towards $H_\mathsf{S}$ until this method works.
+%
+Since HM falls back into regular training when $H_\mathsf{D}=H_\mathsf{S}$,
+we believe our proposed method will work before $H_\mathsf{D}$ is reduced
+to $H_\mathsf{S}$.
 
-Such discussion shall point out any strong assumptions and how robust the
-results are to violations of these assumptions (e.g., independence assumptions,
-noiseless settings, model well-specification, asymptotic approximations only
-held locally). Authors need to reflect on how these assumptions might be
-violated in practice and what the implications would be.
+Hence, this assumption is not expected to be a limitation.
 
-The discussion shall also reflect on the scope of their claims, e.g., if the
-authors only tested their approach on a few datasets or did a few runs. In
-general, empirical results often depend on implicit assumptions, which should
-be articulated. The discussion shall reflect on the factors that influence the
-performance of the approach. For example, a recognition algorithm may perform
-poorly when image resolution is low or images are taken in low lighting.
+(2) \ul{The assumption on optimization of the HM objective.}
+(discussed in \cref{sec:31})
 
-We understand that authors might fear that complete honesty about limitations
-might be used by reviewers as grounds for rejection. It is worth keeping in
-mind that a worse outcome might be if reviewers discover limitations that are
-not acknowledged in the paper. In general, we advise authors to use their best
-judgement and recognize that individual actions in favor of transparency play
-an important role in developing norms that preserve the integrity of the
-community. Reviewers will be specifically instructed to not penalize honesty
-concerning limitations
+Our proposed method HM does not rely on an optimizer that can really optimize
+the HM objective to zero.
+%
+In contrast, the state-of-the-art defense ACT~\cite{robrank} relies on the
+optimizer to successfully push the adversarial positive sample and adversarial
+negative sample close to each other in the embedding space.
+%
+This is hard to achieve given a low adversarial training budget (\eg, $\eta=8$),
+as can be shown in our experiments and acknowledged by \cite{robrank}.
 
-\end{quote}
+(3) \ul{The assumption that $H_\mathsf{D}$ should remain Semihard.}
+(discussed in \cref{sec:32})
+
+This is empirically supported by our experimental observations.
+%
+Even if this assumption is broken under some new experiment settings,
+we can further reduce the range of $H_\mathsf{D}$ until our method works again,
+thanks to the flexibility of HM.
+
+(4) \ul{A factor that influence the performance of our approach, namely
+backbone model.}
+
+The backbone model significantly influences the performance in every aspect, as
+the standard DML adopts ImageNet-initialized backbones for further training.
+%
+In this paper, we adopt ResNet-18 following the state-of-the-art
+defense~\cite{robrank} for fair comparison.
+%
+Since our proposed defense method is independent to backbone selection, it is
+expected to be effective on other backbone models as well.
+
+(5) \ul{A factor that influence the performance of our approach, namely
+adversarial training budget $\eta$.}
+
+As demonstrated in our experiments, the adversarial training budget, namely the
+maximum number of PGD iterations $\eta$ for creating the adversarial examples
+can greatly influence the performance.
+%
+We conduct experiments with multiple choices of $\eta$, and we can see from the
+curves that the model performance has a converging trend with large $\eta$
+settings.
+
+\noindent\textbf{III. Use of Existing Assets.}
+
+(1) \ul{Datasets:} All the datasets used in our paper are public datasets,
+and their corresponding papers are properly cited.
+
+(2) \ul{Code and Implementation:} Our implementation is built upon PyTorch
+and the public code of the state-of-the-art defense method~\cite{robrank}
+(License: Apache-2.0).
 

### 2021-11-06 appendix.tex
app
tex

@@
 
-\section{More Technical Details}
+\section{More Technical and Design Details}
 
-In this section, we provide more details on the reasons of our design,
-additional details of our implementation, as well as more discussions
-on questions that are unsuitable for the main part of manuscript.
+\noindent\textbf{I. Hardware and Software Platform.}
+
+We conduct the experiments with two Nvidia Titan Xp GPUs under the Ubuntu 16.04
+operating system with PyTorch 1.8.2 in distributed data parallel mode.
+
+\noindent\textbf{II. Embedding-Shifted Triplet (EST).}~\cite{advrank}
+
+Embedding-Shifted Triplet (EST)~\cite{advrank} adopts adversarial counterparts
+of $\va,\vp,\vn$ with maximum embedding move distance off their original
+locations, \ie,
+$L_\text{EST}=L_\text{T}(\tilde{\va},\tilde{\vp},\tilde{\vn};\gamma)$ where
+$\tilde{\va}=\phi(X+r^*)$, and $r^*=\arg\max_{r}d_\phi(X+r, X)$.
+%
+The $\tilde{\vp}$ and $\tilde{\vn}$ are obtained similarly.
+
+\ul{Relationship with HM:}
+%
+Since EST only aims to maximize the embedding move distance off its original
+location without specifying any direction, it leads to a random hardness
+value.
+%
+Because the perturbed triplet can be either harder or easier than the benign
+triplet.
+%
+Namely, EST merely indirectly increase the hardness of the training
+triplet, and may even decrease its hardness.
+%
+Thus, EST suffers from inefficiency in adversarial training compared to HM.
+
+\noindent\textbf{III. Anti-Collapse Triplet (ACT).}~\cite{robrank}
+
+Anti-Collapse Triplet (ACT)~\cite{robrank} ``collapses'' the embedding vectors
+of positive and negative sample, and enforces the model to separate them apart,
+\ie, $L_\text{ACT}=L_\text{T}(\va, \overrightarrow{\vp},
+\overleftarrow{\vn};\gamma)$, where $[\overrightarrow{\vp},\overleftarrow{\vn}]
+=[\phi(X_p+r_p^*), \phi(X_n+r_n^*)]$, and $[r_p^*,r_n^*]=\arg\min_{r_p,r_n}
+d_\phi(X_p+r_p, X_n+r_n)$.
+
+\ul{Relationship with HM:}
+
+\oo{todo}
+
+However, compared to the standard min-max adversarial training
+paradigm~\cite{madry}, these methods merely indirectly increase the loss value,
+and thus, suffer from inefficient learning because the adversary is not strong
+enough.
 
@@
 	\item Hardware and software platform?
-
-	\item Details of EST?
-
-	\item Details of ACT?
-%
-Embedding-Shifted Triplet (EST)~\cite{advrank} adopts adversarial counterpars
-of $\va,\vp,\vn$ with maximum embedding move distance off their original
-locations, \ie,
-$L_\text{EST}=L_\text{T}(\tilde{\va},\tilde{\vp},\tilde{\vn};\gamma)$ where
-$\tilde{\va}=\phi(X+r^*)$, $r^*=\arg\max_{r}d_\phi(X+r, X)$.
-%
-Anti-Collapse Triplet (ACT)~\cite{robrank} collapses the embedding vectors of
-positive and negative sample, and enforces the model to separate them apart,
-\ie, $L_\text{ACT}=L_\text{T}(\va, \overrightarrow{\vp},
-\overleftarrow{\vn};\gamma)$, where $[\overrightarrow{\vp},\overleftarrow{\vn}]
-=[\phi(X_p+r_p^*), \phi(X_n+r_n^*)]$, and $[r_p^*,r_n^*]=\arg\min_{r_p,r_n}
-d_\phi(X_p+r_p, X_n+r_n)$.
-%
-However, compared to the standard min-max adversarial training
-paradigm~\cite{madry}, these methods merely indirectly increase the loss value,
-and thus, suffer from inefficient learning because the adversary is not strong
-enough.
 
@@
 
-	\item [?] Can we learn more from the third and fourth standard moments?
-		Namely skewness and kurtosis.
-
-	\item [M] manuscript notes on LGA.
-
 	\item [\cmark] We don't have to mix HM(R,M) and HM(S,M).
@@
 		how they deal with hierarchy. e.g. MS, LSS, GLift, quadrup, etc.
-
-	\item [GA] Also scale the $H_D-H_S$ part?
-		(1) $$ H_\mathsf{GA} \leftarrow (H_\mathsf{D} + U - H_\mathsf{S}) * nL $$
-		(2) $$ H_\mathsf{GA} \leftarrow H_\mathsf{D} + U * nL $$
-		(3) pure GA for ablation $$ H_\mathsf{GA} \leftarrow U * nL $$
-		interpret with lessons learned from HM matrix.
-
-	\item [ICS] Adversarial training (does not allow any distance moving) may
-		encourage collapse (a trivial solution to the requirement). What if we
-		loosen the requirement and convert it into a new constraint? For
-		instance, \[
-			L=L_{base}(a,p,n)+\lambda_{1}L(a,\tilde{a},p)+\lambda_{2}L_{triplet}(a,\tilde{a},n)
-		\] where the $L_{base}$ can be either $L_{triplet}$, $L_{rest}$, or
-		$L_{act}$. Question: should we do this for every sample? i.e., \[
-			L_{loosen}(a,p,n)=L_{base}(a,p,n)+\sum_{x\in\{a,p,n\}}L(x,\tilde{x},n_{x})
-		\]
 

### 2021-11-06 appendix.tex
tex

@@
 
+\tableofcontents
+
 \section{Additional Information}
+\label{sec:a}
 
-\noindent\textbf{I. Potential Societal Impact.}
+\subsection{Potential Societal Impact.}
 
-(1) \ul{Security:} Adversarial attacks may raise security considerations on
+\noindent\textbf{I. Security.}
+
+Adversarial attacks may raise security considerations on
 deep learning applications, and even cause negative effect.
@@
 
-(2) \ul{Environment:} Although adversarial training is not
+~\newline
+\noindent\textbf{II. Environment.}
+
+Although adversarial training is not
 environment-friendly due to its high training cost (in terms of more intensive
@@
 
-\noindent\textbf{II. Limitations.}
+\subsection{Limitations.}
+
+\noindent\textbf{I. Assumptions.}
 
@@
 
-(4) \ul{A factor that influence the performance of our approach, namely
-backbone model.}
+~\newline
+\noindent\textbf{II. Performance-Sensitive Factors.}
+
+(1) \ul{Backbone deep neural network model.}
 
@@
 
-(5) \ul{A factor that influence the performance of our approach, namely
-adversarial training budget $\eta$.}
+Adversarial training requires more time and GPU memory than regular training.
+%
+The adversarial training of ResNet-18 with our method requires about 7\~{}10GB
+of memory per GPU in distributed data parallel mode, which is affordable to
+most researchers in the community.
+%
+Adversarial training of ResNet-50 requires much more than 12GB of memory per
+GPU, which will make it harder for some readers to reproduce the results
+and compare.
+
+(2) \ul{Adversarial training budget $\eta$.}
 
@@
 
+(3) \ul{Source hardness $H_\mathsf{S}$ and destination hardness
+$H_\mathsf{D}$.}
+
+The source hardness $H_\mathsf{S}$ depends on triplet sampling strategy, which
+is another research topic in the DML field.
+%
+The available triplet sampling strategies includes Random, Semihard, Softhard,
+Distance-weighted, as well as within-batch Hardest sampling strategies.
+%
+We conduct experiments and figure out an appropriate choice in our experiments.
+
+The range of choices for $H_\mathsf{D}$ is wider than that of $H_\mathsf{S}$.
+%
+When we use another benign sample triplet to calculate $H_\mathsf{D}$, the
+``another benign sample triplet'' can be sampled with the existing triplet
+sampling strategies as well.
+%
+We tested every combination of sampling strategies in our experiments.
+%
+Besides, $H_\mathsf{D}$ can be a pseudo-hardness function in order to avoid
+disadvantages (discussed in our approach) of using another benign triplet as
+reference.
+%
+Graduate Adversary is a family of such pseudo-hardness functions, and Linear
+Graduate Adversary (LGA) is a simple and straightforward example which is
+already effective.
+%
+Although $H_\mathsf{D}$ can be a constant as well, such choice lacks
+flexibility and is only used for demonstrating the advantage of LGA in our
+experiments.
+
+~\newline
 \noindent\textbf{III. Use of Existing Assets.}
@@
 \section{More Technical and Design Details}
+\label{sec:b}
 
@@
 
+~\newline
 \noindent\textbf{II. Embedding-Shifted Triplet (EST).}~\cite{advrank}
@@
 
-\ul{Relationship with HM:}
+\ul{(1) Relationship with HM:}
+
+Since EST only aims to maximize the embedding move distance off its original
+location without specifying any direction, it leads to a random hardness value.
 %
-Since EST only aims to maximize the embedding move distance off its original
-location without specifying any direction, it leads to a random hardness
-value.
+The expectation $E[H(\cdot)]$ of its resulting adversarial triplet is expected
+to be close to $E[H_\mathsf{S}]$.
 %
@@
 %
-Namely, EST merely indirectly increase the hardness of the training
-triplet, and may even decrease its hardness.
+Namely, EST merely indirectly increase the hardness of the training triplet,
+and may even decrease its hardness.
 %
@@
 
+~\newline
 \noindent\textbf{III. Anti-Collapse Triplet (ACT).}~\cite{robrank}
@@
 
-\ul{Relationship with HM:}
+\ul{(1) Relationship with HM:}
 
-\oo{todo}
+When ACT successively ``collapses'' the positive and negative embedding
+vectors together, the hardness will be zero, \ie, $E[H(\cdot)]=0$.
+%
+But ACT is not equivalent to $HM[\cdot,0]$ because the two methods have
+different objectives and use different gradients.
+%
+Besides, in order to avoid the ``misleading gradients''~\cite{robrank}, ACT
+fixes the anchor and only perturb the positive and negative samples, which
+makes the objective for creating adversarial examples more difficult to
+optimize in practice.
+%
+In brief, ACT is also indirectly increasing the loss value, suffering from
+inefficient adversarial learning.
 
-However, compared to the standard min-max adversarial training
-paradigm~\cite{madry}, these methods merely indirectly increase the loss value,
-and thus, suffer from inefficient learning because the adversary is not strong
-enough.
+~\newline
+\noindent\textbf{IV. Hardness Manipulation (HM).}
 

### 2021-11-06 appendix.tex
tex

@@
 experiments.
+
+The $H_\mathsf{S}$ and $H_\mathsf{D}$ are the only two tunables of Hardness
+Manipulation.
+
+(4) \ul{Parameters in $g_\mathsf{LGA}$ and $g_\mathsf{B}$.}
+
+A constant $u$ is used to normalize the loss value of the previous training
+iteration $\ell_{t-1}$ into $\bar{\ell}_{t-1}\in[0,1]$.
+%
+The constant is empirically selected as $u=\gamma$ in our experiment.
+%
+According to our observation, the loss value will quickly decrease below
+$\gamma$, and will remain in the $[0,\gamma]$ range for the whole training
+process.
+%
+If we set $u$ to a larger constant than $\gamma$, the normalized loss
+$\bar{\ell}_{t-1}$ will be smaller, and results in stronger adversarial
+examples through HM and harms the model performance on benign examples.
+
+A parameter $\xi$ is used by $g_\mathsf{B}$ to slightly boost a given
+$H_\mathsf{D}$ calculated from another benign triplet.
+%
+As mentioned in the experiments section, $\xi$ is set to $0.1$ in our
+experiment.
+%
+We refrain from conducting further parameter search because $g_\mathsf{B}$
+is only proposed to demonstrate that the problem in the late phase of
+training can be alleviated in our step-by-step description of our approach.
+%
+And $g_\mathsf{B}$ does not alleviate the problem in the early phase of
+training, and hence it does not belong to Graduate Adversary.
+%
+The function $g_\mathsf{B}$ is not a key point.
+
+Our LGA function $g_\mathsf{LGA}$ reuses the triplet margin parameter $\gamma$
+in order to remain in the range of Semihard, \ie, $-\gamma<g_\mathsf{LGA}<0$.
+%
+Apart from this, LGA is parameter-free.
+
+(5) \ul{Weight constant $\lambda$ of ICS loss term $L_\text{ICS}$.}
+
+The weight constant $\lambda$ is set as $0.5$ by default, and $0.05$ on SOP.
+%
+As demonstrated in the experiments, there is a trade-off between robustness and
+performance on benign examples when tuning the $\lambda$ parameter.
+%
+Our experiments demonstrate that the ICS loss term is effective in improving
+adversarial training efficiency and model robustness, but in practice, the
+adopters of our method may need to re-evaluate the trade-off between
+performance and robustness, and ajudst $\lambda$ accordingly.
 

### 2021-11-06 appendix.tex
tex

@@
 
-\subsection{Potential Societal Impact.}
+\subsection{Potential Societal Impact}
 
@@
 
-\subsection{Limitations.}
+\subsection{Limitations of Our Method}
 
@@
 
-\section{More Technical and Design Details}
+\section{More Technical Details}
 \label{sec:b}
 
-\noindent\textbf{I. Hardware and Software Platform.}
+\subsection{Hardware and Software Platform}
 
-We conduct the experiments with two Nvidia Titan Xp GPUs under the Ubuntu 16.04
-operating system with PyTorch 1.8.2 in distributed data parallel mode.
+We conduct the experiments with two Nvidia Titan Xp GPUs (12GB of memory each)
+under the Ubuntu 16.04 operating system with PyTorch 1.8.2 in distributed data
+parallel mode.
 
-~\newline
-\noindent\textbf{II. Embedding-Shifted Triplet (EST).}~\cite{advrank}
+\subsection{State-of-The-Art Defenses}
+
+\noindent\textbf{I. Embedding-Shifted Triplet (EST).}~\cite{advrank}
 
@@
 ~\newline
-\noindent\textbf{III. Anti-Collapse Triplet (ACT).}~\cite{robrank}
+\noindent\textbf{II. Anti-Collapse Triplet (ACT).}~\cite{robrank}
 
@@
 
-~\newline
-\noindent\textbf{IV. Hardness Manipulation (HM).}
+\subsection{Hardness Manipulation (HM)}
+
+\oo{todo}
 

### 2021-11-06 appendix.tex
tex

@@
 \subsection{Potential Societal Impact}
+\label{sec:a1}
 
@@
 \subsection{Limitations of Our Method}
+\label{sec:a2}
 
@@
 
-\oo{todo}
+	 fix the anchor like ACT?
+		not quite helpful. not necessary.
 
-%\begin{enumerate}[noitemsep, label={Q{\arabic*}.}]
-\begin{enumerate}[noitemsep]
-		%
-	\item \ul{\it There is only $L_\text{T}(\va, \tilde{\va}, \vp)$ in the ICS
+	 What if we mix HM(RM) and HM(SM)?
+		works but not good enough.
+
+	 Note, naive combination of benign training and adv train does not lead to better result, why? mix 0.5
+
+\subsection{Graduate Adversary}
+
+	 Another example for the GA pseudo-hardness function family?
+		sqaure and sqrt.
+
+	 Loss normalization with $u$?
+
+\subsection{Intra-Class Structure (ICS)}
+
+	 Gradient in figure 5?
+
+	\ul{\it There is only $L_\text{T}(\va, \tilde{\va}, \vp)$ in the ICS
 		term.  Is it possible to introduce any other triplet combinations among
@@
 
-	\item Gradient in figure 5?
+	 Why not aa~p~ in ICS?
+		less adversarial, further.
 
-	\item Why not aa~p~ in ICS?
-		less adversarial, further.
-	\item Have you tried FAT?
-	\item What if we mix HM(RM) and HM(SM)?
-		works but not good enough.
-	\item Another example for the GA pseudo-hardness function family?
-		sqaure and sqrt.
-	\item Why not ResNet-50?
+	 [ICS] adversarial training that does not allow embedding move may
+		encourage model collapse. Maybe we just apply some loosened restrction
+		such as aap? i.e. $(a,\tilde{a},p;\gamma=0)$.
+
+\subsection{Empirical Robustness Score (ERS)}
+
+\subsection{Experiment and Evaluation}
+
+	 why experiment, 8 step by default
+
+	 Why not ResNet-50?
 		ttx and video memory.
-	\item fix the anchor like ACT?
-		not quite helpful. not necessary.
-	\item Why compare in theoretical time cost instead of walltime cost?
+
+	 Why compare in theoretical time cost instead of walltime cost?
 		Walltime cost does not precisely indicate the true efficiency
@@
 		as well as software / hardware differences.
-	\item full data sheet for tab 2?
+
+	 Complete Table for Sec~4.1 Hardness Selection?
+
+	 full data sheet for tab 2?
 		\cref{tab:srcdest}
 
-	\item Details of existing defense methods?
+	[\xmark] Multicard DDP and single card training leads to different
+		performance, regardless of the exact model of GPUs.
+		%
+		According to the observation, single card training leadss to a lower
+		recall performance and a higher robustness score.
+		%
+		More efficient? This should be ok.
+		%
+		But be careful when doing ablation studies as this will greatly
+		interfere with the conclusions.
 
-	\item Loss normalization with $u$?
+\subsection{Potential Future Work}
 
-	\item Hardware and software platform?
+	 Have you tried FAT?
 
-	\item Complete Table for Sec~4.1 Hardness Selection?
-
-	\item Why not wall time as training cost?
-
-	\item the destination hardness is semihard (or something between semihard
+	 the destination hardness is semihard (or something between semihard
 		and softhard, we leave new sampling strategy for future work).
-
-	\item Note, naive combination of benign training and adv train does not lead to better
-result, why? mix 0.5
-
-	\item why experiment, 8 step by default
-
-\end{enumerate}
 
@@
 \begin{itemize}
-
-	\item [\xmark] Multicard DDP and single card training leads to different
-		performance, regardless of the exact model of GPUs.
-		%
-		According to the observation, single card training leadss to a lower
-		recall performance and a higher robustness score.
-		%
-		More efficient? This should be ok.
-		%
-		But be careful when doing ablation studies as this will greatly
-		interfere with the conclusions.
 
@@
 
-	\item [Q] Is ACT equivalent to $HM(H_\mathsf{S},0)$.
-
 	\item [ICS] should investigate other metric learning loss functions and see
 		how they deal with hierarchy. e.g. MS, LSS, GLift, quadrup, etc.
-
-	\item [ICS] adversarial training that does not allow embedding move may
-		encourage model collapse. Maybe we just apply some loosened restrction
-		such as aap? i.e. $(a,\tilde{a},p;\gamma=0)$.
 

### 2021-11-06 appendix.tex
tex

@@
 locations, \ie,
-$L_\text{EST}=L_\text{T}(\tilde{\va},\tilde{\vp},\tilde{\vn};\gamma)$ where
-$\tilde{\va}=\phi(X+r^*)$, and $r^*=\arg\max_{r}d_\phi(X+r, X)$.
+%
+\begin{equation}
+%
+L_\text{EST}=L_\text{T}(\tilde{\va},\tilde{\vp},\tilde{\vn};\gamma)
+%
+\end{equation}
+%
+where
+$\tilde{\va}=\phi(\mA+\vr^*)$, and $\vr^*=\arg\max_{\vr}d_\phi(\mA+\vr, \mA)$.
 %
@@
 of positive and negative sample, and enforces the model to separate them apart,
-\ie, $L_\text{ACT}=L_\text{T}(\va, \overrightarrow{\vp},
-\overleftarrow{\vn};\gamma)$, where $[\overrightarrow{\vp},\overleftarrow{\vn}]
-=[\phi(X_p+r_p^*), \phi(X_n+r_n^*)]$, and $[r_p^*,r_n^*]=\arg\min_{r_p,r_n}
-d_\phi(X_p+r_p, X_n+r_n)$.
+\ie,
+%
+\begin{align}
+%
+	L_\text{ACT} &=L_\text{T}(\va, \overrightarrow{\vp},
+\overleftarrow{\vn};\gamma),\\
+%
+	[\overrightarrow{\vp},\overleftarrow{\vn}] & =[\phi(\mP+\vr_p^*), \phi(\mN+\vr_n^*)]\\
+%
+	[\vr_p^*,\vr_n^*] &= \argmin_{\vr_p,\vr_n} d_\phi(\mP+\vr_p, \mN+\vr_n).
+%
+\end{align}
 
@@
 \subsection{Hardness Manipulation (HM)}
+
+\noindent\textbf{I. Range of Hardness.}
+
+As reflected in Sec.~3.1 and Fig.~2, the range of $H(\cdot)$ is $[-2, 2]$.
+%
+The embedding vectors have been normalized to the real unit hypersphere
+as pointed out in the manuscript.
+%
+And the range of distance between any two points on the hypersphere is
+$[0,2]$.
+%
+Hence
+%
+\begin{align}
+	& \max H(\mA, \mP, \mN)\\
+	=& \max [d_\phi(\mA, \mP) - d_\phi(\mA, \mN)]\\
+	=& \max [d_\phi(\mA, \mP)] - \min [d_\phi(\mA, \mN)]\\
+	=& 2 - 0,
+\end{align}
+%
+\begin{align}
+	& \min H(\mA, \mP, \mN)\\
+	=& \min [d_\phi(\mA, \mP) - d_\phi(\mA, \mN)]\\
+	=& \min [d_\phi(\mA, \mP)] - \max [d_\phi(\mA, \mN)]\\
+	=& 0 - 2.
+\end{align}
+%
+Namely $H(\cdot)\in[-2,2]$. Meanwhile, since
+%
+\begin{equation}
+%
+L_\text{T}(\mA, \mP, \mN; \gamma) = \max(0, H(\mA, \mP, \mN) + \gamma),
+%
+\end{equation}
+%
+we have $L_\text{T}\in[0, 2+\gamma]$.
 

### 2021-11-06 appendix.tex
tex

@@
 
+~\newline
+\noindent\textbf{II. Parameters or Adjustable Items}
+
+The only two tunables in HM are $H_\mathsf{S}$ and $H_\mathsf{D}$.
+%
+They are further discussed in the previous section in this supplementary
+material (see the ``Performance-Sensitive Factors'' part of the previous
+section).
+
+Since PGD~\cite{madry} is adopted for optimizing the objective of HM, the
+PGD parameters (including perturbation budget $\varepsilon$, maximum step
+$\eta$, as well as step size $\alpha$) will also influence the result.
+%
+We following the parameter setting following the state-of-the-art
+defense~\cite{robrank} for fair comparison.
+
 	 fix the anchor like ACT?

### 2021-11-06 appendix.tex
tex

@@
 
-\subsection{Hardware and Software Platform}
-
-We conduct the experiments with two Nvidia Titan Xp GPUs (12GB of memory each)
-under the Ubuntu 16.04 operating system with PyTorch 1.8.2 in distributed data
-parallel mode.
-
 \subsection{State-of-The-Art Defenses}
@@
 \subsection{Empirical Robustness Score (ERS)}
+
+\subsection{Hardware and Software Platform}
+
+We conduct the experiments with two Nvidia Titan Xp GPUs (12GB of memory each)
+under the Ubuntu 16.04 operating system with PyTorch 1.8.2 in distributed data
+parallel mode.
+%
+Note, the training result of all methods in distributed data parallel mode
+slightly differs from the result obtained in single-GPU mode, due to the
+asynchronized gradient updates in the distributed mode (this is a common
+phenomenon in distributed deep learning).
+%
+In fact, our method can be even more efficient in single-GPU mode thanks to the
+synchornized gradients, but single-GPU mode will be extremely time consuming
+(more than a week for a single run of the most time-consuming experiment).
+%
+All of our experiments are conducted in distributed data parallel mode for ease
+of comparison, as well as controlling the time cost.
 

### 2021-11-06 appendix.tex
tex

@@
 \subsection{Hardness Manipulation (HM)}
+\label{sec:b2}
 
@@
 %
-Hence
+Hence the extreme values are:
 %
@@
 
-The only two tunables in HM are $H_\mathsf{S}$ and $H_\mathsf{D}$.
+The only two adjustable items in HM are $H_\mathsf{S}$ and $H_\mathsf{D}$.
 %
@@
 %
-We following the parameter setting following the state-of-the-art
+We use the parameter setting following the state-of-the-art
 defense~\cite{robrank} for fair comparison.
 
-	 fix the anchor like ACT?
-		not quite helpful. not necessary.
+In most experiments that demonstrate the effectiveness of our method, the
+$\eta$ is set as $8$ because the ERS start to plateau with a larger $\eta$
+according to our observation.
+
+~\newline
+\noindent\textbf{III. HM and ACT}
+
+ACT~\cite{robrank} is proposed in order to address the ``misleading gradient''
+and ``inefficient mini-batch exploitation'' problems.
+%
+HM does not push the embeddings towards arbitrary directions, and hence does
+not suffer from both issues.
+%
+On the other hand, ACT does not perturb the anchor sample, and the same
+can be done in HM.
+%
+When the anchor sample is unperturbed, adversarial training with HM leads to
+a higher performance on benign examples but a lower robustness.
+%
+Unlike perturbing $(\mA, \mP, \mN)$ altogether, only perturbing $(\mP, \mN)$
+leads to a weaker adversarial examples, and hence lower robustness.
+%
+Our first priority is to improve model robustness, so the case with fixed
+anchor is omitted from manuscript to avoid complexity.
+
+~\newline
+\noindent\textbf{IV. Mixing HM[$\mathcal{R},\mathcal{M}$] and
+HM[$\mathcal{S},\mathcal{M}$]}
 
@@
 \subsection{Experiment and Evaluation}
-
-	 why experiment, 8 step by default
 

### 2021-11-06 appendix.tex
tex

@@
 
-The $H_\mathsf{S}$ and $H_\mathsf{D}$ are the only two tunables of Hardness
-Manipulation.
+The $H_\mathsf{S}$ and $H_\mathsf{D}$ are the only two adjustable items of
+Hardness Manipulation.
 
@@
 \subsection{State-of-The-Art Defenses}
+\label{sec:b1}
 
@@
 
-	 What if we mix HM(RM) and HM(SM)?
-		works but not good enough.
-
-	 Note, naive combination of benign training and adv train does not lead to better result, why? mix 0.5
+According to the experimental results, HM[$\mathcal{R},\mathcal{M}$] achieves 
+a high ERS and adversarial training efficiency, but suffers from a low R@1.
+%
+HM[$\mathcal{S},\mathcal{M}$] achieves a high R@1, but its ERS and efficiency
+could be further improved.
+%
+They can be mixed for adversarial training with a probability $p$ to combine
+their advantages, but the eventual overall performance is still lower than
+that of HM[$\mathcal{S},g_\mathsf{LGA}$] according to our observation.
 
 \subsection{Graduate Adversary}
+\label{sec:b3}
 

### 2021-11-06 appendix.tex
tex

@@
 
-	 Another example for the GA pseudo-hardness function family?
-		sqaure and sqrt.
+\noindent\textbf{I. Parameters or Adjustable Items}
 
-	 Loss normalization with $u$?
+The parameters, namely $u$ and $\xi$ are discussed in the previous section
+of this supplementary material, see ``Performance-Sensitive Factors''.
+
+~\newline
+\noindent\textbf{II. Non-linear Graduate Adversary}
+
+In the manuscript, Linear Graduate Adversarial is demonstrated effective,
+and more complicated choices are left for future work.
+%
+Here we provide two Non-linear Graduate Adversary examples, namely
+$g_\mathsf{2}$ and $g_\mathsf{1/2}$, as follows:
+%
+\begin{align}
+	g_\mathsf{2}(\cdot)   &= -\gamma \cdot (\bar{\ell}_{t-1})^{2}  &~ \in [-\gamma,0]\\
+	g_\mathsf{1/2}(\cdot) &= -\gamma \cdot (\bar{\ell}_{t-1})^{1/2} &~ \in [-\gamma, 0]
+\end{align}
+%
+Compared to LGA, $g_\mathsf{2}$ is more ``eager'' to result in strong adversarial
+examples in the early phase of training, while $g_\mathsf{1/2}$ is more ``conservative''
+in creating strong adversarial examples in the early phase of training
+(adversarial examples from HM are stronger if the function value is closer to $0$).
 

### 2021-11-07 appendix.tex
tex

@@
 
-	 Gradient in figure 5?
+\noindent\textbf{I. Parameters or Adjustable Items}
+
+The ICS loss term can be appended to the loss for adversarial training.
+%
+The only parameter for ICS loss term is the weight constant $\lambda$.
+%
+The selection of this parameter is discussed in the previous section of this
+supplementary material (see ``Performance-Sensitive Factors'').
+
+~\newline
+\noindent\textbf{II. Gradients in Fig.~5 (a) in Manuscript}
+
+According to \cite{robrank}, when the embedding vectors are normalized onto the
+real unit hypersphere and Euclidean distance is used, the gradients of the
+triplet loss with respect to the anchor, positive, and negative embedding
+vectors are respectively:
+%
+\begin{align}
+%
+	\frac{\partial L_\text{T}}{\partial \va} &= \frac{\va - \vp}{\|\va - \vp\|}
+	- \frac{\va - \vn}{\| \va - \vn \|} \\
+	\frac{\partial L_\text{T}}{\partial \vp} &= \frac{\vp - \va}{\|\va - \vp\|} \\
+	\frac{\partial L_\text{T}}{\partial \vn} &= \frac{\va - \vn}{\|\va - \vn\|},
+%
+\end{align}
+%
+when $L_\text{T}>0$.
+And the above equations have been reflected in Fig.~5 (a) with correct directions.
+
+~\newline
+\noindent\textbf{III. Alternative Design for Exploiting Sextuplet}
 
@@
 
-\subsection{Experiment and Evaluation}
+\subsection{Experiments and Evaluation}
 
@@
 		and softhard, we leave new sampling strategy for future work).
+
+	 [\xmark] Faster training (algorithm tweak) based FAT/other | this is
+		a dead end. ACT has a different loss function to the outer minimization
+		problem, and hence result in different gradient and we cannot reuse
+		these gradients for algorithms like free adversarial training.
+		Re-calculating the gradients we need would simple double the
+		computational cost of the algorithm and diminish the gain from Free
+		Adversarial Training. We are no longer using the core benefit of FAT in
+		this way. In contrast, the AMD / AMDhm formulation can benefit from
+		this setup. | Further experiments suggest very weak robustness and the
+		models are very prone to collapse due to the non-zero initial delta
+		(results in too hard adversarial example).  | gradient approximation
+		does not look convincing. triplet gradient and ACT gradient does not
+		look convertible.
+
+	 [\cmark] implement FAT for faster exp iteration | works on toy
+		dataset. too prone to collapse. if we try to avoid model collapse, the
+		adversarial robustness will decrease significantly.
+
+	 [\cmark] what if we use stopat for RAMD? | similar effect to amdsemi.
+		misguiding gradient does not significantly affect AMD defense. So it
+		is not quite necessary.
 
@@
 
-	\item [\xmark] do we fix the anchor like ACT? | negative result observed
-		on fashion-mnist (rhetrm).
-
-	\item [\xmark] What if we truncate $H_D$. Clamp it with $\min=-\gamma$.
-		| clipping leads to negative effect on fashion-mnist. (ghmetrm 8)
-		Not every triplet is useful in this regard. Not all of them have to
-		contribute to the final gradient.
-
-	\item [\xmark] Re-design Gradual Adversary (Linear Addition)
-		\[
-			\big(1-\frac{\text{Clip}_0^{U_L}[l_{t-1}]}{U_L} \big)\times U_H
-		\]
-		Increase $E[H]$ to $E[H]+\alpha U_H$. $E[H]$ is expected to decrease
-		with a well-learned model. So without GA, the strength of adversary
-		will decrease. | Linear GA has a negative effect as observed on
-		Fashion-MNIST.
-
 	\item [-] effectiveness of AMD Semi is to be verified. | as effective
@@
 
-	\item [\xmark] mixing amdsemi and act for adversarial training. They are good
-		at different aspects. | not necessary for now. harms novelty.
-
-	\item [\xmark] Combine and even better. | Mixing ACT and AMDsemi does result
-		in clearly better results. It's on par with AMDsemi. Are they really
-		that different?
-
 	\item [\xmark] re-design Gradual Adversary for HM based on that for the amdsemi. |
@@
 
-	\item [\cmark] revise HM. align dap dan directly instead of the loss.
-
 	\item [\cmark] \checkmark dynamically changing schedule for amdsemi? |
@@
 
-	\item [\cmark] (codecheck) does amd really honour the pgditer parameter? |
-		direct adoptation of madry defense is really prone to model collapse.
-
-	\item [\xmark] MSE attack? | TMA is already close enough to it.
-
-	\item [\xmark] Faster training (algorithm tweak) based FAT/other | this is
-		a dead end. ACT has a different loss function to the outer minimization
-		problem, and hence result in different gradient and we cannot reuse
-		these gradients for algorithms like free adversarial training.
-		Re-calculating the gradients we need would simple double the
-		computational cost of the algorithm and diminish the gain from Free
-		Adversarial Training. We are no longer using the core benefit of FAT in
-		this way. In contrast, the AMD / AMDhm formulation can benefit from
-		this setup. | Further experiments suggest very weak robustness and the
-		models are very prone to collapse due to the non-zero initial delta
-		(results in too hard adversarial example).  | gradient approximation
-		does not look convincing. triplet gradient and ACT gradient does not
-		look convertible.
-
-	\item [\cmark] implement FAT for faster exp iteration | works on toy
-		dataset. too prone to collapse. if we try to avoid model collapse, the
-		adversarial robustness will decrease significantly.
-
-	\item [\cmark] what if we use stopat for RAMD? | similar effect to amdsemi.
-		misguiding gradient does not significantly affect AMD defense. So it
-		is not quite necessary.
-
 \end{enumerate}

### 2021-11-07 appendix.tex
tex

@@
 
+\oo{experiments?}
+
 \subsection{Intra-Class Structure (ICS)}
@@
 
+Let $\tilde{\va}$, $\tilde{\vp}$, and $\tilde{\vn}$ be $\phi(\mA+\hat{\vr}_a)$,
+$\phi(\mP+\hat{\vr}_p)$ and $\phi(\mN+\hat{\vr}_n)$ respectively.
+%
+In our proposed ICS loss term, only $(\va, \tilde{\va}, \vp)$ are involved.
+%
+Other alternative sections of triplets from the sextuplet are also
+possible.
+
+\ul{(1) Why not use $L_\text{T}(\va, \tilde{\va}, \tilde{\vp})$? }
+
+As shown in Fig.~5 (c) in the manuscript, the position of $\tilde{\vp}$ is
+always further away from both $\va$ and $\tilde{\va}$ than $\vp$ due to
+the gradient direction.
+%
+Thus, the loss term in the question is not as effective as $L_\text{ICS}$.
+
+	 Why not aa~p~ in ICS?
+		less adversarial, further.
+
 	\ul{\it There is only $L_\text{T}(\va, \tilde{\va}, \vp)$ in the ICS
@@
 		on benign examples, but drastically reduce robustness.
-
-	 Why not aa~p~ in ICS?
-		less adversarial, further.
 

### 2021-11-07 appendix.tex
tex

@@
 
-	 Why not aa~p~ in ICS?
-		less adversarial, further.
+\ul{(2) What if $L_\text{T}(\va, \vp, \vn)$ is used? Namely, the regular training
+and adversarial training are mixed together.}
 
-	\ul{\it There is only $L_\text{T}(\va, \tilde{\va}, \vp)$ in the ICS
-		term.  Is it possible to introduce any other triplet combinations among
-		the six samples (\ie, three benign and three adversarial)?}\\
+According to our observation, mixing regular training and adversarial training
+leads to better R@1 but very drastic robustness degradation for both ACT and
+our proposed defense.
+
+\ul{(3) Why not use the symmetric counterpart of $L_\text{ICS}$, \ie,
+		$L_\text{T}(\vp, \tilde{\vp}, \va)$?}
+
+Every sample in the training dataset will be used as anchor for once per
+epoch.
 %
-		A: We have tried some other combinations, and they are either not
-		effective, or causing negative effects.
+Such symmetric loss term is duplication to $L_\text{ICS}$ and is
+not necessary.
 %
-		In particular, (1) adding $L_\text{T}(\va, \vp, \vn)$ on top of the
-		adversarial training loss
-		$L_\text{T}(\tilde{\va},\tilde{\vp},\tilde{\vn})$ can improve
-		performance on benign examples, but will drastically reduce model
-		robustness;
+Experimental results suggest negligible difference.
+
+\ul{(4) $\tilde{\vn}$ is very close to $\va$ in Fig.~5 in manuscript.
+Why not use $L_\text{T}(\va, \tilde{\va}, \tilde{\vn})$?}
+
+The loss term in question is enforcing inter-class structure instead of
+intra-class structure.
 %
-		(2) $L_\text{T}(\vp, \tilde{\vp}, \va)$ \oo{is duplicated, not necessary.}
+Besides, experimental results suggest negligible difference.
 %
-		(3) $L_\text{T}(\va, \tilde{\va}, \tilde{\vn})$ no distinct difference.
-		%
-		(4) $L_\text{T}(\va, \vp, \tilde{\vn})$ leads to better performance
-		on benign examples, but drastically reduce robustness.
+We speculate this loss term is duplicated to the adversarial training term,
+\ie, $L_\text{T}(\tilde{\va}, \tilde{\vp}, \tilde{\vn})$, which enforces
+inter-class structure in a stronger manner.
 
-	 [ICS] adversarial training that does not allow embedding move may
-		encourage model collapse. Maybe we just apply some loosened restrction
-		such as aap? i.e. $(a,\tilde{a},p;\gamma=0)$.
+\ul{(5) Similar to question (4), why not use $L_\text{T}(\va, \vp, \tilde{\vn})$ ?}
+
+According to our observation, it leads to better R@1 performance on benign
+examples, but drastically reduce the robustness.
 

### 2021-11-07 appendix.tex
tex

@@
 
+\oo{todo}
+
 \subsection{Hardware and Software Platform}
@@
 
-	 Why not ResNet-50?
-		ttx and video memory.
+\noindent\textbf{I. Training Cost}
 
-	 Why compare in theoretical time cost instead of walltime cost?
-		Walltime cost does not precisely indicate the true efficiency
-		of a defense method, and may even result in unfair comparison.
-		isolate the discrepancy from implementation and engineering tricks,
-		as well as software / hardware differences.
+In the manuscript, the training cost of adversarial training is caluclated as
+$\eta+1$, which is a theoretical number of forward-backward propagation
+involved in each iteration of the training process.
+%
+The wall time is not used, because the wall time is noisy, and will be affected
+by many irrevevant factors which eventually makes the result uncomparable or
+unfair.
+%
+The factors that affect the wall time for adversarial training include but are
+not limited to:
+%
+(1) GPU Performance. For instance, the wall time reported based on eight Nvidia
+A100 GPUs will not be valuable for readers who do not have access to the same
+hardware;
+%
+(2) System load when training, CPU performance, and I/O device performance;
+%
+(3) Code implementation and engineering tricks. Well-optimized code will
+consume less time.
+%
+Namely, the wall time is a noisy measure of training cost which will render
+invalid comparison or unfair comparison.
+%
+In contrast, the training cost measure ($\eta+1$) in the manuscript has
+isolated all irrelevant factors.
 
-	 Complete Table for Sec~4.1 Hardness Selection?
+~\newline
+\noindent\textbf{II. Complete Experimental Results for Tab.~2 in Manuscript}
 
-	 full data sheet for tab 2?
-		\cref{tab:srcdest}
+They can be found in \cref{tab:srcdest} of this supplementary material.
+
+\hrule
 
@@
 
+\begin{comment}
 \section{Visualizations}
-
 Visualize robustness through the image retrieval task.
+\end{comment}
 

### 2021-11-07 appendix.tex
tex

@@
 
+For reference, the adversarial training cost of RN18 with two Nvidia Titan Xp
+GPUs in terms of wall time is summarized in
+%
+\oo{todo}
+
 ~\newline
-\noindent\textbf{II. Complete Experimental Results for Tab.~2 in Manuscript}
+\noindent\textbf{II. Complete Results for Tab.~2 in Manuscript}
 
-They can be found in \cref{tab:srcdest} of this supplementary material.
-
-\hrule
-
-	[\xmark] Multicard DDP and single card training leads to different
-		performance, regardless of the exact model of GPUs.
-		%
-		According to the observation, single card training leadss to a lower
-		recall performance and a higher robustness score.
-		%
-		More efficient? This should be ok.
-		%
-		But be careful when doing ablation studies as this will greatly
-		interfere with the conclusions.
+Complete experimental results for ``Tab.~2: Combinations of Source \&
+Destination Hardness. \ldots'' can be found in \cref{tab:srcdest} of this
+supplementary material.
 
 \subsection{Potential Future Work}
+
+\noindent\textbf{I. Further Improving Efficiency of HM}
+
+Being able to gain a higher robustness at a lower training cost indiates a
+higher efficiency.
+%
+As discusssed in Sec.~3.1, one potential way to further improve the adversarial
+training efficiency is to incorporate adversarial training acceleration methods
+such as Free Adversarial Training~\cite{freeat} (for classification) into our
+DML adversarial training.
 

### 2021-11-07 appendix.tex
tex

@@
 
-(1) \ul{The assumption that an ``intermediate point'' exists between regular
+(1) \ul{Triplet Assumption.}
+
+This paper assums training with sample triplets.
+%
+When other deep metric learning loss functions are used, our proposed method
+may not be compatible.
+%
+This assumption is a limitation of our method.
+%
+Adversarial training with other DML loss functions is unexplored and is left
+for future study.
+
+(2) \ul{The assumption that an ``intermediate point'' exists between regular
 training of DML model and min-max adversarial training of DML model.}
-(discussed in \cref{sec:1}; this is the motivation of HM)
+(discussed in Sec.~1; this is the motivation of HM)
 
@@
 
-(2) \ul{The assumption on optimization of the HM objective.}
-(discussed in \cref{sec:31})
+(3) \ul{The assumption on optimization of the HM objective.}
+(discussed in Sec.~3.1)
 
@@
 
-(3) \ul{The assumption that $H_\mathsf{D}$ should remain Semihard.}
-(discussed in \cref{sec:32})
+(4) \ul{The assumption that $H_\mathsf{D}$ should remain Semihard.}
+(discussed in Sec.~3.2)
 
@@
 
+\input{tab-srcdest.tex}
+
 Complete experimental results for ``Tab.~2: Combinations of Source \&
@@
 
-Being able to gain a higher robustness at a lower training cost indiates a
+Being able to gain a higher robustness at a lower training cost indicates a
 higher efficiency.
 %
-As discusssed in Sec.~3.1, one potential way to further improve the adversarial
+As discussed in Sec.~3.1, one potential way to further improve the adversarial
 training efficiency is to incorporate adversarial training acceleration methods
-such as Free Adversarial Training~\cite{freeat} (for classification) into our
-DML adversarial training.
+such as Free Adversarial Training (FAT)~\cite{freeat} (for classification) into
+our DML adversarial training.
 
-	 Have you tried FAT?
+We have tried to direct adopt FAT for adversarial training of DML model.
+%
+According to our observation, the model (RN18 on CUB dataset) is still prone
+to collapse because the FAT algorithm can be interpreted as to maintain
+a universal (agnostic to sample) perturbation that can maximize the loss.
+%
+Simple workarounds such as decaying the perturbation does not address this
+issue.
 
-	 the destination hardness is semihard (or something between semihard
-		and softhard, we leave new sampling strategy for future work).
+Thus, our conclusion is that a non-trivial modification is still required
+to incorporate the idea of FAT into adversarial training of DML model.
 
-	 [\xmark] Faster training (algorithm tweak) based FAT/other | this is
-		a dead end. ACT has a different loss function to the outer minimization
-		problem, and hence result in different gradient and we cannot reuse
-		these gradients for algorithms like free adversarial training.
-		Re-calculating the gradients we need would simple double the
-		computational cost of the algorithm and diminish the gain from Free
-		Adversarial Training. We are no longer using the core benefit of FAT in
-		this way. In contrast, the AMD / AMDhm formulation can benefit from
-		this setup. | Further experiments suggest very weak robustness and the
-		models are very prone to collapse due to the non-zero initial delta
-		(results in too hard adversarial example).  | gradient approximation
-		does not look convincing. triplet gradient and ACT gradient does not
-		look convertible.
-
-	 [\cmark] implement FAT for faster exp iteration | works on toy
-		dataset. too prone to collapse. if we try to avoid model collapse, the
-		adversarial robustness will decrease significantly.
-
-	 [\cmark] what if we use stopat for RAMD? | similar effect to amdsemi.
-		misguiding gradient does not significantly affect AMD defense. So it
-		is not quite necessary.
-
-\input{tab-srcdest.tex}
+On the other hand, ACT~\cite{robrank} has a different inner loss function to
+the outer minimization problem, and hence result in different gradients in the
+inner and outer problems.
+%
+In this way, the gradients cannot be reused by FAT.
+%
+Re-calculating the gradients we need would simply double the
+computational cost of the algorithm and halves the efficiency gain from FAT.
 
 \begin{comment}
-\section{Visualizations}
-Visualize robustness through the image retrieval task.
+FAT works on toy dataset only for adversarial DML.
+
+Further experiments suggest very weak robustness and the
+models are very prone to collapse due to the non-zero initial delta
+(results in too hard adversarial example).
+
+Gradient approximation does not work. Triplet gradient and ACT
+gradient are convertible.
+
+Does the new generic HM work under FAT?
+	Previous FAT leads to collapse because (even if in the amdsemi +fat
+	experiment due to implementation issue) the delta is going to be universal
+	so that for every input $x$ it will increase $H[L(x)]$ as much as possible.
+	This is too prone to lead to collpase. Can we reuse the gradient for 
+	Hardness Manipulation then? We linearly scale down the delta?
+	We want to minimize $E[|H_{src}(x)-H_{dst}(x)|]$ (to a specified hardness).
 \end{comment}
 
-\section{My Memo}
+~\newline\textbf{II. More Appropriate Destination Hardness}
 
-\subsection{To be investigated}
+We drew the conclusion that ``adversarial triplets should remain Semihard''
+based on the empirical experimental results in Tab.~2 in the manuscript.
+%
+However, a better choice for $H_\mathsf{D}$ may exist between ``Semihard''
+and ``Softhard''.
+%
+Exploration of a better source triplet sampling strategy for adversarial
+training, as well as a better hardness range for adversarial triplets
+may also be a direction for further robustness improvement.
+%
+In the manuscript, we only use the existing sampling methods in order to focus
+on our contributions.
 
-\begin{itemize}
+~\newline\textbf{III. Other DML Loss Functions}
 
-	\item [T] Sam's idea is interesting. By incorporating the idea of
+Although the traditional triplet loss could reach the state-of-the-art
+performance with an appropriate sampling strategy, many other DML loss
+functions are proposed.
+%
+Adversarial trainig with other DML loss functions is unexplored.
+%
+New metric learning loss functions oriented for adversarial training is
+also left for future study.
+
+\oo{[TODO] arxiv 2105.04906 for collapse issue.}
+
+\begin{comment}
+
+ [T] By incorporating the idea of
 	on-manifold adversarial example to adversarial training, the
@@
 
-	\item [T] Face recognition methods such as ArcFace can be used for
+ [T] Face recognition methods such as ArcFace can be used for
 	metric learning.
-		%
-		We have an opportunity of smooth transition to defense for face
-		recognition methods.
 	%
@@
 
-	\item [TODO] arxiv 2105.04906 for collapse issue.
+ [T] Unsup learning with DML robustness.
 
-	\item [\cmark] We don't have to mix HM(R,M) and HM(S,M).
-
-	\item [ICS] should investigate other metric learning loss functions and see
-		how they deal with hierarchy. e.g. MS, LSS, GLift, quadrup, etc.
-
-	\item [?] verify model collapse. are the parameters really going towards zero?
-
-	\item [T] does the new generic HM work under FAT?
-		Previous FAT leads to collapse because (even if in the amdsemi +fat
-		experiment due to implementation issue) the delta is going to be universal
-		so that for every input $x$ it will increase $H[L(x)]$ as much as possible.
-		This is too prone to lead to collpase. Can we reuse the gradient for 
-		Hardness Manipulation then? We linearly scale down the delta?
-		We want to minimize $E[|H_{src}(x)-H_{dst}(x)|]$ (to a specified hardness).
-
-	\item [T] Face verification (biometrics) and DML robustness.
-
-	\item [T] Unsup learning with DML robustness.
-
-	\item [T] APGD as the optimization algorithm? | postpone
-
-	\item [T] benchmark other metric learning loss functions for adversarial
-		training. Can HM or GradualAdversary be adopted for other loss functions?
-
-	\item [T]  what about other types of metric learining loss functions? |
-		investigating (we first make the most classical method work)
-
-	\item [T] Revise and incorporate the state-of-the-art adversarial training
-		acceleration method (\ie, Free Adversarial Training~\cite{freeat},
-		which is designed for classification) into adversarial training of 
-		deep metric learning models. It will greatly improve the efficiency
-		of adversarial training.
-		%
-	\item [T] Benchmark of existing metric learning loss functions under
-		adversarial training scenario, and analyze their different
-		characteristics for future reference.
-		%
-	\item [T] Explore the possibility of proposing a new metric learning loss
-		function oriented for adversarial training, starting from scratch or
-		from an existing metric learning loss.
-		%
-\end{itemize}
-
-\subsection{Lessons Learned}
-
-\input{fat-attempt-1.tex}
-
-\begin{enumerate}
-
-	\item [-] effectiveness of AMD Semi is to be verified. | as effective
-		as ACT, reaches slightly higher ERS. But performs worse than ACT on
-		some attacks, while performs better one some other attacks. | needs to
-		be interpreted.
-
-	\item [\cmark] 7-step PGD (as well as 16-step PGD) and better aligned comparison:
-		compare when these methods reach similar retrieval performance.
-		Meanwhile we can do experiments much faster.
-
-	\item [\cmark] HM method: KL, L2, L2+threshold. L2 is $\|H_s-H_d\|^2$.
-		In L2 the adversarial sample may vibrate around the boundary due to
-		the minimum perturbation precision limit of $1/255$. The attacker
-		may turn to reduce the hardness when $H_s>H_d$. We don't want that
-		to happen.  L2+threshold (ET) is $\|\min(0,H_s-H_d)\|^2$. In this case,
-		the adversarial example will not vibrate around the boundary, and will
-		automatically stop when $H_s>H_d$.
-
-	\item [\xmark] re-design Gradual Adversary for HM based on that for the amdsemi. |
-		\[
-			(1-\frac{\text{prev\_loss}|_0^{2+\beta}}{2+\beta}) \times
-			(\phi - H_\text{dst})\mathbb{I}\{\phi > H_\text{dst}\}
-		\]
-		So that for triplets that are not hard enoguh, when
-		$prevloss \rightarrow 0$, $E[H_\text{dst}]\rightarrow \phi$.
-		| This has a weak effect. Redesign required.
-
-	\item [\cmark] \checkmark dynamically changing schedule for amdsemi? |
-		looks good | the sqrt scheme works the best. (gradually increasing the
-		hardness makes sense)
-
-\end{enumerate}
+ [T] APGD as the optimization algorithm? | postpone.
+	Just shifting robustness of all methods down by a bit.
+	Robust methods are still robust. Unrobust methods are still not robust.
+\end{comment}

### 2021-11-08 appendix.tex
tex

@@
 \appendix
+
+\section*{Supplementary Material}
+
+In this supplementary material, we provide further technical details and
+discussions that are not included in the manuscript due to space limit.
+%
+Discussions required by the author guidelines can also be found in this
+supplementary material.
 
@@
 The adversarial training of ResNet-18 with our method requires about 7\~{}10GB
-of memory per GPU in distributed data parallel mode, which is affordable to
-most researchers in the community.
+of memory per GPU in distributed data parallel mode.
 %
-Adversarial training of ResNet-50 requires much more than 12GB of memory per
-GPU, which will make it harder for some readers to reproduce the results
-and compare.
+%Adversarial training of ResNet-50 requires much more than 12GB of memory per
+%GPU, which will make it harder for some readers to reproduce the results
+%and compare.
 
@@
 
-\noindent\textbf{I. Training Cost}
+\noindent\textbf{I. Detailed Interpretation of Experimental Results}
+
+\ul{(1) Table.~1: ``Mean \& Variance ...'''}
+
+\ul{(2) Table.~2: ``... Source \& Destination Hardness ...''}
+
+\ul{(3) Table.~3: ``Hardness Manipulation ...'' and Fig.~6}
+
+\ul{(4) Table.~4: ``... Graduate Adversary ...'' and Fig.~7}
+
+\ul{(5) Table.~5: ``Intra-Class Structure ...'' and Fig.~8}
+
+\ul{(6) Table.~6: ``... State-of-The-Art ...''}
+
+\oo{todo}
+
+~\newline
+\noindent\textbf{II. Training Cost}
 
@@
 
-For reference, the adversarial training cost of RN18 with two Nvidia Titan Xp
-GPUs in terms of wall time is summarized in
+For reference, the most time-consuming experiment is
+HM[$\mathcal{S},g_\mathsf{LGA}$] on the SOP dataset.
 %
-\oo{todo}
+When $\eta=8$, the experiment takes $32$ hours with two Nvidia Titan Xp GPUs;
+%
+When $\eta=32$, the experiment takes $105$ hours with two Nvidia Titan Xp GPUs.
 
 ~\newline
-\noindent\textbf{II. Complete Results for Tab.~2 in Manuscript}
+\noindent\textbf{III. Complete Results for Tab.~2 in Manuscript}
 
@@
 
+~\newline\textbf{IV. DML \& Classification}
+
+It is unknown how defense methods for DML relates to the classification defense
+task.
+%
+DML is closely related to self-supervised learning.
+%
+It is also unknown if a defense for the supervised learning scenario will
+inspire the defense for unsupervised robust feature learning.
+
 \begin{comment}
@@
 
- [T] Face recognition methods such as ArcFace can be used for
-	metric learning.
-	%
-	Is defense for face recognition missing from the literature?
-
- [T] Unsup learning with DML robustness.
-
  [T] APGD as the optimization algorithm? | postpone.

### 2021-11-08 appendix.tex
tex

@@
 performance and robustness, and ajudst $\lambda$ accordingly.
+
+(6) \ul{Optimization algorithm for adversarial attacks.}
+
+In this paper, PGD~\cite{madry} is adopted as the optimization algorithm for
+creating adversarial examples.
+%
+It is also adopted by the ERS metric~\cite{robrank} for robustness evaluation
+with a collection of white-box attacks.
+%
+In the literature, some other optimization methods exists, such as
+APGD~\cite{apgd}.
+%
+However, we adopt PGD~\cite{madry} to keep aligned with the state-of-the-art
+work for sake of fair comparison.
+
+A replacement of such algorithm for adversarial training will affect the
+model's performance on benign examples and robustness.
+%
+Stronger adversarial examples during adversarial training may further boost the
+robustness of a model, and further reduce the performance on benign examples.
+
+A replacement of such algorithm for ERS evaluation will affect the robustness
+score for all existing methods.
+%
+All existing methods are expected to have a lower (to a certain extent)
+robustness against a stronger algorithm than PGD.
+%
+In this case, a robust method still remains robust, and a not robust method
+remains not robust.
 
@@
 
- [T] APGD as the optimization algorithm? | postpone.
-	Just shifting robustness of all methods down by a bit.
-	Robust methods are still robust. Unrobust methods are still not robust.
 \end{comment}

### 2021-11-08 appendix.tex
svgtex

@@
 for future study.
+
+(2) \ul{Embedding Space Assumption.}
+
+In this paper, we follow the common assumptions of deep metric
+learning~\cite{revisiting} on the embedding space.
+%
+Namely, we assume the embedding vectors are normalized onto the real unit
+hypersphere.
+%
+Meanwhile, the distance function $d(\cdot,\cdot)$ is assumed to be Euclidean
+distance.
+%
+Our formulations are developed on the two assumptions.
+%
+It is unknown whether the proposed method method will be effective on an
+embedding vectors that are NOT normalized.
+%
+And it is unknown whether the proposed method will be effective when
+$d(\cdot,\cdot)$ is replaced as, \eg, cosine distance.
+%
+The gradient directions in Fig.~5 (a) in the manuscript are established on the
+two assumptions (the gradient directions will differ if the two assumptions are
+not satisfied).
+%
+We follow the common choice~\cite{revisiting,robrank} in the two aspects.
+%
+But we acknowledge the effectiveness of our method is unknown when the
+two assumptions are broken.
+%
+And they may become limintations of our method.
 

### 2021-11-08 robdml.tex
app
tesx

@@
 
-Previous works suggest that an appropriate adversary for the inner
+Previous works imply that an appropriate adversary for the inner
 \emph{maximization} problem should increase the loss to an ``intermediate''
@@
 
-The use of existing assets, limitations and societal impact of our method
-are discussed in supplementary material.
+Further technical details, discussions, limitations and societal impact of our
+method are presented in supplementary.
 

### 2021-11-09 robdml.tex
tex

@@
 	% merit
-	It is flexible as regular training and min-max adversarial training
+	It is flexible since regular training and min-max adversarial training
 	are its boundary cases.
@@
 Since training cost is already a serious issue of adversarial training, the
-efficiency in gaining higher adversarial robustness under a fixed budget is
+efficiency in gaining higher adversarial robustness under a lower budget is
 inevitable and important for DML defense.

### 2021-11-09 robdml.tex
tex

@@
 %
-In this case, the \emph{intra-class} structure can be enforced, has been
+In this case, the \emph{intra-class} structure can be enforced, which has been
 neglected by existing methods.
@@
 % contributions
-In brief, our contributions include:
+In brief, our contributions include proposing:
 %
@@
 	%
-	\item {\textit{Hardness Manipulation}} (HM) is proposed as a flexible and
-		efficient tool to create adversarial example triplets for subsequent
-		adversarial training of DML model.
-		%
-	\item \textit{Linear Gradual Adversary} (LGA) is proposed as a
-		pseudo-hardness function for HM, which incorporates our empirical
+	\item {\textit{Hardness Manipulation}} (HM) as a flexible and efficient
+		tool to create adversarial example triplets for subsequent adversarial
+		training of DML model.
+		%
+	\item \textit{Linear Gradual Adversary} (LGA) as a Graduate Adversary, \ie,
+		a pseudo-hardness function for HM, which incorporates our empirical
 		observations and can balance the training objectives during the
@@
 		%
-	\item \textit{Intra-Class Structure} (ICS) loss term is proposed to further
-		improve the DML model robustness, while such possibility is neglected
-		by existing methods. 
+	\item \textit{Intra-Class Structure} (ICS) loss term to further improve
+		model robustness (especially intra-class-wise), while such structure is
+		neglected by existing methods. 
 		%
@@
 %
-Although independent to HM, ACT is incompatible with $L_\text{ICS}$ as it does
-not create an adversarial anchor.
+$L_\text{ICS}$ is independent to HM, but is not incompatible with ACT as it
+does not create adversarial anchor.
 %
@@
 As shown in \cref{tab:ics} and \cref{fig:ics}, $L_\text{ICS}$ consistently
-leads to a higher efficiency in gaining robustness, while retaining a
-good trade-off between ERS and R@1.
+leads to a higher efficiency in gaining robustness (especially
+intra-class-wise), while retaining an acceptable trade-off in R@1.
 

### 2021-11-09 robdml.tex
tex

@@
 %
-$L_\text{ICS}$ is independent to HM, but is not incompatible with ACT as it
+$L_\text{ICS}$ is independent to HM, but is incompatible with ACT as it
 does not create adversarial anchor.
@@
 
-Further technical details, discussions, limitations and societal impact of our
-method are presented in supplementary.
+Further experiment discussions, technical details, limitations and societal
+impact are presented in supplementary.
 

### 2021-11-09 sotaplot.py
delete junk

@@ -1,175 +1,0 @@
-import numpy as np
-import matplotlib.pyplot as plt
-import rich
-import argparse
-c = rich.get_console()
-plt.rcParams['font.family'] = 'serif'
-plt.rcParams['font.serif'] = 'FreeSerif'
-plt.rcParams['font.size'] = 15
-plt.rcParams['text.usetex'] = False
-plt.rcParams['mathtext.fallback'] = 'cm'
-
-data_cub = {
-    'ACT[R]': (
-        (30.6, 27.5), (9.0, 33.0), (31.3, 33.9) ),
-    'HM[S,LGA]': (
-        (38.0, 36.5), (9.0, 33.0), (32.4, 35.9) ),
-    'HM[S,LGA]ICS': (
-        (37.2, 34.9), (9.0, 33.0), (33.5, 36.0) ),
-}
-data_cars = {
-    'ACT[R]': (
-        (46.8, 43.4), (9.0, 33.0), (39.8, 38.6) ),
-    'HM[S,LGA]': (
-        (63.2, 62.3), (9.0, 33.0), (42.4, 44.9) ),
-    'HM[S,LGA]ICS': (
-        (60.2, 60.2), (9.0, 33.0), (46.0, 46.0) ),
-}
-data_sop = {
-    'ACT[R]': (
-        (45.1, 47.5), (9.0, 33.0), (50.3, 50.8) ),
-    'HM[S,LGA]': (
-        (49.0, 49.0), (9.0, 33.0), (61.7, 61.7) ),
-}
-
-styledict = {
-    'ACT[R]': {
-        'marker': '.',
-        'linestyle': ':',
-        'color': 'tab:cyan',
-        'linewidth': 2.0,
-    },
-    'ACT[S]': {
-        'marker': '.',
-        'linestyle': ':',
-        'color': 'tab:orange',
-        'linewidth': 2.0,
-    },
-    'HM[R,M]': {
-        'marker': 'v',
-        'linestyle': '-.',
-        'color': 'tab:blue',
-        'linewidth': 2.0,
-    },
-    'HM[S,M]': {
-        'marker': '^',
-        'linestyle': '-.',
-        'color': 'tab:red',
-        'linewidth': 2.0,
-    },
-    'HM[S,LGA]': {
-        'marker': 'h',
-        'linestyle': '-',
-        'color': 'tab:pink',
-        'linewidth': 2.0,
-    },
-    'HM[S,-r/2]': {
-        'marker': '+',
[…]

### 2021-11-09 robdml.tex
delete junk
tex

@@
 promising empirical robustness, although suffers from high training
-cost and a performance drop on benign examples.
+cost and performance drop on benign examples~\cite{odds}.
 
@@
 
-\begin{comment}
-\begin{figure}[t]
-	\includegraphics[width=\columnwidth]{sotaplot.pdf}
-	\caption{sota plot}
-\end{figure}
-\end{comment}
-
 For adversarial training of a DML model, selectiveness on both benign and

### 2021-11-10 robdml.tex
typo

@@
 In contrast, black-box attacks have been explored by query-based
-methods~\cite{nes-atk,spsa-atk} and transferrability-based
+methods~\cite{nes-atk,spsa-atk} and transferability-based
 methods~\cite{di-fgsm}, which are more practical for real-world scenarios.

### 2021-11-11 robdml.tex
tex

@@
 	\item \textit{Intra-Class Structure} (ICS) loss term to further improve
-		model robustness (especially intra-class-wise), while such structure is
+		model robustness and adversarial training efficiency, while such structure is
 		neglected by existing methods. 

### 2021-11-11 robdml.tex
tex

@@
 %
-$L_\text{ICS}$ is independent to HM, but is incompatible with ACT as it
-does not create adversarial anchor.
+$L_\text{ICS}$ is independent to HM, but is incompatible with ACT as it does
+not create adversarial anchor.
 %
@@
 As shown in \cref{tab:ics} and \cref{fig:ics}, $L_\text{ICS}$ consistently
-leads to a higher efficiency in gaining robustness (especially
-intra-class-wise), while retaining an acceptable trade-off in R@1.
+leads to a higher efficiency in gaining higher robustness at a low training
+cost, while retaining an acceptable trade-off in R@1.
 

### 2021-11-13 robdml.tex
import vishal's changes, part 2 (end)

@@
 Despite the advancements in this field thanks to deep learning, recent studies
-find DML models vulnerable to adversarial attack, where an imperceptible
-perturbation can incur unexpected retrieval result, or covertly change the
+find DML models vulnerable to adversarial attacks, where  imperceptible
+perturbations can incur unexpected retrieval result, or covertly change the
 rankings~\cite{advrank,advorder}.
 %
-Such vulnerability raises security, safety, and fairness concerns in DML
+Such vulnerability raises security, safety, and fairness concerns in the DML
 applications.
@@
 		%
-		Comparison in Robustness, Training Cost, and Recall@1 
-		between Our Method (\ie, ``HM[$\mathcal{S},g_\mathsf{LGA}$]\&ICS'')
-		and the State-of-The-Art Method (\ie, ``ACT[$\mathcal{R}$]'' and
-		``ACT[$\mathcal{S}$]'') on CUB Dataset.
+		Comparison in robustness, training cost, and recall@1 
+		between our method (\ie, ``HM[$\mathcal{S},g_\mathsf{LGA}$]\&ICS'')
+		and the state-of-the-art method (\ie, ``ACT[$\mathcal{R}$]'' and
+		``ACT[$\mathcal{S}$]'') on the CUB Dataset.
 		%
@@
 
-Previous works imply that an appropriate adversary for the inner
+{\bf{Previous works \cite{} imply that an appropriate adversary for the inner
 \emph{maximization} problem should increase the loss to an ``intermediate''
 point between that of benign examples (\ie, unperturbed examples) and the
-theoretical upper bound.
+theoretical upper bound.}}
 %
@@
 %
-Namely, a better \emph{destination} hardness should be able to balance the
+In particular, a better \emph{destination} hardness should be able to balance the
 training objectives in the early and late phases of training.
@@
 A function that leads to relatively weak and relatively strong adversarial
-examples respectively in the early and late phase of training belongs to this
+examples, respectively in the early and late phase of training belongs to this
 family.
@@
 	\vspace{-1.8em}
-	\caption{Flexibility of Hardness Manipulation.
+	\caption{Flexibility of hardness manipulation.
 	%
@@
 % contributions
-In brief, our contributions include proposing:
+In summary, our contributions include proposing:
 %
@@
 		tool to create adversarial example triplets for subsequent adversarial
-		training of DML model.
+		training of a DML model.
 		%
@@
 To battle against the attacks, some defenses incur gradient masking
-effect, but leads to a false sense of security~\cite{obfuscated}.
-%
-Defensive distillation~\cite{distill2} is compromised~\cite{cw}.
-%
-Ensemble of weak defenses is not robust~\cite{ensembleweak}.
+effect, but often lead to a false sense of security~\cite{obfuscated}.
+%
+Defensive distillation~\cite{distill2} is compromised in~\cite{cw}.
+%
+It has been shown that ensemble of weak defenses is not robust~\cite{ensembleweak}.
 %
@@
 %
-But many defenses are still susceptible to adaptive attack~\cite{adaptive}.
+But many defenses are still susceptible to adaptive attacks~\cite{adaptive}.
 %
 Of all defenses, adversarial training remains to be one of the most effective
-method~\cite{bilateral,advtrain-triplet,benchmarking}, consistently showing
+methods~\cite{bilateral,advtrain-triplet,benchmarking}, consistently showing
 promising empirical robustness, although suffers from high training
@@
 %
-The existing attacks aims to completely subvert the image retrieval
+The existing attacks aim to completely subvert the image retrieval
 results~\cite{qair,learn-to-misrank,advdpqn,advpattern,flowertower,universalret},
@@
 However, the existing defense methods suffer from low efficiency as the
-inner problem is replaced into a indirect form in order to avoid model collapse.
+inner problem is replaced into an indirect form in order to avoid model collapse.
 
@@
 
-In Deep Metric Learning (DML)~\cite{revisiting,dmlreality}, an embedding
+In DML~\cite{revisiting,dmlreality}, an embedding
 function $\phi:\mathcal{X}\mapsto \Phi \subseteq \mathbb{R}^D$ is learned to
@@
 Then the triplet loss~\cite{facenet} is defined as:
-%
-$
+\setlength{\belowdisplayskip}{0pt} \setlength{\belowdisplayshortskip}{0pt}
+\setlength{\abovedisplayskip}{0pt} \setlength{\abovedisplayshortskip}{0pt}
+%
+\begin{equation}
 %
@@
 	\gamma),
-%
-$
+	\end{equation}
+%
+%$
 %
@@
 %
-The \cref{eq:hm} is written in the L-$2$ norm form instead of the standard Mean
+ \cref{eq:hm} is written in the L-$2$ norm form instead of the standard Mean
 Squared Error because HM can be directly extended into vector form for a
@@
 	\vspace{-1.8em}
-	\caption{Illustration of Hardness Manipulation.}
+	\caption{Illustration of hardness manipulation.}
 	\label{fig:hm}
@@
 If we have a strong prior knowledge on what the \emph{destination} hardness
-should be, we can even use a pseudo-hardness function $g(\cdot)$, \ie, a
+should be, then we can even use a pseudo-hardness function $g(\cdot)$, \ie, a
 customized scalar function.
@@
 	\includegraphics[width=\columnwidth]{gaillust.pdf}
-	\caption{Illustration of (Linear) Gradual Adversary.}
+	\caption{Illustration of (linear) gradual adversary.}
 	\label{fig:ga}
@@
 Intuitively, such deficiency can be alleviated with a \emph{pseudo-hardness}
-function that slightly increase the value of $H_\mathsf{D}$ in the late phase
+function that slightly increases the value of $H_\mathsf{D}$ in the late phase
 of training.
@@
 %
-More complicated or non-linear pseudo-hardness functions are left for future study
-for sake of simplicity.
+More complicated or non-linear pseudo-hardness functions are left for future study.
+%for sake of simplicity.
 %
@@
 	\includegraphics[width=1.0\columnwidth]{icsapn.pdf}
-	\caption{Illustration of Intra-Class Structure Loss Term.}
+	\caption{Illustration of intra-class structure loss term.}
 	\label{fig:ics}
@@
 %
-We follow the same experiment setup as the state-of-the-art work~\cite{robrank,revisiting}
+We follow the same experimental setup as that used in the state-of-the-art works~\cite{robrank,revisiting}
 for ease of comparison.
@@
 %
-The margin $\gamma$ in triplet loss is $0.2$, which is consistent to standard
+The margin $\gamma$ in the triplet loss is $0.2$, which is consistent with the standard
 DML~\cite{revisiting}.
@@
 
-The model performance on benign (\ie, unperturbed) examples is measured in
+The model performance on the benign (\ie, unperturbed) examples is measured in terms of 
 Recall@1 (R@1), Recall@2 (R@2), mAP and NMI
@@
 
-Concretely, the collection of attacks for ERS includes:
+Concretely, the collection of attacks for ERS include:
 %
@@
 %
-Further details can be found in \cite{robrank} or the supplementary.
+Further details can be found in \cite{robrank} and in the supplementary document.
 
@@
 %
-Then we adversarially train models on CUB dataset with all combinations
+Then we adversarially train models on the CUB dataset with all combinations
 respectively, and summarize their R@1 and ERS in \cref{tab:desth}.
@@
 %
-According to \cref{fig:hmeff}, HM[$\mathcal{R},\mathcal{M}$] achieves the
+As can be seen from \cref{fig:hmeff}, HM[$\mathcal{R},\mathcal{M}$] achieves the
 highest ERS and efficiency but with the most significant drop in R@1, which is
@@
 %
-As discussed in \cref{sec:32}, the HM[$\mathcal{S},\mathcal{M}$] may still
+As discussed in \cref{sec:32},  HM[$\mathcal{S},\mathcal{M}$] may still
 suffer from the imbalance between learning the embeddings and gaining
@@
 %
-As shown in \cref{tab:ics} and \cref{fig:ics}, $L_\text{ICS}$ consistently
+{\bf{As shown in \cref{tab:ics} and \cref{fig:ics}, $L_\text{ICS}$ consistently
 leads to a higher efficiency in gaining higher robustness at a low training
-cost, while retaining an acceptable trade-off in R@1.
+cost, while retaining an acceptable trade-off in R@1.}}
 
@@
 with the state-of-the-art defense methods, \ie, EST~\cite{advrank}
-and ACT~\cite{robrank}, as shown in \cref{tab:sota}.
+and ACT~\cite{robrank}. The corresponding results are shown in \cref{tab:sota}.
 %
@@
 
-Further experiment discussions, technical details, limitations and societal
-impact are presented in supplementary.
+Further discussions on experiments, technical details, limitations and societal
+impact are presented in the supplementary document.
 

### 2021-11-13 robdml.tex
pp1

@@
 
-{\bf{Previous works \cite{} imply that an appropriate adversary for the inner
-\emph{maximization} problem should increase the loss to an ``intermediate''
+Inspired by previous works~\cite{advrank,robrank}, we conjecture that an
+appropriate adversary for the inner \emph{maximization} problem should
+increase the loss to an ``intermediate''
 point between that of benign examples (\ie, unperturbed examples) and the
-theoretical upper bound.}}
-%
-In this paper, we argue such point can be reached by a direct and efficient
-adversary.
-%
-Besides, we conjecture the triplet sampling strategy has a key impact in
+theoretical upper bound.
+%
+Such point should be reached by an efficient adversary directly.
+%
+Besides, we speculate the triplet sampling strategy has a key impact in
 adversarial training, because it is also able to greatly influence the

### 2021-11-13 robdml.tex
pp2

@@
 cross-modal retrieval~\cite{ladderloss}, and face recognition~\cite{facenet}
-can be formulated as Deep Metric Learning.
+can be formulated as DML problem.
 %
 A well-designed loss function and a proper sampling method are crucial for DML
-performance~\cite{dmlreality}.  As suggested by recent study, the classical
-triplet loss could reach state-of-the-art performance with an appropriate
-triplet sampling strategy~\cite{revisiting}.
+performance~\cite{dmlreality}.  For instance, the classical
+triplet loss~\cite{facenet} could reach state-of-the-art performance with an appropriate
+sampling strategy~\cite{revisiting}.
 
@@
 Then the triplet loss~\cite{facenet} is defined as:
-\setlength{\belowdisplayskip}{0pt} \setlength{\belowdisplayshortskip}{0pt}
-\setlength{\abovedisplayskip}{0pt} \setlength{\abovedisplayshortskip}{0pt}
+%\setlength{\belowdisplayskip}{0pt} \setlength{\belowdisplayshortskip}{0pt}
+%\setlength{\abovedisplayskip}{0pt} \setlength{\abovedisplayshortskip}{0pt}
 %

### 2021-11-13 robdml.tex
pp3

@@
 %
-\textbf{Defenses in DML.} Different from attacks, defense methods are less
-explored.
+\textbf{Defenses in DML.} Unlike attacks, defenses are less explored.
 %
@@
 %
+The state-of-the-art method, \ie,
 Anti-Collapse Triplet (ACT)~\cite{robrank} forces the model to separate
 collapsed positive and negative samples apart in order to learn robust
-features, which achieves the state-of-the-art robustness.
-%
-However, the existing defense methods suffer from low efficiency as the
-inner problem is replaced into an indirect form in order to avoid model collapse.
+features.
+%
+However, both EST and ACT suffer from low efficiency as the
+inner problem is replaced into an indirect adversary.
 
@@
 
-In DML~\cite{revisiting,dmlreality}, an embedding
-function $\phi:\mathcal{X}\mapsto \Phi \subseteq \mathbb{R}^D$ is learned to
+In DML~\cite{revisiting,dmlreality}, a 
+function $\phi:\mathcal{X}{\mapsto}\Phi \subseteq \mathbb{R}^D$ is learned to
 map data points $\mX\in\mathcal{X}$ into an embedding space $\Phi$, which is usually
@@
 %
-In a typical setting, the triplet loss~\cite{facenet} can be used to learn the
+Typically, the triplet loss~\cite{facenet} can be used to learn the
 embedding function, and it could reach the state-of-the-art performance with an
@@
 
-Given a sample triplet of anchor, positive, negative images, \ie, $\mA, \mP,
-\mN \in \mathcal{X}$, we first calculate their embeddings with $\phi(\cdot)$ as
+Given a triplet of anchor, positive, negative images, \ie, $\mA, \mP,
+\mN \in \mathcal{X}$, we can calculate their embeddings with $\phi(\cdot)$ as
 $\va, \vp, \vn$, respectively.
 %
-Then the triplet loss~\cite{facenet} is defined as:
+Then triplet loss~\cite{facenet} is defined as:
 %\setlength{\belowdisplayskip}{0pt} \setlength{\belowdisplayshortskip}{0pt}

### 2021-11-13 robdml.tex
pp5

@@
 
-To validate the proposed defense, we conduct experiments
+To validate our defense method, we conduct experiments
 on three commonly used DML datasets: CUB-200-2011 (CUB)~\cite{cub200}, Cars-196
-(CARS)~\cite{cars196}, and Stanford-Online-Products (SOP)~\cite{sop}.
-%
-We follow the same experimental setup as that used in the state-of-the-art works~\cite{robrank,revisiting}
-for ease of comparison.
+(CARS)~\cite{cars196}, and Stanford-Online-Product (SOP)~\cite{sop}.
+%
+We follow the same experimental setup as that used in the state-of-the-art
+defense work~\cite{robrank} and standard DML~\cite{revisiting} for ease of comparison.
 
@@
 %
-The margin $\gamma$ in the triplet loss is $0.2$, which is consistent with the standard
-DML~\cite{revisiting}.
+The margin $\gamma$ in the triplet loss is $0.2$.
 %
@@
 %
-Adversarial examples are created under the perturbation budget
-$\varepsilon{=}8/255$ in infinity norm, using PGD~\cite{madry} with step size
+Adversarial examples are created within $\Gamma$ with
+$\varepsilon{=}8/255$ and $p{=}\infty$, using PGD~\cite{madry} with step size
 $\alpha{=}1/255$ and a default maximum step number $\eta{=}8$.

### 2021-11-13 robdml.tex
pp5

@@
 (ERS)~\cite{robrank}, a normalized score (the higher the better) from
-an collection of existing attacks against DML or their simplified white-box
-alternatives optimized with PGD ($\eta=32$ for strong attack).
+a collection of (simplified white-box) attacks against DML, which are
+optimized with PGD ($\eta=32$ for strong attack).
 %
@@
 %
-Further details can be found in \cite{robrank} and in the supplementary document.
+Further details of these attacks can be found in \cite{robrank}.
 

### 2021-11-13 robdml.tex
pp7

@@
 %
-As discussed in \cref{sec:32},  HM[$\mathcal{S},\mathcal{M}$] may still
+HM[$\mathcal{S},\mathcal{M}$] may still
 suffer from the imbalance between learning the embeddings and gaining
-adversarial robustness.
+adversarial robustness as discussed in \cref{sec:32}.
 %

### 2021-11-13 robdml.tex
pp7

@@
 \begin{figure}[t]
-	\vspace{-1em}
+	\vspace{-1.5em}
 	\includegraphics[width=\columnwidth]{figgaeff.pdf}
@@
 Compared to HM[$\mathcal{S},\mathcal{M}$], slightly boosting the hardness
-training with $g_\mathsf{B}(\cdot)$ where $\xi{=}0.1$ benefits the ERS, but
+with $g_\mathsf{B}(\cdot)$ benefits the ERS, but
 results in a notably lower R@1;
@@
 %
-$H_\mathsf{D}{=}-\gamma/2$ provides a balance in training objectives, but
+$H_\mathsf{D}{=}-\gamma/2$ provides a fair balance in training objectives, but
 still suffers from inflexibility.
@@
 HM[$\mathcal{S},\mathcal{M}$], but is at the lowest R@1 performance penalty among all choices.
+%
+Its ERS is marginally lower than HM[$\mathcal{S},{-}\gamma/2$] because the
+loss value eventually converges around ${-}\gamma/2$ due to optimization
+difficulty, which means
+adversarial triplets with $H_\mathsf{D}{\in}[{-}\gamma/2,0]$
+are seldom used.
 
 \begin{figure}[t]
-	\vspace{-1em}
+	\vspace{-1.5em}
 	\includegraphics[width=\columnwidth]{figics.pdf}

### 2021-11-13 robdml.tex
pp7
tex

@@
 	\cref{tab:gaeff}.}
+	\vspace{-1em}
 	\label{fig:gaeff}
@@
 adversarial triplets with $H_\mathsf{D}{\in}[{-}\gamma/2,0]$
-are seldom used.
+are seldom created.
 
@@
 	\caption{Performance of ``HM[$\mathcal{S},g_\mathsf{LGA}$]\&ICS'' in \cref{tab:ics}.}
+	\vspace{-1em}
+	\label{fig:icscurve}
 \end{figure}
@@
 %
-{\bf{As shown in \cref{tab:ics} and \cref{fig:ics}, $L_\text{ICS}$ consistently
+{\bf{As shown in \cref{tab:ics} and \cref{fig:icscurve}, $L_\text{ICS}$ consistently
 leads to a higher efficiency in gaining higher robustness at a low training

### 2021-11-14 robdml.tex
tex

@@
 %
-{\bf{As shown in \cref{tab:ics} and \cref{fig:icscurve}, $L_\text{ICS}$ consistently
+As shown in \cref{tab:ics} and \cref{fig:icscurve}, $L_\text{ICS}$ consistently
 leads to a higher efficiency in gaining higher robustness at a low training
-cost, while retaining an acceptable trade-off in R@1.}}
+cost, while retaining an acceptable trade-off in R@1.
+
+\noindent\textbf{IV. Summary.}
+%
+Eventually, HM[$\mathcal{S},g_\mathsf{LGA}$]\&ICS overwhelmingly outperforms
+the state-of-the-art defense in robustness, training cost, and R@1 
+performance, as shown in \cref{fig:introplot}.
 
@@
 
-Apart from that, our method HM[$\mathcal{S},g_\mathsf{LGA}$] outperforms the
+Apart from that, our method HM[$\mathcal{S},g_\mathsf{LGA}$]\&ICS outperforms the
 previous methods in every aspect, as shown in \cref{fig:introplot} for 

### 2021-11-15 robdml.tex
tex

@@
 %
-Experiments for EST[$\mathcal{S}$] are omitted as they are expected to result in
-even much lower ERS based on the observations in previous subsections, and EST
-has been greatly outperformed by ACT~\cite{robrank}.
+Experiments for EST[$\mathcal{S}$] are omitted as EST has been greatly
+outperformed by ACT~\cite{robrank}, and it is expected to result in
+even lower ERS based on the observations in previous subsections.
 %
@@
 
-Apart from that, our method HM[$\mathcal{S},g_\mathsf{LGA}$]\&ICS outperforms the
+Apart from that, our method outperforms the
 previous methods in every aspect, as shown in \cref{fig:introplot} for 

### 2021-11-15 robdml.tex
tex

@@
 
-Apart from that, our method outperforms the
-previous methods in every aspect, as shown in \cref{fig:introplot} for 
-example.
-%
-Although HM[$\mathcal{R},\mathcal{M}$] and HM[$\mathcal{R},g_\mathsf{LGA}$] can reach
-a higher ERS, they are excluded from comparison because they induce a
-significant performance drop in R@1.
+Apart from that, our method outperforms the previous methods in every important
+aspect, \ie, ERS, training cost (efficiency), and R@1, as shown in
+\cref{tab:sota}.
+%
+HM[$\mathcal{R},\mathcal{M}$] and HM[$\mathcal{R},g_\mathsf{LGA}$] can reach a
+higher ERS, but are excluded from comparison due to significant performance
+drop in R@1.
 

### 2021-11-15 robdml.tex
tex

@@
 It \emph{must} be acknowledged that the high R@1 performance of our method
-largely stems from the source triplet sampling strategy, namely Softhard,
+largely stems from the source triplet sampling strategy, \ie, Softhard,
 instead of our contribution.
 %
-In terms of the overall performance, our method can achieve the highest ERS at
-the lowest performance drop in R@1 under a fixed training cost.
-%
-The existing methods are overwhelmingly outperformed by our method in overall
-performance.
-
-For adversarial training of a DML model, selectiveness on both benign and
+But the other methods cannot reach the same level of robustness with the same
+sampling strategy.
+%
+Besides, our method achieves the highest ERS at
+the lowest R@1 drop under a fixed training cost.
+%
+Thus, our proposed method overwhelmingly outperforms the existing defenses
+in overall performance.
+%
+
+Conclusively, being selective on both benign and
 adversarial training samples is crucial for preventing model collapse, and
@@
 %
-HM is a flexible tool for specifying such a ``selection'',
-while LGA is a selection rule for adversarial examples.
-%
-ICS loss term helps the model exploit more information from the
-given sextuplet.
-
-Further discussions on experiments, technical details, limitations and societal
-impact are presented in the supplementary document.
+HM is a flexible tool for specifying such ``selection'' of adversarial
+examples, while LGA can be interpreted as a concrete ``selection''.
+%
+ICS loss further exploits the given sextuplet.
+
+Further discussions, technical details, and limitations, \etc,
+are presented in the supplementary document.
 

### 2021-11-16 robdml.tex
tex
comment appendix

@@
 
-Apart from that, our method outperforms the previous methods in every important
+In most cases, our method outperforms the previous methods in every important
 aspect, \ie, ERS, training cost (efficiency), and R@1, as shown in
@@
 
-Adversarial robustness is crucial for DML applications.
-%
-In this paper, we improve adversarial training efficiency through HM.
-%
-Since regular training and the min-max adversarial training can be expressed as
-two boundary cases of HM, Graduate Adversary has been demonstrated effective as
-an ``intermediate point'' between the two cases.
-%
-Enforcing the previously neglected Intra-Class Structure can further improve
-model robustness and adversarial training efficiency.
-%
-%Our method outperforms previous methods.
+%Adversarial robustness is crucial for applications.
+%
+In this paper, HM efficiently and flexibly creates adversarial examples for
+adversarial training;
+%
+LGA specifies an ``intermediate'' destination hardness for balancing robustness
+and performance on benign examples;
+%
+ICS loss term further improves model robustness.
+%
+The state-of-the-art defenses have been surpassed in terms of overall performance.
 
@@
 
-\input{appendix.tex}
+%\input{appendix.tex}
 

### 2021-11-16 robdml.tex
tex

@@
 
-In most cases, our method outperforms the previous methods in every important
-aspect, \ie, ERS, training cost (efficiency), and R@1, as shown in
-\cref{tab:sota}.
-%
-HM[$\mathcal{R},\mathcal{M}$] and HM[$\mathcal{R},g_\mathsf{LGA}$] can reach a
-higher ERS, but are excluded from comparison due to significant performance
-drop in R@1.
+Our method overwhelmingly outperforms the previous methods in terms of the
+overall performance. Namely, our method achieves the highest ERS with a very
+low decrement in R@1 under a fixed training cost.
+%
+HM[$\mathcal{R},\mathcal{M}$] or HM[$\mathcal{R},g_\mathsf{LGA}$] can reach an
+even higher ERS, but are excluded from comparison due to significant drop in
+R@1.
+%
 
 It \emph{must} be acknowledged that the high R@1 performance of our method
-largely stems from the source triplet sampling strategy, \ie, Softhard,
-instead of our contribution.
-%
-But the other methods cannot reach the same level of robustness with the same
-sampling strategy.
-%
-Besides, our method achieves the highest ERS at
-the lowest R@1 drop under a fixed training cost.
-%
-Thus, our proposed method overwhelmingly outperforms the existing defenses
-in overall performance.
-%
+largely stems from the source triplet sampling strategy, \ie, Softhard, instead
+of our contribution.
+%
+Nevertheless, the state-of-the-art method, \ie, ACT could not reach the same
+level of robustness with the same sampling strategy.
 

### 2021-11-16 robdml.tex
tex

@@
 %
-(2) TMA~\cite{flowertower} which increases the cosine similarity between two selected samples;
+(2) TMA~\cite{flowertower} which increases the cosine similarity between two arbitrary samples;
 %
@@
 
+It \emph{should} be noted that the $L_\text{ICS}$ term improves 
+robustness against most attacks involved in ERS, but also increases the
+tendency to collapse (observed from the score for TMA~\cite{flowertower} --
+high cosine similarity between two arbitrary benign examples).
+%
+In some cases (\eg, on SOP), the performance drop \emph{w.r.t} TMA may
+neutralize the ERS gain from other attacks.
+
 Conclusively, being selective on both benign and

### 2021-11-16 robdml.tex
tex

@@
 robustness against most attacks involved in ERS, but also increases the
-tendency to collapse (observed from the score for TMA~\cite{flowertower} --
+tendency to collapse (observed during TMA~\cite{flowertower} attack --
 high cosine similarity between two arbitrary benign examples).
@@
 
-Further discussions, technical details, and limitations, \etc,
+Further analysis, technical details, and limitations, \etc,
 are presented in the supplementary document.

### 2021-11-16 robdml.tex
tex

@@
 %
-To battle against the attacks, some defenses incur gradient masking
-effect, but often lead to a false sense of security~\cite{obfuscated}.
+To battle against the attacks, some defenses incur gradient masking effect, but
+often lead to a false sense of security~\cite{obfuscated}.
 %
@@
 %
-It has been shown that ensemble of weak defenses is not robust~\cite{ensembleweak}.
+It has been shown that ensemble of weak defenses is not
+robust~\cite{ensembleweak}.
 %
@@
 %
-Of all defenses, adversarial training remains to be one of the most effective
-methods~\cite{bilateral,advtrain-triplet,benchmarking}, consistently showing
-promising empirical robustness, although suffers from high training
-cost and performance drop on benign examples~\cite{odds}.
+Of all defenses, adversarial training consistently remains to be one of the
+most effective
+methods~\cite{bilateral,advtrain-triplet,benchmarking,smoothat,trades,robustwrn,gowal,weightperturb},
+but suffers from high training cost~\cite{freeat} and performance drop on
+benign examples~\cite{odds,overfitting,geometry}.
 

### 2021-11-16 robdml.tex
tex

--- 2021-11-16 robdml.tex
@@
 %
-Of all defenses, adversarial training remains to be one of the most effective
-methods~\cite{bilateral,advtrain-triplet,benchmarking}, consistently showing
-promising empirical robustness, although suffers from high training
-cost and performance drop on benign examples~\cite{odds}.
+Of all defenses, adversarial training~\cite{madry} consistently remains to be one of the
+most effective
+methods~\cite{bilateral,advtrain-triplet,benchmarking,smoothat,trades,robustwrn,gowal,weightperturb},
+but suffers from high training cost~\cite{freeat,yopo} and performance drop on
+benign examples~\cite{odds,overfitting,geometry,onmanifold}.
 

### 2021-11-16 robdml.tex
tex

--- 2021-11-16 robdml.tex
@@
 %
-To battle against the attacks, some defenses incur gradient masking
-effect, but often lead to a false sense of security~\cite{obfuscated}.
+Various defenses are proposed to counter the attacks.
+%
+However, defenses incurring gradient masking
+lead to a false sense of robustness~\cite{obfuscated}.
 %
@@
 %
-It has been shown that ensemble of weak defenses is not robust~\cite{ensembleweak}.
-%
-Other defenses are also proposed, such as input
-preprocessing~\cite{deflecting}, or a randomization inside the
-network~\cite{self-ensemble}.
-%
-But many defenses are still susceptible to adaptive attacks~\cite{adaptive}.
-%
-Of all defenses, adversarial training remains to be one of the most effective
-methods~\cite{bilateral,advtrain-triplet,benchmarking}, consistently showing
-promising empirical robustness, although suffers from high training
-cost and performance drop on benign examples~\cite{odds}.
+Ensemble of weak defenses is not
+robust~\cite{ensembleweak}.
+%
+Other defenses such as input
+preprocessing~\cite{deflecting}, or a randomization~\cite{self-ensemble} are proposed.
+%
+But many of them are still susceptible to adaptive attacks~\cite{adaptive}.
+%
+Of all defenses, adversarial training~\cite{madry} consistently remains to be one of the
+most effective
+methods~\cite{bilateral,advtrain-triplet,benchmarking,smoothat,trades,robustwrn,weightperturb,featurescatter},
+but suffers from high training cost~\cite{freeat,fastat,yopo}, performance drop on
+benign examples~\cite{odds,geometry,onmanifold}, and overfitting on adversarial examples~\cite{bagoftricks,overfitting}.
 

### 2021-11-16 robdml.tex
tex
p1

@@
 	Additionally, an Intra-Class Structure loss term among benign and adversarial
-	examples further improves training efficiency and model robustness.
+	examples further improves model robustness and efficiency.
 	% Experiment and Conclusion
@@
 	although simple in its form, overwhelmingly outperforms the
-	state-of-the-art defenses in terms of training cost,
-	robustness, as well as performance on benign examples.
+	state-of-the-art defenses in terms of robustness, training efficiency,
+	as well as performance on benign examples.
 %
@@
 However, in order to avoid model collapse due to excessively hard examples, the
-existing defenses refrain from directly adopting such min-max paradigm, but
+existing DML defenses refrain from directly adopting such min-max paradigm, but
 instead replace the inner problem to indirectly increase the loss value to a
@@
 Subsequent first-order gradient-based methods can compromise the DNNs more
-effectively under the white-box assumption~\cite{i-fgsm,madry,apgd}.
+effectively under the white-box assumption~\cite{i-fgsm,madry,apgd,lafeat}.
 %

### 2021-11-16 robdml.tex
p2

@@
 %
-HM is flexible as regular training and min-max adversarial training
+HM is flexible as regular training and min-max adversarial training~\cite{madry}
 can be expressed as its boundary cases, as shown in \cref{fig:hmflexible}.
@@
 efficient \emph{maximization} process of the loss which stops halfway at the
-specified \emph{destination} hardness level, \ie, the ``intermediate'' point.
+specified \emph{destination} hardness level, \ie, the aforementioned ``intermediate'' point.
 

### 2021-11-16 robdml.tex
p2

@@
 we propose a simple \emph{intra-class} structure loss term for adversarial
-training, which is expected to further improve robustness.
+training, which is expected to further improve adversarial robustness.
 
@@
 The proposed method overwhelmingly outperforms the state-of-the-art defense in
-terms of training cost, robustness, as well as the performance on benign
+terms of robustness, training efficiency, as well as the performance on benign
 examples.
@@
 		model robustness and adversarial training efficiency, while such structure is
-		neglected by existing methods. 
+		neglected by existing defenses. 
 		%
@@
 Other defenses such as input
-preprocessing~\cite{deflecting}, or a randomization~\cite{self-ensemble} are proposed.
+preprocessing~\cite{deflecting}, or randomization~\cite{self-ensemble} are proposed.
 %

### 2021-11-16 robdml.tex
p2

@@
 cross-modal retrieval~\cite{ladderloss}, and face recognition~\cite{facenet}
-can be formulated as DML problem.
+can be formulated as a DML problem.
 %

### 2021-11-16 robdml.tex
p3

@@
 %
-The most important metrics for a good defense is training cost, adversarial
-robustness, and performance drop on benign examples.
+The most important metrics for a good defense are adversarial
+robustness, training efficiency, and performance on benign examples.
 
@@
 The $\max(0,\cdot)$ part in \cref{eq:hm} truncates the gradient when
-$H_\mathsf{S}>H_\mathsf{D}$, automatically stopping the optimization, because
-$H_\mathsf{S}$ is not desired to be reduced once it exceeds $H_\mathsf{D}$.
+$\tilde{H}_\mathsf{S}>H_\mathsf{D}$, automatically stopping the optimization, because
+$\tilde{H}_\mathsf{S}$ is not desired to be reduced once it exceeds $H_\mathsf{D}$.
 %
@@
 we abbreviate the adversarial training with adversarial examples created
-through this way as $\text{HM}[H_\mathsf{S},H_\mathsf{D}]$ in this paper.
+through this way as ``$\text{HM}[H_\mathsf{S},H_\mathsf{D}]$'' in this paper.
 

### 2021-11-16 robdml.tex
p4

@@
 %
-A satisfactory pseudo-hardness function is a ``Graduate Adversary'', as
-illustrated in \cref{fig:ga}.
+A satisfactory pseudo-hardness function is a ``Graduate Adversary''.
 
@@
 As an example, we propose a ``Linear Gradual Adversary'' (LGA) pseudo-hardness
-function that is independent to any benign triplets, incorporating an empirical
+function that is independent to any benign triplets, incorporating our empirical
 observation that $H_\mathsf{D}$ should remain Semihard~\cite{facenet}, as
@@
 \end{equation}
+%
+Our empirical observation is obtained from \cref{sec:41}.
 %
@@
 $\text{HM}[H_\mathsf{S},g_\mathsf{LGA}]$, leading to a better eventual overall
-performance.
+performance, as illustrated in \cref{fig:ga}.
 %

### 2021-11-16 robdml.tex
tex
p5

@@
 \usepackage{todonotes}
+\usepackage{siunitx}
 
@@
 %
-The setup of all the attacks for robustness evaluation are unchanged from
+The setup of all the attacks for robustness evaluation is unchanged from
 \cite{robrank} for fair comparison.
@@
 %
-Although almost all of them end up with model collapse, the
+Although almost all of these cases end up with model collapse, the
 $\text{HM}[\mathcal{R},\mathcal{M}]$ is still effective in improving the

### 2021-11-16 robdml.tex
p7

@@
 Its ERS is marginally lower than HM[$\mathcal{S},{-}\gamma/2$] because the
-loss value eventually converges around ${-}\gamma/2$ due to optimization
+observed loss value converges around ${-}\gamma/2$ due to optimization
 difficulty, which means
@@
 %
-Eventually, HM[$\mathcal{S},g_\mathsf{LGA}$]\&ICS overwhelmingly outperforms
-the state-of-the-art defense in robustness, training cost, and R@1 
+Eventually, HM[$\mathcal{S},g_\mathsf{LGA}$]\&ICS outperforms
+the state-of-the-art defense in robustness, training efficiency, and R@1 
 performance, as shown in \cref{fig:introplot}.

### 2021-11-16 robdml.tex
p8

@@
 Our method overwhelmingly outperforms the previous methods in terms of the
-overall performance. Namely, our method achieves the highest ERS with a very
+overall performance. Namely, our method efficiently reaches the highest ERS with a very
 low decrement in R@1 under a fixed training cost.
@@
 %
-In some cases (\eg, on SOP), the performance drop \emph{w.r.t} TMA may
+In some cases (\eg, on SOP), the robustness drop \emph{w.r.t} TMA may
 neutralize the ERS gain from other attacks.

### 2021-11-18 appendix.tex
tex
sup

--- 2021-11-08 appendix.tex
@@
 
-In this supplementary material, we provide further technical details and
-discussions that are not included in the manuscript due to space limit.
+In this supplementary material, we provide further technical details and the
+less important discussions that are not included in the manuscript due to space
+limit.
 %
-Discussions required by the author guidelines can also be found in this
+Discussions required by the author guidelines are also included in this
 supplementary material.
@@
 
-Adversarial attacks may raise security considerations on
-deep learning applications, and even cause negative effect.
-%
-In contrast, in this manuscript, we focus on defending against the attacks and
-enhancing a model's adversarial robustness, and hence is expected to have a
-positive impact instead.
-
-~\newline
-\noindent\textbf{II. Environment.}
-
-Although adversarial training is not
-environment-friendly due to its high training cost (in terms of more intensive
-computation than regular training), our method has significantly improved the
-adversarial training efficiency compared to the previous works (hence is a
-little bit more environment-friendly).
+Adversarial defenses alleviate the negative societal impact of adversarial
+attacks, and hence have positive societal impact.
 
@@
 
-(1) \ul{Triplet Assumption.}
+~\newline
+\noindent \ul{(1) Triplet Training Assumption.}
 
-This paper assums training with sample triplets.
+Our method assumes sample triplets are used for training.
 %
-When other deep metric learning loss functions are used, our proposed method
-may not be compatible.
+Our method may not be compatible to other non-triplet DML loss functions.
 %
-This assumption is a limitation of our method.
+Adversarial training with other DML loss functions is left for future study.
+
+~\newline
+\noindent \ul{(2) Embedding Space Assumption.}
+
+We follow the common setups~\cite{revisiting,robrank} on the embedding space.
 %
-Adversarial training with other DML loss functions is unexplored and is left
-for future study.
+Namely, (1) the embedding vectors are normalized onto the real unit
+hypersphere;
+%
+(2) the distance function $d(\cdot,\cdot)$ is Euclidean distance.
+%
+Our formulations are developed upon the two assumptions.
+%
+It is unknown whether our method method will be effective when embedding
+vectors are \emph{not} normalized.
+%
+And it is unknown whether our method will be effective when $d(\cdot,\cdot)$ is
+replaced as other distance metrics, \eg, cosine distance.
+
+~\newline
+\noindent\textbf{II. Performance-Sensitive Factors.}
+
+~\newline
+\noindent \ul{(1) Maximum number of PGD iterations $\eta$.}
+
+Our method's sensitivity to $\eta$ has been demonstrated by Tab.~3-6 and
+Fig.~6-8.
+%
+A larger $\eta$ indicates higher training cost, and stronger adversarial
+examples are created for adversarial training.
+%
+As a result, a larger $\eta$ leads to a higher robustness (ERS) and a lower
+R@1 performance.
+%
+Our method consistently achieves a higher ERS under different $\eta$ settings
+compared to previous methods, and hence are the most efficient defense method.
+%
+Experiments with $\eta$ larger than $32$ are not necessary because ERS plateaus
+according to Fig.~6-8.
+
+~\newline
+\noindent \ul{(2) Source hardness $H_\mathsf{S}$ and destination hardness
+$H_\mathsf{D}$.}
+
+The $H_\mathsf{S}$ and $H_\mathsf{D}$ are the only two adjustable items in HM.
+
+The source hardness $H_\mathsf{S}$ depends on triplet sampling strategy.
+%
+We conduct experiments with existing triplet sampling strategies in order to
+focus on defense.
+
+The choices for $H_\mathsf{D}$ are more flexible than those of $H_\mathsf{S}$,
+as discussed in Sec.~3.1.
+%
+In the experiments, we study some possible choices following the discussion and
+design LGA based on the empirical observations.
+
+~\newline
+\noindent\ul{(3) Parameters involved in $g_\mathsf{LGA}$.}
+
+\begin{table*}
+\resizebox{\linewidth}{!}{
+\setlength{\tabcolsep}{0.47em}
+\renewcommand{\arraystretch}{1.1}%
+\begin{tabular}{c|cc|cccc|ccccc|ccccc|c}
+\hline
+\multirow{2}{*}{\textbf{Dataset}} & \multirow{2}{*}{\textbf{Defense}} & \multirow{2}{*}{$\eta$} & \multicolumn{4}{c|}{\textbf{Benign Example}} & \multicolumn{10}{c|}{\textbf{White-Box Attacks for Robustness Evaluation}} & \multirow{2}{*}{\textbf{ERS$\uparrow$}}\tabularnewline
+\cline{4-17} \cline{5-17} \cline{6-17} \cline{7-17} \cline{8-17} \cline{9-17} \cline{10-17} \cline{11-17} \cline{12-17} \cline{13-17} \cline{14-17} \cline{15-17} \cline{16-17} \cline{17-17}
+ &  &  & R@1$\uparrow$ & R@2$\uparrow$ & mAP$\uparrow$ & NMI$\uparrow$ & CA+$\uparrow$ & CA-$\downarrow$ & QA+$\uparrow$ & QA-$\downarrow$ & TMA$\downarrow$ & ES:D$\downarrow$ & ES:R$\uparrow$ & LTM$\uparrow$ & GTM$\uparrow$ & GTT$\uparrow$ & \tabularnewline
+\hline
+\hline
+\multirow{2}{*}{CUB} & HM{[}$\mathcal{S},g_{\mathsf{LGA}}${]} & 8 & 38.0 & 48.3 & 21.8 & 49.3 & 12.7 & 46.4 & 11.6 & 39.9 & 0.567 & 0.783 & 16.8 & 11.9 & 27.9 & 1.4 & 32.4\tabularnewline
+ & HM{[}$\mathcal{S},g_{\mathsf{LGA}}${]} ($u=2.2$) &  & 34.8 & 45.5 & 15.2 & 47.1 & 13.4 & 36.0 & 17.2 & 26.1 & 0.934 & 0.244 & 20.1 & 15.9 & 27.3 & 3.8 & 36.1\tabularnewline
+\end{tabular}}
+\end{table*}
+
+A constant $u$ is used to normalize the loss value of the previous training
+iteration $\ell_{t-1}$ into $\bar{\ell}_{t-1}\in[0,1]$.
+%
+The constant is empirically selected as $u=\gamma$ in our experiment.
+%
+According to our observation, the loss value will quickly decrease below
+$\gamma$, and will remain in the $[0,\gamma]$ range for the whole training
+process.
+%
+If we set $u$ to a larger constant than $\gamma$, the normalized loss
+$\bar{\ell}_{t-1}$ will be smaller, and results in stronger adversarial
+examples through HM and harms the model performance on benign examples.
+
+Our LGA function $g_\mathsf{LGA}$ reuses the triplet margin parameter $\gamma$
+in order to remain in the range of Semihard, \ie, $-\gamma<g_\mathsf{LGA}<0$.
+%
+Apart from this, LGA is parameter-free.
+
+(5) \ul{Weight constant $\lambda$ of ICS loss term $L_\text{ICS}$.}
+
+The weight constant $\lambda$ is set as $0.5$ by default, and $0.05$ on SOP.
+%
+As demonstrated in the experiments, there is a trade-off between robustness and
+performance on benign examples when tuning the $\lambda$ parameter.
+%
+Our experiments demonstrate that the ICS loss term is effective in improving
+adversarial training efficiency and model robustness, but in practice, the
+adopters of our method may need to re-evaluate the trade-off between
+performance and robustness, and ajudst $\lambda$ accordingly.
+
+(6) \ul{Optimization algorithm for adversarial attacks.}
+
+In this paper, PGD~\cite{madry} is adopted as the optimization algorithm for
+creating adversarial examples.
+%
+It is also adopted by the ERS metric~\cite{robrank} for robustness evaluation
+with a collection of white-box attacks.
+%
+In the literature, some other optimization methods exists, such as
+APGD~\cite{apgd}.
+%
+However, we adopt PGD~\cite{madry} to keep aligned with the state-of-the-art
+work for sake of fair comparison.
+
+A replacement of such algorithm for adversarial training will affect the
+model's performance on benign examples and robustness.
+%
+Stronger adversarial examples during adversarial training may further boost the
+robustness of a model, and further reduce the performance on benign examples.
+
+A replacement of such algorithm for ERS evaluation will affect the robustness
+score for all existing methods.
+%
+All existing methods are expected to have a lower (to a certain extent)
+robustness against a stronger algorithm than PGD.
+%
+In this case, a robust method still remains robust, and a not robust method
+remains not robust.
+
+~\newline
+\noindent\ul{Backbone deep neural network model.}
+
+The backbone model significantly influences the performance in every aspect, as
+the standard DML adopts ImageNet-initialized backbones for further training.
+%
+In this paper, we adopt ResNet-18 following the state-of-the-art
+defense~\cite{robrank} for fair comparison.
+%
+Since our proposed defense method is independent to backbone selection, it is
+expected to be effective on other backbone models as well.
+
+Adversarial training requires more time and GPU memory than regular training.
+%
+The adversarial training of ResNet-18 with our method requires about 7\~{}10GB
+of memory per GPU in distributed data parallel mode.
+
+\subsection{Use of Existing Assets}
+
+(1) \ul{Datasets:} All the datasets used in our paper are public datasets,
+and their corresponding papers are properly cited.
+
+(2) \ul{Code and Implementation:} Our implementation is built upon PyTorch
+and the public code of the state-of-the-art defense method~\cite{robrank}
+(License: Apache-2.0).
+
+\section{More Technical Details}
+\label{sec:b}
+
+\oo{FIXME}
 
@@
 thanks to the flexibility of HM.
-
-~\newline
-\noindent\textbf{II. Performance-Sensitive Factors.}
-
-(1) \ul{Backbone deep neural network model.}
-
-The backbone model significantly influences the performance in every aspect, as
-the standard DML adopts ImageNet-initialized backbones for further training.
-%
-In this paper, we adopt ResNet-18 following the state-of-the-art
-defense~\cite{robrank} for fair comparison.
-%
-Since our proposed defense method is independent to backbone selection, it is
-expected to be effective on other backbone models as well.
-
-Adversarial training requires more time and GPU memory than regular training.
-%
-The adversarial training of ResNet-18 with our method requires about 7\~{}10GB
-of memory per GPU in distributed data parallel mode.
-%
-%Adversarial training of ResNet-50 requires much more than 12GB of memory per
-%GPU, which will make it harder for some readers to reproduce the results
-%and compare.
-
-(2) \ul{Adversarial training budget $\eta$.}
-
-As demonstrated in our experiments, the adversarial training budget, namely the
-maximum number of PGD iterations $\eta$ for creating the adversarial examples
-can greatly influence the performance.
-%
-We conduct experiments with multiple choices of $\eta$, and we can see from the
-curves that the model performance has a converging trend with large $\eta$
-settings.
-
-(3) \ul{Source hardness $H_\mathsf{S}$ and destination hardness
-$H_\mathsf{D}$.}
-
-The source hardness $H_\mathsf{S}$ depends on triplet sampling strategy, which
-is another research topic in the DML field.
-%
-The available triplet sampling strategies includes Random, Semihard, Softhard,
-Distance-weighted, as well as within-batch Hardest sampling strategies.
-%
-We conduct experiments and figure out an appropriate choice in our experiments.
-
-The range of choices for $H_\mathsf{D}$ is wider than that of $H_\mathsf{S}$.
-%
-When we use another benign sample triplet to calculate $H_\mathsf{D}$, the
-``another benign sample triplet'' can be sampled with the existing triplet
-sampling strategies as well.
-%
-We tested every combination of sampling strategies in our experiments.
-%
-Besides, $H_\mathsf{D}$ can be a pseudo-hardness function in order to avoid
-disadvantages (discussed in our approach) of using another benign triplet as
-reference.
-%
-Graduate Adversary is a family of such pseudo-hardness functions, and Linear
-Graduate Adversary (LGA) is a simple and straightforward example which is
-already effective.
-%
-Although $H_\mathsf{D}$ can be a constant as well, such choice lacks
-flexibility and is only used for demonstrating the advantage of LGA in our
-experiments.
-
-The $H_\mathsf{S}$ and $H_\mathsf{D}$ are the only two adjustable items of
-Hardness Manipulation.
-
-(4) \ul{Parameters in $g_\mathsf{LGA}$ and $g_\mathsf{B}$.}
-
-A constant $u$ is used to normalize the loss value of the previous training
-iteration $\ell_{t-1}$ into $\bar{\ell}_{t-1}\in[0,1]$.
-%
-The constant is empirically selected as $u=\gamma$ in our experiment.
-%
-According to our observation, the loss value will quickly decrease below
-$\gamma$, and will remain in the $[0,\gamma]$ range for the whole training
-process.
-%
-If we set $u$ to a larger constant than $\gamma$, the normalized loss
-$\bar{\ell}_{t-1}$ will be smaller, and results in stronger adversarial
-examples through HM and harms the model performance on benign examples.
-
-A parameter $\xi$ is used by $g_\mathsf{B}$ to slightly boost a given
-$H_\mathsf{D}$ calculated from another benign triplet.
-%
-As mentioned in the experiments section, $\xi$ is set to $0.1$ in our
-experiment.
-%
-We refrain from conducting further parameter search because $g_\mathsf{B}$
-is only proposed to demonstrate that the problem in the late phase of
-training can be alleviated in our step-by-step description of our approach.
-%
-And $g_\mathsf{B}$ does not alleviate the problem in the early phase of
-training, and hence it does not belong to Graduate Adversary.
-%
-The function $g_\mathsf{B}$ is not a key point.
-
-Our LGA function $g_\mathsf{LGA}$ reuses the triplet margin parameter $\gamma$
-in order to remain in the range of Semihard, \ie, $-\gamma<g_\mathsf{LGA}<0$.
-%
-Apart from this, LGA is parameter-free.
-
-(5) \ul{Weight constant $\lambda$ of ICS loss term $L_\text{ICS}$.}
-
-The weight constant $\lambda$ is set as $0.5$ by default, and $0.05$ on SOP.
-%
-As demonstrated in the experiments, there is a trade-off between robustness and
-performance on benign examples when tuning the $\lambda$ parameter.
-%
-Our experiments demonstrate that the ICS loss term is effective in improving
-adversarial training efficiency and model robustness, but in practice, the
-adopters of our method may need to re-evaluate the trade-off between
-performance and robustness, and ajudst $\lambda$ accordingly.
-
-(6) \ul{Optimization algorithm for adversarial attacks.}
-
-In this paper, PGD~\cite{madry} is adopted as the optimization algorithm for
-creating adversarial examples.
-%
-It is also adopted by the ERS metric~\cite{robrank} for robustness evaluation
-with a collection of white-box attacks.
-%
-In the literature, some other optimization methods exists, such as
-APGD~\cite{apgd}.
-%
-However, we adopt PGD~\cite{madry} to keep aligned with the state-of-the-art
-work for sake of fair comparison.
-
-A replacement of such algorithm for adversarial training will affect the
-model's performance on benign examples and robustness.
-%
-Stronger adversarial examples during adversarial training may further boost the
-robustness of a model, and further reduce the performance on benign examples.
-
-A replacement of such algorithm for ERS evaluation will affect the robustness
-score for all existing methods.
-%
-All existing methods are expected to have a lower (to a certain extent)
-robustness against a stronger algorithm than PGD.
-%
-In this case, a robust method still remains robust, and a not robust method
-remains not robust.
-
-~\newline
-\noindent\textbf{III. Use of Existing Assets.}
-
-(1) \ul{Datasets:} All the datasets used in our paper are public datasets,
-and their corresponding papers are properly cited.
-
-(2) \ul{Code and Implementation:} Our implementation is built upon PyTorch
-and the public code of the state-of-the-art defense method~\cite{robrank}
-(License: Apache-2.0).
-
-\section{More Technical Details}
-\label{sec:b}
 
@@
 inefficient adversarial learning.
+
+~\newline\textbf{III. Min-max Adversarial Training with Triplet Loss.}
+
+TODO
+
+Collapse even with $\eta=2$ and $\alpha=1$.
 
@@
 
- [T] By incorporating the idea of
-	on-manifold adversarial example to adversarial training, the
-	performance on benign example is greatly improved.
+ [T] By incorporating the idea of on-manifold adversarial example to
+	adversarial training, the performance on benign example is greatly
+	improved.
 	%
-	That idea can be interpreted as to be selective on the adversarial
-	example used for trianing.
+	That idea can be interpreted as to be selective on the adversarial example
+	used for trianing.
 	%
-	Here, in our observation, we are also selective on the adversarial
-	examples used for training.
+	Here, in our observation, we are also selective on the adversarial examples
+	used for training.
 	%
@@
 
+[TODO LIST]
+
+Before deadline
+
+* Revise figures
+
+* Revise manuscript
+
+After deadline: supplementary
+
+* add discussions and additional experiments
 \end{comment}
+
+\oo{explain lower ERS with high eta? overfit.}
+
+\begin{table*}
+\resizebox{\linewidth}{!}{
+\setlength{\tabcolsep}{0.47em}
+\renewcommand{\arraystretch}{1.1}%
+\begin{tabular}{c|cc|cccc|ccccc|ccccc|c}
+\hline
+\multirow{2}{*}{\textbf{Dataset}} & \multirow{2}{*}{\textbf{Defense}} & \multirow{2}{*}{$\eta$} & \multicolumn{4}{c|}{\textbf{Benign Example}} & \multicolumn{10}{c|}{\textbf{White-Box Attacks for Robustness Evaluation}} & \multirow{2}{*}{\textbf{ERS$\uparrow$}}\tabularnewline
+\cline{4-17} \cline{5-17} \cline{6-17} \cline{7-17} \cline{8-17} \cline{9-17} \cline{10-17} \cline{11-17} \cline{12-17} \cline{13-17} \cline{14-17} \cline{15-17} \cline{16-17} \cline{17-17}
+ &  &  & R@1$\uparrow$ & R@2$\uparrow$ & mAP$\uparrow$ & NMI$\uparrow$ & CA+$\uparrow$ & CA-$\downarrow$ & QA+$\uparrow$ & QA-$\downarrow$ & TMA$\downarrow$ & ES:D$\downarrow$ & ES:R$\uparrow$ & LTM$\uparrow$ & GTM$\uparrow$ & GTT$\uparrow$ & \tabularnewline
+\hline
+\hline
+\multirow{6}{*}{CUB} & HM{[}$\mathcal{R},\mathcal{M}${]} & 8 & 27.0 & 36.0 & 13.2 & 42.5 & 19.4 & 48.0 & 22.2 & 32.0 & 0.535 & 0.867 & 11.6 & 10.4 & 19.3 & 2.9 & 35.1\tabularnewline
+ & HM{[}$\mathcal{R},g_{\mathsf{B}}(\mathcal{M})${]} & 8 & 24.9 & 33.4 & 12.0 & 41.7 & 21.6 & 45.1 & 24.9 & 29.1 & 0.515 & 0.780 & 12.3 & 12.1 & 19.7 & 3.7 & 37.6\tabularnewline
+ & HM{[}$\mathcal{R},0${]} & 8 & 2.4 & 3.8 & 1.1 & 21.7 & 40.8 & 22.3 & 42.2 & 16.7 & 1.000 & 0.000 & 1.6 & 1.2 & 1.7 & 7.0 & 43.9\tabularnewline
+ & HM{[}$\mathcal{R},-\gamma/2${]} & 8 & 25.5 & 34.5 & 12.8 & 41.7 & 21.9 & 41.5 & 23.8 & 27.0 & 0.493 & 0.784 & 13.5 & 11.8 & 20.3 & 3.6 & 38.3\tabularnewline
+ & HM{[}$\mathcal{R},-\gamma${]} & 8 & 27.5 & 36.5 & 13.5 & 42.5 & 18.1 & 54.0 & 19.9 & 37.5 & 0.561 & 0.925 & 9.9 & 9.7 & 18.6 & 1.7 & 32.2\tabularnewline
+ & HM{[}$\mathcal{R},g_{\mathsf{LGA}}${]} & 8 & 24.8 & 33.9 & 12.2 & 41.6 & 21.4 & 45.0 & 21.7 & 31.3 & 0.452 & 0.846 & 13.2 & 12.0 & 20.9 & 4.6 & 37.3\tabularnewline
+\multicolumn{1}{c}{} & HM{[}$\mathcal{S},g_{\mathsf{1/2}}${]} & 8 & 37.7 & 48.5 & 22.0 & 49.2 & 12.6 & 48.6 & 12.3 & 41.3 & 0.562 & 0.825 & 13.5 & 12.9 & 26.9 & 1.8 & 31.7\tabularnewline
+\multicolumn{1}{c}{} & HM{[}$\mathcal{S},g_{\mathsf{LGA}}${]} & 8 & 38.0 & 48.3 & 21.8 & 49.3 & 12.7 & 46.4 & 11.6 & 39.9 & 0.567 & 0.783 & 16.8 & 11.9 & 27.9 & 1.4 & 32.4\tabularnewline
+\multicolumn{1}{c}{} & HM{[}$\mathcal{S},g_{\mathsf{2}}${]} & 8 & 37.4 & 48.2 & 17.1 & 49.2 & 12.9 & 45.1 & 13.2 & 39.1 & 0.599 & 0.738 & 17.7 & 12.8 & 27.5 & 1.9 & 33.1\tabularnewline
+\multicolumn{1}{c}{} & LGA u=2.2 &  & 34.8 & 45.5 & 15.2 & 47.1 & 13.4 & 36.0 & 17.2 & 26.1 & 0.934 & 0.244 & 20.1 & 15.9 & 27.3 & 3.8 & 36.1\tabularnewline
+\end{tabular}}
+\end{table*}
+
+\begin{table*}
+\resizebox{\linewidth}{!}{
+\setlength{\tabcolsep}{0.3em}
+\renewcommand{\arraystretch}{1.1}%
+\begin{tabular}{ccc|cccc|ccccc|ccccc|c}
+\hline
+\multicolumn{1}{c|}{\multirow{2}{*}{\textbf{Dataset}}} & \multirow{2}{*}{\textbf{Defense}} & \multirow{2}{*}{$\eta$} & \multicolumn{4}{c|}{\textbf{Benign Example}} & \multicolumn{10}{c|}{\textbf{White-Box Attacks for Robustness Evaluation}} & \multirow{2}{*}{\textbf{ERS$\uparrow$}}\tabularnewline
+\cline{4-17} \cline{5-17} \cline{6-17} \cline{7-17} \cline{8-17} \cline{9-17} \cline{10-17} \cline{11-17} \cline{12-17} \cline{13-17} \cline{14-17} \cline{15-17} \cline{16-17} \cline{17-17}
+ &  &  & R@1$\uparrow$ & R@2$\uparrow$ & mAP$\uparrow$ & NMI$\uparrow$ & CA+$\uparrow$ & CA-$\downarrow$ & QA+$\uparrow$ & QA-$\downarrow$ & TMA$\downarrow$ & ES:D$\downarrow$ & ES:R$\uparrow$ & LTM$\uparrow$ & GTM$\uparrow$ & GTT$\uparrow$ & \tabularnewline
+\hline
+{*} & HM{[}$\mathcal{S},g_{\mathsf{LGA}}${]} & 8 & 35.5 & 46.3 & 20.3 & 47.5 & 14.6 & 41.1 & 14.3 & 34.5 & 0.530 & 0.739 & 18.1 & 13.1 & 27.9 & 2.1 & 35.3\tabularnewline
+ & +0.5i aap & 8 & 34.8 & 45.2 & 19.8 & 47.6 & 15.6 & 35.9 & 18.5 & 28.2 & 0.802 & 0.447 & 19.2 & 13.9 & 26.3 & 2.9 & 36.4\tabularnewline
+ & +i aap & 8 & 34.7 & 45.6 & 19.5 & 46.9 & 16.9 & 34.2 & 18.9 & 26.7 & 0.904 & 0.296 & 20.4 & 16.1 & 26.6 & 4.2 & 37.3\tabularnewline
+ & +i aap aan){*}1.0 & 8 & 34.2 & 44.7 & 19.3 & 47.9 & 15.2 & 35.2 & 18.0 & 27.1 & 0.902 & 0.301 & 17.9 & 15.0 & 28.5 & 3.0 & 36.3\tabularnewline
+ & +i aa\textasciitilde p apn\textasciitilde{} 1.0 & 8 & 37.9 & 49.4 & 22.5 & 49.2 & 12.9 & 45.9 & 15.0 & 38.9 & 0.909 & 0.378 & 14.8 & 11.7 & 25.3 & 0.9 & 31.4\tabularnewline
+ & ICS gamma 0.2 &  & 35.8 & 46.6 & 16.4 & 48.3 & 13.2 & 39.9 & 12.7 & 33.3 & 0.775 & 0.507 & 15.9 & 14.9 & 27.2 & 2.7 & 33.6\tabularnewline
+\end{tabular}}
+\end{table*}
+
+\begin{table*}
+\resizebox{\linewidth}{!}{
+\setlength{\tabcolsep}{0.3em}
+\renewcommand{\arraystretch}{1.1}%
+\begin{tabular}{c|cc|cccc|ccccc|ccccc|c}
+\hline
+\multirow{2}{*}{\textbf{Dataset}} & \multirow{2}{*}{\textbf{Defense}} & \multirow{2}{*}{$\eta$} & \multicolumn{4}{c|}{\textbf{Benign Example}} & \multicolumn{10}{c|}{\textbf{White-Box Attacks for Robustness Evaluation}} & \multirow{2}{*}{\textbf{ERS$\uparrow$}}\tabularnewline
+\cline{4-17} \cline{5-17} \cline{6-17} \cline{7-17} \cline{8-17} \cline{9-17} \cline{10-17} \cline{11-17} \cline{12-17} \cline{13-17} \cline{14-17} \cline{15-17} \cline{16-17} \cline{17-17}
+ &  &  & R@1$\uparrow$ & R@2$\uparrow$ & mAP$\uparrow$ & NMI$\uparrow$ & CA+$\uparrow$ & CA-$\downarrow$ & QA+$\uparrow$ & QA-$\downarrow$ & TMA$\downarrow$ & ES:D$\downarrow$ & ES:R$\uparrow$ & LTM$\uparrow$ & GTM$\uparrow$ & GTT$\uparrow$ & \tabularnewline
+\hline
+\hline
+\multirow{2}{*}{SOP} & HM{[}$\mathcal{S},g_{\mathsf{LGA}}${]}\&ICS ($\lambda=0.5$) & 8 & 42.4 & 47.1 & 10.2 & 84.2 & 34.9 & 3.8 & 36.7 & 2.3 & 0.879 & 0.093 & 35.3 & 36.5 & 35.2 & 49.1 & 60.1\tabularnewline
+\cline{2-18} \cline{3-18} \cline{4-18} \cline{5-18} \cline{6-18} \cline{7-18} \cline{8-18} \cline{9-18} \cline{10-18} \cline{11-18} \cline{12-18} \cline{13-18} \cline{14-18} \cline{15-18} \cline{16-18} \cline{17-18} \cline{18-18}
+ & HM{[}$\mathcal{S},g_{\mathsf{LGA}}${]}\&ICS ($\lambda=0.5$) & 32 & 41.5 & 46.1 & 9.9 & 84.1 & 36.1 & 3.1 & 37.6 & 2.1 & 0.873 & 0.086 & 35.7 & 36.8 & 34.7 & 50.2 & 60.8\tabularnewline
+\end{tabular}}
+\end{table*}

### 2021-11-18 appendix.tex
sup

@@
 \appendix
+
+\setcounter{figure}{8}
+\setcounter{table}{6}
 
@@
 ~\newline
+\noindent \ul{(3) Optimizer Assumption.}
+
+Our method assumes PGD~\cite{madry} is used for optimizing the HM objective
+to create adversarial examples.
+%
+The Eq.~(4)-(5) may not necessarily hold with other possible optimizers.
+
+~\newline
 \noindent\textbf{II. Performance-Sensitive Factors.}
@@
 \begin{tabular}{c|cc|cccc|ccccc|ccccc|c}
-\hline
+	\toprule
 \multirow{2}{*}{\textbf{Dataset}} & \multirow{2}{*}{\textbf{Defense}} & \multirow{2}{*}{$\eta$} & \multicolumn{4}{c|}{\textbf{Benign Example}} & \multicolumn{10}{c|}{\textbf{White-Box Attacks for Robustness Evaluation}} & \multirow{2}{*}{\textbf{ERS$\uparrow$}}\tabularnewline
@@
  &  &  & R@1$\uparrow$ & R@2$\uparrow$ & mAP$\uparrow$ & NMI$\uparrow$ & CA+$\uparrow$ & CA-$\downarrow$ & QA+$\uparrow$ & QA-$\downarrow$ & TMA$\downarrow$ & ES:D$\downarrow$ & ES:R$\uparrow$ & LTM$\uparrow$ & GTM$\uparrow$ & GTT$\uparrow$ & \tabularnewline
-\hline
-\hline
+ \midrule
 \multirow{2}{*}{CUB} & HM{[}$\mathcal{S},g_{\mathsf{LGA}}${]} & 8 & 38.0 & 48.3 & 21.8 & 49.3 & 12.7 & 46.4 & 11.6 & 39.9 & 0.567 & 0.783 & 16.8 & 11.9 & 27.9 & 1.4 & 32.4\tabularnewline
- & HM{[}$\mathcal{S},g_{\mathsf{LGA}}${]} ($u=2.2$) &  & 34.8 & 45.5 & 15.2 & 47.1 & 13.4 & 36.0 & 17.2 & 26.1 & 0.934 & 0.244 & 20.1 & 15.9 & 27.3 & 3.8 & 36.1\tabularnewline
+ & HM{[}$\mathcal{S},g_{\mathsf{LGA}}${]} ($u=2.2$) & 8 & 34.8 & 45.5 & 15.2 & 47.1 & 13.4 & 36.0 & 17.2 & 26.1 & 0.934 & 0.244 & 20.1 & 15.9 & 27.3 & 3.8 & 36.1\tabularnewline
+ \bottomrule
 \end{tabular}}
+	\caption{The efficacy of parameter $u$ for clipping loss value $\ell_{t-1}$.
+	%
+	Stronger adversarial examples will be created for training if the loss value is not
+	clipped (equivalent to setting $u$ to the theoretical upper bound of loss,
+	\ie, 2.2).
+	}
+	\label{tab:u}
 \end{table*}
@@
 $\bar{\ell}_{t-1}$ will be smaller, and results in stronger adversarial
-examples through HM and harms the model performance on benign examples.
+examples through HM[$\mathsf{S},g_\mathsf{LGA}$] and harms the model performance on benign examples,
+as shown in \cref{tab:u}.
 
-Our LGA function $g_\mathsf{LGA}$ reuses the triplet margin parameter $\gamma$
-in order to remain in the range of Semihard, \ie, $-\gamma<g_\mathsf{LGA}<0$.
+Another parameter in $g_\mathsf{LGA}$ is the triplet margin parameter $\gamma$
+in order to align to the hardness range of Semihard triplets, \ie, $-\gamma<g_\mathsf{LGA}<0$.
 %
-Apart from this, LGA is parameter-free.
-
-(5) \ul{Weight constant $\lambda$ of ICS loss term $L_\text{ICS}$.}
-
-The weight constant $\lambda$ is set as $0.5$ by default, and $0.05$ on SOP.
-%
-As demonstrated in the experiments, there is a trade-off between robustness and
-performance on benign examples when tuning the $\lambda$ parameter.
-%
-Our experiments demonstrate that the ICS loss term is effective in improving
-adversarial training efficiency and model robustness, but in practice, the
-adopters of our method may need to re-evaluate the trade-off between
-performance and robustness, and ajudst $\lambda$ accordingly.
-
-(6) \ul{Optimization algorithm for adversarial attacks.}
-
-In this paper, PGD~\cite{madry} is adopted as the optimization algorithm for
-creating adversarial examples.
-%
-It is also adopted by the ERS metric~\cite{robrank} for robustness evaluation
-with a collection of white-box attacks.
-%
-In the literature, some other optimization methods exists, such as
-APGD~\cite{apgd}.
-%
-However, we adopt PGD~\cite{madry} to keep aligned with the state-of-the-art
-work for sake of fair comparison.
-
-A replacement of such algorithm for adversarial training will affect the
-model's performance on benign examples and robustness.
-%
-Stronger adversarial examples during adversarial training may further boost the
-robustness of a model, and further reduce the performance on benign examples.
-
-A replacement of such algorithm for ERS evaluation will affect the robustness
-score for all existing methods.
-%
-All existing methods are expected to have a lower (to a certain extent)
-robustness against a stronger algorithm than PGD.
-%
-In this case, a robust method still remains robust, and a not robust method
-remains not robust.
+We follow the common setup~\cite{revisiting} for this parameter.
 
 ~\newline
-\noindent\ul{Backbone deep neural network model.}
+\noindent\ul{(4) Constant parameter $\lambda$ for ICS loss term $L_\text{ICS}$.}
 
-The backbone model significantly influences the performance in every aspect, as
-the standard DML adopts ImageNet-initialized backbones for further training.
+The weight constant $\lambda$ is set as $0.5$ by default, and $0.05$ on the SOP dataset.
 %
-In this paper, we adopt ResNet-18 following the state-of-the-art
-defense~\cite{robrank} for fair comparison.
+As demonstrated in Tab.~5, there is a trade-off between robustness and
+performance on benign examples when tuning the $\lambda$ parameter.
+
+Additional experiments with $\lambda=0.5$ on the SOP dataset can be found in \cref{tab:soplambda}.
 %
-Since our proposed defense method is independent to backbone selection, it is
-expected to be effective on other backbone models as well.
+Our method is sensitive to this parameter.
+An excessively large $\lambda$ on the SOP datasets leads to worse performance on benign examples
+and worse robustness.
 
-Adversarial training requires more time and GPU memory than regular training.
+\begin{table*}
+\resizebox{\linewidth}{!}{
+\setlength{\tabcolsep}{0.42em}
+\renewcommand{\arraystretch}{1.1}%
+\begin{tabular}{c|cc|cccc|ccccc|ccccc|c}
+	\toprule
+\multirow{2}{*}{\textbf{Dataset}} & \multirow{2}{*}{\textbf{Defense}} & \multirow{2}{*}{$\eta$} & \multicolumn{4}{c|}{\textbf{Benign Example}} & \multicolumn{10}{c|}{\textbf{White-Box Attacks for Robustness Evaluation}} & \multirow{2}{*}{\textbf{ERS$\uparrow$}}\tabularnewline
+\cline{4-17} \cline{5-17} \cline{6-17} \cline{7-17} \cline{8-17} \cline{9-17} \cline{10-17} \cline{11-17} \cline{12-17} \cline{13-17} \cline{14-17} \cline{15-17} \cline{16-17} \cline{17-17}
+ &  &  & R@1$\uparrow$ & R@2$\uparrow$ & mAP$\uparrow$ & NMI$\uparrow$ & CA+$\uparrow$ & CA-$\downarrow$ & QA+$\uparrow$ & QA-$\downarrow$ & TMA$\downarrow$ & ES:D$\downarrow$ & ES:R$\uparrow$ & LTM$\uparrow$ & GTM$\uparrow$ & GTT$\uparrow$ & \tabularnewline
+ \midrule
+\multirow{2}{*}{SOP} & HM{[}$\mathcal{S},g_{\mathsf{LGA}}${]}\&ICS ($\lambda=0.5$) & 8 & 42.4 & 47.1 & 10.2 & 84.2 & 34.9 & 3.8 & 36.7 & 2.3 & 0.879 & 0.093 & 35.3 & 36.5 & 35.2 & 49.1 & 60.1\tabularnewline
+ & HM{[}$\mathcal{S},g_{\mathsf{LGA}}${]}\&ICS ($\lambda=0.5$) & 32 & 41.5 & 46.1 & 9.9 & 84.1 & 36.1 & 3.1 & 37.6 & 2.1 & 0.873 & 0.086 & 35.7 & 36.8 & 34.7 & 50.2 & 60.8\tabularnewline
+ \bottomrule
+\end{tabular}}
+	\caption{An excessively large $\lambda$ may lead to worse performance and robustness.}
+	\label{tab:soplambda}
+\end{table*}
+
+~\newline
+\noindent\ul{(5) Backbone deep neural network.}
+
+We adopt ResNet-18 following the state-of-the-art defense~\cite{robrank} for fair comparison.
 %
-The adversarial training of ResNet-18 with our method requires about 7\~{}10GB
-of memory per GPU in distributed data parallel mode.
+Different backbone models are expected to achieve significantly different
+robustness and benign example performance.
 
@@
 
-(1) \ul{Datasets:} All the datasets used in our paper are public datasets,
-and their corresponding papers are properly cited.
+\noindent\ul{(1) Datasets.}
 
-(2) \ul{Code and Implementation:} Our implementation is built upon PyTorch
-and the public code of the state-of-the-art defense method~\cite{robrank}
+All the datasets used in our paper are public datasets,
+and their corresponding papers are cited.
+%
+The CUB~\cite{cub200} dataset includes images of birds.
+%
+The CARS~\cite{cars196} dataset includes images of cars.
+%
+The SOP~\cite{sop} dataset includes images of online products.
+
+~\newline
+\noindent\ul{(2) Code and Implementation.}
+
+Our implementation is built upon PyTorch
+and the public code of the state-of-the-art defense method ACT~\cite{robrank}
 (License: Apache-2.0).
 
-\section{More Technical Details}
+\section{Technical Details \& Minor Discussions}
 \label{sec:b}
-
-\oo{FIXME}
-
-(2) \ul{The assumption that an ``intermediate point'' exists between regular
-training of DML model and min-max adversarial training of DML model.}
-(discussed in Sec.~1; this is the motivation of HM)
-
-We propose the flexible tool HM where regular training and min-max adversarial
-training are equivalent to its boundary cases.
-%
-By adjusting the destination hardness $H_\mathsf{D}$ in HM, we can obtain
-different results from adversarial training.
-%
-In the experiments section, we empirically search for valid options of the
-destination hardness, and add further improvements (\ie, LGA and ICS) on top of
-them.
-%
-The proposed method has been validated on three commonly used dataset, which
-demonstrates its robustness empirically.
-
-Even if the proposed method stopped working in a new dataset or with some other
-different experimental settings, we can reduce
-the value $H_\mathsf{D}$ towards $H_\mathsf{S}$ until this method works.
-%
-Since HM falls back into regular training when $H_\mathsf{D}=H_\mathsf{S}$,
-we believe our proposed method will work before $H_\mathsf{D}$ is reduced
-to $H_\mathsf{S}$.
-
-Hence, this assumption is not expected to be a limitation.
-
-(3) \ul{The assumption on optimization of the HM objective.}
-(discussed in Sec.~3.1)
-
-Our proposed method HM does not rely on an optimizer that can really optimize
-the HM objective to zero.
-%
-In contrast, the state-of-the-art defense ACT~\cite{robrank} relies on the
-optimizer to successfully push the adversarial positive sample and adversarial
-negative sample close to each other in the embedding space.
-%
-This is hard to achieve given a low adversarial training budget (\eg, $\eta=8$),
-as can be shown in our experiments and acknowledged by \cite{robrank}.
-
-(4) \ul{The assumption that $H_\mathsf{D}$ should remain Semihard.}
-(discussed in Sec.~3.2)
-
-This is empirically supported by our experimental observations.
-%
-Even if this assumption is broken under some new experiment settings,
-we can further reduce the range of $H_\mathsf{D}$ until our method works again,
-thanks to the flexibility of HM.
 
@@
 
-TODO
+The direct formulation of min-max adversarial training~\cite{madry} for
+triplet loss-based DML is:
+%
+\begin{equation}
+%
+	\theta^* = \argmin_\theta [ \argmax_{\vr_a, \vr_p, \vr_n} L_\text{T}(
+	\mA + \vr_a, \mP + \vr_p, \mN + \vr_n)]
+%
+\end{equation}
+%
+Previous works~\cite{advrank,robrank} point out this method will easily lead
+to model collapse.
+%
+Our observation is the same.
 
-Collapse even with $\eta=2$ and $\alpha=1$.
+\ul{(1) Relationship with HM:}
+
+Maximizing $L_\text{T}$ is equivalent to maximizing $\tilde{H}_\mathsf{S}$.
+%
+This can be expressed as HM[$H_\mathsf{S},2$] as discussed in Sec.~3.1.
 
@@
 \end{table*}
-
-\begin{table*}
-\resizebox{\linewidth}{!}{
-\setlength{\tabcolsep}{0.3em}
-\renewcommand{\arraystretch}{1.1}%
-\begin{tabular}{c|cc|cccc|ccccc|ccccc|c}
-\hline
-\multirow{2}{*}{\textbf{Dataset}} & \multirow{2}{*}{\textbf{Defense}} & \multirow{2}{*}{$\eta$} & \multicolumn{4}{c|}{\textbf{Benign Example}} & \multicolumn{10}{c|}{\textbf{White-Box Attacks for Robustness Evaluation}} & \multirow{2}{*}{\textbf{ERS$\uparrow$}}\tabularnewline
-\cline{4-17} \cline{5-17} \cline{6-17} \cline{7-17} \cline{8-17} \cline{9-17} \cline{10-17} \cline{11-17} \cline{12-17} \cline{13-17} \cline{14-17} \cline{15-17} \cline{16-17} \cline{17-17}
- &  &  & R@1$\uparrow$ & R@2$\uparrow$ & mAP$\uparrow$ & NMI$\uparrow$ & CA+$\uparrow$ & CA-$\downarrow$ & QA+$\uparrow$ & QA-$\downarrow$ & TMA$\downarrow$ & ES:D$\downarrow$ & ES:R$\uparrow$ & LTM$\uparrow$ & GTM$\uparrow$ & GTT$\uparrow$ & \tabularnewline
-\hline
-\hline
-\multirow{2}{*}{SOP} & HM{[}$\mathcal{S},g_{\mathsf{LGA}}${]}\&ICS ($\lambda=0.5$) & 8 & 42.4 & 47.1 & 10.2 & 84.2 & 34.9 & 3.8 & 36.7 & 2.3 & 0.879 & 0.093 & 35.3 & 36.5 & 35.2 & 49.1 & 60.1\tabularnewline
-\cline{2-18} \cline{3-18} \cline{4-18} \cline{5-18} \cline{6-18} \cline{7-18} \cline{8-18} \cline{9-18} \cline{10-18} \cline{11-18} \cline{12-18} \cline{13-18} \cline{14-18} \cline{15-18} \cline{16-18} \cline{17-18} \cline{18-18}
- & HM{[}$\mathcal{S},g_{\mathsf{LGA}}${]}\&ICS ($\lambda=0.5$) & 32 & 41.5 & 46.1 & 9.9 & 84.1 & 36.1 & 3.1 & 37.6 & 2.1 & 0.873 & 0.086 & 35.7 & 36.8 & 34.7 & 50.2 & 60.8\tabularnewline
-\end{tabular}}
-\end{table*}

### 2021-11-18 appendix.tex
tex

@@
 
+\begin{table*}[t]
+\resizebox{\linewidth}{!}{
+\setlength{\tabcolsep}{0.47em}
+\renewcommand{\arraystretch}{1.1}%
+\begin{tabular}{c|cc|cccc|ccccc|ccccc|c}
+	\toprule
+\multirow{2}{*}{\textbf{Dataset}} & \multirow{2}{*}{\textbf{Defense}} & \multirow{2}{*}{$\eta$} & \multicolumn{4}{c|}{\textbf{Benign Example}} & \multicolumn{10}{c|}{\textbf{White-Box Attacks for Robustness Evaluation}} & \multirow{2}{*}{\textbf{ERS$\uparrow$}}\tabularnewline
+\cline{4-17} \cline{5-17} \cline{6-17} \cline{7-17} \cline{8-17} \cline{9-17} \cline{10-17} \cline{11-17} \cline{12-17} \cline{13-17} \cline{14-17} \cline{15-17} \cline{16-17} \cline{17-17}
+ &  &  & R@1$\uparrow$ & R@2$\uparrow$ & mAP$\uparrow$ & NMI$\uparrow$ & CA+$\uparrow$ & CA-$\downarrow$ & QA+$\uparrow$ & QA-$\downarrow$ & TMA$\downarrow$ & ES:D$\downarrow$ & ES:R$\uparrow$ & LTM$\uparrow$ & GTM$\uparrow$ & GTT$\uparrow$ & \tabularnewline
+ \midrule
+\multirow{3}{*}{CUB} & HM{[}$\mathcal{S},g_{\mathsf{1/2}}${]} & 8 & 38.7 & 48.5 & 22.0 & 49.2 & 12.6 & 48.6 & 12.3 & 41.3 & 0.562 & 0.825 & 13.5 & 12.9 & 26.9 & 1.8 & 31.7\tabularnewline
+& HM{[}$\mathcal{S},g_{\mathsf{LGA}}${]} & 8 & 38.0 & 48.3 & 21.8 & 49.3 & 12.7 & 46.4 & 11.6 & 39.9 & 0.567 & 0.783 & 16.8 & 11.9 & 27.9 & 1.4 & 32.4\tabularnewline
+& HM{[}$\mathcal{S},g_{\mathsf{2}}${]} & 8 & 37.4 & 48.2 & 17.1 & 49.2 & 12.9 & 45.1 & 13.2 & 39.1 & 0.599 & 0.738 & 17.7 & 12.8 & 27.5 & 1.9 & 33.1\tabularnewline
+\bottomrule
+\end{tabular}}
+	\caption{Non-linear Gradual Adversary Examples.}
+	\label{tab:nonlinga}
+\end{table*}
+
 ~\newline\textbf{III. Min-max Adversarial Training with Triplet Loss.}
@@
 
-\noindent\textbf{I. Range of Hardness.}
+\noindent\textbf{I. Adjustable Items}
+
+The only two adjustable items in HM are $H_\mathsf{S}$ and $H_\mathsf{D}$.
+%
+They are discussed in the ``Performance-Sensitive Factors'' part of the
+previous section.
+
+~\newline
+\noindent\textbf{II. Range of Hardness.}
 
@@
 ~\newline
-\noindent\textbf{II. Parameters or Adjustable Items}
-
-The only two adjustable items in HM are $H_\mathsf{S}$ and $H_\mathsf{D}$.
-%
-They are further discussed in the previous section in this supplementary
-material (see the ``Performance-Sensitive Factors'' part of the previous
-section).
-
-Since PGD~\cite{madry} is adopted for optimizing the objective of HM, the
-PGD parameters (including perturbation budget $\varepsilon$, maximum step
-$\eta$, as well as step size $\alpha$) will also influence the result.
-%
-We use the parameter setting following the state-of-the-art
-defense~\cite{robrank} for fair comparison.
-
-In most experiments that demonstrate the effectiveness of our method, the
-$\eta$ is set as $8$ because the ERS start to plateau with a larger $\eta$
-according to our observation.
-
-~\newline
-\noindent\textbf{III. HM and ACT}
-
-ACT~\cite{robrank} is proposed in order to address the ``misleading gradient''
-and ``inefficient mini-batch exploitation'' problems.
-%
-HM does not push the embeddings towards arbitrary directions, and hence does
-not suffer from both issues.
-%
-On the other hand, ACT does not perturb the anchor sample, and the same
-can be done in HM.
-%
-When the anchor sample is unperturbed, adversarial training with HM leads to
-a higher performance on benign examples but a lower robustness.
-%
-Unlike perturbing $(\mA, \mP, \mN)$ altogether, only perturbing $(\mP, \mN)$
-leads to a weaker adversarial examples, and hence lower robustness.
-%
-Our first priority is to improve model robustness, so the case with fixed
-anchor is omitted from manuscript to avoid complexity.
-
-~\newline
-\noindent\textbf{IV. Mixing HM[$\mathcal{R},\mathcal{M}$] and
+\noindent\textbf{III. Mixing HM[$\mathcal{R},\mathcal{M}$] and
 HM[$\mathcal{S},\mathcal{M}$]}
@@
 
-\noindent\textbf{I. Parameters or Adjustable Items}
+\noindent\textbf{I. Parameters}
 
-The parameters, namely $u$ and $\xi$ are discussed in the previous section
+The parameters, namely $u$ and $\gamma$ are discussed in the previous section
 of this supplementary material, see ``Performance-Sensitive Factors''.
+
+The parameter $\xi$ in $g_\mathsf{B}$ is set as $0.1$, but it is not an important parameter.
+%
+The function $g_\mathsf{B}$ is only used for demonstrating that ``slightly
+boosting the destination hardness can further increase ERS'' as discussed
+in Sec.~3.1.
 
@@
 
-In the manuscript, Linear Graduate Adversarial is demonstrated effective,
-and more complicated choices are left for future work.
+In Sec.~3.2, more complicated designs are left for future work.
 %
-Here we provide two Non-linear Graduate Adversary examples, namely
+We provide two Non-linear Graduate Adversary examples, namely
 $g_\mathsf{2}$ and $g_\mathsf{1/2}$, as follows:
@@
 (adversarial examples from HM are stronger if the function value is closer to $0$).
+%
+The corresponding experiments can be found in \cref{tab:nonlinga}.
 
-\oo{experiments?}
+\oo{TODO}
 

### 2021-11-18 appendix.tex
sup

@@
 
-In this supplementary material, we provide further technical details and the
-less important discussions that are not included in the manuscript due to space
+In this supplementary material, we provide more technical details and
+additional discussions that are excluded from the manuscript due to space
 limit.
-%
-Discussions required by the author guidelines are also included in this
-supplementary material.
 
@@
 
-We adopt ResNet-18 following the state-of-the-art defense~\cite{robrank} for fair comparison.
+We adopt ResNet-18 following the state-of-the-art defense~\cite{robrank} for
+fair comparison.
 %
-Different backbone models are expected to achieve significantly different
-robustness and benign example performance.
+Since our proposed method is independent to the backbone choice, and hence
+is expected to be effective with different backbone models.
+
+\oo{TODO: mnasnet ghmetsm ghmetsmi}
 
@@
 
-\subsection{State-of-The-Art Defenses}
+\subsection{Difference between Existing Defenses \& HM}
 \label{sec:b1}
@@
 %
-Our observation is the same.
+Our observation suggests the same.
 
@@
 ~\newline
-\noindent\textbf{II. Range of Hardness.}
+\noindent\textbf{II. Extreme Values of Hardness.}
 
@@
 
-~\newline
-\noindent\textbf{III. Mixing HM[$\mathcal{R},\mathcal{M}$] and
-HM[$\mathcal{S},\mathcal{M}$]}
-
-According to the experimental results, HM[$\mathcal{R},\mathcal{M}$] achieves 
-a high ERS and adversarial training efficiency, but suffers from a low R@1.
-%
-HM[$\mathcal{S},\mathcal{M}$] achieves a high R@1, but its ERS and efficiency
-could be further improved.
-%
-They can be mixed for adversarial training with a probability $p$ to combine
-their advantages, but the eventual overall performance is still lower than
-that of HM[$\mathcal{S},g_\mathsf{LGA}$] according to our observation.
-
 \subsection{Graduate Adversary}
@@
 
-\oo{TODO}
-
 \subsection{Intra-Class Structure (ICS)}
 
-\noindent\textbf{I. Parameters or Adjustable Items}
+\noindent\textbf{I. Parameters}
 
@@
 %
-The only parameter for ICS loss term is the weight constant $\lambda$.
-%
-The selection of this parameter is discussed in the previous section of this
-supplementary material (see ``Performance-Sensitive Factors'').
+The only parameter for ICS loss term is the weight constant $\lambda$,
+and has been discussed in the ``Performance-Sensitive Factors'' part
+of the previous section.
 
@@
 when $L_\text{T}>0$.
-And the above equations have been reflected in Fig.~5 (a) with correct directions.
+And the above equations have been reflected in Fig.~5 (a) in terms of vector direction.
 
@@
 %
-Other alternative sections of triplets from the sextuplet are also
-possible.
+Other alternative selections of triplets from the sextuplet are possible,
+but are not as effective as $L_\text{ICS}$ for improving adversarial robustness.
 
-\ul{(1) Why not use $L_\text{T}(\va, \tilde{\va}, \tilde{\vp})$? }
+\ul{(1) $L_\text{T}(\va, \tilde{\va}, \tilde{\vp})$}
 
@@
 %
-Thus, the loss term in the question is not as effective as $L_\text{ICS}$.
+Thus, the loss value of $L_\text{T}(\va, \tilde{\va}, \tilde{\vp})$ will always
+be smaller than $L_\text{ICS}$, and hence is less effective than $L_\text{ICS}$.
 
-\ul{(2) What if $L_\text{T}(\va, \vp, \vn)$ is used? Namely, the regular training
-and adversarial training are mixed together.}
+\ul{(2) $L_\text{T}(\va, \vp, \vn)$: Mixing regular training
+and adversarial training.}
 
 According to our observation, mixing regular training and adversarial training
-leads to better R@1 but very drastic robustness degradation for both ACT and
-our proposed defense.
+leads to better R@1 with drastic robustness degradation for both ACT and
+our defense.
 
-\ul{(3) Why not use the symmetric counterpart of $L_\text{ICS}$, \ie,
-		$L_\text{T}(\vp, \tilde{\vp}, \va)$?}
+\ul{(3) $L_\text{T}(\vp, \tilde{\vp}, \va)$: Symmetric counterpart of $L_\text{ICS}$.}
 
@@
 %
-Such symmetric loss term is duplication to $L_\text{ICS}$ and is
+Such symmetric loss term is duplicated to $L_\text{ICS}$ and is
 not necessary.
 %
-Experimental results suggest negligible difference.
+Experimental results suggest negligible difference compared to $L_\text{ICS}$.
 
-\ul{(4) $\tilde{\vn}$ is very close to $\va$ in Fig.~5 in manuscript.
-Why not use $L_\text{T}(\va, \tilde{\va}, \tilde{\vn})$?}
+\ul{(4) $L_\text{T}(\va, \tilde{\va}, \tilde{\vn})$: $\tilde{\vn}$ is very close to $\va$ in Fig.~5.}
 
-The loss term in question is enforcing inter-class structure instead of
-intra-class structure.
+It enforces \emph{inter}-class structure instead of intra-class structure.
 %
@@
 %
-We speculate this loss term is duplicated to the adversarial training term,
+We speculate this loss term is duplicated to the adversarial training loss term,
 \ie, $L_\text{T}(\tilde{\va}, \tilde{\vp}, \tilde{\vn})$, which enforces
-inter-class structure in a stronger manner.
+inter-class structure as well in a stronger manner.
 
-\ul{(5) Similar to question (4), why not use $L_\text{T}(\va, \vp, \tilde{\vn})$ ?}
+\ul{(5) $L_\text{T}(\va, \vp, \tilde{\vn})$}
 
@@
 
-\subsection{Empirical Robustness Score (ERS)}
+\subsection{Experiments and Evaluation}
 
-\oo{todo}
-
-\subsection{Hardware and Software Platform}
+\noindent\textbf{I Hardware and Software Configuration}
 
@@
 under the Ubuntu 16.04 operating system with PyTorch 1.8.2 in distributed data
-parallel mode.
-%
-Note, the training result of all methods in distributed data parallel mode
-slightly differs from the result obtained in single-GPU mode, due to the
-asynchronized gradient updates in the distributed mode (this is a common
-phenomenon in distributed deep learning).
-%
-In fact, our method can be even more efficient in single-GPU mode thanks to the
-synchornized gradients, but single-GPU mode will be extremely time consuming
-(more than a week for a single run of the most time-consuming experiment).
-%
-All of our experiments are conducted in distributed data parallel mode for ease
-of comparison, as well as controlling the time cost.
-
-\subsection{Experiments and Evaluation}
+parallel.
 

### 2021-11-18 appendix.tex
sup

@@
 
-\noindent\textbf{I. Detailed Interpretation of Experimental Results}
-
-\ul{(1) Table.~1: ``Mean \& Variance ...'''}
-
-\ul{(2) Table.~2: ``... Source \& Destination Hardness ...''}
-
-\ul{(3) Table.~3: ``Hardness Manipulation ...'' and Fig.~6}
-
-\ul{(4) Table.~4: ``... Graduate Adversary ...'' and Fig.~7}
-
-\ul{(5) Table.~5: ``Intra-Class Structure ...'' and Fig.~8}
-
-\ul{(6) Table.~6: ``... State-of-The-Art ...''}
-
-\oo{todo}
-
 ~\newline
@@
 In the manuscript, the training cost of adversarial training is caluclated as
-$\eta+1$, which is a theoretical number of forward-backward propagation
-involved in each iteration of the training process.
+$\eta+1$, which is the number of forward-backward propagation involved in each
+iteration of the training process, in order to reflect the training efficiency
+(gain as high robustness as possible given a fixed number of foward-backward
+calculation for adversarial training) of different defense methods.
 %
-The wall time is not used, because the wall time is noisy, and will be affected
-by many irrevevant factors which eventually makes the result uncomparable or
-unfair.
+Specifically, PGD creates adversarial examples from the $\eta$ times of
+forward-backward computation.
 %
-The factors that affect the wall time for adversarial training include but are
-not limited to:
-%
-(1) GPU Performance. For instance, the wall time reported based on eight Nvidia
-A100 GPUs will not be valuable for readers who do not have access to the same
-hardware;
-%
-(2) System load when training, CPU performance, and I/O device performance;
-%
-(3) Code implementation and engineering tricks. Well-optimized code will
-consume less time.
-%
-Namely, the wall time is a noisy measure of training cost which will render
-invalid comparison or unfair comparison.
-%
-In contrast, the training cost measure ($\eta+1$) in the manuscript has
-isolated all irrelevant factors.
-
-For reference, the most time-consuming experiment is
-HM[$\mathcal{S},g_\mathsf{LGA}$] on the SOP dataset.
-%
-When $\eta=8$, the experiment takes $32$ hours with two Nvidia Titan Xp GPUs;
-%
-When $\eta=32$, the experiment takes $105$ hours with two Nvidia Titan Xp GPUs.
+With the resulting adversarial examples, the network requires once
+more forward-backward computation to update the model parameters.
 

### 2021-11-18 appendix.tex
tex

@@
 
+\begin{table*}
+\resizebox{\linewidth}{!}{
+\setlength{\tabcolsep}{0.47em}
+\renewcommand{\arraystretch}{1.1}%
+\begin{tabular}{c|cc|cccc|ccccc|ccccc|c}
+	\toprule
+\multicolumn{1}{c|}{\multirow{2}{*}{\textbf{Dataset}}} & \multirow{2}{*}{\textbf{Defense}} & \multirow{2}{*}{$\eta$} & \multicolumn{4}{c|}{\textbf{Benign Example}} & \multicolumn{10}{c|}{\textbf{White-Box Attacks for Robustness Evaluation}} & \multirow{2}{*}{\textbf{ERS$\uparrow$}}\tabularnewline
+\cline{4-17} \cline{5-17} \cline{6-17} \cline{7-17} \cline{8-17} \cline{9-17} \cline{10-17} \cline{11-17} \cline{12-17} \cline{13-17} \cline{14-17} \cline{15-17} \cline{16-17} \cline{17-17}
+ &  &  & R@1$\uparrow$ & R@2$\uparrow$ & mAP$\uparrow$ & NMI$\uparrow$ & CA+$\uparrow$ & CA-$\downarrow$ & QA+$\uparrow$ & QA-$\downarrow$ & TMA$\downarrow$ & ES:D$\downarrow$ & ES:R$\uparrow$ & LTM$\uparrow$ & GTM$\uparrow$ & GTT$\uparrow$ & \tabularnewline
+ \midrule
+\multirow{2}{*}{CUB} & HM{[}$\mathcal{S},g_{\mathsf{LGA}}${]}\&ICS & 8 & 37.2 & 47.8 & 21.4 & 48.4 & 12.9 & 40.9 & 14.7 & 33.7 & 0.806 & 0.487 & 17.1 & 13.2 & 26.3 & 2.3 & 33.5\tabularnewline
+& HM[$\mathcal{S},g_\mathsf{LGA}$]\&$L_\text{ICS}(\cdots;\gamma=0.2)$ & 8 & 35.8 & 46.6 & 16.4 & 48.3 & 13.2 & 39.9 & 12.7 & 33.3 & 0.775 & 0.507 & 15.9 & 14.9 & 27.2 & 2.7 & 33.6\tabularnewline
+ \bottomrule
+\end{tabular}}
+	\caption{The margin parameter is set to $0$ in order to avoid negative effect.
+	%
+	R@1 performance drops with marginal robustness gain.}
+	\label{tab:0margin}
+\end{table*}
+
 \subsection{Intra-Class Structure (ICS)}
@@
 of the previous section.
+
+The margin parameter is set to $0$ in order to avoid negative effect in $L_\text{ICS}$,
+as shown in \cref{tab:0margin}.
 
@@
 \oo{explain lower ERS with high eta? overfit.}
-
-\begin{table*}
-\resizebox{\linewidth}{!}{
-\setlength{\tabcolsep}{0.47em}
-\renewcommand{\arraystretch}{1.1}%
-\begin{tabular}{c|cc|cccc|ccccc|ccccc|c}
-\hline
-\multirow{2}{*}{\textbf{Dataset}} & \multirow{2}{*}{\textbf{Defense}} & \multirow{2}{*}{$\eta$} & \multicolumn{4}{c|}{\textbf{Benign Example}} & \multicolumn{10}{c|}{\textbf{White-Box Attacks for Robustness Evaluation}} & \multirow{2}{*}{\textbf{ERS$\uparrow$}}\tabularnewline
-\cline{4-17} \cline{5-17} \cline{6-17} \cline{7-17} \cline{8-17} \cline{9-17} \cline{10-17} \cline{11-17} \cline{12-17} \cline{13-17} \cline{14-17} \cline{15-17} \cline{16-17} \cline{17-17}
- &  &  & R@1$\uparrow$ & R@2$\uparrow$ & mAP$\uparrow$ & NMI$\uparrow$ & CA+$\uparrow$ & CA-$\downarrow$ & QA+$\uparrow$ & QA-$\downarrow$ & TMA$\downarrow$ & ES:D$\downarrow$ & ES:R$\uparrow$ & LTM$\uparrow$ & GTM$\uparrow$ & GTT$\uparrow$ & \tabularnewline
-\hline
-\hline
-\multirow{6}{*}{CUB} & HM{[}$\mathcal{R},\mathcal{M}${]} & 8 & 27.0 & 36.0 & 13.2 & 42.5 & 19.4 & 48.0 & 22.2 & 32.0 & 0.535 & 0.867 & 11.6 & 10.4 & 19.3 & 2.9 & 35.1\tabularnewline
- & HM{[}$\mathcal{R},g_{\mathsf{B}}(\mathcal{M})${]} & 8 & 24.9 & 33.4 & 12.0 & 41.7 & 21.6 & 45.1 & 24.9 & 29.1 & 0.515 & 0.780 & 12.3 & 12.1 & 19.7 & 3.7 & 37.6\tabularnewline
- & HM{[}$\mathcal{R},0${]} & 8 & 2.4 & 3.8 & 1.1 & 21.7 & 40.8 & 22.3 & 42.2 & 16.7 & 1.000 & 0.000 & 1.6 & 1.2 & 1.7 & 7.0 & 43.9\tabularnewline
- & HM{[}$\mathcal{R},-\gamma/2${]} & 8 & 25.5 & 34.5 & 12.8 & 41.7 & 21.9 & 41.5 & 23.8 & 27.0 & 0.493 & 0.784 & 13.5 & 11.8 & 20.3 & 3.6 & 38.3\tabularnewline
- & HM{[}$\mathcal{R},-\gamma${]} & 8 & 27.5 & 36.5 & 13.5 & 42.5 & 18.1 & 54.0 & 19.9 & 37.5 & 0.561 & 0.925 & 9.9 & 9.7 & 18.6 & 1.7 & 32.2\tabularnewline
- & HM{[}$\mathcal{R},g_{\mathsf{LGA}}${]} & 8 & 24.8 & 33.9 & 12.2 & 41.6 & 21.4 & 45.0 & 21.7 & 31.3 & 0.452 & 0.846 & 13.2 & 12.0 & 20.9 & 4.6 & 37.3\tabularnewline
-\multicolumn{1}{c}{} & HM{[}$\mathcal{S},g_{\mathsf{1/2}}${]} & 8 & 37.7 & 48.5 & 22.0 & 49.2 & 12.6 & 48.6 & 12.3 & 41.3 & 0.562 & 0.825 & 13.5 & 12.9 & 26.9 & 1.8 & 31.7\tabularnewline
-\multicolumn{1}{c}{} & HM{[}$\mathcal{S},g_{\mathsf{LGA}}${]} & 8 & 38.0 & 48.3 & 21.8 & 49.3 & 12.7 & 46.4 & 11.6 & 39.9 & 0.567 & 0.783 & 16.8 & 11.9 & 27.9 & 1.4 & 32.4\tabularnewline
-\multicolumn{1}{c}{} & HM{[}$\mathcal{S},g_{\mathsf{2}}${]} & 8 & 37.4 & 48.2 & 17.1 & 49.2 & 12.9 & 45.1 & 13.2 & 39.1 & 0.599 & 0.738 & 17.7 & 12.8 & 27.5 & 1.9 & 33.1\tabularnewline
-\multicolumn{1}{c}{} & LGA u=2.2 &  & 34.8 & 45.5 & 15.2 & 47.1 & 13.4 & 36.0 & 17.2 & 26.1 & 0.934 & 0.244 & 20.1 & 15.9 & 27.3 & 3.8 & 36.1\tabularnewline
-\end{tabular}}
-\end{table*}
-
-\begin{table*}
-\resizebox{\linewidth}{!}{
-\setlength{\tabcolsep}{0.3em}
-\renewcommand{\arraystretch}{1.1}%
-\begin{tabular}{ccc|cccc|ccccc|ccccc|c}
-\hline
-\multicolumn{1}{c|}{\multirow{2}{*}{\textbf{Dataset}}} & \multirow{2}{*}{\textbf{Defense}} & \multirow{2}{*}{$\eta$} & \multicolumn{4}{c|}{\textbf{Benign Example}} & \multicolumn{10}{c|}{\textbf{White-Box Attacks for Robustness Evaluation}} & \multirow{2}{*}{\textbf{ERS$\uparrow$}}\tabularnewline
-\cline{4-17} \cline{5-17} \cline{6-17} \cline{7-17} \cline{8-17} \cline{9-17} \cline{10-17} \cline{11-17} \cline{12-17} \cline{13-17} \cline{14-17} \cline{15-17} \cline{16-17} \cline{17-17}
- &  &  & R@1$\uparrow$ & R@2$\uparrow$ & mAP$\uparrow$ & NMI$\uparrow$ & CA+$\uparrow$ & CA-$\downarrow$ & QA+$\uparrow$ & QA-$\downarrow$ & TMA$\downarrow$ & ES:D$\downarrow$ & ES:R$\uparrow$ & LTM$\uparrow$ & GTM$\uparrow$ & GTT$\uparrow$ & \tabularnewline
-\hline
-{*} & HM{[}$\mathcal{S},g_{\mathsf{LGA}}${]} & 8 & 35.5 & 46.3 & 20.3 & 47.5 & 14.6 & 41.1 & 14.3 & 34.5 & 0.530 & 0.739 & 18.1 & 13.1 & 27.9 & 2.1 & 35.3\tabularnewline
- & +0.5i aap & 8 & 34.8 & 45.2 & 19.8 & 47.6 & 15.6 & 35.9 & 18.5 & 28.2 & 0.802 & 0.447 & 19.2 & 13.9 & 26.3 & 2.9 & 36.4\tabularnewline
- & +i aap & 8 & 34.7 & 45.6 & 19.5 & 46.9 & 16.9 & 34.2 & 18.9 & 26.7 & 0.904 & 0.296 & 20.4 & 16.1 & 26.6 & 4.2 & 37.3\tabularnewline
- & +i aap aan){*}1.0 & 8 & 34.2 & 44.7 & 19.3 & 47.9 & 15.2 & 35.2 & 18.0 & 27.1 & 0.902 & 0.301 & 17.9 & 15.0 & 28.5 & 3.0 & 36.3\tabularnewline
- & +i aa\textasciitilde p apn\textasciitilde{} 1.0 & 8 & 37.9 & 49.4 & 22.5 & 49.2 & 12.9 & 45.9 & 15.0 & 38.9 & 0.909 & 0.378 & 14.8 & 11.7 & 25.3 & 0.9 & 31.4\tabularnewline
- & ICS gamma 0.2 &  & 35.8 & 46.6 & 16.4 & 48.3 & 13.2 & 39.9 & 12.7 & 33.3 & 0.775 & 0.507 & 15.9 & 14.9 & 27.2 & 2.7 & 33.6\tabularnewline
-\end{tabular}}
-\end{table*}

### 2021-11-18 appendix.tex
sup

@@
 
-~\newline\textbf{III. Other DML Loss Functions}
+~\newline\textbf{III. Other Loss Functions}
 
-Although the traditional triplet loss could reach the state-of-the-art
-performance with an appropriate sampling strategy, many other DML loss
-functions are proposed.
+Adversarial trainig with DML loss functions other than triplet loss is
+insufficiently explored.
 %
-Adversarial trainig with other DML loss functions is unexplored.
+New metric learning loss functions oriented for adversarial training are also
+left for future study.
 %
-New metric learning loss functions oriented for adversarial training is
-also left for future study.
+Besides, model collapse is an inevitable problem for adversarial training
+with triplet loss, and it is unknown whether other loss functions could
+mitigate this issue.
 

### 2021-11-18 appendix.tex
sup

@@
 
-\noindent\textbf{I. Further Improving Efficiency of HM}
+\noindent\textbf{I. Faster Adversarial Training with HM}
 
-Being able to gain a higher robustness at a lower training cost indicates a
-higher efficiency.
+As discussed in Sec.~3.1, one potential adversarial training acceleration
+method is to incorporate Free Adversarial Training (FAT)~\cite{freeat}
+(originally for classification) into our DML adversarial training with HM.
 %
-As discussed in Sec.~3.1, one potential way to further improve the adversarial
-training efficiency is to incorporate adversarial training acceleration methods
-such as Free Adversarial Training (FAT)~\cite{freeat} (for classification) into
-our DML adversarial training.
-
-We have tried to direct adopt FAT for adversarial training of DML model.
+Besides, directly incorporating FAT into the min-max adversarial training of
+DML will easily result in model collapse as well, because the FAT algorithm can
+be interpreted as to maintain a universal (agnostic to sample) perturbation
+that can maximize the loss.
 %
-According to our observation, the model (RN18 on CUB dataset) is still prone
-to collapse because the FAT algorithm can be interpreted as to maintain
-a universal (agnostic to sample) perturbation that can maximize the loss.
-%
-Simple workarounds such as decaying the perturbation does not address this
-issue.
-
-Thus, our conclusion is that a non-trivial modification is still required
-to incorporate the idea of FAT into adversarial training of DML model.
-
-On the other hand, ACT~\cite{robrank} has a different inner loss function to
-the outer minimization problem, and hence result in different gradients in the
-inner and outer problems.
-%
-In this way, the gradients cannot be reused by FAT.
-%
-Re-calculating the gradients we need would simply double the
-computational cost of the algorithm and halves the efficiency gain from FAT.
+Thus, non-trivial modifications are still required to incorporate FAT FAT into
+adversarial training with HM. This is left for future work.
 
@@
 
-~\newline\textbf{II. More Appropriate Destination Hardness}
+~\newline\textbf{II. Better Choice for Destination Hardness}
 
-We drew the conclusion that ``adversarial triplets should remain Semihard''
-based on the empirical experimental results in Tab.~2 in the manuscript.
+The proposed LGA function incorporates our empirical observation that
+``adversarial triplets should remain Semihard'' based on the results in Tab.~2.
 %
-However, a better choice for $H_\mathsf{D}$ may exist between ``Semihard''
-and ``Softhard''.
+However, a better choice for $H_\mathsf{D}$ may exist between ``Semihard'' and
+``Softhard'' that can achieve better overall performance.
 %
-Exploration of a better source triplet sampling strategy for adversarial
-training, as well as a better hardness range for adversarial triplets
-may also be a direction for further robustness improvement.
-%
-In the manuscript, we only use the existing sampling methods in order to focus
-on our contributions.
+In the manuscript, we only use the existing sampling methods and simple
+pseudo-hardness functions in order to avoid distraction from our focus.
 
@@
 
-It is unknown how defense methods for DML relates to the classification defense
-task.
-%
-DML is closely related to self-supervised learning.
-%
-It is also unknown if a defense for the supervised learning scenario will
-inspire the defense for unsupervised robust feature learning.
+It is unknown whether DML defenses will improve the robustness in the
+classification task.
 

### 2021-11-18 appendix.tex
sup

@@
 
+~\newline
+\noindent\textbf{IV. Additional Notes on the Experimental Results}
+
+\oo{explain lower ERS with high eta? overfit.}
+
 \subsection{Potential Future Work}
@@
 classification task.
-
-\begin{comment}
-
- [T] By incorporating the idea of on-manifold adversarial example to
-	adversarial training, the performance on benign example is greatly
-	improved.
-	%
-	That idea can be interpreted as to be selective on the adversarial example
-	used for trianing.
-	%
-	Here, in our observation, we are also selective on the adversarial examples
-	used for training.
-	%
-	Is there anything in common?
-
-[TODO LIST]
-
-Before deadline
-
-* Revise figures
-
-* Revise manuscript
-
-After deadline: supplementary
-
-* add discussions and additional experiments
-\end{comment}
-
-\oo{explain lower ERS with high eta? overfit.}

### 2021-11-18 appendix.tex
sup

@@
 
-\oo{explain lower ERS with high eta? overfit.}
+\noindent\ul{(1) Slight ERS decrease with a larger $\eta$}
+
+In some cases, \eg, HM[$\mathcal{S},g_\mathsf{LGA}$]\&ICS on the CARS dataset
+reaches a slightly lower ERS with $\eta=32$ compared to that with $\eta=8$.
+%
+We speculate this is because adversarial training suffers from overfitting~\cite{bagoftricks,overfitting}
+on adversarial examples, as mentioned in Sec.~2.
 
@@
 adversarial training with HM. This is left for future work.
-
-\begin{comment}
-FAT works on toy dataset only for adversarial DML.
-
-Further experiments suggest very weak robustness and the
-models are very prone to collapse due to the non-zero initial delta
-(results in too hard adversarial example).
-
-Gradient approximation does not work. Triplet gradient and ACT
-gradient are convertible.
-
-Does the new generic HM work under FAT?
-	Previous FAT leads to collapse because (even if in the amdsemi +fat
-	experiment due to implementation issue) the delta is going to be universal
-	so that for every input $x$ it will increase $H[L(x)]$ as much as possible.
-	This is too prone to lead to collpase. Can we reuse the gradient for 
-	Hardness Manipulation then? We linearly scale down the delta?
-	We want to minimize $E[|H_{src}(x)-H_{dst}(x)|]$ (to a specified hardness).
-\end{comment}
 
@@
 
-\oo{[TODO] arxiv 2105.04906 for collapse issue.}
-
 ~\newline\textbf{IV. DML \& Classification}

### 2021-11-18 appendix.tex
typo

@@
 iteration of the training process, in order to reflect the training efficiency
-(gain as high robustness as possible given a fixed number of foward-backward
+(gain as high robustness as possible given a fixed number of forward-backward
 calculation for adversarial training) of different defense methods.

### 2022-01-24 reb/RebuttalTemplate.tex
reb

\documentclass[10pt,twocolumn,letterpaper]{article}
\usepackage[rebuttal]{cvpr}

% Include other packages here, before hyperref.
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref,breaklinks,colorlinks,bookmarks=false]{hyperref}

% Support for easy cross-referencing
\usepackage[capitalize]{cleveref}
\crefname{section}{Sec.}{Secs.}
\Crefname{section}{Section}{Sections}
\Crefname{table}{Table}{Tables}
\crefname{table}{Tab.}{Tabs.}

% If you wish to avoid re-using figure, table, and equation numbers from
% the main paper, please uncomment the following and change the numbers
% appropriately.
%\setcounter{figure}{2}
%\setcounter{table}{1}
%\setcounter{equation}{2}

% If you wish to avoid re-using reference numbers from the main paper,
% please uncomment the following and change the counter for `enumiv' to
% the number of references you have in the main paper (here, 6).
%\let\oldthebibliography=\thebibliography
%\let\oldendthebibliography=\endthebibliography
%\renewenvironment{thebibliography}[1]{%
%     \oldthebibliography{#1}%
%     \setcounter{enumiv}{6}%
%}{\oldendthebibliography}

%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\cvprPaperID{201}% *** Enter the CVPR Paper ID here
\def\confName{CVPR}
\def\confYear{2022}

\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{Enhancing Adversarial Robustness for Deep Metric Learning -- Author Response}  % **** Enter the paper title here

\maketitle
\thispagestyle{empty}
\appendix

%%%%%%%%% BODY TEXT - ENTER YOUR RESPONSE BELOW
\section{To Reviewer \#1}

This manuscript investigates the joint area of DML and robustness against adversarial attacks of deep model. I understand that some DML applications may require robustness. However, the potential impact of the research topic is limited. From my view, the DML models are not special in terms of robustness against adversarial attacks compared to other deep models.

Another non-negligible problem is the discussion of the relationship between the proposed method and a series of adversarial training algorithms is missing. I’m hoping that the author could complete it in the related works section, including reference 29. “Sat: Improving adversarial training via curriculum-based loss smoothing” in the original manuscript and some other studies, such as [1] and [2]. I think the idea of the proposed method bears a certain similarity to these.

[1]. Cai, Qi-Zhi, et al. "Curriculum adversarial training." arXiv preprint arXiv:1805.04807 (2018).

[2]. Zhu, Xiaojin. "An optimal control view of adversarial machine learning." arXiv preprint arXiv:1811.04422 (2018).

\section{To Reviewer \#2}

- Paper is sometimes hard to read, sentences tend to be too long and complex, method abbreviations are confusing and hard to remember.

- Tables are hard to grasp at a first glance, too many abbreviations and notations. It would be useful to make captions self explanatory and refresh the notation in them so that I dont have to search for them in different places of the paper. Also, some color coding or marking the most important results would be useful it is hard to ONE table with 20 rows and 20 columns, even harder with 5 such tables.

- Paragraph on memory and time complexity between methods missing, are they all equal?

\section{To Reviewer \#3}

1. Robustness is important and many novel methods have been proposed, e.g., TRADES and AWP. I wonder whether these methods are not suitable for the metric learning task, and why the robustness of the metric learning task is unique.

2. The main motivation of this work is that previous works suffer from excessively hard examples and this work aims to control the hardness. Does simple tricks like mixup work for adjusting the hardness.

3. Tables (e.g., Tab.3) is hard to read. The authors may need to re-organize them and highlight somewhere.

4. The performance on benign examples seems to drop a lot. Does it mean the HM is just another trade-off way?

%%%%%%%%% REFERENCES
{\small
\bibliographystyle{ieee_fullname}
\bibliography{egbib}
}

\end{document}

### 2022-01-24 reb/RebuttalTemplate.tex
reb

@@
 \usepackage{booktabs}
+\usepackage{microtype}
+\usepackage{soul}
 
@@
 %%%%%%%%% BODY TEXT - ENTER YOUR RESPONSE BELOW
-\section{To Reviewer \#1}
+\section*{To Reviewer \#1}
 
-This manuscript investigates the joint area of DML and robustness against adversarial attacks of deep model.
-I understand that some DML applications may require robustness.
-However, the potential impact of the research topic is limited.
-From my view, the DML models are not special in terms of robustness against adversarial attacks compared to other deep models.
+\noindent\textbf{Q1.}
+%
+\ul{
+From my view, the DML models are not special in terms of robustness against
+adversarial attacks compared to other deep models.
+}
 
-Another non-negligible problem is the discussion of the relationship between the proposed method and a series of adversarial training algorithms is missing.
-I’m hoping that the author could complete it in the related works section, including reference 29.
-“Sat: Improving adversarial training via curriculum-based loss smoothing” in the original manuscript and some other studies, such as [1] and [2].
-I think the idea of the proposed method bears a certain similarity to these.
+\noindent\textbf{Q2.}
+%
+\ul{
+The discussion of the relationship between the proposed method and a series of
+adversarial training algorithms is missing.
+}
+
+I’m hoping that the author could complete it in the related works section,
+including reference 29. “Sat: Improving adversarial training via
+curriculum-based loss smoothing” in the original manuscript and some other
+studies, such as [1] and [2]. I think the idea of the proposed method bears a
+certain similarity to these.
 
@@
 
-\section{To Reviewer \#2}
+\section*{To Reviewer \#2}
 
-- Paper is sometimes hard to read, sentences tend to be too long and complex, method abbreviations are confusing and hard to remember.
+\noindent\textbf{Q1.}
+%
+\ul{
+Sentences tend to be too long and complex; Method abbreviations are confusing
+and hard to remember.
+}
 
-- Tables are hard to grasp at a first glance, too many abbreviations and notations.
-It would be useful to make captions self explanatory and refresh the notation in them so that I dont have to search for them in different places of the paper.
-Also, some color coding or marking the most important results would be useful it is hard to ONE table with 20 rows and 20 columns, even harder with 5 such tables.
+\noindent\textbf{Q2.}
+%
+\ul{
+Tables are hard to grasp at a first glance, too many abbreviations and
+notations. It would be useful to make captions self explanatory and refresh the
+notation in them so that I dont have to search for them in different places of
+the paper. Also, some color coding or marking the most important results would
+be useful it is hard to ONE table with 20 rows and 20 columns, even harder with
+5 such tables.
+}
 
-- Paragraph on memory and time complexity between methods missing, are they all equal?
+\noindent\textbf{Q3.}
+%
+\ul{
+Paragraph on memory and time complexity between methods missing, are they all
+equal?
+}
 
@@
 
-1.
+\noindent\textbf{Q1.}
+%
+\ul{
 Robustness is important and many novel methods have been proposed, e.g., TRADES and AWP.
 I wonder whether these methods are not suitable for the metric learning task, and why the robustness of the metric learning task is unique.
+}
 
-2.
-The main motivation of this work is that previous works suffer from excessively hard examples and this work aims to control the hardness.
-Does simple tricks like mixup work for adjusting the hardness.
+\noindent\textbf{Q2.}
+%
+The main motivation of this work is that previous works suffer from excessively hard examples and this work aims to control the hardness. Does simple tricks like mixup work for adjusting the hardness.
 
-3. Tables (e.g., Tab.3) is hard to read. The authors may need to re-organize them and highlight somewhere.
+\noindent\textbf{Q3.}
+%
+Tables (e.g., Tab.3) is hard to read. The authors may need to re-organize them and highlight somewhere.
 
-4. The performance on benign examples seems to drop a lot. Does it mean the HM is just another trade-off way?
+\noindent\textbf{Q4.}
+%
+The performance on benign examples seems to drop a lot. Does it mean the HM is just another trade-off way?
 

### 2022-01-26 reb/RebuttalTemplate.tex
reb

@@
 \ul{
-From my view, the DML models are not special in terms of robustness against
+The DML models are not special in terms of robustness against
 adversarial attacks compared to other deep models.
 }
+
+\textbf{A:} 
+%
+We agree with the reviewer. Adversarial robustness at the visual representation
+level remains to be an open but insightful problem. Since deep metric learning
+can be interpreted as ``representation learning in metric space'', we believe
+the defense for deep metric learning is one step closer to the
+representation-level robustness, and may inspire future works for 
+robustness disentangled from specific vision tasks.
 
@@
 
-\section{To Reviewer \#3}
+\section*{To Reviewer \#3}
 

### 2022-01-26 reb/RebuttalTemplate.tex
reb

@@
 \usepackage{soul}
+\usepackage{xpatch}
 
@@
 \usepackage[pagebackref,breaklinks,colorlinks,bookmarks=false]{hyperref}
+
+%%START
+%% https://tex.stackexchange.com/questions/378160/how-to-customize-bibtex-numbering-in-a-document
+\makeatletter
+\xpatchcmd{\@bibitem}
+%  {\item}
+  {\H@item}
+  {\item[\@biblabel{\changekey{#1}}]}
+  {}{}
+\xpatchcmd{\@bibitem}
+  {\the\value{\@listctr}}
+  {\changekey{#1}}
+  {}{}
+\makeatother
+
+\ExplSyntaxOn
+\cs_new:Npn \changekey #1
+ {
+  \str_case:nVF {#1} \g_changekey_list_tl { ?? }
+ }
+\cs_new_protected:Npn \setchangekey #1 #2
+ {
+  \tl_gput_right:Nn \g_changekey_list_tl { {#1}{#2} }
+ }
+\tl_new:N \g_changekey_list_tl
+\cs_generate_variant:Nn \str_case:nnF { nV }
+\ExplSyntaxOff
+
+\setchangekey{currat}{10}
+\setchangekey{smoothat}{29}
+%%END
 
@@
 We agree with the reviewer. Adversarial robustness at the visual representation
-level remains to be an open but insightful problem. Since deep metric learning
-can be interpreted as ``representation learning in metric space'', we believe
-the defense for deep metric learning is one step closer to the
-representation-level robustness, and may inspire future works for 
-robustness disentangled from specific vision tasks.
+level remains to be an open but insightful problem. Since DML can be
+interpreted as ``representation learning in metric space'', we believe the
+defense for DML is one step closer to the representation-level robustness,
+which is disentangled from specific vision tasks.
 
@@
 \ul{
-The discussion of the relationship between the proposed method and a series of
-adversarial training algorithms is missing.
+The relationship between the proposed method and a series of
+adversarial training algorithms.
 }
+
+\cite{smoothat}
 
@@
 [1]. Cai, Qi-Zhi, et al. "Curriculum adversarial training." arXiv preprint arXiv:1805.04807 (2018).
+\cite{currat}
 

### 2022-01-26 reb/RebuttalTemplate.tex
reb

@@
 
+\textbf{A:} Thanks for the suggestion. We will polish the sentences to make
+them shorter and simpler, as well as use better abbreviations in the next
+revision.
+
 \noindent\textbf{Q2.}
@@
 \ul{
-Tables are hard to grasp at a first glance, too many abbreviations and
-notations. It would be useful to make captions self explanatory and refresh the
-notation in them so that I dont have to search for them in different places of
-the paper. Also, some color coding or marking the most important results would
-be useful it is hard to ONE table with 20 rows and 20 columns, even harder with
-5 such tables.
+Tables are hard to grasp at a first glance due to too many abbreviations and
+notations.
 }
+
+\textbf{A:} Thanks for the suggestion. In order to make the table easier to
+read in the next revision, we will (1) extend the captions to make them
+self-explanatory; (2) repeat the definitions of symbols and abbreviations in
+caption; (3) highlight the columns for imporant performance metrics; (4)
+colorize the text abbreviations for different methods in the same way as the
+corresponding colored legends in the figures.
 

### 2022-01-26 reb/RebuttalTemplate.tex
reb

@@
 
-\textbf{A:} Thanks for the suggestion. In order to make the table easier to
+\textbf{A:} Thanks for the suggestion. In order to make the tables easier to
 read in the next revision, we will (1) extend the captions to make them
 self-explanatory; (2) repeat the definitions of symbols and abbreviations in
-caption; (3) highlight the columns for imporant performance metrics; (4)
-colorize the text abbreviations for different methods in the same way as the
-corresponding colored legends in the figures.
+caption; (3) highlight the columns for imporant performance metrics
+(\emph{i.e.}, R@1 and ERS); (4) colorize the text abbreviations for different
+methods in the same way as the corresponding colored legends in the figures.
 
@@
 \ul{
-Paragraph on memory and time complexity between methods missing, are they all
+Paragraph on memory and time complexity between methods missing. Are they all
 equal?

### 2022-01-27 reb/RebuttalTemplate.tex
mm

@@
 \ul{
-Paragraph on memory and time complexity between methods missing. Are they all
+Comparison in memory and time complexity between defense methods is missing. Are they all
 equal?
 }
+
+\textbf{A:}
+%
+Not equal but similar in practice.
+%
+As a common part across methods, PGD has the same
+space and time complexities for every sample triplet across methods.
+%
+The difference in complexities stem from triplet sampling strategy and
+adversarial perturbation object functions.
+%
+In terms of time complexity, EST O(), ACT O(), HM O().
+In terms of space complexity, EST O(), ACT O(), HM O().
+%
+In practice, such difference lead to minor difference in training time
+and memory consumption.
+%
+Take the CUB datset with
+$\eta=32$ as example, the TODO.
+%
+We note these values are sensitive to hardware, software, and
+programming tricks, which makes it uneasy for future works to compare.
+%
+This information in the revised manuscript.
 

### 2022-01-27 reb/RebuttalTemplate.tex
reb

@@
 
-\setchangekey{currat}{10}
+\setchangekey{optcontrolaml}{55}
+\setchangekey{currat}{54}
 \setchangekey{smoothat}{29}
@@
 
-\textbf{A:} 
+\noindent\textbf{A:} 
 %
-We agree with the reviewer. Adversarial robustness at the visual representation
-level remains to be an open but insightful problem. Since DML can be
+We agree with the reviewer. Robustness at the visual representation
+level remains an open problem. Since DML can be
 interpreted as ``representation learning in metric space'', we believe the
@@
 The relationship between the proposed method and a series of
-adversarial training algorithms.
-}
+adversarial training algorithms
+}(\cite{smoothat,currat,optcontrolaml}).
 
@@
 
-[2]. Zhu, Xiaojin. "An optimal control view of adversarial machine learning." arXiv preprint arXiv:1811.04422 (2018).
+[2]. Zhu, Xiaojin. "An optimal control view of adversarial machine learning." arXiv preprint arXiv:1811.04422 (2018). \cite{optcontrolaml}
 

### 2022-01-28 reb/RebuttalTemplate.tex
reb

@@
 \usepackage{xpatch}
+\usepackage{comment}
 
@@
 The relationship between the proposed method and a series of
-adversarial training algorithms
-}(\cite{smoothat,currat,optcontrolaml}).
+adversarial training algorithms}~\cite{smoothat,currat,optcontrolaml}.
 
@@
 
-\textbf{A:} Thanks for the suggestion. We will polish the sentences to make
+\noindent\textbf{A:} Thanks for the suggestion. We will polish the sentences to make
 them shorter and simpler, as well as use better abbreviations in the next
@@
 
-\textbf{A:} Thanks for the suggestion. In order to make the tables easier to
+\noindent\textbf{A:} Thanks for the suggestion. In order to make the tables easier to
 read in the next revision, we will (1) extend the captions to make them
@@
 
-\textbf{A:}
+\noindent\textbf{A:}
 %
@@
 \ul{
-Robustness is important and many novel methods have been proposed, e.g., TRADES and AWP.
+Many novel methods have been proposed, e.g., TRADES and AWP.
 I wonder whether these methods are not suitable for the metric learning task, and why the robustness of the metric learning task is unique.
@@
 
+\noindent\textbf{A:}
+
+\begin{comment}
+\noindent\textbf{Q2.} \ul{Does simple tricks for adjusting the hardness.}
+\end{comment}
+
 \noindent\textbf{Q2.}
 %
-The main motivation of this work is that previous works suffer from excessively hard examples and this work aims to control the hardness. Does simple tricks like mixup work for adjusting the hardness.
+Tables (e.g., Tab.3) is hard to read. The authors may need to re-organize them and highlight somewhere.
 
@@
 %
-Tables (e.g., Tab.3) is hard to read. The authors may need to re-organize them and highlight somewhere.
+The performance on benign examples seems to drop a lot. Does it mean the HM is just another trade-off way?
 
-\noindent\textbf{Q4.}
-%
-The performance on benign examples seems to drop a lot. Does it mean the HM is just another trade-off way?
+\emph{The main motivation of this work is that previous works suffer from excessively hard examples and this work aims to control the hardness.}
 

### 2022-01-28 reb/RebuttalTemplate.tex
reb

@@
 
-\cite{smoothat}
-
-I’m hoping that the author could complete it in the related works section,
-including reference 29. “Sat: Improving adversarial training via
-curriculum-based loss smoothing” in the original manuscript and some other
-studies, such as [1] and [2]. I think the idea of the proposed method bears a
-certain similarity to these.
-
-[1]. Cai, Qi-Zhi, et al. "Curriculum adversarial training." arXiv preprint arXiv:1805.04807 (2018).
-\cite{currat}
-
-[2]. Zhu, Xiaojin. "An optimal control view of adversarial machine learning." arXiv preprint arXiv:1811.04422 (2018). \cite{optcontrolaml}
+\noindent\textbf{A:}
+%
+CAT~\cite{currat} creates adversarial examples with gradually increasing
+strength (\emph{i.e.}, PGD step) for adversarial training, while our
+LGA gradually increases destination hardness $H_\mathsf{D}$ (with a
+fixed PGD step) based on loss value.
+%
+SAT~\cite{smoothat} TODO.
+%
+Zhu~\emph{et al.}~\cite{optcontrolaml} TODO.
+%
+We will discuss these similar works in the revised manuscript.
 
@@
 %
-Tables (e.g., Tab.3) is hard to read. The authors may need to re-organize them and highlight somewhere.
+\ul{Tables (e.g., Tab.~3) are hard to read.}
+
+\noindent\textbf{A:} Thanks for the suggestion. We will improve the tables as described in the answer to Q2 of Reviewer \#2.
 

### 2022-01-29 reb/RebuttalTemplate.tex
reb

@@
 %
-CAT~\cite{currat} creates adversarial examples with gradually increasing
-strength (\emph{i.e.}, PGD step) for adversarial training, while our
-LGA gradually increases destination hardness $H_\mathsf{D}$ (with a
-fixed PGD step) based on loss value.
+CAT~\cite{currat} uses adversarial examples with gradually increasing strength
+(\emph{i.e.}, PGD step), while our LGA gradually increases destination hardness
+$H_\mathsf{D}$ (with a fixed PGD step).
 %
-SAT~\cite{smoothat} TODO.
+SAT~\cite{smoothat} gradually increases the difficulty of adversarial examples
+in order to achieve smoothness of loss landscape, while our HM is similar to
+``early termination of PGD''~\cite{smoothat} with a dynamic ``termination''
+threshold determined by LGA.
 %
@@
 %
-We will discuss these similar works in the revised manuscript.
+Although these works focus on classification instead of DML, these similarities
+will be included in the next reivision.
 

### 2022-01-29 reb/RebuttalTemplate.tex
reb

@@
 %
-We agree with the reviewer. Robustness at the visual representation
-level remains an open problem. Since DML can be
-interpreted as ``representation learning in metric space'', we believe the
-defense for DML is one step closer to the representation-level robustness,
-which is disentangled from specific vision tasks.
+We agree with the reviewer. Robustness at the visual representation level
+remains an open problem. Since DML can be interpreted as ``representation
+learning in metric space'' and inspire visual representation learning, we
+believe the defense for DML is one step closer to the representation-level
+robustness disentangled from specific tasks.
 

### 2022-01-29 reb/RebuttalTemplate.tex
reb

@@
 %
-Zhu~\emph{et al.}~\cite{optcontrolaml} TODO.
+Zhu~\emph{et al.}~\cite{optcontrolaml} presents an optimal control view of
+adversarial machine learning,
 %
@@
 
-\noindent\textbf{A:} Thanks for the suggestion. In order to make the tables easier to
-read in the next revision, we will (1) extend the captions to make them
+\noindent\textbf{A:} Thanks for the suggestion.
+In the next revision, we will (1) extend the captions to make them
 self-explanatory; (2) repeat the definitions of symbols and abbreviations in
 caption; (3) highlight the columns for imporant performance metrics
-(\emph{i.e.}, R@1 and ERS); (4) colorize the text abbreviations for different
-methods in the same way as the corresponding colored legends in the figures.
+(\emph{i.e.}, R@1 and ERS); (4) colorize the abbreviations for different
+defense methods in the same color as their corresponding legends in the figures.
 

### 2022-01-29 reb/RebuttalTemplate.tex
reb

@@
 Zhu~\emph{et al.}~\cite{optcontrolaml} presents an optimal control view of
-adversarial machine learning,
+adversarial machine learning, where our method can also be interpreted as
+``adversarial training against test-time attack''.
 %
-Although these works focus on classification instead of DML, these similarities
-will be included in the next reivision.
+Although these works do not mention DML, these similarities will be included in
+the next reivision.
 

### 2022-01-29 reb/RebuttalTemplate.tex
reb

@@
 %
-Although these works do not mention DML, these similarities will be included in
-the next reivision.
+Although they do not mention DML, the similarities will be included in
+introduction and related works for next reivision.
 
@@
 self-explanatory; (2) repeat the definitions of symbols and abbreviations in
-caption; (3) highlight the columns for imporant performance metrics
+captions; (3) highlight the columns for imporant performance metrics
 (\emph{i.e.}, R@1 and ERS); (4) colorize the abbreviations for different
-defense methods in the same color as their corresponding legends in the figures.
+defense methods in the same color as their corresponding legends in the
+performance curve figures.
 

### 2022-01-29 reb/RebuttalTemplate.tex
reb

--- 2022-01-29 reb/RebuttalTemplate.tex
@@
 \usepackage{comment}
+\usepackage{booktabs}
 
@@
 %
-Although these works do not mention DML, these similarities will be included in
-the next reivision.
+Although they do not mention DML, the similarities will be included in
+introduction and related works for next revision.
 
@@
 self-explanatory; (2) repeat the definitions of symbols and abbreviations in
-caption; (3) highlight the columns for imporant performance metrics
+captions; (3) highlight the columns for important performance metrics
 (\emph{i.e.}, R@1 and ERS); (4) colorize the abbreviations for different
-defense methods in the same color as their corresponding legends in the figures.
+defense methods in the same color as their corresponding legends in the
+performance curve figures.
 
@@
 %
-Not equal but similar in practice.
+Not equal but only introduce minor difference in practice.
 %
-As a common part across methods, PGD has the same
-space and time complexities for every sample triplet across methods.
+We conduct experiments with two ``Nvidia TITAN Xp'' GPUs on the CUB dataset
+with $\eta{=}8$, as follows:
 %
-The difference in complexities stem from triplet sampling strategy and
-adversarial perturbation object functions.
+\noindent%
+\resizebox{1.0\columnwidth}{!}{
+\begin{tabular}{c|c|c|c|c}
+	\toprule
+	 & EST[$\mathcal{S}$]
+	 & ACT[$\mathcal{S}$]
+	 & HM[$\mathcal{S},g_\mathsf{LGA}$]
+	 & HM[$\mathcal{S},g_\mathsf{LGA}$]\&ICS \\
+	 \midrule
+	Time Complexity
+	& $\mathcal{O}_\mathsf{PGD} + \mathcal{O}_\mathsf{sampler}$
+	& $\mathcal{O}_\mathsf{PGD} + \mathcal{O}_\mathsf{sampler}$
+	&
+	& \\
+	Actual Training Time
+	& 2.2hour 
+	&
+	&
+	& \\
+	\hline
+	Space Complexity & & & & \\
+	GPU Memory Usage & & & & \\
+	\bottomrule
+\end{tabular}
+	}
 %
-In terms of time complexity, EST O(), ACT O(), HM O().
-In terms of space complexity, EST O(), ACT O(), HM O().
+The PGD complexities per adversarial
+example are identical across different defenses, and hence omitted.
 %
-In practice, such difference lead to minor difference in training time
-and memory consumption.
+As triplet sampler complexities differ across strategies, all defenses use
+``Softhard'' for fair comparison in the above table.
 %
-Take the CUB datset with
-$\eta=32$ as example, the TODO.
+Apart from these, the complexities stem from the adversarial perturbation
+objective functions.
 %
-We note these values are sensitive to hardware, software, and
-programming tricks, which makes it uneasy for future works to compare.
+Note, the reported values are subject to change in GPU, software, and
+programming tricks, \emph{etc.}, which makes them uneasy to compare for future
+works.
 %
-This information in the revised manuscript.
+These will be provided in the next revision.
 

### 2022-01-29 reb/RebuttalTemplate.tex
reb

@@
 
+\setchangekey{trades}{47}
 \setchangekey{optcontrolaml}{55}
@@
 	\hline
-	Space Complexity & & & & \\
-	GPU Memory Usage & & & & \\
+	Space Complexity 
+	&
+	&
+	&
+	& \\
+	GPU Memory Usage 
+	& 
+	& 
+	& 
+	& 8385 MB\\
 	\bottomrule
@@
 %
-\ul{
-Many novel methods have been proposed, e.g., TRADES and AWP.
+\ul{Many methods have been proposed, e.g., TRADES}\cite{trades} \ul{and AWP.
 I wonder whether these methods are not suitable for the metric learning task, and why the robustness of the metric learning task is unique.
@@
 %
-The performance on benign examples seems to drop a lot. Does it mean the HM is just another trade-off way?
+\ul{The performance on benign examples seems to drop a lot. Does it mean the
+HM is just another trade-off way?}
 

### 2022-01-29 reb/RebuttalTemplate.tex
reb

@@
 
-\setchangekey{trades}{47}
+\setchangekey{awp}{56}
 \setchangekey{optcontrolaml}{55}
 \setchangekey{currat}{54}
+\setchangekey{trades}{47}
 \setchangekey{smoothat}{29}
@@
 %
-\ul{Many methods have been proposed, e.g., TRADES}\cite{trades} \ul{and AWP.
-I wonder whether these methods are not suitable for the metric learning task, and why the robustness of the metric learning task is unique.
+\ul{Many methods have been proposed, e.g., TRADES}\cite{trades} \ul{and AWP}\cite{awp}.
+\ul{I wonder whether these methods are not suitable for the metric learning task, and why the robustness of the metric learning task is unique.
 }

### 2022-01-29 reb/RebuttalTemplate.tex
reb

@@
 	&
-	& \\
+	& 3.4 hour \\
 	\hline

### 2022-01-29 reb/RebuttalTemplate.tex
reb

@@
 \setchangekey{currat}{54}
+\setchangekey{robrank}{53}
+\setchangekey{advrank}{51}
 \setchangekey{trades}{47}
 \setchangekey{smoothat}{29}
+\setchangekey{madry}{19}
 %%END
@@
 
+\noindent\textbf{A:}
+%
+Performance drop on benign example is inevitable for adversarial training
+methods \cite{madry,trades,awp,advrank,robrank}, and they face a trade-off
+between benign example performance and robustness via hyper-parameters
+(\emph{e.g.}, $\varepsilon$).
+%
+Our proposed method is not a trade-off method, because it quantitatively
+achieves higher robustness, training efficiency, and benign example performance
+than previous state-of-the-arts~\cite{advrank,robrank}.
+
 \emph{The main motivation of this work is that previous works suffer from excessively hard examples and this work aims to control the hardness.}

### 2022-01-29 reb/RebuttalTemplate.tex
reb

--- 2022-01-29 reb/RebuttalTemplate.tex
@@
 
+\emph{The main motivation of this work is that previous works suffer from excessively hard examples and this work aims to control the hardness.}
+
 \begin{comment}
@@
 
-\emph{The main motivation of this work is that previous works suffer from excessively hard examples and this work aims to control the hardness.}
+\noindent\textbf{A:}
+%
+Performance drop on benign example is inevitable for adversarial training
+\cite{madry,trades,awp,advrank,robrank}, and the trade-off exists
+between benign example performance and robustness via hyper-parameters
+(\emph{e.g.}, $\varepsilon$).
+%
+Our method is not a trade-off way, because trade-off method cannot
+simultaneously achieve higher robustness, training efficiency, and benign
+example performance than previous state-of-the-arts~\cite{advrank,robrank}.
 

### 2022-01-29 reb/RebuttalTemplate.tex
reb

@@
 %%%%%%%%% BODY TEXT - ENTER YOUR RESPONSE BELOW
-\section*{To Reviewer \#1}
+%\subsubsection*{To Reviewer \#1}
+\noindent\textbf{To Reviewer \#1}
+\vspace{0.3em}
 
@@
 
-\section*{To Reviewer \#2}
+%\subsubsection*{To Reviewer \#2}
+\vspace{0.3em}
+\noindent\textbf{To Reviewer \#2}\vspace{0.3em}
 
@@
 %
-Not equal but only introduce minor difference in practice.
+They do not equal but only lead to minor difference in practice.
 %
@@
 %
-As triplet sampler complexities differ across strategies, all defenses use
-``Softhard'' for fair comparison in the above table.
+Triplet sampler has been aligned to ``Softhard'' for identical complexities, and
+hence omitted.
 %
-Apart from these, the complexities stem from the adversarial perturbation
-objective functions.
+The rest complexities stem from the adversarial perturbation objective functions,
+as reported in table.
 %
-Note, the reported values are subject to change in GPU, software, and
-programming tricks, \emph{etc.}, which makes them uneasy to compare for future
-works.
+Note, the reported values are sensitive to hardware, software, and
+programming tricks, which makes them uneasy to compare for future works.
 %
@@
 
-\section*{To Reviewer \#3}
+%\subsubsection*{To Reviewer \#3}
+~\newline
+\noindent\textbf{To Reviewer \#3}
 

### 2022-01-29 reb/RebuttalTemplate.tex
reb

@@
 %%%%%%%%% TITLE - PLEASE UPDATE
-\title{Enhancing Adversarial Robustness for Deep Metric Learning -- Author Response}  % **** Enter the paper title here
+\title{Enhancing Adversarial Robustness for Deep Metric Learning}  % **** Enter the paper title here
 
@@
 %
-These will be provided in the next revision.
+These information will be provided in the next revision.
 

### 2022-01-29 reb/RebuttalTemplate.tex
reb

@@
 %
-Our method is not a trade-off way, because trade-off method cannot
+Our method is not a trade-off way, because a trade-off method cannot
 simultaneously achieve higher robustness, training efficiency, and benign

### 2022-01-29 reb/RebuttalTemplate.tex
reb

@@
 \noindent\textbf{A:}
-
-\emph{The main motivation of this work is that previous works suffer from excessively hard examples and this work aims to control the hardness.}
-
-\begin{comment}
-\noindent\textbf{Q2.} \ul{Does simple tricks for adjusting the hardness.}
-\end{comment}
+%
+They are designed for classification instead of DML, and the cross-entropy loss
+used by them is unsuitable for metric learning.
+%
+The adaptation of TRADES, namely minimizing a benign triplet loss plus the
+maximized embedding move distance (lead by adversarial attack) has been
+demonstrated less effective than ACT in \cite{robrank} (see Eq.~19 ``SES loss''
+and Table.~5 of \cite{robrank}).
 

### 2022-01-29 reb/RebuttalTemplate.tex
reb

@@
 %\subsubsection*{To Reviewer \#3}
-~\newline
+\vspace{0.3em}
 \noindent\textbf{To Reviewer \#3}
+\vspace{0.3em}
 
@@
 demonstrated less effective than ACT in \cite{robrank} (see Eq.~19 ``SES loss''
-and Table.~5 of \cite{robrank}).
+and Table.~5 of \cite{robrank}), while ACT is outperformed by our method.
 

### 2022-01-29 reb/RebuttalTemplate.tex
reb

--- 2022-01-29 reb/RebuttalTemplate.tex
@@
 	Actual Training Time
-	& 2.2hour 
+	& XYZ hour 
 	&
@@
 %
-The adaptation of TRADES, namely minimizing a benign triplet loss plus the
+The adaptation of TRADES (Eq.~5 in \cite{trades}), namely minimizing a benign triplet loss plus the
 maximized embedding move distance (lead by adversarial attack) has been
 demonstrated less effective than ACT in \cite{robrank} (see Eq.~19 ``SES loss''
-and Table.~5 of \cite{robrank}).
+and Table.~5 of \cite{robrank}), while ACT is outperformed by our method.
+%
+These details will be included in the next revision.
 

### 2022-01-29 reb/RebuttalTemplate.tex
reb

@@
 	Actual Training Time
-	& XYZ hour 
-	&
-	&
+	& hour 
+	& hour
+	& 3.1 hour
 	& 3.4 hour \\
@@
 	GPU Memory Usage 
-	& 
-	& 
-	& 
+	& MB
+	& MB
+	& MB
 	& 8385 MB\\
@@
 %
-\ul{Many methods have been proposed, e.g., TRADES}\cite{trades} \ul{and AWP}\cite{awp}.
-\ul{I wonder whether these methods are not suitable for the metric learning task, and why the robustness of the metric learning task is unique.
-}
+\ul{Many methods have been proposed, e.g., TRADES}\cite{trades} \ul{and
+AWP}\cite{awp}.  \ul{I wonder whether these methods are not suitable for the
+metric learning task, and why the robustness of the metric learning task is
+unique.}
 
@@
 %
-The adaptation of TRADES (Eq.~5 in \cite{trades}), namely minimizing a benign triplet loss plus the
-maximized embedding move distance (lead by adversarial attack) has been
-demonstrated less effective than ACT in \cite{robrank} (see Eq.~19 ``SES loss''
-and Table.~5 of \cite{robrank}), while ACT is outperformed by our method.
+The adaptation of TRADES (Eq.~5 in \cite{trades}), namely minimizing a benign
+triplet loss plus the maximized embedding move distance (lead by adversarial
+attack) has been demonstrated less effective than ACT in \cite{robrank} (see
+Eq.~19 ``SES loss'' and Table.~5 of \cite{robrank}), while ACT is outperformed
+by our method.
+%
+Apart from that, the robustness that is not task-specific remains an open
+problem as explained in the answer to Q1 of Reviewer \#1.
 %

### 2022-01-29 reb/RebuttalTemplate.tex
reb

@@
 %
-The adaptation of TRADES (Eq.~5 in \cite{trades}), namely minimizing a benign
+Adaptation of TRADES (Eq.~5 in \cite{trades}), namely minimizing a benign
 triplet loss plus the maximized embedding move distance (lead by adversarial
@@
 %
+Adaptation of AWP (Eq.~7 in \cite{awp}) involves direct maximization
+of loss, which still does not address the model collapse issue on
+excessively hard examples for DML.
+%
 Apart from that, the robustness that is not task-specific remains an open
@@
 %
-These details will be included in the next revision.
+These will be included in the next revision.
 

### 2022-01-29 reb/RebuttalTemplate.tex
reb

@@
 %
-Triplet sampler has been aligned to ``Softhard'' for identical complexities, and
-hence omitted.
+Triplet sampler is aligned to ``Softhard'' in the table for identical
+sampling complexities, and hence omitted.
 %
-The rest complexities stem from the adversarial perturbation objective functions,
-as reported in table.
+The rest complexities stem from adversarial perturbation objective functions.
 %
-Note, the reported values are sensitive to hardware, software, and
+Note, the values are sensitive to factors including hardware, software, and
 programming tricks, which makes them uneasy to compare for future works.
 %
-These information will be provided in the next revision.
+The comparison will be provided.
 
@@
 %
-They are designed for classification instead of DML, and the cross-entropy loss
-used by them is unsuitable for metric learning.
+They are designed for classification instead of DML, and their cross-entropy
+loss is unsuitable for DML.
 %
@@
 %%%%%%%%% REFERENCES
+%\vspace{-0.5em}
 {\small

### 2022-01-30 reb/RebuttalTemplate.tex
reb

@@
 We conduct experiments with two ``Nvidia TITAN Xp'' GPUs on the CUB dataset
-with $\eta{=}8$, as follows:
+with $\eta{=}32$, as follows:
 %
@@
 	Actual Training Time
+	& 8.4 hour 
 	& hour
-	& hour
-	& 3.1 hour
-	& 3.4 hour \\
+	& 9.1 hour
+	& 9.4 hour \\
 	\hline

### 2022-01-30 reb/RebuttalTemplate.tex
reb

@@
 	GPU Memory Usage 
+	& 4559 MB
 	& MB
-	& MB
-	& MB
+	& 6657 MB
 	& 8385 MB\\
@@
 The PGD complexities per adversarial
-example are identical across different defenses, and hence omitted.
+example are identical across different defenses.
 %
-Triplet sampler is aligned to ``Softhard'' in the table for identical
-sampling complexities, and hence omitted.
+Triplet sampler is aligned in the table for identical
+sampling complexities.
 %
-The rest complexities stem from adversarial perturbation objective functions.
+Training loss complexities are also identical.
 %
-Note, the values are sensitive to factors including hardware, software, and
-programming tricks, which makes them uneasy to compare for future works.
+Omitting the identical terms, the rest stem from adversarial perturbation objective functions.
 %
-The comparison will be provided.
+The reported values are uneasy to compare for future work as they are sensitive
+to hardware, software, and programming tricks.
+%
+The paragraph will be provided.
 

### 2022-01-30 reb/RebuttalTemplate.tex
reb

@@
 	GPU Memory Usage 
-	& 4559 MB
-	& MB
+	& 6559 MB
+	& 6617 MB
 	& 6657 MB
@@
 %
-Training loss complexities are also identical.
-%
-Omitting the identical terms, the rest stem from adversarial perturbation objective functions.
+Omitting the identical terms, the rest stem from adversarial perturbation objective functions and loss function.
 %
@@
 %
-The paragraph will be provided.
+The paragraph will be provided in the next revision.
 

### 2022-01-30 reb/RebuttalTemplate.tex
reb

@@
 	Time Complexity
-	& $\mathcal{O}_\mathsf{PGD} + \mathcal{O}_\mathsf{sampler}$
+	& $\mathcal{O}(D)$
 	& $\mathcal{O}_\mathsf{PGD} + \mathcal{O}_\mathsf{sampler}$
@@
 	Space Complexity 
-	&
+	& $\mathcal{O}(D)$
 	&

### 2022-01-30 reb/RebuttalTemplate.tex
reb

@@
 	Time Complexity
-	& $\mathcal{O}(D)$
-	& $\mathcal{O}_\mathsf{PGD} + \mathcal{O}_\mathsf{sampler}$
+	& $\mathcal{O}(\eta D)$
+	& $\mathcal{O}(\eta D)$
 	&
@@
 	Space Complexity 
-	& $\mathcal{O}(D)$
-	&
+	& $\mathcal{O}(\eta D)$
+	& $\mathcal{O}(\eta D)$
 	&

### 2022-01-30 reb/RebuttalTemplate.tex
reb

@@
 %
-They do not equal but only lead to minor difference in practice.
+They have same complexity polynomials in terms of time and space.
 %
@@
 	Time Complexity
-	& $\mathcal{O}(\eta D)$
-	& $\mathcal{O}(\eta D)$
-	&
-	& \\
+	& $\mathcal{O}(\eta D + 1)$
+	& $\mathcal{O}(\eta D + 1)$
+	& $\mathcal{O}(\eta D + 1)$
+	& $\mathcal{O}(\eta D + 1)$\\
 	Actual Training Time
@@
 	Space Complexity 
-	& $\mathcal{O}(\eta D)$
-	& $\mathcal{O}(\eta D)$
-	&
-	& \\
+	& $\mathcal{O}(\eta D + 1)$
+	& $\mathcal{O}(\eta D + 1)$
+	& $\mathcal{O}(\eta D + 1)$
+	& $\mathcal{O}(\eta D + 1)$\\
 	GPU Memory Usage 
@@
 %
-Omitting the identical terms, the rest stem from adversarial perturbation objective functions and loss function.
+Omitting the identical terms, the rest complexity stems from adversarial perturbation objective functions and loss function.
 %

### 2022-01-30 reb/RebuttalTemplate.tex
reb

@@
 	Time Complexity
-	& $\mathcal{O}(\eta D + 1)$
-	& $\mathcal{O}(\eta D + 1)$
-	& $\mathcal{O}(\eta D + 1)$
-	& $\mathcal{O}(\eta D + 1)$\\
+	& $\mathcal{O}(\eta D + \eta)$
+	& $\mathcal{O}(\eta D + \eta)$
+	& $\mathcal{O}(\eta D + \eta)$
+	& $\mathcal{O}(\eta D + \eta)$\\
 	Actual Training Time

### 2022-01-30 reb/RebuttalTemplate.tex
reb

--- 2022-01-30 reb/RebuttalTemplate.tex
@@
 	\toprule
+	 Defense Method
 	 & EST[$\mathcal{S}$]
@@
 	Time Complexity
-	& $\mathcal{O}(\eta D + 1)$
-	& $\mathcal{O}(\eta D + 1)$
-	& $\mathcal{O}(\eta D + 1)$
-	& $\mathcal{O}(\eta D + 1)$\\
+	& $\mathcal{O}(\eta D + \eta + 1)$
+	& $\mathcal{O}(\eta D + \eta + 1)$
+	& $\mathcal{O}(\eta D + \eta + 1)$
+	& $\mathcal{O}(\eta D + \eta + 1)$\\
 	Actual Training Time
 	& 8.4 hour 
-	& hour
+	& 9.3 hour
 	& 9.1 hour
@@
 	Space Complexity 
-	& $\mathcal{O}(\eta D + 1)$
-	& $\mathcal{O}(\eta D + 1)$
-	& $\mathcal{O}(\eta D + 1)$
-	& $\mathcal{O}(\eta D + 1)$\\
+	& $\mathcal{O}(D + 1)$
+	& $\mathcal{O}(D + 1)$
+	& $\mathcal{O}(D + 1)$
+	& $\mathcal{O}(D + 1)$\\
 	GPU Memory Usage 

### 2022-01-31 reb/RebuttalTemplate.tex
merge changes from vishal

@@
 Although they do not mention DML, the similarities will be included in
-introduction and related works for next revision.
+introduction and related work sections in our revised version.
 
@@
 \noindent\textbf{A:} Thanks for the suggestion. We will polish the sentences to make
-them shorter and simpler, as well as use better abbreviations in the next
-revision.
+them shorter and simpler, as well as use better abbreviations in the 
+revised version.
 
@@
 %
-They have same complexity polynomials in terms of time and space.
+They have the same complexity polynomials in terms of time and space.
 %
@@
 %
-Omitting the identical terms, the rest complexity stems from adversarial perturbation objective functions and loss function.
+Omitting the identical terms, the remaining complexity stems from adversarial perturbation objective functions and loss function.
 %
-The reported values are uneasy to compare for future work as they are sensitive
+The reported values are difficult to compare for future work as they are sensitive
 to hardware, software, and programming tricks.
 %
-The paragraph will be provided in the next revision.
+The paragraph will be provided in the revised version.
 
@@
 %
-These will be included in the next revision.
+These will be included in the revised version of our paper.
 
@@
 %
-Our method is not a trade-off way, because a trade-off method cannot
+Our method is not a trade-off way of dealing with this problem, because a trade-off method cannot
 simultaneously achieve higher robustness, training efficiency, and benign

### 2022-03-02 robdml.tex
tex
remove unnecessary acks.
robdml

@@
 \usepackage{siunitx}
+
+\definecolor{cyan}{rgb}{0.0, 0.72, 0.92}
 
@@
 most effective
-methods~\cite{bilateral,advtrain-triplet,benchmarking,smoothat,trades,robustwrn,weightperturb,featurescatter},
+methods~\cite{bilateral,advtrain-triplet,benchmarking,smoothat,trades,robustwrn,weightperturb,featurescatter,currat,awp},
 but suffers from high training cost~\cite{freeat,fastat,yopo}, performance drop on
@@
 
+\textbf{Acknowledgements.} This research was supported by []. We thank
+Kangfu Mei for helpful discussions and feedbacks.
+
 %%%%%%%%% REFERENCES

### 2022-03-02 tab-hmeff.tex
tex
import vishal's changes, part 1
tab

--- 2021-10-25 tab-hmeff.tex
@@
 
-\multirow{2}{*}{\textbf{Dataset}} & \multirow{2}{*}{\textbf{Defense}} & \multirow{2}{*}{$\eta$} & \multicolumn{4}{c|}{\textbf{Benign Example}} & \multicolumn{10}{c|}{\textbf{White-Box Attacks for Robustness Evaluation}} & \multirow{2}{*}{\textbf{ERS$\uparrow$}}\tabularnewline
+\rowcolor{black!12} & & & \multicolumn{4}{c|}{\textbf{Benign Example}} & \multicolumn{10}{c|}{\textbf{White-Box Attacks for Robustness Evaluation}} & \tabularnewline
 \cline{4-17} \cline{5-17} \cline{6-17} \cline{7-17} \cline{8-17} \cline{9-17} \cline{10-17} \cline{11-17} \cline{12-17} \cline{13-17} \cline{14-17} \cline{15-17} \cline{16-17} \cline{17-17}
- &  &  & R@1$\uparrow$ & R@2$\uparrow$ & mAP$\uparrow$ & NMI$\uparrow$ & CA+$\uparrow$ & CA-$\downarrow$ & QA+$\uparrow$ & QA-$\downarrow$ & TMA$\downarrow$ & ES:D$\downarrow$ & ES:R$\uparrow$ & LTM$\uparrow$ & GTM$\uparrow$ & GTT$\uparrow$ & \tabularnewline
+\rowcolor{black!12}\multirow{-2}{*}{\textbf{Dataset}} & \multirow{-2}{*}{\textbf{Defense}} & \multirow{-2}{*}{$\eta$} & R@1$\uparrow$ & R@2$\uparrow$ & mAP$\uparrow$ & NMI$\uparrow$ & CA+$\uparrow$ & CA-$\downarrow$ & QA+$\uparrow$ & QA-$\downarrow$ & TMA$\downarrow$ & ES:D$\downarrow$ & ES:R$\uparrow$ & LTM$\uparrow$ & GTM$\uparrow$ & GTT$\uparrow$ & \multirow{-2}{*}{\textbf{ERS$\uparrow$}}\tabularnewline
 
@@
 \hline
-\multirow{5}{*}{CUB} & ACT{[}$\mathcal{R}${]} & 2 & 46.5 & 58.4 & 29.1 & 55.6 & 0.6 & 98.9 & 0.4 & 98.1 & 0.837 & 1.666 & 0.2 & 0.2 & 19.6 & 0.0 & 5.8\tabularnewline
- & ACT{[}$\mathcal{R}${]} & 4 & 38.4 & 49.8 & 22.8 & 49.7 & 4.6 & 81.9 & 2.8 & 80.5 & 0.695 & 1.366 & 2.9 & 2.3 & 18.8 & 0.1 & 13.9\tabularnewline
- & ACT{[}$\mathcal{R}${]} & 8 & 30.6 & 40.1 & 16.5 & 45.6 & 13.7 & 46.8 & 12.6 & 39.3 & 0.547 & 0.902 & 13.6 & 9.8 & 21.9 & 1.3 & 31.3\tabularnewline
- & ACT{[}$\mathcal{R}${]} & 16 & 28.6 & 38.7 & 15.1 & 43.7 & 15.8 & 37.9 & 16.0 & 31.5 & 0.496 & 0.834 & 11.3 & 9.8 & 21.2 & 2.1 & 34.7\tabularnewline
- & ACT{[}$\mathcal{R}${]} & 32 & 27.5 & 38.2 & 12.2 & 43.0 & 15.5 & 37.7 & 15.1 & 32.2 & 0.472 & 0.821 & 11.1 & 9.4 & 14.9 & 1.0 & 33.9\tabularnewline
+\multirow{5}{*}{CUB} & \textcolor{tab:cyan}{ACT{[}$\mathcal{R}${]}}\cite{robrank} & 2 & 46.5 & 58.4 & 29.1 & 55.6 & 0.6 & 98.9 & 0.4 & 98.1 & 0.837 & 1.666 & 0.2 & 0.2 & 19.6 & 0.0 & 5.8\tabularnewline
+\rowcolor{black!7}\cellcolor{white} & \textcolor{tab:cyan}{ACT{[}$\mathcal{R}${]}}\cite{robrank} & 4 & 38.4 & 49.8 & 22.8 & 49.7 & 4.6 & 81.9 & 2.8 & 80.5 & 0.695 & 1.366 & 2.9 & 2.3 & 18.8 & 0.1 & 13.9\tabularnewline
+ & \textcolor{tab:cyan}{ACT{[}$\mathcal{R}${]}}\cite{robrank} & 8 & 30.6 & 40.1 & 16.5 & 45.6 & 13.7 & 46.8 & 12.6 & 39.3 & 0.547 & 0.902 & 13.6 & 9.8 & 21.9 & 1.3 & 31.3\tabularnewline
+\rowcolor{black!7}\cellcolor{white} & \textcolor{tab:cyan}{ACT{[}$\mathcal{R}${]}}\cite{robrank} & 16 & 28.6 & 38.7 & 15.1 & 43.7 & 15.8 & 37.9 & 16.0 & 31.5 & 0.496 & 0.834 & 11.3 & 9.8 & 21.2 & 2.1 & 34.7\tabularnewline
+ & \textcolor{tab:cyan}{ACT{[}$\mathcal{R}${]}}\cite{robrank} & 32 & 27.5 & 38.2 & 12.2 & 43.0 & 15.5 & 37.7 & 15.1 & 32.2 & 0.472 & 0.821 & 11.1 & 9.4 & 14.9 & 1.0 & 33.9\tabularnewline
 \hline
-\multirow{5}{*}{CUB} & ACT{[}$\mathcal{S}${]} & 2 & 53.0 & 65.1 & 34.7 & 59.9 & 0.0 & 100.0 & 0.0 & 99.8 & 0.877 & 1.637 & 0.0 & 0.0 & 20.4 & 0.0 & 5.1\tabularnewline
- & ACT{[}$\mathcal{S}${]} & 4 & 49.3 & 61.0 & 31.5 & 56.6 & 0.6 & 97.6 & 0.2 & 98.1 & 0.799 & 1.485 & 0.3 & 0.2 & 18.9 & 0.0 & 7.1\tabularnewline
- & ACT{[}$\mathcal{S}${]} & 8 & 42.8 & 54.7 & 26.6 & 53.3 & 4.8 & 72.8 & 2.7 & 73.3 & 0.619 & 1.148 & 8.3 & 4.9 & 23.5 & 0.3 & 18.7\tabularnewline
- & ACT{[}$\mathcal{S}${]} & 16 & 40.5 & 51.6 & 24.8 & 51.7 & 6.7 & 62.1 & 4.9 & 60.6 & 0.566 & 1.014 & 12.4 & 8.6 & 22.5 & 0.9 & 23.7\tabularnewline
- & ACT{[}$\mathcal{S}${]} & 32 & 39.4 & 50.2 & 18.6 & 51.3 & 6.8 & 61.5 & 5.2 & 60.4 & 0.506 & 1.032 & 12.8 & 11.3 & 17.7 & 0.3 & 24.2\tabularnewline
+\multirow{5}{*}{CUB} & \textcolor{tab:orange}{ACT{[}$\mathcal{S}${]}}\cite{robrank} & 2 & 53.0 & 65.1 & 34.7 & 59.9 & 0.0 & 100.0 & 0.0 & 99.8 & 0.877 & 1.637 & 0.0 & 0.0 & 20.4 & 0.0 & 5.1\tabularnewline
+\rowcolor{black!7}\cellcolor{white}& \textcolor{tab:orange}{ACT{[}$\mathcal{S}${]}}\cite{robrank} & 4 & 49.3 & 61.0 & 31.5 & 56.6 & 0.6 & 97.6 & 0.2 & 98.1 & 0.799 & 1.485 & 0.3 & 0.2 & 18.9 & 0.0 & 7.1\tabularnewline
+& \textcolor{tab:orange}{ACT{[}$\mathcal{S}${]}}\cite{robrank} & 8 & 42.8 & 54.7 & 26.6 & 53.3 & 4.8 & 72.8 & 2.7 & 73.3 & 0.619 & 1.148 & 8.3 & 4.9 & 23.5 & 0.3 & 18.7\tabularnewline
+\rowcolor{black!7}\cellcolor{white}& \textcolor{tab:orange}{ACT{[}$\mathcal{S}${]}}\cite{robrank} & 16 & 40.5 & 51.6 & 24.8 & 51.7 & 6.7 & 62.1 & 4.9 & 60.6 & 0.566 & 1.014 & 12.4 & 8.6 & 22.5 & 0.9 & 23.7\tabularnewline
+& \textcolor{tab:orange}{ACT{[}$\mathcal{S}${]}}\cite{robrank} & 32 & 39.4 & 50.2 & 18.6 & 51.3 & 6.8 & 61.5 & 5.2 & 60.4 & 0.506 & 1.032 & 12.8 & 11.3 & 17.7 & 0.3 & 24.2\tabularnewline
 \hline
 \multirow{5}{*}{CUB} & HM{[}$\mathcal{R},\mathcal{M}${]} & 2 & 34.3 & 44.9 & 19.5 & 47.4 & 7.7 & 77.5 & 6.5 & 70.8 & 0.636 & 1.281 & 4.3 & 2.6 & 21.1 & 0.2 & 18.1\tabularnewline
- & HM{[}$\mathcal{R},\mathcal{M}${]} & 4 & 30.7 & 40.3 & 16.4 & 45.3 & 13.9 & 60.4 & 13.5 & 48.1 & 0.582 & 1.041 & 6.6 & 6.6 & 20.2 & 1.2 & 27.1\tabularnewline
+\rowcolor{black!7}\cellcolor{white} & HM{[}$\mathcal{R},\mathcal{M}${]} & 4 & 30.7 & 40.3 & 16.4 & 45.3 & 13.9 & 60.4 & 13.5 & 48.1 & 0.582 & 1.041 & 6.6 & 6.6 & 20.2 & 1.2 & 27.1\tabularnewline
  & HM{[}$\mathcal{R},\mathcal{M}${]} & 8 & 27.0 & 36.0 & 13.2 & 42.5 & 19.4 & 48.0 & 22.2 & 32.0 & 0.535 & 0.867 & 11.6 & 10.4 & 19.3 & 2.9 & 35.1\tabularnewline
- & HM{[}$\mathcal{R},\mathcal{M}${]}  & 16 & 23.8 & 32.6 & 11.6 & 40.6 & 20.9 & 45.0 & 24.6 & 28.6 & 0.494 & 0.805 & 15.6 & 11.3 & 22.1 & 3.2 & 38.0\tabularnewline
+\rowcolor{black!7}\cellcolor{white} & HM{[}$\mathcal{R},\mathcal{M}${]}  & 16 & 23.8 & 32.6 & 11.6 & 40.6 & 20.9 & 45.0 & 24.6 & 28.6 & 0.494 & 0.805 & 15.6 & 11.3 & 22.1 & 3.2 & 38.0\tabularnewline
  & HM{[}$\mathcal{R},\mathcal{M}${]} & 32 & 23.1 & 31.9 & 11.3 & 40.3 & 22.8 & 46.0 & 24.3 & 28.3 & 0.495 & 0.800 & 14.2 & 11.7 & 19.7 & 3.8 & 38.0\tabularnewline
@@
 \multirow{5}{*}{CUB} & HM{[}$\mathcal{S},\mathcal{M}${]} & 2 & 44.5 & 56.1 & 27.8 & 53.3 & 1.9 & 87.7 & 1.6 & 88.8 & 0.827 & 1.101 & 3.7 & 0.3 & 19.0 & 0.0 & 11.6\tabularnewline
- & HM{[}$\mathcal{S},\mathcal{M}${]} & 4 & 40.6 & 51.8 & 24.2 & 51.0 & 7.3 & 64.1 & 6.3 & 60.9 & 0.715 & 0.894 & 7.9 & 4.4 & 22.8 & 0.2 & 22.1\tabularnewline
+\rowcolor{black!7}\cellcolor{white} & HM{[}$\mathcal{S},\mathcal{M}${]} & 4 & 40.6 & 51.8 & 24.2 & 51.0 & 7.3 & 64.1 & 6.3 & 60.9 & 0.715 & 0.894 & 7.9 & 4.4 & 22.8 & 0.2 & 22.1\tabularnewline
  & HM{[}$\mathcal{S},\mathcal{M}${]} & 8 & 38.4 & 49.7 & 22.9 & 50.3 & 10.9 & 50.5 & 10.8 & 44.6 & 0.680 & 0.722 & 13.3 & 11.2 & 25.8 & 1.2 & 29.6\tabularnewline
- & HM{[}$\mathcal{S},\mathcal{M}${]} & 16 & 37.4 & 47.3 & 21.0 & 48.2 & 14.4 & 42.0 & 14.8 & 34.7 & 0.599 & 0.693 & 17.5 & 14.4 & 26.5 & 2.4 & 34.8\tabularnewline
+\rowcolor{black!7}\cellcolor{white} & HM{[}$\mathcal{S},\mathcal{M}${]} & 16 & 37.4 & 47.3 & 21.0 & 48.2 & 14.4 & 42.0 & 14.8 & 34.7 & 0.599 & 0.693 & 17.5 & 14.4 & 26.5 & 2.4 & 34.8\tabularnewline
  & HM{[}$\mathcal{S},\mathcal{M}${]} & 32 & 35.3 & 46.1 & 20.2 & 48.0 & 15.1 & 41.8 & 15.2 & 33.0 & 0.589 & 0.686 & 18.7 & 14.9 & 27.8 & 2.9 & 35.7\tabularnewline
@@
 
+} \vspace{-0.5em}
+	%
+\caption{Hardness manipulation in adversarial training.
+%
+The ``$\uparrow$'' mark means ``the higher the better'', while ``$\downarrow$''
+	means the opposite.
+%
 	}
-
-\caption{Effectiveness of Hardness Manipulation for Adversarial Training.}
+	%
 \label{tab:hmeff}
+%
 \end{table*}

### 2022-03-02 robdml.tex
tab
finish colorizing tab3
typofix-tab

@@
 
-\definecolor{cyan}{rgb}{0.0, 0.72, 0.92}
+%TABLEAU_COLORS = {
+%    'tab:blue': '#1f77b4',
+%    'tab:orange': '#ff7f0e',
+%    'tab:green': '#2ca02c',
+%    'tab:red': '#d62728',
+%    'tab:purple': '#9467bd',
+%    'tab:brown': '#8c564b',
+%    'tab:pink': '#e377c2',
+%    'tab:olive': '#bcbd22',
+%    'tab:cyan': '#17becf',
+%}
+\definecolor{crimson}{HTML}{DC143C}
+\definecolor{tab:gray}{HTML}{7f7f7f}
+\definecolor{tab:pink}{HTML}{e377c2}
+\definecolor{tab:cyan}{HTML}{17becf}
+\definecolor{tab:orange}{HTML}{ff7f0e}
+\definecolor{tab:blue}{HTML}{1f77b4}
+\definecolor{tab:red}{HTML}{d62728}
 
@@
 
-To this end, Graduate Adversary, a family of pseudo-hardness functions is
+To this end, Gradual Adversary, a family of pseudo-hardness functions is
 proposed, which can be used as the \emph{destination} hardness.
@@
 %
-As an example, we design a ``Linear Graduate Adversary'' (LGA)
+As an example, we design a ``Linear Gradual Adversary'' (LGA)
 function as the linearly scaled negative triplet margin, incorporating a strong
@@
 		%
-	\item \textit{Linear Gradual Adversary} (LGA) as a Graduate Adversary, \ie,
+	\item \textit{Linear Gradual Adversary} (LGA) as a Gradual Adversary, \ie,
 		a pseudo-hardness function for HM, which incorporates our empirical
@@
 %
-A satisfactory pseudo-hardness function is a ``Graduate Adversary''.
-
-% Linear graduate adversary
+A satisfactory pseudo-hardness function is a ``Gradual Adversary''.
+
+% Linear gradual adversary
 

### 2022-03-08 tex/robdml.tex
move everything under tex/

--- 2022-03-02 robdml.tex
@@
 %%%%%%%%% PAPER TYPE  - PLEASE UPDATE FOR FINAL VERSION
-\usepackage[review]{cvpr}      % To produce the REVIEW version
+%\usepackage[review]{cvpr}      % To produce the REVIEW version
 %\usepackage{cvpr}              % To produce the CAMERA-READY version
-%\usepackage[pagenumbers]{cvpr} % To force page numbers, e.g. for an arXiv version
+\usepackage[pagenumbers]{cvpr} % To force page numbers, e.g. for an arXiv version
 
@@
 \newcommand{\oo}[1]{\textcolor{orange}{#1}}
-\include{math_commands.tex}
+\input{math_commands.tex}
 \usepackage{pifont}
@@
 \usepackage{comment}
-\usepackage{todonotes}
-\usepackage{siunitx}
-
-%TABLEAU_COLORS = {
-%    'tab:blue': '#1f77b4',
-%    'tab:orange': '#ff7f0e',
-%    'tab:green': '#2ca02c',
-%    'tab:red': '#d62728',
-%    'tab:purple': '#9467bd',
-%    'tab:brown': '#8c564b',
-%    'tab:pink': '#e377c2',
-%    'tab:olive': '#bcbd22',
-%    'tab:cyan': '#17becf',
-%}
+%\usepackage{todonotes}
+%\usepackage{siunitx}
+
 \definecolor{crimson}{HTML}{DC143C}
@@
 \and
-Vishal Patel\\
+Vishal M. Patel\\
 Johns Hopkins University\\
@@
 
-\textbf{Acknowledgements.} This research was supported by []. We thank
-Kangfu Mei for helpful discussions and feedbacks.
+%\textbf{Acknowledgements.} This research was supported by []. We thank
+%Kangfu Mei for helpful discussions and feedbacks.
 
@@
 \bibliographystyle{ieee_fullname}
-\bibliography{egbib}
+\bibliography{robdml}
 }
 
-%\input{appendix.tex}
+\input{appendix.tex}
 

### 2022-03-08 tex/tab-hmeff.tex
move everything under tex/

\begin{table*}
\resizebox{\linewidth}{!}{
\setlength{\tabcolsep}{0.48em}%
\renewcommand{\arraystretch}{1.05}

\begin{tabular}{c|cc|cccc|ccccc|ccccc|c}

	\toprule

\rowcolor{black!12} & & & \multicolumn{4}{c|}{\textbf{Benign Example}} & \multicolumn{10}{c|}{\textbf{White-Box Attacks for Robustness Evaluation}} & \tabularnewline
\cline{4-17} \cline{5-17} \cline{6-17} \cline{7-17} \cline{8-17} \cline{9-17} \cline{10-17} \cline{11-17} \cline{12-17} \cline{13-17} \cline{14-17} \cline{15-17} \cline{16-17} \cline{17-17}
\rowcolor{black!12}\multirow{-2}{*}{\textbf{Dataset}} & \multirow{-2}{*}{\textbf{Defense}} & \multirow{-2}{*}{$\eta$} & R@1$\uparrow$ & R@2$\uparrow$ & mAP$\uparrow$ & NMI$\uparrow$ & CA+$\uparrow$ & CA-$\downarrow$ & QA+$\uparrow$ & QA-$\downarrow$ & TMA$\downarrow$ & ES:D$\downarrow$ & ES:R$\uparrow$ & LTM$\uparrow$ & GTM$\uparrow$ & GTT$\uparrow$ & \multirow{-2}{*}{\textbf{ERS$\uparrow$}}\tabularnewline

	\midrule

CUB & N/A{[}$\mathcal{R}${]} & N/A & 53.9 & 66.4 & 26.1 & 59.5 & 0.0 & 100.0 & 0.0 & 99.9 & 0.883 & 1.762 & 0.0 & 0.0 & 14.1 & 0.0 & 3.8\tabularnewline
\hline
\multirow{5}{*}{CUB} & \textcolor{tab:cyan}{ACT{[}$\mathcal{R}${]}}\cite{robrank} & 2 & 46.5 & 58.4 & 29.1 & 55.6 & 0.6 & 98.9 & 0.4 & 98.1 & 0.837 & 1.666 & 0.2 & 0.2 & 19.6 & 0.0 & 5.8\tabularnewline
\rowcolor{black!7}\cellcolor{white} & \textcolor{tab:cyan}{ACT{[}$\mathcal{R}${]}}\cite{robrank} & 4 & 38.4 & 49.8 & 22.8 & 49.7 & 4.6 & 81.9 & 2.8 & 80.5 & 0.695 & 1.366 & 2.9 & 2.3 & 18.8 & 0.1 & 13.9\tabularnewline
 & \textcolor{tab:cyan}{ACT{[}$\mathcal{R}${]}}\cite{robrank} & 8 & 30.6 & 40.1 & 16.5 & 45.6 & 13.7 & 46.8 & 12.6 & 39.3 & 0.547 & 0.902 & 13.6 & 9.8 & 21.9 & 1.3 & 31.3\tabularnewline
\rowcolor{black!7}\cellcolor{white} & \textcolor{tab:cyan}{ACT{[}$\mathcal{R}${]}}\cite{robrank} & 16 & 28.6 & 38.7 & 15.1 & 43.7 & 15.8 & 37.9 & 16.0 & 31.5 & 0.496 & 0.834 & 11.3 & 9.8 & 21.2 & 2.1 & 34.7\tabularnewline
 & \textcolor{tab:cyan}{ACT{[}$\mathcal{R}${]}}\cite{robrank} & 32 & 27.5 & 38.2 & 12.2 & 43.0 & 15.5 & 37.7 & 15.1 & 32.2 & 0.472 & 0.821 & 11.1 & 9.4 & 14.9 & 1.0 & 33.9\tabularnewline
\hline
\multirow{5}{*}{CUB} & \textcolor{tab:orange}{ACT{[}$\mathcal{S}${]}}\cite{robrank} & 2 & 53.0 & 65.1 & 34.7 & 59.9 & 0.0 & 100.0 & 0.0 & 99.8 & 0.877 & 1.637 & 0.0 & 0.0 & 20.4 & 0.0 & 5.1\tabularnewline
\rowcolor{black!7}\cellcolor{white}& \textcolor{tab:orange}{ACT{[}$\mathcal{S}${]}}\cite{robrank} & 4 & 49.3 & 61.0 & 31.5 & 56.6 & 0.6 & 97.6 & 0.2 & 98.1 & 0.799 & 1.485 & 0.3 & 0.2 & 18.9 & 0.0 & 7.1\tabularnewline
& \textcolor{tab:orange}{ACT{[}$\mathcal{S}${]}}\cite{robrank} & 8 & 42.8 & 54.7 & 26.6 & 53.3 & 4.8 & 72.8 & 2.7 & 73.3 & 0.619 & 1.148 & 8.3 & 4.9 & 23.5 & 0.3 & 18.7\tabularnewline
\rowcolor{black!7}\cellcolor{white}& \textcolor{tab:orange}{ACT{[}$\mathcal{S}${]}}\cite{robrank} & 16 & 40.5 & 51.6 & 24.8 & 51.7 & 6.7 & 62.1 & 4.9 & 60.6 & 0.566 & 1.014 & 12.4 & 8.6 & 22.5 & 0.9 & 23.7\tabularnewline
& \textcolor{tab:orange}{ACT{[}$\mathcal{S}${]}}\cite{robrank} & 32 & 39.4 & 50.2 & 18.6 & 51.3 & 6.8 & 61.5 & 5.2 & 60.4 & 0.506 & 1.032 & 12.8 & 11.3 & 17.7 & 0.3 & 24.2\tabularnewline
\hline
\multirow{5}{*}{CUB} & \textcolor{tab:blue}{HM{[}$\mathcal{R},\mathcal{M}${]}} & 2 & 34.3 & 44.9 & 19.5 & 47.4 & 7.7 & 77.5 & 6.5 & 70.8 & 0.636 & 1.281 & 4.3 & 2.6 & 21.1 & 0.2 & 18.1\tabularnewline
\rowcolor{black!7}\cellcolor{white} & \textcolor{tab:blue}{HM{[}$\mathcal{R},\mathcal{M}${]}} & 4 & 30.7 & 40.3 & 16.4 & 45.3 & 13.9 & 60.4 & 13.5 & 48.1 & 0.582 & 1.041 & 6.6 & 6.6 & 20.2 & 1.2 & 27.1\tabularnewline
 & \textcolor{tab:blue}{HM{[}$\mathcal{R},\mathcal{M}${]}} & 8 & 27.0 & 36.0 & 13.2 & 42.5 & 19.4 & 48.0 & 22.2 & 32.0 & 0.535 & 0.867 & 11.6 & 10.4 & 19.3 & 2.9 & 35.1\tabularnewline
\rowcolor{black!7}\cellcolor{white} & \textcolor{tab:blue}{HM{[}$\mathcal{R},\mathcal{M}${]}} & 16 & 23.8 & 32.6 & 11.6 & 40.6 & 20.9 & 45.0 & 24.6 & 28.6 & 0.494 & 0.805 & 15.6 & 11.3 & 22.1 & 3.2 & 38.0\tabularnewline
 & \textcolor{tab:blue}{HM{[}$\mathcal{R},\mathcal{M}${]}} & 32 & 23.1 & 31.9 & 11.3 & 40.3 & 22.8 & 46.0 & 24.3 & 28.3 & 0.495 & 0.800 & 14.2 & 11.7 & 19.7 & 3.8 & 38.0\tabularnewline
\hline
\multirow{5}{*}{CUB} & \textcolor{tab:red}{HM{[}$\mathcal{S},\mathcal{M}${]}} & 2 & 44.5 & 56.1 & 27.8 & 53.3 & 1.9 & 87.7 & 1.6 & 88.8 & 0.827 & 1.101 & 3.7 & 0.3 & 19.0 & 0.0 & 11.6\tabularnewline
\rowcolor{black!7}\cellcolor{white} & \textcolor{tab:red}{HM{[}$\mathcal{S},\mathcal{M}${]}} & 4 & 40.6 & 51.8 & 24.2 & 51.0 & 7.3 & 64.1 & 6.3 & 60.9 & 0.715 & 0.894 & 7.9 & 4.4 & 22.8 & 0.2 & 22.1\tabularnewline
 & \textcolor{tab:red}{HM{[}$\mathcal{S},\mathcal{M}${]}} & 8 & 38.4 & 49.7 & 22.9 & 50.3 & 10.9 & 50.5 & 10.8 & 44.6 & 0.680 & 0.722 & 13.3 & 11.2 & 25.8 & 1.2 & 29.6\tabularnewline
\rowcolor{black!7}\cellcolor{white} & \textcolor{tab:red}{HM{[}$\mathcal{S},\mathcal{M}${]}} & 16 & 37.4 & 47.3 & 21.0 & 48.2 & 14.4 & 42.0 & 14.8 & 34.7 & 0.599 & 0.693 & 17.5 & 14.4 & 26.5 & 2.4 & 34.8\tabularnewline
 & \textcolor{tab:red}{HM{[}$\mathcal{S},\mathcal{M}${]}} & 32 & 35.3 & 46.1 & 20.2 & 48.0 & 15.1 & 41.8 & 15.2 & 33.0 & 0.589 & 0.686 & 18.7 & 14.9 & 27.8 & 2.9 & 35.7\tabularnewline

	\bottomrule

\end{tabular}

} \vspace{-0.5em}
	%
\caption{Hardness manipulation in adversarial training.
%
The ``$\uparrow$'' mark means ``the higher the better'', while ``$\downarrow$''
	means the opposite.
%
	}
	%
\label{tab:hmeff}
%
\end{table*}

### 2022-03-08 tex/introplot.py
add license headers

@@ -1,3 +1,7 @@
+'''
+Copyright (C) 2021-2022 Mo Zhou <cdluminate@gmail.com>
+License: Apache-2.0
+'''
 import numpy as np
 import matplotlib.pyplot as plt
 import rich

### 2022-03-09 tex/robdml.tex
tex: add macro and switch to camera ready

@@
+% Copyright (C) 2021-2022 Mo Zhou <cdluminate@gmail.com>
+% License: CC-BY-NC-SA-4.0
+% Preprint: https://arxiv.org/abs/2203.01439
+% Preprint License: CC-BY-NC-SA-4.0
+
 % CVPR 2022 Paper Template
@@
 \documentclass[10pt,twocolumn,letterpaper]{article}
+\newif\ifarxiv
+
+%\arxivtrue % XXX
+\arxivfalse % XXX
 
@@
 %\usepackage[review]{cvpr}      % To produce the REVIEW version
-%\usepackage{cvpr}              % To produce the CAMERA-READY version
+\ifarxiv
 \usepackage[pagenumbers]{cvpr} % To force page numbers, e.g. for an arXiv version
+\else
+\usepackage{cvpr}              % To produce the CAMERA-READY version
+\fi
 
@@
 
+\ifarxiv
 Further analysis, technical details, and limitations, \etc,
 are presented in the supplementary document.
+\else
+\fi
 
@@
 
-%\textbf{Acknowledgements.} This research was supported by []. We thank
-%Kangfu Mei for helpful discussions and feedbacks.
+\ifarxiv
+\else
+{\scriptsize
+\textbf{Acknowledgements.} This work was supported by the DARPA GARD Program
+HR001119S0026-GARD-FP-052. We thank Kangfu Mei for helpful feedbacks.
+}
+\fi
 
@@
 
+\ifarxiv
 \input{appendix.tex}
+\else
+\fi
 

### 2022-05-28 tex/appendix.tex
add license headers
appendix: add a small detail

--- 2021-11-18 appendix.tex
@@
+% Copyright (C) 2021-2022 Mo Zhou <cdluminate@gmail.com>
+% License: CC-BY-NC-SA-4.0
+% Preprint: https://arxiv.org/abs/2203.01439
+% Preprint License: CC-BY-NC-SA-4.0
+
 \clearpage
@@
 
-\oo{TODO: mnasnet ghmetsm ghmetsmi}
-
 \subsection{Use of Existing Assets}
@@
 
-\subsection{Graduate Adversary}
+\subsection{Gradual Adversary}
 \label{sec:b3}
@@
 ~\newline
-\noindent\textbf{II. Non-linear Graduate Adversary}
+\noindent\textbf{II. Non-linear Gradual Adversary}
 
@@
 %
-We provide two Non-linear Graduate Adversary examples, namely
+We provide two Non-linear Gradual Adversary examples, namely
 $g_\mathsf{2}$ and $g_\mathsf{1/2}$, as follows:
@@
 classification task.
+
+~\newline\textbf{V. Overfitting Issue}
+
+Actually overfitting is still observed for our method. Early stopping
+is possibly going to bring performance gain at this point. But in order
+to make comparison with previous works with controled variable, we did not
+investigate into this in detail.
